### 2014-02-23 presentation-plan/presentation-plan.tex
Moving some files around

%%%%%%%%%%%%%%%%%%%%%%% file ff-replan.tex %%%%%%%%%%%%%%%%%%%%%%%%
%
% 	Presentation Plan Arian Stolwijk & Imara Speek
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

\usepackage{url}
\urldef{\mailsa}\path|{i.c.t.m.speek, a.c.stolwijk}@student.tudelft.nl|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip%
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter% start of an individual contribution

% first the title is needed
\title{Presentation Plan\\
FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains}

% a short form should be given in case it is too long for the running head
\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}

\author{I.C.T.M Speek, A.C. Stolwijk}

%
\authorrunning{Presentation Plan Seminar Algorithms FF-replan \& RFF}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Seminar Algorithms, Embedded Software,
Msc Embedded Systems,\\
Delft University of Technology\\
\mailsa\\
}

\toctitle{Lecture Notes in Computer Science}
\tocauthor{Authors' Instructions}
\maketitle

\section{Summary of given papers}

At the first international probabilistic planning competition IPPC-04, most
entries were Markov Decision Processes. The winner, FF-Replan, however was
based on deterministic planning techniques.

By relying on search, FF-Replan could function with enormous speed and efficiency.

Until the paper there have been two IPPC conferences.

\section{Questions that arose}

\section{Criticism on the contribution of the paper}

\section{Relevant literature on the subject}

\section{Presentation setup}

\end{document}

### 2014-02-23 presentation-plan/presentation-plan.tex
First start for the summary of Incremental Aggregation Plan

@@
-%%%%%%%%%%%%%%%%%%%%%%% file ff-replan.tex %%%%%%%%%%%%%%%%%%%%%%%%
-%
-% 	Presentation Plan Arian Stolwijk & Imara Speek
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \documentclass[runningheads,a4paper]{llncs}
@@
 
+\subsection{FF-Replan: A Baseline for Probabilistic Planning}
+
 At the first international probabilistic planning competition IPPC-04, most
@@
 Until the paper there have been two IPPC conferences.
+
+\subsection{Incremental Plan Aggregation for Generating Policies in MDPs}
+
+Markov Decision Processes (MDPs) is the best known formalism for planning under
+uncertainty. It can however be computationally intensive if large parts of the
+policies are tried to optimize at once. Most recent MDP planning techniques are
+using the following steps as a basis approach:
+
+\begin{enumerate}
+	\item Take MDP problem
+	\item ``Determize''  it into a classical planning problem
+	\item Generate sequence of actions that represent a possible exectution
+			path
+	\item MDP planner executes plan:
+		\begin{itemize}
+			\item If goal is reached, reports success
+			\item Otherwise algorithm generates a new plan from failed state of the world
+		\end{itemize}
+\end{enumerate}
 

### 2014-02-23 presentation-plan/presentation-plan.tex
Add some more to the incremental plan aggregation summary

@@
 	\item Take MDP problem
-	\item ``Determize''  it into a classical planning problem
-	\item Generate sequence of actions that represent a possible exectution
+	\item ``Determinize''  it into a classical planning problem
+	\item Generate sequence of actions that represent a possible execution
 		path
@@
 		\end{itemize}
+\end{enumerate}
+
+There are some issues with this approach:
+
+\begin{itemize}
+	\item It stops after the first computed path to a goal which is likely to fail
+	\item May result in generating the same path over and over again
+	\item Only generates an execution path, not a policy
+\end{itemize}
+
+The authors identified four aspects of policy generation for MDP planning
+problems using a classical planning algorithm:
+
+\begin{enumerate}
+	\item How to determinize the MDP planning problem
+	\item which plan (initial state, goal) to ask for
+	\item How to incrementally aggregate the plans by the classical planner
+		into a solution policy
+	\item How to combine this coherently
 \end{enumerate}

### 2014-02-23 presentation-plan/presentation-plan.tex
Explain the basic algorithm a little

@@
 			\item If goal is reached, reports success
-			\item Otherwise algorithm generates a new plan from failed state of the world
+			\item Otherwise algorithm generates a new plan from failed state of
+				the world
 		\end{itemize}
@@
 
+The paper presents the Robust FF (\texttt{RFF}) planner, which should solve the
+issues. \texttt{RFF} first generates an initial plan from the initial state to
+some goal using \texttt{FF} on a determination of the MDP\@. Then for each
+state in the plan, the successors of that state are added too. This is
+expanding the execution structure. For the new state the probability to reach
+this state should be higher than a certain threshold and if \texttt{FF} does
+not return a failure for this state and a certain goal.
+
 \section{Questions that arose}

### 2014-02-23 presentation-plan/presentation-plan.tex
initial ff-replan summary

--- 2014-02-23 presentation-plan/presentation-plan.tex
@@
 
-At the first international probabilistic planning competition IPPC-04, most
-entries were Markov Decision Processes. The winner, FF-Replan, however was
-based on deterministic planning techniques.
+At the first international probabilistic planning competition IPPC-04, most entries were Markov Decision Processes. The winner, FF-Replan, however was based on deterministic planning techniques.
+
+FF-Replan is an action selection algorithm for online planning in probabilistic domains.
+Given a domain description, a goal and an initial state as a probabilistic planning problem, FF-Replan generates a deterministic planning problem.
+It determinizes the input domain at the start of the planning into a deterministic different domain.
+They consider two methods of determinization:
+\begin{enumerate}
+	\item \emph{Single-outcome determinization}: selects one outcome for each probabilistic construct using a variety of heuristics.
+The performance strongly depends on the methods for choosing the outcomes.
+	\item \emph{All-outcomes determinization}: considers every probabilistic outcome as a dinstinct deterministic action.
+For each possible outcome  FF-Replan generates one seperate action for each effect.
+For nested probabilities, the all-outcomes procedure is applied recursively.
+This implies that FF-Replan will ceise selection actions whenever it enters a dead state.
+However when given no information, all probabilistic effects will be considered as equal which is a potential weakness.
+\end{enumerate}
+
+After determinization FF-Replan then uses the deterministic FF planner to compute an ordered plan for the generated deterministic problem.
+This process is repeated when countering an unexpected state untill a goal state is reached.
+It maintains a partial state-action mapping using a hash-table which is initially empty.
+Whenever FF-Replan encounters a state which is not in the table, it determinizes the problem and synthesizes a plan using FF.
+It then simulates the plan according to the deterministic action definitions resulting in a state-action sequence whose pairs are put in the hash table .
+The first action of the plan in then executed in the environment, returning a new state.
+This partial policy is this produces in an online fashion.
+It would be valuable to look into incremental planning approaches that don't create a deterministic plan from scratch whenever an unexpected state is encountered or reusing previous planning effort.
+
+FF-Replan has some obvious shortcomings as it first determinizes the input domain, removing all probabilistic information from the problem and then synthesizes a plan.
+If an unexpected state should occur whilst executing, the planner replans in the same determinization.
+It also does not consider multiple potential effects if an action.
 
 By relying on search, FF-Replan could function with enormous speed and efficiency.
-
-Until the paper there have been two IPPC conferences.
+However when dealing with difficult probabilistic problems attempting to span the spectrum of complexity ranging from deterministic problems to highly stochastic problems, FF-Replan is expected to come short.
+Because FF-Replan is developed hoping to inspire extensions and insight into the approach and planning domains, the authors can only hope to achieve this.
 

### 2014-02-23 presentation-plan/presentation-plan.tex
Adding theorems of the paper

--- 2014-02-23 presentation-plan/presentation-plan.tex
@@
 \usepackage{graphicx}
+\usepackage{hyperref}
+\usepackage{fixltx2e}
 
@@
 this state should be higher than a certain threshold and if \texttt{FF} does
-not return a failure for this state and a certain goal.
+not return a failure for this state and a certain goal. The calculation of the
+probability to a state from the initial state can be costly. To optimize this
+in \texttt{RFF} a Monte-Carlo (MC) simulation is used. \texttt{RFF} terminates
+if either the global probability is lower than the threshold, or there are no
+new terminal states to be added.
+
+Three theorems, one lemma and one corollary about MDP problems using
+\texttt{RFF} are given:
+
+\begin{description}
+	\item[Lemma 1] For every MDP planning problem RFF terminates in
+		finite time
+	\item[Theorem 1] (Soundness of \texttt{RFF\textsubscript{MPO}}). For every
+		MDP planning problem, every solution that
+		\texttt{RFF\textsubscript{MPO}} finds is correct
+	\item[Theorem 2] (Completeness of \texttt{RFF\textsubscript{AO}}). For
+		every MDP planning problem, if a solution exists, it is found by
+		\texttt{RFF\textsubscript{AO}} or returns a failure
+	\item[Corollary 1] (Soundness of \texttt{RFF\textsubscript{AO}}). For every
+		MDP planning problem, every solution that
+		\texttt{RFF\textsubscript{AO}} finds is correct
+	\item[Theorem 3] If there are no unsolvable states in the MDP, then the
+		probability of success of any solution found by \texttt{RFF} is
+		higher than $1 - \rho$ where $\rho$ is the threshold probability
+\end{description}
 

### 2014-02-23 presentation-plan/presentation-plan.tex
I think the summary includes everything now.

@@
 % a short form should be given in case it is too long for the running head
-\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}
+\titlerunning{Presentation Plan}
 
@@
 
-\toctitle{Lecture Notes in Computer Science}
-\tocauthor{Authors' Instructions}
+%\toctitle{Lecture Notes in Computer Science}
+%\tocauthor{Authors' Instructions}
+
 \maketitle
@@
 issues. \texttt{RFF} first generates an initial plan from the initial state to
-some goal using \texttt{FF} on a determination of the MDP\@. Then for each
-state in the plan, the successors of that state are added too. This is
-expanding the execution structure. For the new state the probability to reach
-this state should be higher than a certain threshold and if \texttt{FF} does
-not return a failure for this state and a certain goal. The calculation of the
+some goal using \texttt{FF} on a determination of the MDP\@. There are several
+strategies to do this. \textsc{MostProbableOutcome} (MPO) only uses the action
+from a state with the highest probability. \textsc{AllOutcomes} (AO) uses all
+actions from a state. Then for each state in the plan, the successors of that
+state are added too. This is expanding the execution structure. For the new
+state the probability to reach this state should be higher than a certain
+threshold and if \texttt{FF} does not return a failure for this state and a
+certain goal. The goals can be chosen in three different ways, using
+\textsc{ProblemGoal}, which uses the goals of the MDP, \textsc{RandomGoal},
+which randomly picks some states from the policy graph and \textsc{BestGoal}
+which picks the best states from the policy graph. The calculation of the
 probability to a state from the initial state can be costly. To optimize this
@@
 
+For the IPC-08 the authors have implemented \texttt{RFF} in C++ to perform
+experiments. It performed experiments on the ``fully-observable probabilistic
+(FOP) planning track''. At IPC-08 it performed better than other competitors.
+The experiments confirmed Theorem 3, a higher threshold mean that \texttt{RFF}
+will generate policies that are more prone to replanning.
+
+In the experiments different Goal-Selection strategies were tested.
+\textsc{ProblemGoal} (PG) performed the worst. \textsc{RandomGoal} performed
+better and \textsc{BestGoal} generally produced higher quality goals, but also
+took more time.
+
+The different ways of determinizing MDPs was also tested. It turned out that
+\textsc{AllOutcomes} solve much larger problems. However
+\textsc{MostProbableOutcome} generally solve more problems in less time.
+
 \section{Questions that arose}

### 2014-02-23 presentation-plan/presentation-plan.tex
Add 2 related papers

@@
 
+\begin{itemize}
+	\item Teichteil-Koenigsbuch, Florent, Guillaume Infantes, and Ugur Kuter.
+``RFF: A robust, FF-based MDP planning algorithm for generating policies with low probability of failure.'' \emph{Sixth International Planning Competition at ICAPS} 8 (2008).
+	\item Weld, Andrey Kolobov Mausam Daniel S. ``Determinize, Solve, and Generalize: Classical Planning for MDP Heuristics.''
+\end{itemize}
+
 \section{Presentation setup}

### 2014-02-23 presentation-plan/presentation-plan.tex
Some trivial presentation setup
added small last changes

@@
 For nested probabilities, the all-outcomes procedure is applied recursively.
-This implies that FF-Replan will ceise selection actions whenever it enters a dead state.
+This implies that FF-Replan will ceise selecting actions whenever it enters a dead state.
 However when given no information, all probabilistic effects will be considered as equal which is a potential weakness.
@@
 Whenever FF-Replan encounters a state which is not in the table, it determinizes the problem and synthesizes a plan using FF.
-It then simulates the plan according to the deterministic action definitions resulting in a state-action sequence whose pairs are put in the hash table .
-The first action of the plan in then executed in the environment, returning a new state.
+It then simulates the plan according to the deterministic action definitions resulting in a state-action sequence whose pairs are put in the hash table.
+The first action of the plan is then executed in the environment, returning a new state.
 This partial policy is this produces in an online fashion.
@@
 However when dealing with difficult probabilistic problems attempting to span the spectrum of complexity ranging from deterministic problems to highly stochastic problems, FF-Replan is expected to come short.
-Because FF-Replan is developed hoping to inspire extensions and insight into the approach and planning domains, the authors can only hope to achieve this.
+Because FF-Replan is developed hoping to inspire extensions and insight into the approach and planning domains, the authors are hoping to achieve this.
 
@@
 
-\section{Questions that arose}
-
 \section{Criticism on the contribution of the paper}
@@
 
+\begin{itemize}
+	\item Introduction 
+	\item Brief introduction to prior knowledge
+	\item Summary of the papers
+		\item Advantages and disadvantages
+	\item Comparison with ideas of other papers
+	\item Some initial ideas of improvements
+\end{itemize}
+
 \end{document}

### 2014-02-23 presentation-plan/presentation-plan.tex
Add a question about RFF

@@
 The performance strongly depends on the methods for choosing the outcomes.
-	\item \emph{All-outcomes determinization}: considers every probabilistic outcome as a dinstinct deterministic action.
+	\item \emph{All-outcomes determinization}: considers every probabilistic outcome as a distinct deterministic action.
 For each possible outcome  FF-Replan generates one seperate action for each effect.
@@
 
+\section{Questions that arose}
+
+\begin{enumerate}
+	\item Are there scenarios where the optional step for optimizing the
+		shortest stochastic path is beneficial, so where the quality
+		improves enough to compensate the extra computational cost?
+	\item -
+\end{enumerate}
+
 \section{Criticism on the contribution of the paper}

### 2014-02-23 presentation-plan/presentation-plan.tex
Spelling typos

@@
 For nested probabilities, the all-outcomes procedure is applied recursively.
-This implies that FF-Replan will ceise selecting actions whenever it enters a dead state.
+This implies that FF-Replan will cease selecting actions whenever it enters a dead state.
 However when given no information, all probabilistic effects will be considered as equal which is a potential weakness.
@@
 After determinization FF-Replan then uses the deterministic FF planner to compute an ordered plan for the generated deterministic problem.
-This process is repeated when countering an unexpected state untill a goal state is reached.
+This process is repeated when countering an unexpected state until a goal state is reached.
 It maintains a partial state-action mapping using a hash-table which is initially empty.

### 2014-02-26 presentation-plan/presentation-plan.tex
Add new outline for the presentation
Start adding information about the introduction of planners

@@
 	\item Weld, Andrey Kolobov Mausam Daniel S. ``Determinize, Solve, and Generalize: Classical Planning for MDP Heuristics.''
+	\item http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.83.1757\&rep=rep1\&type=pdf
+	\item http://wwwold.cs.umd.edu/class/spring2004/cmsc421/planning.pdf
 \end{itemize}
@@
 
+\subsection{Introduction to a planner (A)}
+
+Examples of planning problems:
+
 \begin{itemize}
-	\item Introduction
-	\item Brief introduction to prior knowledge
-	\item Summary of the papers
-	\item Advantages and disadvantages
-	\item Comparison with ideas of other papers
-	\item Some initial ideas of improvements
+	\item Blocks World
+	\item Motion Planning
 \end{itemize}
 
+Planning Problem:
+
+\begin{itemize}
+	\item Initial State
+	\item Goal State
+	\item Set of actions
+\end{itemize}
+
+Planning Plan:
+
+\begin{itemize}
+	\item Set of actions
+	\item Executable in the initial state
+	\item Resulting in a state that satisfies the goal state
+\end{itemize}
+
+\subsection{What is uncertainty (I)}
+
+\subsubsection{Domains \& Applications (I)}
+
+\subsection{Historic Overview}
+
+\subsubsection{$<$ 1990 (A)}
+
+\begin{itemize}
+	\item STRIPS
+\end{itemize}
+
+\subsubsection{1990 - 2000 (I)}
+
+\subsubsection{Introducing the FF planner (I)}
+
+\subsubsection{2000 - 2005 (A)}
+
+\subsubsection{FF-Replan (I)}
+
+\subsubsection{RFF (A)}
+
+\subsubsection{Compare FF-Replan with RFF (I\&A)}
+
+\subsubsection{How did FF-Replan inspire (I)}
+
+\subsubsection{Alternatives FF-Replan ()}
+
+\subsubsection{What after? Any new methods (A)}
+
+\subsection{Present goal of paper (I\&A)}
+
+\subsection{Is it time to reconsider classical planners (I\&A)}
+
 \end{document}

### 2014-02-26 presentation-plan/Plan_presentation_monday.tex
changed previous file, added uncertainty in new plan presentation

--- 2014-02-23 presentation-plan/presentation-plan.tex
@@
 
-\section{Summary of given papers}
+\section{Introduction to a planner (A)}
 
-\subsection{FF-Replan: A Baseline for Probabilistic Planning}
-
-At the first international probabilistic planning competition IPPC-04, most entries were Markov Decision Processes. The winner, FF-Replan, however was based on deterministic planning techniques.
-
-FF-Replan is an action selection algorithm for online planning in probabilistic domains.
-Given a domain description, a goal and an initial state as a probabilistic planning problem, FF-Replan generates a deterministic planning problem.
-It determinizes the input domain at the start of the planning into a deterministic different domain.
-They consider two methods of determinization:
-\begin{enumerate}
-	\item \emph{Single-outcome determinization}: selects one outcome for each probabilistic construct using a variety of heuristics.
-The performance strongly depends on the methods for choosing the outcomes.
-	\item \emph{All-outcomes determinization}: considers every probabilistic outcome as a distinct deterministic action.
-For each possible outcome  FF-Replan generates one seperate action for each effect.
-For nested probabilities, the all-outcomes procedure is applied recursively.
-This implies that FF-Replan will cease selecting actions whenever it enters a dead state.
-However when given no information, all probabilistic effects will be considered as equal which is a potential weakness.
-\end{enumerate}
-
-After determinization FF-Replan then uses the deterministic FF planner to compute an ordered plan for the generated deterministic problem.
-This process is repeated when countering an unexpected state until a goal state is reached.
-It maintains a partial state-action mapping using a hash-table which is initially empty.
-Whenever FF-Replan encounters a state which is not in the table, it determinizes the problem and synthesizes a plan using FF.
-It then simulates the plan according to the deterministic action definitions resulting in a state-action sequence whose pairs are put in the hash table.
-The first action of the plan is then executed in the environment, returning a new state.
-This partial policy is this produces in an online fashion.
-It would be valuable to look into incremental planning approaches that don't create a deterministic plan from scratch whenever an unexpected state is encountered or reusing previous planning effort.
-
-FF-Replan has some obvious shortcomings as it first determinizes the input domain, removing all probabilistic information from the problem and then synthesizes a plan.
-If an unexpected state should occur whilst executing, the planner replans in the same determinization.
-It also does not consider multiple potential effects if an action.
-
-By relying on search, FF-Replan could function with enormous speed and efficiency.
-However when dealing with difficult probabilistic problems attempting to span the spectrum of complexity ranging from deterministic problems to highly stochastic problems, FF-Replan is expected to come short.
-Because FF-Replan is developed hoping to inspire extensions and insight into the approach and planning domains, the authors are hoping to achieve this.
-
-\subsection{Incremental Plan Aggregation for Generating Policies in MDPs}
-
-Markov Decision Processes (MDPs) is the best known formalism for planning under
-uncertainty. It can however be computationally intensive if large parts of the
-policies are tried to optimize at once. Most recent MDP planning techniques are
-using the following steps as a basis approach:
-
-\begin{enumerate}
-	\item Take MDP problem
-	\item ``Determinize''  it into a classical planning problem
-	\item Generate sequence of actions that represent a possible execution
-		path
-	\item MDP planner executes plan:
-		\begin{itemize}
-			\item If goal is reached, reports success
-			\item Otherwise algorithm generates a new plan from failed state of
-				the world
-		\end{itemize}
-\end{enumerate}
-
-There are some issues with this approach:
+Examples of planning problems:
 
 \begin{itemize}
-	\item It stops after the first computed path to a goal which is likely to fail
-	\item May result in generating the same path over and over again
-	\item Only generates an execution path, not a policy
+	\item Blocks World
+	\item Motion Planning
 \end{itemize}
 
-The authors identified four aspects of policy generation for MDP planning
-problems using a classical planning algorithm:
-
-\begin{enumerate}
-	\item How to determinize the MDP planning problem
-	\item which plan (initial state, goal) to ask for
-	\item How to incrementally aggregate the plans by the classical planner
-		into a solution policy
-	\item How to combine this coherently
-\end{enumerate}
-
-The paper presents the Robust FF (\texttt{RFF}) planner, which should solve the
-issues. \texttt{RFF} first generates an initial plan from the initial state to
-some goal using \texttt{FF} on a determination of the MDP\@. There are several
-strategies to do this. \textsc{MostProbableOutcome} (MPO) only uses the action
-from a state with the highest probability. \textsc{AllOutcomes} (AO) uses all
-actions from a state. Then for each state in the plan, the successors of that
-state are added too. This is expanding the execution structure. For the new
-state the probability to reach this state should be higher than a certain
-threshold and if \texttt{FF} does not return a failure for this state and a
-certain goal. The goals can be chosen in three different ways, using
-\textsc{ProblemGoal}, which uses the goals of the MDP, \textsc{RandomGoal},
-which randomly picks some states from the policy graph and \textsc{BestGoal}
-which picks the best states from the policy graph. The calculation of the
-probability to a state from the initial state can be costly. To optimize this
-in \texttt{RFF} a Monte-Carlo (MC) simulation is used. \texttt{RFF} terminates
-if either the global probability is lower than the threshold, or there are no
-new terminal states to be added.
-
-Three theorems, one lemma and one corollary about MDP problems using
-\texttt{RFF} are given:
-
-\begin{description}
-	\item[Lemma 1] For every MDP planning problem RFF terminates in
-		finite time
-	\item[Theorem 1] (Soundness of \texttt{RFF\textsubscript{MPO}}). For every
-		MDP planning problem, every solution that
-		\texttt{RFF\textsubscript{MPO}} finds is correct
-	\item[Theorem 2] (Completeness of \texttt{RFF\textsubscript{AO}}). For
-		every MDP planning problem, if a solution exists, it is found by
-		\texttt{RFF\textsubscript{AO}} or returns a failure
-	\item[Corollary 1] (Soundness of \texttt{RFF\textsubscript{AO}}). For every
-		MDP planning problem, every solution that
-		\texttt{RFF\textsubscript{AO}} finds is correct
-	\item[Theorem 3] If there are no unsolvable states in the MDP, then the
-		probability of success of any solution found by \texttt{RFF} is
-		higher than $1 - \rho$ where $\rho$ is the threshold probability
-\end{description}
-
-For the IPC-08 the authors have implemented \texttt{RFF} in C++ to perform
-experiments. It performed experiments on the ``fully-observable probabilistic
-(FOP) planning track''. At IPC-08 it performed better than other competitors.
-The experiments confirmed Theorem 3, a higher threshold mean that \texttt{RFF}
-will generate policies that are more prone to replanning.
-
-In the experiments different Goal-Selection strategies were tested.
-\textsc{ProblemGoal} (PG) performed the worst. \textsc{RandomGoal} performed
-better and \textsc{BestGoal} generally produced higher quality goals, but also
-took more time.
-
-The different ways of determinizing MDPs was also tested. It turned out that
-\textsc{AllOutcomes} solve much larger problems. However
-\textsc{MostProbableOutcome} generally solve more problems in less time.
-
-\section{Questions that arose}
-
-\begin{enumerate}
-	\item Are there scenarios where the optional step for optimizing the
-		shortest stochastic path is beneficial, so where the quality
-		improves enough to compensate the extra computational cost?
-	\item -
-\end{enumerate}
-
-\section{Criticism on the contribution of the paper}
-
-\section{Relevant literature on the subject}
+Planning Problem:
 
 \begin{itemize}
-	\item Teichteil-Koenigsbuch, Florent, Guillaume Infantes, and Ugur Kuter.
-``RFF: A robust, FF-based MDP planning algorithm for generating policies with low probability of failure.'' \emph{Sixth International Planning Competition at ICAPS} 8 (2008).
-	\item Weld, Andrey Kolobov Mausam Daniel S. ``Determinize, Solve, and Generalize: Classical Planning for MDP Heuristics.''
+	\item Initial State
+	\item Goal State
+	\item Set of actions
 \end{itemize}
 
-\section{Presentation setup}
+Planning Plan:
 
 \begin{itemize}
-	\item Introduction
-	\item Brief introduction to prior knowledge
-	\item Summary of the papers
-	\item Advantages and disadvantages
-	\item Comparison with ideas of other papers
-	\item Some initial ideas of improvements
+	\item Set of actions
+	\item Executable in the initial state
+	\item Resulting in a state that satisfies the goal state
 \end{itemize}
 
+\section{What is uncertainty (I)}
+\emph{Uncertainty applies to predictions of future events, to physical measurements that are already made, or to the unknown.
+Uncertainty arises in partially observable and/or stochastic environments, as well as due to ignorance and/or indolence} [1].
+\\
+
+Uncertain (adjective). \\
+1. not able to be relied on; not known or definite. [2]
+
+\subsection{Real world examples}
+
+Growing plants is an extremely uncertain domain.
+When everything goes well, it should be fine to water it once a week.
+However my room environment has proven to be an uncertain domain where wind, temperature and sunlight severely impacts my abality to plan for nurturing my plants.
+
+\subsection{Embedded Systems in uncertain domains}
+
+Cruise control (stabilizing systems), quad rotor, AI, robots
+
+\subsection{Benchmarking for uncertain domains}
+
+Traffic control benchmark for the 2014 IPCC probabilistic continuous domain.
+Tidybot: a housecleaning robot [3]. \\
+
+\noindent [1] [Wikipedia http://en.wikipedia.org/wiki/Uncertainty]
+[2] [Google definition]
+[3] [http://www.plg.inf.uc3m.es/ipc2011-deterministic/DomainsSequential.html\#Barman]
+
+\subsection{Domains \& Applications (I)}
+
+\section{Historic Overview}
+
+\subsection{$<$ 1990 (A)}
+
+\begin{itemize}
+	\item STRIPS
+\end{itemize}
+
+\subsubsection{1990 - 2000 (I)}
+
+\subsection{Introducing the FF planner (I)}
+
+\subsection{2000 - 2005 (A)}
+
+\subsection{FF-Replan (I)}
+
+\subsection{RFF (A)}
+
+\subsection{Compare FF-Replan with RFF (I\&A)}
+
+\subsection{How did FF-Replan inspire (I)}
+
+\subsection{Alternatives FF-Replan ()}
+
+\subsection{What after? Any new methods (A)}
+
+\section{Present goal of paper (I\&A)}
+
+\section{Is it time to reconsider classical planners (I\&A)}
+
 \end{document}

### 2014-02-27 presentation-plan/Plan_presentation_monday.tex
Fixing my makefile

@@
 \section{What is uncertainty (I)}
+
 \emph{Uncertainty applies to predictions of future events, to physical measurements that are already made, or to the unknown.
@@
 1. not able to be relied on; not known or definite. [2]
+
+In the rest of this topic discuss the different domains and applications.
 
@@
 
-\subsection{Domains \& Applications (I)}
-
 \section{Historic Overview}
+A swift introduction to the evolution of planning algorithms. For every problem state the:
+\begin{itemize}
+	\item The problem definition
+	\item The motivation for the solution
+	\item The strengths
+	\item The weaknesses
+\end{itemize}
 
@@
 
-\subsubsection{1990 - 2000 (I)}
+\subsection{1990 - 2000 (I)}
+Choose 3 of these depending on what comes out in the different era's:
+
+Model Checking, search techniques, least commitment - probabilistic planner (BURIDAN), DMCPs, dynamic programming, graphplan
+
+Still need to check papers, but already have a bunch.
 
@@
 
-\subsection{Compare FF-Replan with RFF (I\&A)}
+\section{Compare FF-Replan with RFF (I\&A)}
 
@@
 
-\subsection{Alternatives FF-Replan ()}
-
-\subsection{What after? Any new methods (A)}
+\section{What after? Any new methods (A)}
 

### 2014-02-27 presentation-plan/Plan_presentation_monday.tex
Add bibtex, explain STRIPS from the 1970s

@@
 \begin{itemize}
-	\item STRIPS
+	\item STRIPS \cite{fikes1971strips}
+\end{itemize}
+
+\subsubsection{STRIPS}
+
+STRIPS~\cite{fikes1971strips} is a influential method of defining planning
+problems.
+
+Take for example~\ref{fig:strips}. R is the robot, B and C are two objects at
+places a, b and c. The goal is to achieve the configuration such that B is at
+place k and in which C is not at place c. The robot can move to an object and
+it can push objects to another position.
+
+\begin{figure}[htb]%
+\includegraphics[width=0.8\columnwidth]{strips-example.pdf}%
+\caption{Configuration of objects and robot for example problem (Figure from~\cite{fikes1971strips})}%
+\label{fig:strips}%
+\end{figure}
+
+The goal could be written as
+
+\[
+	(\exists s) [ AT(B,k,s) \land \neg AT(C,c,s) ]
+\]
+
+If we find an instance of s, the problem is solved.
+
+STRIPS also defines operators. In this instance examples can be \texttt{goto}
+and \texttt{push}.
+
+\begin{description}
+	\item[push(u,x,y)] Robot pushes object \texttt{u} from \texttt{x} to
+		position \texttt{y}
+	\begin{description}
+		\item[Precondition:] $(\exists s) [AT(u,x,s) \land ATR(x,s)]$
+		\item[Delete list:] $\{AT(u,x,s), ATR(x,s)\}$
+		\item[Add list:] $\{AT(u,y,push'(u,x,y,s^*)), ATR(y,push'(u,x,y,s^*))\}$
+	\end{description}
+	\item[goto(x,y)] Robot goes from place \texttt{x} to \texttt{y}
+	\begin{description}
+		\item[Precondition:] $(\exists s) [ATR(x,s)]$
+		\item[Delete list:] $\{ATR(x,s)\}$
+		\item[Add list:] $\{ATR(y,goto'(x,y,s^*))\}$
+	\end{description}
+\end{description}
+
+The initial world model can be described by:
+
+\[
+	s_0 : \{ ATR(a,x_0), AT(B,b,s_0), AT(C,c,s_0) \}
+\]
+
+Besides that there is a global requirement that two blocks cannot be at the
+same position at any time.
+
+\paragraph{Problems}
+
+\begin{itemize}
+	\item How to efficiently store nodes (states) of the world.~\cite{fikes1971strips}.
+	\item ...
 \end{itemize}
@@
 
+\bibliographystyle{plain}
+\bibliography{Plan_presentation_monday}
+
 \end{document}

### 2014-02-27 presentation-plan/Plan_presentation_monday.tex
Add some extra limitations of STRIP

@@
 \begin{itemize}
-	\item How to efficiently store nodes (states) of the world.~\cite{fikes1971strips}.
-	\item ...
+	\item How to efficiently store nodes (states) of the
+		world.~\cite{fikes1971strips}
+	\item Arbitrary STRIPS planning problem is a PSPACE complete
+		problem.~\cite{mcallester1991systematic}
+	\item Extremely limited in scope of planning problems and complexity of
+		problems it can solve.~\cite{fikes1994strips}
 \end{itemize}

### 2014-03-01 presentation-plan/Plan_presentation_monday.tex
More <1990
changed structure presentation, don't think STRIP should be presented as well

--- 2014-02-27 presentation-plan/Plan_presentation_monday.tex
@@
 \section{Introduction to a planner (A)}
+
+What is a planner? [Will need some more detailing].\\
 
@@
 
-\subsection{$<$ 1990 (A)}
+%\begin{itemize}
+%	\item STRIPS \cite{fikes1971strips}
+%\end{itemize}
+%
+%\subsubsection{STRIPS}
+%
+%STRIPS~\cite{fikes1971strips} is a influential method of defining planning
+%problems.
+%
+%Take for example~\ref{fig:strips}. R is the robot, B and C are two objects at
+%places a, b and c. The goal is to achieve the configuration such that B is at
+%place k and in which C is not at place c. The robot can move to an object and
+%it can push objects to another position.
+%
+%\begin{figure}[htb]%
+%\includegraphics[width=0.8\columnwidth]{strips-example.pdf}%
+%\caption{Configuration of objects and robot for example problem (Figure from~\cite{fikes1971strips})}%
+%\label{fig:strips}%
+%\end{figure}
+%
+%The goal could be written as
+%
+%\[(\exists s) [ AT(B,k,s) \land \neg AT(C,c,s) ]\]
+%
+%If we find an instance of s, the problem is solved.
+%
+%STRIPS also defines operators. In this instance examples can be \texttt{goto}
+%and \texttt{push}.
+%
+%\begin{description}
+%	\item[push(u,x,y)] Robot pushes object \texttt{u} from \texttt{x} to
+%		position \texttt{y}
+%	\begin{description}
+%		\item[Precondition:] $(\exists s) [AT(u,x,s) \land ATR(x,s)]$
+%		\item[Delete list:] $\{AT(u,x,s), ATR(x,s)\}$
+%		\item[Add list:] $\{AT(u,y,push'(u,x,y,s^*)), ATR(y,push'(u,x,y,s^*))\}$
+%	\end{description}
+%	\item[goto(x,y)] Robot goes from place \texttt{x} to \texttt{y}
+%	\begin{description}
+%		\item[Precondition:] $(\exists s) [ATR(x,s)]$
+%		\item[Delete list:] $\{ATR(x,s)\}$
+%		\item[Add list:] $\{ATR(y,goto'(x,y,s^*))\}$
+%	\end{description}
+%\end{description}
+%
+%The initial world model can be described by:
+%
+%\[
+%	s_0 : \{ ATR(a,x_0), AT(B,b,s_0), AT(C,c,s_0) \}
+%\]
+%
+%Besides that there is a global requirement that two blocks cannot be at the
+%same position at any time.
+%
+%\paragraph{Problems}
+%
+%\begin{itemize}
+%	\item How to efficiently store nodes (states) of the
+%		world.~\cite{fikes1971strips}
+%	\item Arbitrary STRIPS planning problem is a PSPACE complete
+%		problem.~\cite{mcallester1991systematic}
+%	\item Extremely limited in scope of planning problems and complexity of
+%		problems it can solve.~\cite{fikes1994strips}
+%	\item When executing a plan in a real environment, the resulting state
+%		of the world is often different from the state expected by the
+%		planner.~\cite{fikes1994strips}
+%\end{itemize}
+%
+%\paragraph{Strengths}
+%
+%\begin{itemize}
+%	\item Formed the basis for many extensions
+%
+%\end{itemize}
 
-\begin{itemize}
-	\item STRIPS
-\end{itemize}
+\subsection{Classical Planners}
 
-\subsection{1990 - 2000 (I)}
-Choose 3 of these depending on what comes out in the different era's:
+\subsection{Planning graphs}
 
-Model Checking, search techniques, least commitment - probabilistic planner (BURIDAN), DMCPs, dynamic programming, graphplan
+\subsection{Planning as a satisfiability}
 
-Still need to check papers, but already have a bunch.
+\subsection{Heuristic search Planning (HSP)}
 
-\subsection{Introducing the FF planner (I)}
+\subsection{FF Planner (I)}
+Use this: \cite{Hoffmann01theff}
 
-\subsection{2000 - 2005 (A)}
+\subsection{Markov Decision Processes}
 
-\subsection{FF-Replan (I)}
+State what's \cite{monahan1982state} is saying about the state of the art MDPs
+in the 1980s.
+
+\section{Planning under uncertainty}
+
+\subsection{FF-replan (I)}
 
@@
 
-\section{Compare FF-Replan with RFF (I\&A)}
+\subsection{Compare FF-Replan with RFF (I\&A)}
 
-\subsection{How did FF-Replan inspire (I)}
+\subsection{How did FF-Replan and RFF inspire (I)}
+
+\section{Current state-of-the-art planning algorithms}
 
@@
 
-\section{Is it time to reconsider classical planners (I\&A)}
+\section{Is it time to reconsider classical planners under uncertainty (I\&A)}
+
+\bibliographystyle{plain}
+\bibliography{Plan_presentation_monday}
 

### 2014-03-02 presentation-plan/Plan_presentation_monday.tex

@@
 
-%\begin{itemize}
-%	\item STRIPS \cite{fikes1971strips}
-%\end{itemize}
-%
-%\subsubsection{STRIPS}
-%
-%STRIPS~\cite{fikes1971strips} is a influential method of defining planning
-%problems.
-%
-%Take for example~\ref{fig:strips}. R is the robot, B and C are two objects at
-%places a, b and c. The goal is to achieve the configuration such that B is at
-%place k and in which C is not at place c. The robot can move to an object and
-%it can push objects to another position.
-%
-%\begin{figure}[htb]%
-%\includegraphics[width=0.8\columnwidth]{strips-example.pdf}%
-%\caption{Configuration of objects and robot for example problem (Figure from~\cite{fikes1971strips})}%
-%\label{fig:strips}%
-%\end{figure}
-%
-%The goal could be written as
-%
-%\[(\exists s) [ AT(B,k,s) \land \neg AT(C,c,s) ]\]
-%
-%If we find an instance of s, the problem is solved.
-%
-%STRIPS also defines operators. In this instance examples can be \texttt{goto}
-%and \texttt{push}.
-%
-%\begin{description}
-%	\item[push(u,x,y)] Robot pushes object \texttt{u} from \texttt{x} to
-%		position \texttt{y}
-%	\begin{description}
-%		\item[Precondition:] $(\exists s) [AT(u,x,s) \land ATR(x,s)]$
-%		\item[Delete list:] $\{AT(u,x,s), ATR(x,s)\}$
-%		\item[Add list:] $\{AT(u,y,push'(u,x,y,s^*)), ATR(y,push'(u,x,y,s^*))\}$
-%	\end{description}
-%	\item[goto(x,y)] Robot goes from place \texttt{x} to \texttt{y}
-%	\begin{description}
-%		\item[Precondition:] $(\exists s) [ATR(x,s)]$
-%		\item[Delete list:] $\{ATR(x,s)\}$
-%		\item[Add list:] $\{ATR(y,goto'(x,y,s^*))\}$
-%	\end{description}
-%\end{description}
-%
-%The initial world model can be described by:
-%
-%\[
-%	s_0 : \{ ATR(a,x_0), AT(B,b,s_0), AT(C,c,s_0) \}
-%\]
-%
-%Besides that there is a global requirement that two blocks cannot be at the
-%same position at any time.
-%
-%\paragraph{Problems}
-%
-%\begin{itemize}
-%	\item How to efficiently store nodes (states) of the
-%		world.~\cite{fikes1971strips}
-%	\item Arbitrary STRIPS planning problem is a PSPACE complete
-%		problem.~\cite{mcallester1991systematic}
-%	\item Extremely limited in scope of planning problems and complexity of
-%		problems it can solve.~\cite{fikes1994strips}
-%	\item When executing a plan in a real environment, the resulting state
-%		of the world is often different from the state expected by the
-%		planner.~\cite{fikes1994strips}
-%\end{itemize}
-%
-%\paragraph{Strengths}
-%
-%\begin{itemize}
-%	\item Formed the basis for many extensions
-%
-%\end{itemize}
-
 \subsection{Classical Planners}
@@
 
-\subsection{FF-replan (I)}
+\subsection{FF-replan \cite{FFReplan}}
+%Define the problem considering probabilistic and deterministic planning
+
+\subsubsection{Problem definition} 
+Probabilistic planning is naturally formulated using Markov Decision Processes.
+These probabilistic planners focus on the entire state space.
+Deterministic planning has developed heuristic funtions enabling exploration of restricted portions of the state space enroute to the goal state.
+This enables the planner to account for unexpected states rather than ending up in a dead-end.
+MDP's had been the standard in planning algorithms [FOR HOW LONG]?
+However by relying on search and current available processing power, deterministic planners function with enormous speed and efficiency.
+This has been a motivation for combining deterministic and probabilistic planners in the planning communities.
+
+\subsubsection{Motivation for the solution}
+FF-Replan is an action selection algorithm for online planning in probabilistic domains.
+An important notice is that the authors of the paper merely hoped to promote cross-fertilization of deterministic planning techniques in probabilistic planning.
+The basics of the FF-replan algorithm are simple and are valuable mostly because of the speed and efficiency introduced by relying on search.
+It determinizes the input domain, removing all probabilistic information from the problem and synthesizes a plan.
+During the execution of this plan, should an unexpected state occur, the planner replans in the same determinization.
+
+\subsubsection{Details of the solution}
+FF-Replan used two approaches to determinize the input domain.
+The first is single-outcome determinization which selects one outcome for each probabilistic construct.
+The heuristics determine the performance of the planner and should be chosen with care.
+The second approach uses an all-outcomes determinization and considers every probabilistic outcome as a distinct deterministic action.
+FF-Replan than generates one action for each effect (recursively).
+This ensures that an action in a state is chosen that is the first action of a sequential plan with non-zero probability of reaching the goal.
+
+The planner maintains a partial state-action mapping using a hash-table. It determinizes the states and synthesizes a plan using FF and then places the state-action sequence in the table.
+
+It doesn't deal with quantified goals but it picks an arbitrary grounded form of any existential goal.
+
+\subsubsection{Succes of the solution}
+The planner performs strong on Logistic style domains and dead-end free domains. It performs very fast by relying on search.
+
+\subsubsection{Shortcomings of the solution}
+\begin{enumerate}
+	\item When no info about the probabilistic effects is provided, all effects are treated as equal.
+The FF-replan then doesn't attempt to avoid actions that can potentially end up in a dead end or away from the goal.
+	\item  The planner only works well if the outcomes are likely. It might behave poorly in a very fluctuating behavioural environment. 
+	\item The partial state-action policy does not guarantee quality. It may actually loop forever.  
+	\item Picking arbitrary grounded forms of the goal may end up being unreachable or a lot more expensive to reach.
+	\item The single outcome heuristic does not select the dead end outcomes and thus is completely unaware of them.  
+\end{enumerate}
+
+\subsubsection{Points of improvement}
+\begin{enumerate}
+	\item
+	\item 
+	\item Adaptively repair the partial policy 
+	\item Sampling of the grounded goals and testing with a relaxed reachability analysis
+	\item This is solved by using the all-outcomes approach
+	\item It does not look ahead, but only adjusts when something unexpected has occured
+
+	\item Investigate incremental planning approaches that leverage the most deterministic plan
+\end{enumerate}
+
+\subsubsection{Things to look into}
+\begin{itemize}
+	\item How is the exploding block domain currently tackled as during 2004 and 2006 no one really was able to solve it?
+	\item Is the planning time still a problem as much as it proved to be then with the bigger domains?
+	\item Using hindsight optimization might be more realistic as it is less optimistic. It will eventuall increase the process time, but increase the robustness of the system. 
+	\item Using a look ahead policy enables the planner to avoid dead ends, it however does not avoid cycles.
+\end{itemize}
 

### 2014-03-02 presentation-plan/Plan_presentation_monday.tex
Adding RFF

@@
 
+\subsubsection{Problem definition}
+
+Markov Decision Processes (MDPs) is the best known formalism for planning under
+uncertainty. It can however be computationally intensive if large parts of the
+policies are tried to optimize at once. Typically causes to enumerate the
+entire state and action spaces during planning, which obviously takes a lot of
+memory.
+
+\subsubsection{Motivation for the solution}
+
+A previous success at that time in MDP planning is due determinization and
+replanning techniques like FF-Replan. Although it's demonstrated that they're
+practical for various benchmarks, there are still some issues:
+
+\begin{itemize}
+	\item It stops after the first computed path to a goal which is likely to fail
+	\item May result in generating the same path over and over again
+	\item Only generates an execution path, not a policy
+\end{itemize}
+
+\subsubsection{Details of the solution}
+
+The paper presents the Robust FF (\texttt{RFF}) planner, which should solve the
+issues. \texttt{RFF} first generates an initial plan from the initial state to
+some goal using \texttt{FF} on a determination of the MDP\@. There are several
+strategies to do this. \textsc{MostProbableOutcome} (MPO) only uses the action
+from a state with the highest probability. \textsc{AllOutcomes} (AO) uses all
+actions from a state. Then for each state in the plan, the successors of that
+state are added too. This is expanding the execution structure. For the new
+state the probability to reach this state should be higher than a certain
+threshold and if \texttt{FF} does not return a failure for this state and a
+certain goal. The goals can be chosen in three different ways, using
+\textsc{ProblemGoal}, which uses the goals of the MDP, \textsc{RandomGoal},
+which randomly picks some states from the policy graph and \textsc{BestGoal}
+which picks the best states from the policy graph. The calculation of the
+probability to a state from the initial state can be costly. To optimize this
+in \texttt{RFF} a Monte-Carlo (MC) simulation is used. \texttt{RFF} terminates
+if either the global probability is lower than the threshold, or there are no
+new terminal states to be added.
+
+\subsubsection{Success of the solution}
+
+For the IPC-08 the authors have implemented \texttt{RFF} in C++ to perform
+experiments. It performed experiments on the ``fully-observable probabilistic
+(FOP) planning track''. At IPC-08 it performed better than other competitors.
+The experiments confirmed that the probability of success any solution is found
+by \texttt{RFF} is higher than one minus the threshold probability. A higher
+threshold mean that \texttt{RFF} will generate policies that are more prone to
+replanning.
+
+In the experiments different Goal-Selection strategies were tested.
+\textsc{ProblemGoal} (PG) performed the worst. \textsc{RandomGoal} performed
+better and \textsc{BestGoal} generally produced higher quality goals, but also
+took more time.
+
+The different ways of determinizing MDPs was also tested. It turned out that
+\textsc{AllOutcomes} solve much larger problems. However
+\textsc{MostProbableOutcome} generally solve more problems in less time.
+
+\subsubsection{Points of improvement}
+
+\begin{itemize}
+	\item
+\end{itemize}
+
 \subsection{Compare FF-Replan with RFF (I\&A)}

### 2014-03-02 presentation-plan/Plan_presentation_monday.tex
Add a small example for a simple planning problem.

@@
 
-Planning Problem:
+\begin{figure}[htb]%
+\includegraphics[width=0.4\columnwidth]{blocksworld.pdf}%
+\caption{Blocks World example (Figure from~\url{http://www.cs.utexas.edu/~mooney/cs343/slide-handouts/planning.4.pdf})}%
+\label{fig:blocksworld}%
+\end{figure}
+
+In figure~\ref{fig:blocksworld}, how do you go from the initial state to the
+goal state? First you have to move A from B, before you can put B on C and
+finally A on B. This is a very trivial example of planning. Between each
+action of moving a block, the world is in a certain state. Actions provide
+a way to go from one state to another, but from each state, it is possible
+to do multiple actions. For example in the initial state you can move C onto
+A, but that doesn't help achieving the goal. Finding the right sequence of
+actions is what a planner does. From this we can define:
+
+\noindent \textbf{Planning Problem}:
 
@@
 	\item Set of actions
+	\item Conditions
 \end{itemize}
 
-Planning Plan:
+\noindent And the \textbf{Planning Plan}:
 

### 2014-03-02 presentation-plan/Plan_presentation_monday.tex
Short Classical Planner description

@@
 
+Classical Planners do not take uncertainties into account. Classical Planners
+are deterministic.
+
+STRIPS is considered one of the first planning algorithms and
+representations.~\cite{lavalle2006planning}. It is a very simple logic based
+only on literal. It's very nice to describe planning problems in a
+descriptive way that closely corresponds to the application. Also due to the
+operator definition (action/preconditions) it's possible to describe complex
+
 \subsection{Planning graphs}
+
+With states and actions, it's easy to see that a planning problem can be
+represented by a directed graph, where the states are the nodes, and the
+actions are the edges that connect states. The planning problem is now
+a search problem from the root to the goal states.
+
+A well known planner that uses a planning graph is Graphplan.
+[However that seems, after some investigation, to work in an interesting
+different way\ldots]
 

### 2014-03-03 presentation-plan/Plan_presentation_monday.tex
This is a MDP

@@
 
+\noindent A Markov Decision Process has the form $M = (S, A, app, Pr, R)$
+
+\begin{itemize}
+	\item $S$ and $A$ are the finite set of states and actions
+	\item $app(s)$ is the set of of actions applicable in $s$
+	\item For every $a \in app(s)$, $Pr(s,a,s')$ is the probability of a state
+		transition from $s$ to $s'$
+	\item $R(s,a,s')$ is the \emph{reward} of the transition $(s,a,s')$.
+\end{itemize}
+
 \section{Planning under uncertainty}

### 2014-03-04 presentation-plan/Plan_presentation_monday.tex
added comments from presentation and critism on RFF

@@
 
-\section{Historic Overview}
+\section{Historical background information}
 A swift introduction to the evolution of planning algorithms. For every problem state the:
@@
 	\item $R(s,a,s')$ is the \emph{reward} of the transition $(s,a,s')$.
+\end{itemize}
+
+\subsubsection{Shortcomings MDPs}
+\begin{itemize}
+	\item Is computationally challenging as it tries to optimize large parts of the policy at once 
 \end{itemize}
@@
 
+\subsubsection{Criticism on the paper}
+
+\subsubsection{Questions posted on blackboard}
+
 \subsubsection{Things to look into}
@@
 \subsubsection{Details of the solution}
+
+\emph{state that RFF is not an optimization algorithm, but only asks whether there exists a policy whose probability of reaching a goal-state in non zero and whose probability of replanning when executed is less than p}
 
@@
 
+\emph{We should also show their lemma's including the critism on their proof, as it is not sound}
+
 \subsubsection{Points of improvement}
@@
 
+\subsubsection{Criticism on the paper}
+\begin{itemize}
+	\item They redefine the planning problem by adding a probability threshold.
+They use this to their advantage by stating their algorithm is complete as it finds all solutions in this planning problem.
+When not defining this threshold, it obviously doesn't always find all possible solutions as it neglects the lest probable solutions.
+	\item In the experiment section they clearly state that the search-and-rescue domain cause problems for the algorithm, however they choose not to even display the results as the RFF algorithm is not designed for planning problems without goal states.
+This displayes that RFF is in fact not a very good general planning algorithm.
+\end{itemize}
+
+\emph{ We should really include the graphs as their statements do not match the results from the graphs}
+
+\subsubsection{Questions posted on blackboard}
+
+\subsubsection{Interesting directions to look into}
+generalizing the planning framework to hybrid MDPs in which there are both discrete and continuous valued state variables.
+The factored MDP representations in RFF will be the basis of these generalizations.
+There were currently investigation which classical planners were suitable to incoorporate in RFF.
+
+\emph{we should really look into what they did with this direction!}
+
 \subsection{Compare FF-Replan with RFF (I\&A)}
+RFF is states to solve more (and larger) problem instances than FF-Replan.
+This is because RFF is able to reason, offline, about the terminal states of a policy and the probability of a policy will end up in such a state, when executed.
+It generates policies that avoid executions leading into terminal states, whereas FF-replan does not reason about such states during planning time.
+
+\subsubsection{Domains in which FF-replan is favourable}
+
+\subsubsection{Domains in which RFF is favourable}
 
@@
 \section{Current state-of-the-art planning algorithms}
+
+\section{Discussion}
 

### 2014-03-05 presentation/presa.tex
Initial setup for the presentation slides

% MiKTeX (LaTeX) Beamer Presentation template
% Author: Carl Schneider
% University TUDelft
% November 2011
% Simple example (without TOC)

\documentclass{beamer}

% for matlab plots
\usepackage{pgfplots}
% and optionally (as of Pgfplots 1.3):
\pgfplotsset{compat=newest}
\pgfplotsset{plot coordinates/math parser=false}
\newlength\figureheight
\newlength\figurewidth

% Necessary definitions:
\setbeamersize{sidebar width left=0.5cm}
\usepackage[english]{babel}
\usepackage{tikz}
\newcommand{\field}[1]{\mathbb{#1}}
\newcommand{\Zset}{\field{Z}}
\mode<presentation>
{\usetheme{Boadilla} % This theme will be changed into the TUDelft lay-out
  \setbeamercovered{transparent}
}
\definecolor{tudblue}{HTML}{0092DF} % definition TUDelft blue color
\definecolor{white}{rgb}{1,1,1} % definition TUDelft blue color
\setbeamercolor{structure}{fg=tudblue}
\setbeamercolor{palette primary}{fg=white,bg=tudblue!85}       % Right field
\setbeamercolor{palette secondary}{fg=white,bg=tudblue!85}     % Middle field
\setbeamercolor{palette tertiary}{fg=tudblue!85,bg=tudblue!85} % Left field
\setbeamersize{text margin left=1cm}
\setbeamersize{text margin right=1cm}

%---------------------------------------------------------------------------------
%  Take attention for the parts you may change. See the comment lines with: %>>>
%---------------------------------------------------------------------------------

%>>> You may change the text in this part {Between brackets}:
%>>> This is for the Title page:
\newcommand*\titel{FF-Replan: \& RFF: Exploiting classical AI planning for uncertain and probabilistic domains} % On titelpage and in footer on every page
\newcommand*\subkop{} % In blue color
\newcommand*\naam{Imara Speek \& Arian Stolwijk}
\newcommand*\afdeling{}

\setbeamertemplate{navigation symbols}{}

\setbeamercolor{section in head/foot}{fg=white,bg=tudblue}

\setbeamertemplate{footline}{
  \begin{beamercolorbox}[wd=\paperwidth,leftskip=0.5cm,rightskip=0.5cm]{section in head/foot}
    \inserttitle \hfill \insertframenumber{} / \inserttotalframenumber
  \end{beamercolorbox}
}

\let\origframetitle=\frametitle
\renewcommand\frametitle[1]{\origframetitle{\textbf{\large{\textrm{#1}}}}}

%==============================================================
%%% DO NOT CHANGE this part below %%%
%%% Title Page (belongs to the theme)%%%
% Necessary part for the theme:
\title{\titel} % This title also appears in the TUDelft bar on the next pages
\author[]{\naam}
\institute[]{\subkop \\ TU Delft}
\date[]{\today}
\tikzset{textlabel/.style={color=white}}
\beamertemplatetransparentcovereddynamicmedium

%==============================================================
%%% DO NOT CHANGE this part below, except maybe the folder where you placed the "TUDelft bies"
\begin{document}
% Adjusting boadilla theme lay-out to TUDelft lay-out:
\setbeamertemplate{sidebar left}  % blue square left above
{\vfill
\rlap{%\hskip0.1cm
\includegraphics[scale=0.33]{TUDelft/beamer-tudelft-bies.jpg} }
\vskip-5pt}
%==============================================================

% Title page
%%% This is the first frame of the presentation (Title Page).
%%% DO NOT CHANGE this part except maybe the comment signs in case of a background photo
%%% and the place and name of the photo
\begin{frame}[label=titlepage]
    \begin{tikzpicture} [remember picture, overlay]
        \node [shift={(0.5 cm,-5.35cm)}]  at (current page.north west)
        {
        \begin{tikzpicture}[remember picture, overlay]
            %%% These 2 coming lines you may uncomment if you want to have a photo on the background(2198x1480pixels) of the title page

            \node [shift={(-0.14cm,5.56cm)},right] at (current page.south west)
            {\includegraphics[height=8.65cm]{TUDelft/background-titlepage.jpg}};

            % hide the navigation things.
            \fill [cyan!95!black!70!blue] (0,2.9) -- (0,5.35) -- (-.5,5.35) -- (-.5,2.9) -- cycle ;%squareNorthWest
            \draw [fill=black] (0,0) -- (11,0) -- (11,2.9) -- (0,2.9) -- cycle ;
            %\fill [fill=cyan!65!blue!80] (7,-3.9) -- (12.4,-3.9) -- (12.4,-3.65) -- (7,-3.65) -- cycle;

            \node [shift={(0.8cm,-3.1cm)},textlabel,right,text width=10cm]  at (current page.north west) {\textbf{\large{\textrm{\titel}}}};
            \node [shift={(0.8cm,-4cm)},textlabel,cyan!95!black!70!blue,right,text width=10cm]  at (current page.north west)
            {\textbf{\large{\scriptsize \textrm{\subkop}}}};
            \node [shift={(0.8cm,-4.6cm)},textlabel,right]  at (current page.north west)
            {\normalsize{\naam}};
            \node [shift={(0.8cm,-5cm)},textlabel,right]  at (current page.north west)
            {\normalsize{\today}};
        \end{tikzpicture}};
    \end{tikzpicture}
\end{frame}
%==============================================================

\begin{frame}
  \frametitle{Content of presentation}

\end{frame}

\begin{frame}
  \frametitle{Planners}

  % fancy pictures where planners are used

\end{frame}

\begin{frame}
  \frametitle{Example of a Planning Problem}
\end{frame}

\againframe{titlepage}

\end{document}

### 2014-03-05 presentation-plan/Plan_presentation_monday.tex
Typos

@@
 When everything goes well, it should be fine to water it once a week.
-However my room environment has proven to be an uncertain domain where wind, temperature and sunlight severely impacts my abality to plan for nurturing my plants.
+However my room environment has proven to be an uncertain domain where wind, temperature and sunlight severely impacts my ability to plan for nurturing my plants.
 
@@
 These probabilistic planners focus on the entire state space.
-Deterministic planning has developed heuristic funtions enabling exploration of restricted portions of the state space enroute to the goal state.
+Deterministic planning has developed heuristic functions enabling exploration of restricted portions of the state space enroute to the goal state.
 This enables the planner to account for unexpected states rather than ending up in a dead-end.
@@
 	\item This is solved by using the all-outcomes approach
-	\item It does not look ahead, but only adjusts when something unexpected has occured
+	\item It does not look ahead, but only adjusts when something unexpected has occurred
 
@@
 	\item Is the planning time still a problem as much as it proved to be then with the bigger domains?
-	\item Using hindsight optimization might be more realistic as it is less optimistic. It will eventuall increase the process time, but increase the robustness of the system.
+	\item Using hindsight optimization might be more realistic as it is less optimistic. It will eventually increase the process time, but increase the robustness of the system.
 	\item Using a look ahead policy enables the planner to avoid dead ends, it however does not avoid cycles.
@@
 
-\emph{state that RFF is not an optimization algorithm, but only asks whether there exists a policy whose probability of reaching a goal-state in non zero and whose probability of replanning when executed is less than p}
+\emph{state that RFF is not an optimization algorithm, but only asks whether there exists a policy whose probability of reaching a goal-state in non zero and whose probability of replanning when executed is less than $\rho$}
 
@@
 
-\emph{We should also show their lemma's including the critism on their proof, as it is not sound}
+\emph{We should also show their lemma's including the criticism on their proof, as it is not sound}
 
@@
 	\item In the experiment section they clearly state that the search-and-rescue domain cause problems for the algorithm, however they choose not to even display the results as the RFF algorithm is not designed for planning problems without goal states.
-This displayes that RFF is in fact not a very good general planning algorithm.
+This displays that RFF is in fact not a very good general planning algorithm.
 \end{itemize}
@@
 \subsubsection{Interesting directions to look into}
-generalizing the planning framework to hybrid MDPs in which there are both discrete and continuous valued state variables.
+
+Generalizing the planning framework to hybrid MDPs in which there are both discrete and continuous valued state variables.
 The factored MDP representations in RFF will be the basis of these generalizations.
-There were currently investigation which classical planners were suitable to incoorporate in RFF.
+There were currently investigation which classical planners were suitable to incorporate in RFF.
 

### 2014-03-08 presentation-plan/Plan_presentation_monday.tex
Add some examples of applications of planning problems

@@
 	\item Motion Planning
+	\item Inventory Management~\cite{puterman2009markov}
+	\item Equipment Maintenance~\cite{puterman2009markov}
+	\item Communication Models~\cite{puterman2009markov}
 \end{itemize}
@@
 actions is what a planner does. From this we can define:
+
+\subsubsection{Inventory Management} How much of X do we need to order from the
+supplier every day until the end of the season?
+
+\subsubsection{Equipment Maintenance} A bus company is responsible for keeping
+all buses in a good working condition. One aspect is when to replace the bus
+engines~\cite{puterman2009markov}. This problem could be represented as a
+MDP\@.  When to schedule disruptive maintenance jobs by their deadline?
+
+\subsubsection{Communication Models} Many computer, manufacturing and
+communication systems can be modelled as networks with waiting queues and
+servers. Systems have receiving packages, routing, and varying service rates.
 

### 2014-03-08 presentation/presa.tex
Add some more (empty) slides
Add images of examples, simple blocksworld example slide
Slides to explain RFF

@@
 
-  % fancy pictures where planners are used
+  What is a Planner?
+
+  \begin{itemize}
+    \item From \alert{initial state}
+    \item To \alert{Goal state}
+    \item Through \alert{Actions}
+  \end{itemize}
 
@@
 \begin{frame}
-  \frametitle{Example of a Planning Problem}
+  \frametitle{Examples of a Planning Problem}
+
+  \begin{tabular}{c c}
+    \includegraphics[width=3.5cm]{images/containers.jpg}     &
+    \includegraphics[width=3.5cm]{images/inventory.jpg}      \\
+    \includegraphics[width=3.5cm]{images/airplane-food.jpg}  &
+    \includegraphics[width=3.5cm]{images/mars-rover.jpg}
+  \end{tabular}
+
+\end{frame}
+
+\begin{frame}
+  \frametitle{Classical Planning Example}
+
+  \begin{columns}
+    \column{0.3\textwidth}
+    \includegraphics[width=\textwidth]{../presentation-plan/blocksworld.pdf}
+
+    \column{0.7\textwidth}
+
+    \begin{itemize}
+      \item From initial state to goal state?
+      \item Create a planning plan.
+    \end{itemize}
+
+  \end{columns}
+
+\end{frame}
+
+\begin{frame}
+  \frametitle{Planning with Uncertainty}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Historical background information}
+
+\end{frame}
+
+\begin{frame}
+  \frametitle{Planning under uncertainty: FF-Replan}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Planning under uncertainty: RFF}
+
+  \begin{itemize}
+    \item Problem
+      \begin{itemize}
+        \item MDPs can be computationally intensive
+        \item MDPs typically enumerate the entire state and action space
+      \end{itemize}
+    \item Motivation
+      \begin{itemize}
+        \item FF-Replan showed MDP determinization and replanning techniques
+        \item However, it stops after the first computed path to a goal
+        \item May generate same path over and over
+        \item Does not generate a policy
+      \end{itemize}
+  \end{itemize}
+
+\end{frame}
+
+\begin{frame}
+  \frametitle{RFF Solution}
+
+  \begin{columns}
+    \column{0.3\textwidth}
+    \only<1> {\includegraphics[width=\textwidth]{images/rff-1.pdf}}
+    \only<2> {\includegraphics[width=\textwidth]{images/rff-2.pdf}}
+    \only<3> {\includegraphics[width=\textwidth]{images/rff-3.pdf}}
+    \only<4> {\includegraphics[width=\textwidth]{images/rff-5.pdf}}
+    \only<5> {\includegraphics[width=\textwidth]{images/rff-6.pdf}}
+
+    \column{0.7\textwidth}
+
+    \only<1>{%
+      \begin{itemize}
+        \item Initial state and goal of MDP
+        \item Determinization of MDP
+          \begin{itemize}
+            \item \textsc{MostProbableOutcome} % follows action with highest probability to next state
+            \item \textsc{AllOutcomes} % follows all actions to next states
+          \end{itemize}
+      \end{itemize}
+    }
+    \only<2>{%
+      \begin{itemize}
+        \item Use \texttt{FF} to generate initial plan
+      \end{itemize}
+    }
+    \only<3>{%
+      \begin{itemize}
+        \item Expand structure
+      \end{itemize}
+    }
+    \only<4>{%
+      \begin{itemize}
+        \item Use Monte-Carlo sampling to compute the probability to reach nodes in the structure
+      \end{itemize}
+    }
+    \only<5>{%
+      \begin{itemize}
+        \item If the probability of the MC sampling is higher than $\rho$
+        \item Then \texttt{FF} is called, which trajectory is merged with the graph
+          \begin{itemize}
+            \item \texttt{FF} to \textsc{ProblemGoal}
+            \item \texttt{FF} to \textsc{RandomGoal}
+            \item \texttt{FF} to \textsc{BestGoal}
+          \end{itemize}
+        \item Then go back expanding structure from terminal states
+        \item Or if there are no terminal states with $P_t > \rho$ stop
+      \end{itemize}
+    }
+  \end{columns}
+
+\end{frame}
+
+\begin{frame}
+  \frametitle{RFF Results}
+
+  \includegraphics[width=\textwidth]{images/rff-results.pdf}
+
+\end{frame}
+
+\begin{frame}
+  \frametitle{Planning under uncertainty: FF-Replan vs. RFF}
 \end{frame}

### 2014-03-09 presentation/presa.tex
Adding slide about HRFF, which the RFF authors promise in future work

@@
   \includegraphics[width=\textwidth]{images/rff-results.pdf}
+\end{frame}
+
+\begin{frame}
+  \frametitle{RFF Discussion}
+
+  \begin{itemize}
+    \item Won the IPC-08 competition in the ``Fully Observable Probabilistic'' track
+    \item Probability a sulution is found is $1 - \rho$
+    \item $> \rho$ means more replanning
+  \end{itemize}
+
+  \setbeamertemplate{itemize items}[square]
+  \begin{itemize}
+    \item A clear goal must be defined. Does not perform well for the Search-and-Resque domain
+    \item
+  \end{itemize}
+
+\end{frame}
+
+\begin{frame}
+  \frametitle{After RFF}
+
+  \begin{itemize}
+    \item In the ``Future Work'' the authors promised to generalize to Hybrid MDPs
+    \item \emph{``Fast Incremental Policy Compilation from Plans in Hybrid Probabilistic Domains''}
+      \begin{itemize}
+        \item Extends from discrete states to continues
+        \item Like \texttt{RFF} but additional heuristics and usage of \texttt{Metric-FF}
+      \end{itemize}
+  \end{itemize}
 
@@
   \frametitle{Planning under uncertainty: FF-Replan vs. RFF}
+
+  \begin{itemize}
+    \item
+  \end{itemize}
 \end{frame}

### 2014-03-09 presentation/presa.tex
Add RFF criticism that the solution might not be the best solution
RFF Criticism about RFF_MPO completeness
Fix presentation title

@@
 \newlength\figurewidth
+
+\usepackage{setspace}
 
@@
 %>>> This is for the Title page:
-\newcommand*\titel{FF-Replan: \& RFF: Exploiting classical AI planning for uncertain and probabilistic domains} % On titelpage and in footer on every page
-\newcommand*\subkop{} % In blue color
+\newcommand*\titel{FF-Replan \& RFF} % On titelpage and in footer on every page
+\newcommand*\subkop{A Baseline for Probabilistic Planning \\ Incremental Plan Aggregation for Generating Policies in MDPs} % In blue color
 \newcommand*\naam{Imara Speek \& Arian Stolwijk}
@@
             \node [shift={(0.8cm,-4cm)},textlabel,cyan!95!black!70!blue,right,text width=10cm]  at (current page.north west)
-            {\textbf{\large{\scriptsize \textrm{\subkop}}}};
+            {\textbf{\large{\scriptsize \textrm{\begin{spacing}{0.9}\subkop \end{spacing}}}}};
             \node [shift={(0.8cm,-4.6cm)},textlabel,right]  at (current page.north west)
@@
     \item A clear goal must be defined. Does not perform well for the Search-and-Resque domain
-    \item
+    \item If a solution is found, it is correct, but might not be optimal
+    \item Using \textsc{MostProbableOutcome} no solution might be found, even if it exists
   \end{itemize}

### 2014-03-09 presentation-plan/Plan_presentation_monday.tex
Add images of examples, simple blocksworld example slide
More MDP/Planning applications
Adding slide about HRFF, which the RFF authors promise in future work
added FF replan part

@@
 	\item Communication Models~\cite{puterman2009markov}
+	\item Airline Meal Provisioning
+	% some more found: http://courses.cs.washington.edu/courses/csep573/11wi/lectures/12-mdp.pdf
+	\item Stochastic Games
+	\item Robotics navigation
+	\item Finance: options, investments
+	\item Traffic Flow optimization
+	\item Optimizing software on mobiles
 \end{itemize}
@@
 servers. Systems have receiving packages, routing, and varying service rates.
+
+\subsubsection{Airline Meal Provisioning} In airplanes meals can have high
+costs. Significant time is required to prepare meals, while passenger load
+may vary considerably due last minute ticket purchases, missed flights etc.
+This can be modelled as a Markov Decision Process.~\cite{goto2004coffee}
 
@@
 
-\subsection{Planning as a satisfiability}
+\subsection{FF Planner (2001)}
 
-\subsection{Heuristic search Planning (HSP)}
+"We have presented an approach to domain independent planning that, at the time being, outperforms all existing technology on the majority of the currently available benchmark domains."
 
-\subsection{FF Planner (I)}
-Use this: \cite{Hoffmann01theff}
+Before the FF-planner (short for Fast-Foward) three new approaches in plan generation had significantly increased the efficiency of planning systems\cite{Hoffmann01theff}.
+
+\begin{enumerate}
+	\item Plan generation techniques based on \emph{planning graphs} - much faster than any other technique known, made more fficient and expressive.
+These planning graphs have nodes that are actions and atomic facts arranged into alternate leves and edges from an atomic facts to the actions (a condition) or vise versa (true or false).
+The algorithm iteratively extends the planning graphs by backward chaining and looks for actions and previous states from which goals can be reached.
+% http://en.wikipedia.org/wiki/Graphplan
+
+	\item The \emph{planning as satisfiability method} which translated planning to propositional satisfiability as it was expected that state of the art propositional reasoning systems would advance much faster than in planning systems.
+
+	\item The \emph{heuristic search planning} approach in which a heuristic function is derived from the specification of the planning instance and used for guiging the search through the state space.
+HSP estimates goal distances by approximating solution lengths to a relaxation of the planning task.
+\end{enumerate}
+
+FF relies on forward state space search using a heuristic that estimates goal distances by ignoring delete lists and unlike HSP's heuristic does not assume facts to be independent.
+They introduce a search strategy that combines hill-climbing with systematic search and extracted heuristic information to prune the search space.
+It's base heuristic technique can be seen as an application of GRAPHPLAN to the relaxation.
+It also uses an eforced form of hill-climbing combining local and systematic search.
+
+\subsubsection{Details}
+Upon every search state, the search algorithm \emph{enforced hill-climbing} calls the \emph{relaxed GPAPHPLAN}.
+Given the state, GRAPHPHLAN informs the search with a goal distance estimate and additionally a set of promosing successors for the state (\emph{the helpful actions}).
+Upon termination, a solution plan is outputted or a fail is reported.
+If a planning task contains state where the goal is unreachable enforced hill-climbing invokes a complete heuristic search from scratch (using the hash table with visited states).
+To avoid wasting time in the presence of goal ordering, added goal deletion(where goals have been achieved too early as in Boxworld) and a goal agenda techiques have been added.
+
+Performance with Boxworld depends on the goal ordering
+
+\emph{Add image enforced hill climbed invoking graph plan}
+
+\subsubsection{Advantages}
+\begin{itemize}
+	\item As planning is PSPACE-complete, no efficient algorithmic methods are possible, therefor being efficient on restricted subclasses is valuable 
+	\item Most domains presented in the planning competitions are simple in their structure and are easy to solve for a greedy algorithm like FF
+\end{itemize}
+
+\subsubsection{Disadvantages}
+\begin{itemize}
+	\item Methods are motivated by observing examples, this might influence the completeness of the algorithm. 
+	\item The pruning techniques are not complete, they prune the search space in the single enforced hill-climbing try
+	\item Domains with a lot of dead-ends can make FF fail, encountering a dead end state with enforced hill-climbing.
+Trying to solve the tasks with complete best-first search exhausts memory resources for larger instances.
+\end{itemize}
+
+\subsubsection{Difference to HSP}
+They both use forwards search in state space and heuristic evaluation by ignoring delet lists. However FF differs in estimating goal distances. the search strategu and the pruning techniques.
 
@@
 
-\emph{state that RFF is not an optimization algorithm, but only asks whether there exists a policy whose probability of reaching a goal-state in non zero and whose probability of replanning when executed is less than $\rho$}
+\emph{state that RFF is not an optimization algorithm, but only asks whether
+there exists a policy whose probability of reaching a goal-state in non zero
+and whose probability of replanning when executed is less than $\rho$}
 

### 2014-03-09 presentation-plan/Plan_presentation_monday.tex
Some history or something
Needs some improvements :)

--- 2014-03-08 presentation-plan/Plan_presentation_monday.tex
@@
 operator definition (action/preconditions) it's possible to describe complex
+systems. After STRIPS many STRIPS-inspired have been in introduced.
 

### 2014-03-09 presentation-plan/Plan_presentation_monday.tex
added question answers and als FF planner i think

--- 2014-03-09 presentation-plan/Plan_presentation_monday.tex
@@
 \subsubsection{Details of the solution}
+The probabilistic planning problem consists of a domain description, a goal and initial state
+
 FF-Replan used two approaches to determinize the input domain.
@@
 \subsubsection{Questions posted on blackboard}
+\begin{itemize}
+\item FF-Replan planner replans the same determinization of the problem
+when an unexpected state occurs. After replanning a new unexpected state might occur which makes the planner to replan again.
+Can the planner keep replanning forever i.e. end up in deadlock?
+
+The planning problem states the states are finite, therefor the unexpected states are also finite.
+If an unexpected state is encountered, FF-replan determinizes the problem and synthesizes a finite plan.
+These deterministic actions result in a state-action sequence and are put in pairs in the hash table.
+If no further actions are available, the planner can't return a path.
+Therefor no, the planner can't keep replanning forever.
+
+\item Since the planner replans the determinization each time an unexpected state occurs, is this algorithm suitable for real-time systems?
+
+It depends on the kind of real-time system.
+If the domain is a predictable domain, the single outcome determinization is the fastest planning algorithm within the competitors of the IPPC-06 because of the determinization (depending on the heuristics) making it very suitable for a real time system.
+However when considering planning problems such as the blocksworld domain, the al outcome had a succes rate of 86\%, taking 75 s to process 73 steps, so it would depend on how hard the real time system is.
+However when considering hard real-time systems I would not recommend it.
+
+\emph{add image timing FFR}
+
+\end{itemize}
 
@@
 \subsubsection{Questions posted on blackboard}
+\begin{itemize}
+\item When aggregating RFF does not update the current partial policy. How does this algorithm handles in dynamic environments, whereas the current partial policy might be no longer valid?
+
+\item RFF receives a tuple MDP planning problem (M, s0, G, p), where the states are already defined in M, which means that the environment is known.
+Is RFF applicable in unknown environments? If not, is it possible to adjust it so that it becomes applicable?
+\end{itemize}
 
@@
 
-\subsection{How did FF-Replan and RFF inspire (I)}
-
 \section{Current state-of-the-art planning algorithms}
@@
 
-\section{What after? Any new methods (A)}
-
 \section{Present goal of paper (I\&A)}
-
-\section{Is it time to reconsider classical planners under uncertainty (I\&A)}
 

### 2014-03-09 presentation/presa.tex
Planning of nurturing plants
Some history or something
Needs some improvements :)
Explain what MDPs are.
Added the properties of a classical planner vs. MPD
added ff planner and uncertainty

@@
 \begin{frame}
+  \frametitle{Uncertainty}
+
+\emph{Uncertainty applies to predictions of future events, to physical measurements that are already made, or to the unknown.
+Uncertainty arises in partially observable and/or stochastic environments, as well as due to ignorance and/or indolence}
+
+\end{frame}
+
+\begin{frame}
+  \frametitle{Uncertainty}
+
+Meet my plant
+
+    \includegraphics[scale=0.08]{images/plant.jpg}
+\end{frame}
+
+\begin{frame}
   \frametitle{Planning with Uncertainty}
+
+  \begin{columns}
+    \column{0.3\textwidth}
+    \includegraphics[width=\textwidth]{images/plant.jpg}
+
+    \column{0.7\textwidth}
+    How to plan when to water the plant?
+
+    \begin{itemize}
+      \item Uncertainty from Wind
+      \item Sunlight
+      \item Water
+    \end{itemize}
+
+  \vspace{1cm}
+  What if picking up a block fails?
+
+  \end{columns}
 \end{frame}
@@
 \begin{frame}
+  \frametitle{FF Planner (2001)}
+
+''We have presented an approach to domain independent planning that, \emph{at the time being}, outperforms all existing technology on the majority of the currently available benchmark domains.''
+
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF Planner (2001)}
+
+Inspired by three new approaches in plan generation during that time:
+	\begin{itemize}
+		\item Planning graphs
+		\begin{itemize}
+			\item Nodes are actions and atomic facts arranged into alternate levels
+			\item Edges from atomic facts to actions represents conditions
+			\item Edges from actions to atomic facts represent true or false 
+		\end{itemize}
+		\item Planning as a satisfiability method
+		\item Heuristic search planning approach
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF Planner (2001)}
+
+Relies on a 
+	\begin{itemize}
+		\item Forward state space search that combines hill-climbing and systematic search
+		\item Heuristic estimating goal distances by ignoring delete lists - relaxed GRAPHPLAN
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF Planner (2001)}
+
+Insert image on search state, enforced hill climbing, call relaxed graphplan, inform search with goal distance estimate and maybe promising succesors, solution plan or fail, possible search from scratch using hast tabel with visited states
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF Planner (2001)}
+Same image
+
+To avoid wasting time in the presence of goal ordering:
+	\begin{itemize}
+		\item Goal deletion
+		\item Goal agenda techniques
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Discussing the FF planner}
+
+Perks
+	\begin{itemize}
+		\item No efficient algorithmic methods are possible for PSPACE-complete planning, inspired to focus on being efficient on a restricted subclass
+		\item Most domains in the IPCC are simple in their structure and can be easily solves using gree algorithms like FF
+	\end{itemize}
+
+Criticism
+	\begin{itemize}
+		\item Methods are motivated by observing example domains - might influence the completeness
+		\item Pruning techniques are incomplete
+		\item FF behaves poorly in domains with many dead-ends
+		\item Solving these tasks with complete best-first search exhaust the memory for larger instances
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
   \frametitle{Planning under uncertainty: FF-Replan}
+
+  \begin{itemize}
+    \item Problem
+      \begin{itemize}
+        \item MDPs have been the standard for probabilistic planning algorithms
+        \item 
+      \end{itemize}
+  \end{itemize}
+
 \end{frame}

### 2014-03-09 presentation/presa.tex
added ff planner and uncertainty

@@
       \item Create a planning plan.
+      \item Assumptions:
+        \begin{itemize}
+          \item Determinism
+          \item Full observability
+          \item Reachability goals
         \end{itemize}
-
+    \end{itemize}
   \end{columns}
@@
 
-\emph{Uncertainty applies to predictions of future events, to physical measurements that are already made, or to the unknown.
-Uncertainty arises in partially observable and/or stochastic environments, as well as due to ignorance and/or indolence}
+  \emph{``Uncertainty applies to predictions of future events, to physical
+  measurements that are already made, or to the unknown. Uncertainty arises in
+  partially observable and/or stochastic environments, as well as due to
+  ignorance and/or indolence''}
 
-\end{frame}
+  \vspace{2cm}
 
-\begin{frame}
-  \frametitle{Uncertainty}
+  \tiny{http://en.wikipedia.org/wiki/Uncertainty}
 
-Meet my plant
-
-    \includegraphics[scale=0.08]{images/plant.jpg}
 \end{frame}
@@
   \begin{columns}
-    \column{0.3\textwidth}
+    \column{0.25\textwidth}
+    \uncover<1> {Meet my plant}
     \includegraphics[width=\textwidth]{images/plant.jpg}
 
-    \column{0.7\textwidth}
+    \column{0.75\textwidth}
+    \uncover<2->{%
+
       How to plan when to water the plant?
@@
       \end{itemize}
+    }
+  \end{columns}
 
   \vspace{1cm}
-  What if picking up a block fails?
+  \uncover<3-> {What if picking up a block fails?}
+
+\end{frame}
+
+\begin{frame}
+  \frametitle{Markov Decision Processes}
+
+  \begin{itemize}
+    \item Very much like a Classical Planner
+    \item \alert{except} each action has a \alert{probability}
+      \begin{itemize}
+        \item \alert{Stochastic}
+        \item Full observability
+        \item Reachability goals
+      \end{itemize}
+    \item For example in the Blocksworld: The Pick Up action might fail.
+  \end{itemize}
+
+\end{frame}
+
+\begin{frame}
+  \frametitle{Historical background information}
+
+  \begin{columns}
+    \column{0.8\textwidth}
+
+    \begin{itemize}
+      \item 1970s: STRIPS
+      \item 1995: Graphplan
+      \item 2000: FastForward (FF)
+      \item 2004: FF-Replan
+      \item 2010: RFF
+      \item 2014:~?
+    \end{itemize}
+
+    \column{0.2\textwidth}
+    \includegraphics[width=\textwidth]{images/shakey.png}
 
@@
 \begin{frame}
-  \frametitle{Historical background information}
-
-\end{frame}
-
-\begin{frame}
   \frametitle{FF Planner (2001)}
 
-''We have presented an approach to domain independent planning that, \emph{at the time being}, outperforms all existing technology on the majority of the currently available benchmark domains.''
+  ``We have presented an approach to domain independent planning that, \emph{at
+  the time being}, outperforms all existing technology on the majority of the
+  currently available benchmark domains.''
 
@@
   Inspired by three new approaches in plan generation during that time:
+
   \begin{itemize}
@@
   Relies on a
+
   \begin{itemize}
@@
   \end{itemize}
+
 \end{frame}
@@
 
-Insert image on search state, enforced hill climbing, call relaxed graphplan, inform search with goal distance estimate and maybe promising succesors, solution plan or fail, possible search from scratch using hast tabel with visited states
+  Insert image on search state, enforced hill climbing, call relaxed Graphplan,
+  inform search with goal distance estimate and maybe promising successors,
+  solution plan or fail, possible search from scratch using hast table with
+  visited states
+
 \end{frame}
@@
   To avoid wasting time in the presence of goal ordering:
+
   \begin{itemize}
@@
     \item No efficient algorithmic methods are possible for PSPACE-complete planning, inspired to focus on being efficient on a restricted subclass
-		\item Most domains in the IPCC are simple in their structure and can be easily solves using gree algorithms like FF
+    \item Most domains in the IPCC are simple in their structure and can be easily solves using greedy algorithms like FF
   \end{itemize}
@@
     \item In the ``Future Work'' the authors promised to generalize to Hybrid MDPs
-    \item \emph{``Fast Incremental Policy Compilation from Plans in Hybrid Probabilistic Domains''}
-      \begin{itemize}
-        \item Extends from discrete states to continues
-        \item Like \texttt{RFF} but additional heuristics and usage of \texttt{Metric-FF}
-      \end{itemize}
   \end{itemize}
@@
 
+\begin{frame}
+  \frametitle{State-of-the-Art}
+
+  \begin{itemize}
+    \item \emph{``Probabilistic Planning via Determinization in Hindsight''} (2008) \\
+      Improves FF-Replan with hindsight optimization.
+    \item \emph{``Fast Incremental Policy Compilation from Plans in Hybrid Probabilistic Domains''}
+      \begin{itemize}
+        \item Extends from discrete states to continues
+        \item Like \texttt{RFF} but additional heuristics and usage of \texttt{Metric-FF}
+      \end{itemize}
+    \item \emph{``Planning under partial observability by classical replanning: Theory and experiments''} (2011) \\
+      Translates a POMDP to a classical planning problem where it can use \texttt{FF}.
+  \end{itemize}
+
+\end{frame}
+
 \againframe{titlepage}
 
+\begin{frame}
+  \frametitle{Questions?}
+\end{frame}
+
 \end{document}

### 2014-03-10 presentation/presa.tex
Add 3 newer papers about HRFF, Hindsight FF-Replan and POMDPs with FF

--- 2014-03-09 presentation/presa.tex
@@
       \item Create a planning plan.
+      \item Assumptions:
+        \begin{itemize}
+          \item Determinism
+          \item Full observability
+          \item Reachability goals
+        \end{itemize}
+    \end{itemize}
+  \end{columns}
+
+\end{frame}
+
+\begin{frame}
+  \frametitle{Planning under Uncertainty}
+
+  What if moving picking up a block fails?
+  \vspace{2cm}
+
+  \begin{columns}
+    \column{0.4\textwidth}
+    \includegraphics[width=\textwidth,angle=270]{images/plant.jpg}
+
+    \column{0.9\textwidth}
+
+    How to plan when to water the plant?
+
+    \begin{itemize}
+      \item Uncertainty from Wind
+      \item Sunlight
+      \item Water
     \end{itemize}
@@
 \begin{frame}
-  \frametitle{Planning with Uncertainty}
+  \frametitle{Markov Decision Processes}
+
+  \begin{itemize}
+    \item Very much like a Classical Planner
+    \item \alert{except} each action has a \alert{probability}
+      \begin{itemize}
+        \item \alert{Stochastic}
+        \item Full observability
+        \item Reachability goals
+      \end{itemize}
+    \item For example in the Blocksworld: The Pick Up action might fail.
+  \end{itemize}
+
 \end{frame}
@@
 
+  \begin{columns}
+    \column{0.8\textwidth}
+
+    \begin{itemize}
+      \item 1970s: STRIPS
+      \item 1995: Graphplan
+      \item 2000: FastForward (FF)
+      \item 2004: FF-Replan
+      \item 2010: RFF
+      \item 2014:~?
+    \end{itemize}
+
+    \column{0.2\textwidth}
+    \includegraphics[width=\textwidth]{images/shakey.png}
+
+  \end{columns}
+
 \end{frame}
@@
   \frametitle{Planning under uncertainty: FF-Replan}
+
+  \begin{itemize}
+    \item Problem
+      \begin{itemize}
+        \item MDPs have been the standard for probabilistic planning algorithms
+        \item
+      \end{itemize}
+  \end{itemize}
+
 \end{frame}

### 2014-03-10 presentation/presa.tex
ff replan added

--- 2014-03-09 presentation/presa.tex
@@
 
-  Perks
+\begin{itemize}
+\item  Perks
   \begin{itemize}
@@
   \end{itemize}
-
-  Criticism
+\item Criticism
   \begin{itemize}
@@
     \item Solving these tasks with complete best-first search exhaust the memory for larger instances
+  \end{itemize}
 \end{itemize}
@@
         	\item MDPs have been the standard for probabilistic planning algorithms
+        	\item MDPs can be computationally intensive
+	\item typically enumerate the entire state and action space
+      	\end{itemize}
+   \item Motivation for the FF planner
+	\begin{itemize}
+	\item Technological development within processing units
+	\item Relying on search introduces speed and efficiency
+	\end{itemize}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - details of the solution}
+
+  \begin{itemize}
+    \item The planning problem
+	\begin{itemize}
+        	\item a domain description
+	\item a goal
+	\item an initial state 
+	\end{itemize}
+   \item FF-replan
+	\begin{itemize}
+	\item Generates a deterministic planning problem
+	\item Uses the FF planner to compute a totally-ordered plan
+	\item If during execution an unexpected (not in the hash-table) occurs, the process is repeated using this as an initial state
+	\end{itemize}
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - details of the solution}
+
+  \begin{itemize}
+    \item Determinization
+	\begin{itemize}
+        	\item Single outcome determinization
+	\item All-outcomes determinization
+	\end{itemize}
+   \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - details of the solution}
+
+  \begin{itemize}
+    \item Determinization
+   \item Planning
+	\begin{itemize}
+	\item Partial state-action mapping using an initial empty hash-table
+	\item Unexpected states are determinized and the synthesized plan (by FF) is put in the hash table
+	\end{itemize}
+
+\emph{ insert image how hash table is filled}
+
+   \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - Critism}
+
+  \begin{itemize}
+    \item Shortcomings
+	\begin{itemize}
+        	\item Probabilistic effects are treated as equal
+
+\includegraphics[scale=0.5]{images/blindfold.jpg}
+
+	\end{itemize}
+   \item Means of improvement
+   \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - Critism}
+
+  \begin{itemize}
+    \item Shortcomings
+	\begin{itemize}
+        	\item Probabilistic effects are treated as equal
+	\item Only works well if the outcomes are likely
+\includegraphics[scale=0.5]{images/direction-road-maze.jpg}
+	\end{itemize}
+   \item Means of improvement
+
+   \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - Critism}
+
+  \begin{itemize}
+    \item Shortcomings
+	\begin{itemize}
+        	\item Probabilistic effects are treated as equal
+	\item Only works well if the outcomes are likely
+\includegraphics[scale=0.01]{images/direction-road-maze.jpg}
+	\end{itemize}
+   \item Means of improvement
+	\begin{itemize}
 	\item
@@
    \end{itemize}
-
 \end{frame}

### 2014-03-10 presentation-plan/Plan_presentation_monday.tex
Answer Luis' questions

@@
 \subsubsection{Questions posted on blackboard}
+
 \begin{itemize}
-\item When aggregating RFF does not update the current partial policy. How does this algorithm handles in dynamic environments, whereas the current partial policy might be no longer valid?
+	\item \textbf{Q}: When aggregating RFF does not update the current partial
+		policy. How does this algorithm handles in dynamic environments,
+		whereas the current partial policy might be no longer valid? \\
+		\textbf{A}: RFF assumes a MDP, where everything is known. RFF generates
+		a policy off-line, but if that policy is used in an environment that
+		does not equal to the MDP/world it started with it will fail.
 
-\item RFF receives a tuple MDP planning problem (M, s0, G, p), where the states are already defined in M, which means that the environment is known.
-Is RFF applicable in unknown environments? If not, is it possible to adjust it so that it becomes applicable?
+	\item \textbf{Q}: RFF receives a tuple MDP planning problem $(M, s0, G,
+		\rho)$, where the states are already defined in M, which means that
+		the environment is known.  Is RFF applicable in unknown environments?
+		If not, is it possible to adjust it so that it becomes applicable? \\
+		\textbf{A}: RFF works only for MDPs. In an MDP it is assumed that it
+		is fully observable. In cases you describe, it is not, which people
+		invented POMDPs for. POMDPs have different algorithms, for example in
+		the paper about POMDPs which translates a POMDP to a classical planning
+		problem.
+
 \end{itemize}
@@
 
+	\begin{itemize}
+		\item \emph{``Probabilistic Planning via Determinization in Hindsight''} (2008) \\
+			Improves FF-Replan with hindsight optimization.
+		\item \emph{``Fast Incremental Policy Compilation from Plans in Hybrid Probabilistic Domains''}
+			\begin{itemize}
+				\item Extends from discrete states to continues
+				\item Like \texttt{RFF} but additional heuristics and usage of \texttt{Metric-FF}
+			\end{itemize}
+		\item \emph{``Planning under partial observability by classical replanning: Theory and experiments''} (2011) \\
+			Translates a POMDP to a classical planning problem where it can use \texttt{FF}.
+	\end{itemize}
+
 \section{Discussion}

### 2014-03-10 presentation/presa.tex
Fixing indentation
Add RFF problem description
Answer Luis' questions

@@
 
-\emph{ insert image how hash table is filled}
+      \emph{insert image how hash table is filled}
 
@@
         \item Probabilistic effects are treated as equal
-
           \includegraphics[scale=0.5]{images/blindfold.jpg}
-
       \end{itemize}
@@
         \item Only works well if the outcomes are likely
-\includegraphics[scale=0.5]{images/direction-road-maze.jpg}
+          \includegraphics[scale=0.3]{images/direction-road-maze.jpg}
         \end{itemize}
     \item Means of improvement
-
   \end{itemize}
@@
         \item Does not generate a policy
+      \end{itemize}
+    \item Th planning problem
+      \begin{itemize}
+        \item a domain description
+        \item a goal
+        \item an initial state
+        \item a probability threshold $\rho$
       \end{itemize}
@@
 
+\begin{frame}
+  \frametitle{More Questions}
+
+  \begin{itemize}
+    \only<1> {\item \textbf{Q}: When aggregating RFF does not update the current partial
+      policy. How does this algorithm handles in dynamic environments, whereas
+      the current partial policy might be no longer valid?
+      \\ \textbf{A}: RFF assumes a MDP, where everything is known. RFF generates
+      a policy off-line, but if that policy is used in an environment that does
+      not equal to the MDP/world it started with it will fail.
+    }
+
+    \only<2> {\item \textbf{Q}: RFF receives a tuple MDP planning problem $(M, s0, G,
+      \rho)$, where the states are already defined in M, which means that the
+      environment is known.  Is RFF applicable in unknown environments?  If not,
+      is it possible to adjust it so that it becomes applicable?
+      \\ \textbf{A}: RFF works only for MDPs. In an MDP it is assumed that it is
+      fully observable. In cases you describe, it is not, which people invented
+      POMDPs for. POMDPs have different algorithms, for example in the paper
+      about POMDPs which translates a POMDP to a classical planning problem.
+    }
+  \end{itemize}
+
+\end{frame}
+
 \end{document}

### 2014-03-10 presentation/presa.tex
Some initial summary/conclusions...

@@
 \begin{frame}
-  \frametitle{After RFF}
-
-  \begin{itemize}
-    \item In the ``Future Work'' the authors promised to generalize to Hybrid MDPs
-  \end{itemize}
-
-\end{frame}
-
-\begin{frame}
   \frametitle{Planning under uncertainty: FF-Replan vs. RFF}
@@
       Translates a POMDP to a classical planning problem where it can use \texttt{FF}.
+  \end{itemize}
+
+\end{frame}
+
+\begin{frame}
+  \frametitle{Conclusion}
+
+  \begin{itemize}
+    \item
+    \item FF-Replan introduced MDP determinization to use classical planner with uncertainty
+    \item RFF used this idea to generate policies using aggregation and Monte-Carlo simulations.
+    \item FF-Replan has been improved with hindsight
+    \item RFF has been improved for Hybrid Probabilistic Domains
+    \item Also Determinizing of POMDPs have appeared
   \end{itemize}

### 2014-03-10 presentation/presa.tex
Fix typo in presentation
Content of presentation
last changes

--- 2014-03-10 presentation/presa.tex
@@
     \end{itemize}
+
+What if picking up a block fails?
+
   \end{columns}
@@
   \end{columns}
-
-  \vspace{1cm}
-  \uncover<3-> {What if picking up a block fails?}
 
@@
 
-  Inspired by three new approaches in plan generation during that time:
+  Inspired by new approaches in plan generation during that time:
 
@@
     \end{itemize}
-    \item Planning as a satisfiability method
     \item Heuristic search planning approach
@@
   \begin{itemize}
-    \item Forward state space search that combines hill-climbing and systematic search
-    \item Heuristic estimating goal distances by ignoring delete lists - relaxed GRAPHPLAN
+    \item Forward state space search 
+    \item Heuristic relaxed GRAPHPLAN
   \end{itemize}
+
+  \includegraphics{images/ffplan2.pdf}
 
@@
   \frametitle{FF Planner (2001)}
+\begin{columns}
 
-  Insert image on search state, enforced hill climbing, call relaxed Graphplan,
-  inform search with goal distance estimate and maybe promising successors,
-  solution plan or fail, possible search from scratch using hast table with
-  visited states
+\column{0.4\textwidth}
+  \includegraphics[width=0.8\textwidth]{images/ffplan.pdf}
 
+\column{0.6\textwidth}
+\begin{itemize}
+	\item Expand the current state by doing a breadth-first search
+	\item s:= the child of s for which the heuristic evaluates as closest to the solution
+\end{itemize}
+\end{columns}
 \end{frame}
@@
   \frametitle{FF Planner (2001)}
-    Same image
+\begin{columns}
 
+\column{0.4\textwidth}
+  \includegraphics[width=0.8\textwidth]{images/ffplan.pdf}
+
+\column{0.6\textwidth}
   To avoid wasting time in the presence of goal ordering:
@@
   \end{itemize}
-
+\end{columns}
 \end{frame}
@@
   \begin{itemize}
-    \item No efficient algorithmic methods are possible for PSPACE-complete planning, inspired to focus on being efficient on a restricted subclass
-    \item Most domains in the IPCC are simple in their structure and can be easily solves using greedy algorithms like FF
+    \item Efficient on a restricted subclass
+    \item simple IPCC domains can be easily solved using greedy algorithms like FF
   \end{itemize}
@@
   \begin{itemize}
-    \item Methods are motivated by observing example domains - might influence the completeness
+    \item Methods are motivated by observing example domains
     \item Pruning techniques are incomplete
@@
       \end{itemize}
+   \end{itemize}
+\end{frame}
 
-\emph{ insert image how hash table is filled}
+\begin{frame}
+  \frametitle{FF-Replan - details of the solution}
 
+  \begin{itemize}
+    \item Determinization
+    \item Planning
+ \includegraphics[width=\textwidth]{images/replan1.pdf}
+   \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - details of the solution}
+
+  \begin{itemize}
+    \item Determinization
+    \item Planning
+ \includegraphics[width=\textwidth]{images/replan2.pdf}
+   \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - details of the solution}
+
+  \begin{itemize}
+    \item Determinization
+    \item Planning
+ \includegraphics[width=\textwidth]{images/replan3.pdf}
+   \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - details of the solution}
+
+  \begin{itemize}
+    \item Determinization
+    \item Planning
+ \includegraphics[width=\textwidth]{images/replan4.pdf}
+   \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - details of the solution}
+
+  \begin{itemize}
+    \item Determinization
+    \item Planning
+ \includegraphics[width=\textwidth]{images/replan5.pdf}
    \end{itemize}
@@
         \item Only works well if the outcomes are likely
-\includegraphics[scale=0.5]{images/direction-road-maze.jpg}
+          \includegraphics[scale=0.1]{images/direction-road-maze.jpg}
         \end{itemize}
     \item Means of improvement
-
   \end{itemize}
@@
         \item Only works well if the outcomes are likely
-\includegraphics[scale=0.01]{images/direction-road-maze.jpg}
+	\item Partial state-action policy does not guarantee quality
+ %         \includegraphics[scale=0.01]{images/direction-road-maze.jpg}
+      \end{itemize}
+    \item Means of improvement
+   \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - Critism}
+  \begin{itemize}
+    \item Shortcomings
+      \begin{itemize}
+        \item Probabilistic effects are treated as equal
+        \item Only works well if the outcomes are likely
+	\item Partial state-action policy does not guarantee quality
+	\item Picking Arbitrary grounded forms of the goal may end up being unreachable or a lot more expensive
+%          \includegraphics[scale=0.01]{images/direction-road-maze.jpg}
+      \end{itemize}
+    \item Means of improvement
+   \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - Critism}
+  \begin{itemize}
+    \item Shortcomings
+      \begin{itemize}
+        \item Probabilistic effects are treated as equal
+        \item Only works well if the outcomes are likely
+	\item Partial state-action policy does not guarantee quality
+	\item Picking Arbitrary grounded forms of the goal may end up being unreachable or a lot more expensive
+ %         \includegraphics[scale=0.01]{images/direction-road-maze.jpg}
       \end{itemize}
@@
       \begin{itemize}
-	\item
+        \item Addaptively repair the partial policy by for instance randomizing the determinization heuristics 
       \end{itemize}
+   \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - Critism}
+  \begin{itemize}
+    \item Shortcomings
+      \begin{itemize}
+        \item Probabilistic effects are treated as equal
+        \item Only works well if the outcomes are likely
+	\item Partial state-action policy does not guarantee quality
+	\item Picking Arbitrary grounded forms of the goal may end up being unreachable or a lot more expensive
+ %         \includegraphics[scale=0.01]{images/direction-road-maze.jpg}
+      \end{itemize}
+    \item Means of improvement
+      \begin{itemize}
+        \item Addaptively repair the partial policy by for instance randomizing the determinization heuristics 
+	\item Sampling the grounded goals and testing with a relaxed reachability analysis
+      \end{itemize}
+   \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - Critism}
+  \begin{itemize}
+    \item Shortcomings
+      \begin{itemize}
+        \item Probabilistic effects are treated as equal
+        \item Only works well if the outcomes are likely
+	\item Partial state-action policy does not guarantee quality
+	\item Picking Arbitrary grounded forms of the goal may end up being unreachable or a lot more expensive
+ %         \includegraphics[scale=0.01]{images/direction-road-maze.jpg}
+      \end{itemize}
+    \item Means of improvement
+      \begin{itemize}
+        \item Addaptively repair the partial policy by for instance randomizing the determinization heuristics 
+	\item Sampling the grounded goals and testing with a relaxed reachability analysis
+	\item Utilizing look ahead policies that simulate the actions
+      \end{itemize}
+   \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - Questions}
+  \begin{itemize}
+    \item '' FF-Replan planner replans the same determinization of the problem when an unexpected state occurs.
+After replanning a new unexpected state might occur which makes the planner to replan again.
+Can the planner keep re- planning forever i.e.
+end up in deadlock?
+''
+
+   \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - Questions}
+  \begin{itemize}
+    \item '' FF-Replan planner replans the same determinization of the problem when an unexpected state occurs.
+After replanning a new unexpected state might occur which makes the planner to replan again.
+Can the planner keep re- planning forever i.e.
+end up in deadlock?
+''
+   \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - Questions}
+
+This is possible, but depends on the problem domain. 
+\vspace{1cm}
+\begin{columns}
+\column{0.5\textwidth} Domain without cycles: no
+\includegraphics[scale=0.4]{images/Question1a.png}
+
+\column{0.5\textwidth} Domain with cycles: yes
+\includegraphics[scale=0.4]{images/Question1b.png}
+\end{columns}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - Questions}
+  \begin{itemize}
+	\item '' Since the planner replans the determinization each time an unexpected state occurs, is this algorithm suitable for real-time systems? ''
+
+	\begin{itemize}
+		\item Predictable domain: yes. \\
+It is not as computationally intensive as using MDPs  and was the fastest planning algorithm within the competitors of the IPPC-06, making it very suitable.
+
+	\end{itemize}
+
+   \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{FF-Replan - Questions}
+  \begin{itemize}
+	\item '' Since the planner replans the determinization each time an unexpected state occurs, is this algorithm suitable for real-time systems? ''
+
+	\begin{itemize}
+		\item Unpredictable domain: probably not. \\
+Unpredictable domains result in many unexpected states which cause for a significant amount of replanning.
+
+Blocksworld:
+\begin{itemize}
+	\item Succes rate of 86\%
+	\item Path of 73 actions
+	\item Duration of 75s
+\end{itemize}
+
+\emph{Not recommended}, but still depends on the hardness of the real-time system.
+
+	\end{itemize}
+
    \end{itemize}

### 2014-03-10 presentation/presa.tex

@@
   \frametitle{Content of presentation}
+
+  \begin{enumerate}
+    \item Planners
+    \item Uncertainty
+    \item FastForward
+    \item FF-Replan
+    \item RFF
+    \item What's new?
+  \end{enumerate}
 
@@
       \end{itemize}
-    \item Th planning problem
+    \item The planning problem
       \begin{itemize}
@@
 \begin{frame}
-  \frametitle{State-of-the-Art}
+  \frametitle{What's New?}
 
@@
 
+\begin{frame}
+  \frametitle{Conclusion}
+
+  \begin{itemize}
+    \item
+    \item FF-Replan introduced MDP determinization to use classical planner with uncertainty
+    \item RFF used this idea to generate policies using aggregation and Monte-Carlo simulations.
+    \item FF-Replan has been improved with hindsight
+    \item RFF has been improved for Hybrid Probabilistic Domains
+    \item Also Determinizing of POMDPs have appeared
+  \end{itemize}
+
+\end{frame}
+
 \againframe{titlepage}

### 2014-03-10 presentation/presa.tex
Remove FF-Replan vs. RFF slide

@@
 
-What if picking up a block fails?
+    \uncover<2> {What if picking up a block fails?}
 
@@
   \begin{itemize}
-    \item '' FF-Replan planner replans the same determinization of the problem when an unexpected state occurs.
+    \item ``FF-Replan planner replans the same determinization of the problem when an unexpected state occurs.
 After replanning a new unexpected state might occur which makes the planner to replan again.
 Can the planner keep re- planning forever i.e.
-end up in deadlock?
-''
+end up in deadlock?''
 
-   \end{itemize}
-\end{frame}
-
-\begin{frame}
-  \frametitle{FF-Replan - Questions}
-  \begin{itemize}
-    \item '' FF-Replan planner replans the same determinization of the problem when an unexpected state occurs.
-After replanning a new unexpected state might occur which makes the planner to replan again.
-Can the planner keep re- planning forever i.e.
-end up in deadlock?
-''
    \end{itemize}
@@
 \begin{frame}
-  \frametitle{Planning under uncertainty: FF-Replan vs. RFF}
-
-  \begin{itemize}
-    \item
-  \end{itemize}
-\end{frame}
-
-\begin{frame}
   \frametitle{What's New?}
@@
   \begin{itemize}
-    \item
     \item FF-Replan introduced MDP determinization to use classical planner with uncertainty

### 2014-03-11 paper-plan/paper-plan.tex
Empty document for the paper plan

--- 2014-03-09 presentation-plan/Plan_presentation_monday.tex
@@
 % first the title is needed
-\title{Presentation Plan\\
+\title{Paper Plan\\
 FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains}
@@
 %
-\authorrunning{Presentation Plan Seminar Algorithms FF-replan \& RFF}
+\authorrunning{Paper Plan Seminar Algorithms FF-replan \& RFF}
 % (feature abused for this document to repeat the title also on left hand pages)
@@
 
-\section{Introduction to a planner (A)}
-
-What is a planner? [Will need some more detailing].\\
-
-Examples of planning problems:
-
-\begin{itemize}
-	\item Blocks World
-	\item Motion Planning
-	\item Inventory Management~\cite{puterman2009markov}
-	\item Equipment Maintenance~\cite{puterman2009markov}
-	\item Communication Models~\cite{puterman2009markov}
-	\item Airline Meal Provisioning
-	% some more found: http://courses.cs.washington.edu/courses/csep573/11wi/lectures/12-mdp.pdf
-	\item Stochastic Games
-	\item Robotics navigation
-	\item Finance: options, investments
-	\item Traffic Flow optimization
-	\item Optimizing software on mobiles
-\end{itemize}
-
-\begin{figure}[htb]%
-\includegraphics[width=0.4\columnwidth]{blocksworld.pdf}%
-\caption{Blocks World example (Figure from~\url{http://www.cs.utexas.edu/~mooney/cs343/slide-handouts/planning.4.pdf})}%
-\label{fig:blocksworld}%
-\end{figure}
-
-In figure~\ref{fig:blocksworld}, how do you go from the initial state to the
-goal state? First you have to move A from B, before you can put B on C and
-finally A on B. This is a very trivial example of planning. Between each
-action of moving a block, the world is in a certain state. Actions provide
-a way to go from one state to another, but from each state, it is possible
-to do multiple actions. For example in the initial state you can move C onto
-A, but that doesn't help achieving the goal. Finding the right sequence of
-actions is what a planner does. From this we can define:
-
-\subsubsection{Inventory Management} How much of X do we need to order from the
-supplier every day until the end of the season?
-
-\subsubsection{Equipment Maintenance} A bus company is responsible for keeping
-all buses in a good working condition. One aspect is when to replace the bus
-engines~\cite{puterman2009markov}. This problem could be represented as a
-MDP\@.  When to schedule disruptive maintenance jobs by their deadline?
-
-\subsubsection{Communication Models} Many computer, manufacturing and
-communication systems can be modelled as networks with waiting queues and
-servers. Systems have receiving packages, routing, and varying service rates.
-
-\subsubsection{Airline Meal Provisioning} In airplanes meals can have high
-costs. Significant time is required to prepare meals, while passenger load
-may vary considerably due last minute ticket purchases, missed flights etc.
-This can be modelled as a Markov Decision Process.~\cite{goto2004coffee}
-
-\noindent \textbf{Planning Problem}:
-
-\begin{itemize}
-	\item Initial State
-	\item Goal State
-	\item Set of actions
-	\item Conditions
-\end{itemize}
-
-\noindent And the \textbf{Planning Plan}:
-
-\begin{itemize}
-	\item Set of actions
-	\item Executable in the initial state
-	\item Resulting in a state that satisfies the goal state
-\end{itemize}
-
-\section{What is uncertainty (I)}
-
-\emph{Uncertainty applies to predictions of future events, to physical measurements that are already made, or to the unknown.
-Uncertainty arises in partially observable and/or stochastic environments, as well as due to ignorance and/or indolence} [1].
-\\
-
-Uncertain (adjective). \\
-1. not able to be relied on; not known or definite. [2]
-
-In the rest of this topic discuss the different domains and applications.
-
-\subsection{Real world examples}
-
-Growing plants is an extremely uncertain domain.
-When everything goes well, it should be fine to water it once a week.
-However my room environment has proven to be an uncertain domain where wind, temperature and sunlight severely impacts my ability to plan for nurturing my plants.
-
-\subsection{Embedded Systems in uncertain domains}
-
-Cruise control (stabilizing systems), quad rotor, AI, robots
-
-\subsection{Benchmarking for uncertain domains}
-
-Traffic control benchmark for the 2014 IPCC probabilistic continuous domain.
-Tidybot: a housecleaning robot [3]. \\
-
-\noindent [1] [Wikipedia http://en.wikipedia.org/wiki/Uncertainty]
-[2] [Google definition]
-[3] [http://www.plg.inf.uc3m.es/ipc2011-deterministic/DomainsSequential.html\#Barman]
-
-\section{Historical background information}
-A swift introduction to the evolution of planning algorithms. For every problem state the:
-\begin{itemize}
-	\item The problem definition
-	\item The motivation for the solution
-	\item The strengths
-	\item The weaknesses
-\end{itemize}
-
-\subsection{Classical Planners}
-
-Classical Planners do not take uncertainties into account. Classical Planners
-are deterministic.
-
-STRIPS is considered one of the first planning algorithms and
-representations.~\cite{lavalle2006planning}. It is a very simple logic based
-only on literal. It's very nice to describe planning problems in a
-descriptive way that closely corresponds to the application. Also due to the
-operator definition (action/preconditions) it's possible to describe complex
-systems. After STRIPS many STRIPS-inspired have been in introduced.
-
-\subsection{Planning graphs}
-
-With states and actions, it's easy to see that a planning problem can be
-represented by a directed graph, where the states are the nodes, and the
-actions are the edges that connect states. The planning problem is now
-a search problem from the root to the goal states.
-
-A well known planner that uses a planning graph is Graphplan.
-[However that seems, after some investigation, to work in an interesting
-different way\ldots]
-
-\subsection{Planning as a satisfiability}
-
-\subsection{Heuristic search Planning (HSP)}
-
-\subsection{FF Planner (I)}
-Use this: \cite{Hoffmann01theff}
-
-\subsection{Markov Decision Processes}
-
-State what's \cite{monahan1982state} is saying about the state of the art MDPs
-in the 1980s.
-
-\noindent A Markov Decision Process has the form $M = (S, A, app, Pr, R)$
-
-\begin{itemize}
-	\item $S$ and $A$ are the finite set of states and actions
-	\item $app(s)$ is the set of of actions applicable in $s$
-	\item For every $a \in app(s)$, $Pr(s,a,s')$ is the probability of a state
-		transition from $s$ to $s'$
-	\item $R(s,a,s')$ is the \emph{reward} of the transition $(s,a,s')$.
-\end{itemize}
-
-\subsubsection{Shortcomings MDPs}
-\begin{itemize}
-	\item Is computationally challenging as it tries to optimize large parts of the policy at once
-\end{itemize}
-
-\section{Planning under uncertainty}
-
-\subsection{FF-replan \cite{FFReplan}}
-%Define the problem considering probabilistic and deterministic planning
-
-\subsubsection{Problem definition}
-Probabilistic planning is naturally formulated using Markov Decision Processes.
-These probabilistic planners focus on the entire state space.
-Deterministic planning has developed heuristic functions enabling exploration of restricted portions of the state space enroute to the goal state.
-This enables the planner to account for unexpected states rather than ending up in a dead-end.
-MDP's had been the standard in planning algorithms [FOR HOW LONG]?
-However by relying on search and current available processing power, deterministic planners function with enormous speed and efficiency.
-This has been a motivation for combining deterministic and probabilistic planners in the planning communities.
-
-\subsubsection{Motivation for the solution}
-FF-Replan is an action selection algorithm for online planning in probabilistic domains.
-An important notice is that the authors of the paper merely hoped to promote cross-fertilization of deterministic planning techniques in probabilistic planning.
-The basics of the FF-replan algorithm are simple and are valuable mostly because of the speed and efficiency introduced by relying on search.
-It determinizes the input domain, removing all probabilistic information from the problem and synthesizes a plan.
-During the execution of this plan, should an unexpected state occur, the planner replans in the same determinization.
-
-\subsubsection{Details of the solution}
-FF-Replan used two approaches to determinize the input domain.
-The first is single-outcome determinization which selects one outcome for each probabilistic construct.
-The heuristics determine the performance of the planner and should be chosen with care.
-The second approach uses an all-outcomes determinization and considers every probabilistic outcome as a distinct deterministic action.
-FF-Replan than generates one action for each effect (recursively).
-This ensures that an action in a state is chosen that is the first action of a sequential plan with non-zero probability of reaching the goal.
-
-The planner maintains a partial state-action mapping using a hash-table. It determinizes the states and synthesizes a plan using FF and then places the state-action sequence in the table.
-
-It doesn't deal with quantified goals but it picks an arbitrary grounded form of any existential goal.
-
-\subsubsection{Succes of the solution}
-The planner performs strong on Logistic style domains and dead-end free domains. It performs very fast by relying on search.
-
-\subsubsection{Shortcomings of the solution}
-\begin{enumerate}
-	\item When no info about the probabilistic effects is provided, all effects are treated as equal.
-The FF-replan then doesn't attempt to avoid actions that can potentially end up in a dead end or away from the goal.
-	\item  The planner only works well if the outcomes are likely. It might behave poorly in a very fluctuating behavioural environment.
-	\item The partial state-action policy does not guarantee quality. It may actually loop forever.
-	\item Picking arbitrary grounded forms of the goal may end up being unreachable or a lot more expensive to reach.
-	\item The single outcome heuristic does not select the dead end outcomes and thus is completely unaware of them.
-\end{enumerate}
-
-\subsubsection{Points of improvement}
-\begin{enumerate}
-	\item
-	\item
-	\item Adaptively repair the partial policy
-	\item Sampling of the grounded goals and testing with a relaxed reachability analysis
-	\item This is solved by using the all-outcomes approach
-	\item It does not look ahead, but only adjusts when something unexpected has occurred
-
-	\item Investigate incremental planning approaches that leverage the most deterministic plan
-\end{enumerate}
-
-\subsubsection{Criticism on the paper}
-
-\subsubsection{Questions posted on blackboard}
-
-\subsubsection{Things to look into}
-\begin{itemize}
-	\item How is the exploding block domain currently tackled as during 2004 and 2006 no one really was able to solve it?
-	\item Is the planning time still a problem as much as it proved to be then with the bigger domains?
-	\item Using hindsight optimization might be more realistic as it is less optimistic. It will eventually increase the process time, but increase the robustness of the system.
-	\item Using a look ahead policy enables the planner to avoid dead ends, it however does not avoid cycles.
-\end{itemize}
-
-\subsection{RFF (A)}
-
-\subsubsection{Problem definition}
-
-Markov Decision Processes (MDPs) is the best known formalism for planning under
-uncertainty. It can however be computationally intensive if large parts of the
-policies are tried to optimize at once. Typically causes to enumerate the
-entire state and action spaces during planning, which obviously takes a lot of
-memory.
-
-\subsubsection{Motivation for the solution}
-
-A previous success at that time in MDP planning is due determinization and
-replanning techniques like FF-Replan. Although it's demonstrated that they're
-practical for various benchmarks, there are still some issues:
-
-\begin{itemize}
-	\item It stops after the first computed path to a goal which is likely to fail
-	\item May result in generating the same path over and over again
-	\item Only generates an execution path, not a policy
-\end{itemize}
-
-\subsubsection{Details of the solution}
-
-\emph{state that RFF is not an optimization algorithm, but only asks whether
-there exists a policy whose probability of reaching a goal-state in non zero
-and whose probability of replanning when executed is less than $\rho$}
-
-The paper presents the Robust FF (\texttt{RFF}) planner, which should solve the
-issues. \texttt{RFF} first generates an initial plan from the initial state to
-some goal using \texttt{FF} on a determination of the MDP\@. There are several
-strategies to do this. \textsc{MostProbableOutcome} (MPO) only uses the action
-from a state with the highest probability. \textsc{AllOutcomes} (AO) uses all
-actions from a state. Then for each state in the plan, the successors of that
-state are added too. This is expanding the execution structure. For the new
-state the probability to reach this state should be higher than a certain
-threshold and if \texttt{FF} does not return a failure for this state and a
-certain goal. The goals can be chosen in three different ways, using
-\textsc{ProblemGoal}, which uses the goals of the MDP, \textsc{RandomGoal},
-which randomly picks some states from the policy graph and \textsc{BestGoal}
-which picks the best states from the policy graph. The calculation of the
-probability to a state from the initial state can be costly. To optimize this
-in \texttt{RFF} a Monte-Carlo (MC) simulation is used. \texttt{RFF} terminates
-if either the global probability is lower than the threshold, or there are no
-new terminal states to be added.
-
-\subsubsection{Success of the solution}
-
-For the IPC-08 the authors have implemented \texttt{RFF} in C++ to perform
-experiments. It performed experiments on the ``fully-observable probabilistic
-(FOP) planning track''. At IPC-08 it performed better than other competitors.
-The experiments confirmed that the probability of success any solution is found
-by \texttt{RFF} is higher than one minus the threshold probability. A higher
-threshold mean that \texttt{RFF} will generate policies that are more prone to
-replanning.
-
-In the experiments different Goal-Selection strategies were tested.
-\textsc{ProblemGoal} (PG) performed the worst. \textsc{RandomGoal} performed
-better and \textsc{BestGoal} generally produced higher quality goals, but also
-took more time.
-
-The different ways of determinizing MDPs was also tested. It turned out that
-\textsc{AllOutcomes} solve much larger problems. However
-\textsc{MostProbableOutcome} generally solve more problems in less time.
-
-\emph{We should also show their lemma's including the criticism on their proof, as it is not sound}
-
-\subsubsection{Points of improvement}
-
-\begin{itemize}
-	\item
-\end{itemize}
-
-\subsubsection{Criticism on the paper}
-\begin{itemize}
-	\item They redefine the planning problem by adding a probability threshold.
-They use this to their advantage by stating their algorithm is complete as it finds all solutions in this planning problem.
-When not defining this threshold, it obviously doesn't always find all possible solutions as it neglects the lest probable solutions.
-	\item In the experiment section they clearly state that the search-and-rescue domain cause problems for the algorithm, however they choose not to even display the results as the RFF algorithm is not designed for planning problems without goal states.
-This displays that RFF is in fact not a very good general planning algorithm.
-\end{itemize}
-
-\emph{ We should really include the graphs as their statements do not match the results from the graphs}
-
-\subsubsection{Questions posted on blackboard}
-
-\subsubsection{Interesting directions to look into}
-
-Generalizing the planning framework to hybrid MDPs in which there are both discrete and continuous valued state variables.
-The factored MDP representations in RFF will be the basis of these generalizations.
-There were currently investigation which classical planners were suitable to incorporate in RFF.
-
-\emph{we should really look into what they did with this direction!}
-
-\subsection{Compare FF-Replan with RFF (I\&A)}
-RFF is states to solve more (and larger) problem instances than FF-Replan.
-This is because RFF is able to reason, offline, about the terminal states of a policy and the probability of a policy will end up in such a state, when executed.
-It generates policies that avoid executions leading into terminal states, whereas FF-replan does not reason about such states during planning time.
-
-\subsubsection{Domains in which FF-replan is favourable}
-
-\subsubsection{Domains in which RFF is favourable}
-
-\subsection{How did FF-Replan and RFF inspire (I)}
-
-\section{Current state-of-the-art planning algorithms}
-
-\section{Discussion}
-
-\section{What after? Any new methods (A)}
-
-\section{Present goal of paper (I\&A)}
-
-\section{Is it time to reconsider classical planners under uncertainty (I\&A)}
-
 \bibliographystyle{plain}
-\bibliography{Plan_presentation_monday}
+\bibliography{paper-plan}
 

### 2014-03-11 paper-plan/paper-plan.tex
Some papers
Stupidly simple outline, without real content yet :)

@@
 
+\section{Motivation}
+
+There is some domain in which requires probabilistic planning. As FF-Replan and
+RFF are about using deterministic planners in a probabilistic domain, we like
+to see what's new and if we can find some holes that are still open.
+
+\section{Literature Summaries}
+
+\subsection{Probabilistic Planning in the Graphplan Framework (1999)~\cite{Blum99probabilisticplanning}}
+
+Graphplan is a successful planning algorithm for classical STRIPS domains. This
+paper explores the extend it can be used in \emph{probabilistic} domains. The
+paper discusses two variations of Graphplan: PGraphplan and TGraphplan.
+PGraphplan produces an optimal plan, while TGraphplan produces a sub-optimal
+plan but it has increased speed. By comparing the speed and quality of the
+two planners the authors are able to estimate how far they are from the ideal.
+
+\subsection{Compiling Conformant Probabilistic Planning Problems into Classical Planning (2013)~\cite{taig2013compiling}}
+
+\section{Conclusion from Literature and problem statement}
+
+From the related literature we identify some problems.
+
+\section{Solution for the problem}
+
+We try to find some solution or direction how to solve the problem
+
+\section{Conclusion}
+
+Did it work.
+
+\section{More Literature}
+
+\begin{itemize}
+	\item \cite{Hoffmann01theff}
+	\item \cite{FFReplan}
+	\item \cite{teichteil2010incremental}
+	\item \cite{yoon2008probabilistic}
+	\item \cite{teichteil2012fast}
+	\item \cite{bonet2011planning}
+\end{itemize}
+
 \bibliographystyle{plain}

### 2014-03-11 paper-plan/paper-plan.tex
Related work

@@
 
-\section{Literature Summaries}
+\section{Related Work}
 
@@
 
-\subsection{Compiling Conformant Probabilistic Planning Problems into Classical Planning (2013)~\cite{taig2013compiling}}
+\subsection{Compiling Conformant Probabilistic Planning Problems into Classical Planning (2013)~\cite{taig2013conformant}}
 
-\section{Conclusion from Literature and problem statement}
+\section{Conclusion from Related Work and problem statement}
 
@@
 	\item \cite{bonet2011planning}
+	\item \cite{taig2013translation}
+	\item \cite{martin2013progressive}
+	\item \cite{taig2013conformant}
+	\item \cite{2013workshop}
 \end{itemize}

### 2014-03-11 paper-plan/paper-plan.tex
added setup for paper

@@
 
-\section{Motivation}
+%--------------------------------------------------------------------
+
+\section{Introduction}
+
+\begin{itemize}
+	\item Introduce planning problem
+	\item Introduce planning for uncertainty
+	\item Introduce the problem definition and motivation
+\end{itemize}
 
@@
 
-\subsection{Probabilistic Planning in the Graphplan Framework (1999)~\cite{Blum99probabilisticplanning}}
+%---------------------------------------------------------------------
+
+\section{Related works}
+
+\begin{itemize}
+	\item Introduce the previously read papers
+	\item Introduce the current state of the art papers that use deterministic approaches for probablistic domains deadling with uncertainty
+\end{itemize}
+
+\subsubsection{Probabilistic Planning in the Graphplan Framework (1999)~\cite{Blum99probabilisticplanning}}
 
@@
 
-\subsection{Compiling Conformant Probabilistic Planning Problems into Classical Planning (2013)~\cite{taig2013conformant}}
+\subsubsection{Compiling Conformant Probabilistic Planning Problems into Classical Planning (2013)~\cite{taig2013conformant}}
 
-\section{Conclusion from Related Work and problem statement}
+%---------------------------------------------------------------------
+
+\subsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}
+
+For household robot planning, it appears easy, but actually involves
+uncertainty. For tidying things up objects might not be there, or sensing
+operations might tell things wrong. This paper looks into conditions for
+classical planning in a replanning loop in order to solve nondeterministic
+partially observable open domains This paper looks into conditions for
+classical planning in a replanning loop in order to solve nondeterministic
+partially observable open domains.
+
+\section{Problem formulation}
+\begin{itemize}
+	\item Summarize shortcomings of the previous solutions
+	\item Describe the planning problem
+	\item Argument the choice for 2 current papers to analyze
+	\item Define how we would like to test the planning algorithms in a domain by our choice
+\end{itemize}
 
@@
 
-\section{Solution for the problem}
+%---------------------------------------------------------------------
 
-We try to find some solution or direction how to solve the problem
+\section{Domain description}
+
+\begin{itemize}
+	\item Describe domains from IPPC
+	\item Explain shortcomings
+	\item Evaluate a valuable real-world domain in which we can test 2 papers
+\end{itemize}
+
+%---------------------------------------------------------------------
+
+\section{Theoretical approach}
+
+\begin{itemize}
+	\item Describe how we are using the created domain
+	\item show pseudo code for the 2 papers
+	\item Introduce the improvements (or combination) of the approaches of the papers fitted for the domain
+\end{itemize}
+
+%---------------------------------------------------------------------
+
+\section{Empirical evalution}
+
+\begin{itemize}
+	\item Show results for the experiment
+	\item Critically analyze the results
+	\item Compare with results from the original papers
+\end{itemize}
+
+%---------------------------------------------------------------------
 
@@
 
-Did it work.
-
-\section{More Literature}
+\begin{itemize}
+	\item Conclude on the succes of the 2 approaches
+	\item Conclude the work done in the paper
+	\item Hint to some future work developments
+\end{itemize}
 

### 2014-03-11 paper-plan/paper-plan.tex
HouseHold Robot paper

--- 2014-03-11 paper-plan/paper-plan.tex
@@
 
+\subsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}
+
+For household robot planning, it appears easy, but actually involves
+uncertainty. For tidying things up objects might not be there, or sensing
+operations might tell things wrong. This paper looks into conditions for
+classical planning in a replanning loop in order to solve nondeterministic
+partially observable open domains This paper looks into conditions for
+classical planning in a replanning loop in order to solve nondeterministic
+partially observable open domains.
+
 \section{Conclusion from Related Work and problem statement}

### 2014-03-11 paper-plan/paper-plan.tex
Hindsight FF-Replan + typos

--- 2014-03-11 paper-plan/paper-plan.tex
@@
 
-%---------------------------------------------------------------------
-
 \subsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}
@@
 
+\subsection{Probabilistic Planning via Determinization in Hindsight (2008)~\cite{yoon2008probabilistic}}
+
+Hindsight optimization is an online technique that evaluates one-step-reachable
+states by sampling future outcomes to generate multiple non-stationary planning
+problems which are deterministic and can be used using search. It re-interprets
+FF-Replan's~\ref{FFReplan} strategy randomly generating a set of non-stationary
+determinized problems and combining their solutions.
+
+\subsection{}
+
+%---------------------------------------------------------------------
+
 \section{Problem formulation}
+
 \begin{itemize}
@@
 \end{itemize}
-
-From the related literature we identify some problems.
 
@@
 
-\section{Empirical evalution}
+\section{Empirical evaluation}
 
@@
 \begin{itemize}
-	\item Conclude on the succes of the 2 approaches
+	\item Conclude on the success of the 2 approaches
 	\item Conclude the work done in the paper
@@
 \end{itemize}
+
+\section{Some papers}
 

### 2014-03-11 paper-plan/paper-plan.tex
Updated paper structure

--- 2014-03-11 paper-plan/paper-plan.tex
@@
 
-There is some domain in which requires probabilistic planning. As FF-Replan and
-RFF are about using deterministic planners in a probabilistic domain, we like
-to see what's new and if we can find some holes that are still open.
-
-\section{Related Work}
+We will focus on 2 of the current state of the art probablistic planning algorithms that apply determinization
+in probabilistic domains and critize the approaches by formulating a real-world domain as opposed to the IPPC domains.
+By comparing both approaches and analyzing other state of the art work we will propose some adjustments which we will 
+theoretically test in this domain. If it is realistic, we will also try to create an emphirical evaluation.
 
@@
 
-%---------------------------------------------------------------------
-
-\subsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}
+\subsubsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}
 
@@
 
+%---------------------------------------------------------------------
+
 \section{Problem formulation}
@@
 \begin{itemize}
+	\item Describe the experiment setup
 	\item Show results for the experiment

### 2014-03-11 paper-plan/paper-plan.tex
Updated paper structure

--- 2014-03-11 paper-plan/paper-plan.tex
@@
 
-There is some domain in which requires probabilistic planning. As FF-Replan and
-RFF are about using deterministic planners in a probabilistic domain, we like
-to see what's new and if we can find some holes that are still open.
-
-\section{Related Work}
+We will focus on 2 of the current state of the art probabilistic planning
+algorithms that apply determinization in probabilistic domains and criticize
+the approaches by formulating a real-world domain as opposed to the IPPC
+domains.  By comparing both approaches and analyzing other state of the art
+work we will propose some adjustments which we will theoretically test in this
+domain. If it is realistic, we will also try to create an empirical evaluation.
 
@@
 
-\section{Related works}
+\section{Related Work}
 
@@
 
-\subsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}
+\subsubsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}
 
@@
 
-\subsection{Probabilistic Planning via Determinization in Hindsight (2008)~\cite{yoon2008probabilistic}}
+\subsubsection{Probabilistic Planning via Determinization in Hindsight (2008)~\cite{yoon2008probabilistic}}
 
@@
 
-\subsection{}
+\subsubsection{Progressive heuristic search for probabilistic planning based on interaction estimates (2013)~\ref{martin2013progressive}}
+
+In this paper a probabilistic plan graph heuristic is described which computes
+information about the interaction between actions and between propositions.
+This information is used to find better relaxed plans to compute the
+probability of success. This information guides a forward state space search
+for high probability, non-branching seed plans. These plans are then used in
+a planning and scheduling system that handles unexpected outcomes by runtime
+replanning.
+
+\subsubsection{Translation based approaches to probabilistic planning (2013)~\cite{taig2013translation}}
 

### 2014-03-11 paper-plan/paper-plan.tex
Progressive heuristics thing

@@
 
-\section{Related Work}
-
 %---------------------------------------------------------------------
 
-\section{Related works}
+\section{Related Work}
 
@@
 
-\subsection{}
+\subsubsection{Progressive heuristic search for probabilistic planning based on interaction estimates (2013)~\ref{martin2013progressive}}
+
+In this paper a probabilistic plan graph heuristic is described which computes
+information about the interaction between actions and between propositions.
+This information is used to find better relaxed plans to compute the
+probability of success. This information guides a forward state space search
+for high probability, non-branching seed plans. These plans are then used in
+a planning and scheduling system that handles unexpected outcomes by runtime
+replanning.
+
+\subsection{Translation based approaches to probabilistic planning (2013)~\cite{taig2013translation}}
 

### 2014-03-11 paper-plan/paper-plan.tex
move hindsight of 2008
Adding Improving Determinization of hindsight planning

--- 2014-03-11 paper-plan/paper-plan.tex
@@
 
+\subsubsection{Probabilistic Planning via Determinization in Hindsight (2008)~\cite{yoon2008probabilistic}}
+
+Hindsight optimization is an online technique that evaluates one-step-reachable
+states by sampling future outcomes to generate multiple non-stationary planning
+problems which are deterministic and can be used using search. It re-interprets
+FF-Replan's~\cite{FFReplan} strategy randomly generating a set of non-stationary
+determinized problems and combining their solutions.
+
+\subsubsection{Improving Determinization in Hindsight for Online Probabilistic Planning (2010)~\cite{yoon2010improving}}
+
+Hindsight optimization has enjoyed some success for online probabilistic
+planning. Although it has proven to be effective for many domains, it is
+computationally expensive. This paper presents significant improvements.  1) a
+method for detecting potential useful actions, 2) exploit determinism in the
+domain by reusing relevant plans, 2) improves action evaluation by increasing
+the chance that at least one deterministic plan reaches a goal.
+
 \subsubsection{Probabilistic Planning in the Graphplan Framework (1999)~\cite{Blum99probabilisticplanning}}
@@
 
-\subsubsection{Probabilistic Planning via Determinization in Hindsight (2008)~\cite{yoon2008probabilistic}}
-
-Hindsight optimization is an online technique that evaluates one-step-reachable
-states by sampling future outcomes to generate multiple non-stationary planning
-problems which are deterministic and can be used using search. It re-interprets
-FF-Replan's~\ref{FFReplan} strategy randomly generating a set of non-stationary
-determinized problems and combining their solutions.
-
-\subsubsection{Progressive heuristic search for probabilistic planning based on interaction estimates (2013)~\ref{martin2013progressive}}
+\subsubsection{Progressive heuristic search for probabilistic planning based on interaction estimates (2013)~\cite{martin2013progressive}}
 

### 2014-03-15 Initial-paper/paper.tex
put todo list in readme file and created a setup for the paper itself

--- 2014-03-11 paper-plan/paper-plan.tex
@@
 
+\begin{abstract}
+blabla
+\end{abstract}
+
+%--------------------------------------------------------------------
+
 \section{Introduction}
@@
 \begin{itemize}
-	\item Introduce planning problem
+	\item Describe probabilistic planning problem
 	\item Introduce planning for uncertainty
-	\item Introduce the problem definition and motivation
+	\item Describe how deterministic classical planners can be used in probabilistic domains and motivate why this is interesting
+	\item Introduce the qualities of replanning and the second planning algorithm
+	\item Describe the need for a new domain for real world applications
+	\item Describe the goal and tools used to reach this goal
 \end{itemize}
 
-We will focus on 2 of the current state of the art probabilistic planning
-algorithms that apply determinization in probabilistic domains and criticize
-the approaches by formulating a real-world domain as opposed to the IPPC
-domains.  By comparing both approaches and analyzing other state of the art
-work we will propose some adjustments which we will theoretically test in this
-domain. If it is realistic, we will also try to create an empirical evaluation.
+%---------------------------------------------------------------------
+
+\section{Problem formulation}
+
+\begin{itemize}
+	\item Summarize shortcomings of the previous solutions
+	\item Describe the planning problem
+	\item Argument the choice for 2 current papers to analyze
+	\item Define how we would like to test the planning algorithms in a domain by our choice
+\end{itemize}
+
+%---------------------------------------------------------------------
+
+\section{Domain description}
+
+\begin{itemize}
+	\item Describe domains from IPPC
+	\item Explain shortcomings
+	\item Evaluate a valuable real-world domain in which we can test 2 papers
+\end{itemize}
+
+%---------------------------------------------------------------------
+
+\section{Theoretical approach}
+
+\begin{itemize}
+	\item Describe how we are using the created domain
+	\item show pseudo code for the 2 papers
+	\item Introduce the improvements (or combination) of the approaches of the papers fitted for the domain
+\end{itemize}
+
+%---------------------------------------------------------------------
+
+\section{Empirical evaluation}
+
+\begin{itemize}
+	\item Describe the experiment setup
+	\item Show results for the experiment
+	\item Critically analyze the results
+	\item Compare with results from the original papers
+\end{itemize}
 
@@
 \section{Related Work}
+% Use related work to display the differences with own work
 
 \begin{itemize}
-	\item Introduce the previously read papers
+	\item Discuss the related work and how their approaches are different
+	\item Discuss the other domains and why our domain adds anything to the community
 	\item Introduce the current state of the art papers that use deterministic approaches for probablistic domains deadling with uncertainty
@@
 
-\section{Problem formulation}
-
-\begin{itemize}
-	\item Summarize shortcomings of the previous solutions
-	\item Describe the planning problem
-	\item Argument the choice for 2 current papers to analyze
-	\item Define how we would like to test the planning algorithms in a domain by our choice
-\end{itemize}
-
-%---------------------------------------------------------------------
-
-\section{Domain description}
-
-\begin{itemize}
-	\item Describe domains from IPPC
-	\item Explain shortcomings
-	\item Evaluate a valuable real-world domain in which we can test 2 papers
-\end{itemize}
-
-%---------------------------------------------------------------------
-
-\section{Theoretical approach}
-
-\begin{itemize}
-	\item Describe how we are using the created domain
-	\item show pseudo code for the 2 papers
-	\item Introduce the improvements (or combination) of the approaches of the papers fitted for the domain
-\end{itemize}
-
-%---------------------------------------------------------------------
-
-\section{Empirical evaluation}
-
-\begin{itemize}
-	\item Describe the experiment setup
-	\item Show results for the experiment
-	\item Critically analyze the results
-	\item Compare with results from the original papers
-\end{itemize}
-
-%---------------------------------------------------------------------
-
 \section{Conclusion}

### 2014-03-25 Initial-paper/paper.tex
added important papers and changes paper setup
Write down the goal of the paper what we want to claim/show

@@
 \begin{abstract}
-blabla
+	This paper argues that for many real life domains dead-ends are the end of
+	the world, and by for example human interaction the goal can still be
+	reached. By relaxing the definition of a dead-end, we argue that for many
+	real life domains a simpler planning algorithm, like FF-Replan, can be
+	sufficient, and that it's not needed to have newer and sophisticated
+	probabilistic planners.
 \end{abstract}
@@
 	\item Evaluate a valuable real-world domain in which we can test 2 papers
+	\item Show PPDDL or RDDL of domain (probabilistic extension of PDDL)
 \end{itemize}

### 2014-03-28 Initial-paper/paper.tex
added bib items, new titel, changed README

@@
 % first the title is needed
-\title{Paper Plan\\
-FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains}
+\title{Validating FF-Replan vs. a state-of-the-art propabilistic planner in a real world domain}
 
@@
 
+\subsubsection{Reverse Iterative Deepening for Finite-Horizon MDPs with Large Branching Factors (2012)~\cite{kolobov2012glutton}}
+The IPPC-2011 introduces more realistic MDPs to accomodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
+For this reason planners needed to be scalable and sensitive to the expected reward maximization.
+Glutton introduces an offline algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a succesfull policy can be produced by solving an MDP M(H) for a smaller horizon h.
+Incrementally solving the sequence M(1), M(2) forms the basis of LR\textsuperscript{2}TDP.
+By iterating on the distance from the horizon, data can be reused (and is stored in the cache untill the hash-table is full).
+The max-reward heuristic finds the largest horizon value h' for which already a heuristic value V is estimated.
+The  cmputation time remains much lower because it runs quickly into states that converged while solving M(h-1).
+The max-reward computation relies on knowing the maximum reward any action can yield in any state or an upper bound on it.
+
+%TODO still have to describe the Glutton variation on LR2TDP
+
 %---------------------------------------------------------------------
@@
 	\item \cite{2013workshop}
+	\item \cite{nebel2013much}
+	\item \cite{little2007probvsreplan}
+	\item \cite{keller2012prost}
+	\item \cite{kolobov2012glutton}
 \end{itemize}
@@
 \bibliographystyle{plain}
-\bibliography{paper-plan}
+\bibliography{paper}
 

### 2014-03-28 FinalPaper/paper.tex
added initial part domain, summary of domain paper

--- 2014-03-28 Initial-paper/paper.tex
@@
 %
-\authorrunning{Paper Plan Seminar Algorithms FF-replan \& RFF}
+\authorrunning{Validating planners in a real world domain}
 % (feature abused for this document to repeat the title also on left hand pages)
@@
 	\item Define how we would like to test the planning algorithms in a domain by our choice
+\end{itemize}
+
+\subsection{Probabilistic planning}
+
+\subsection{Replanning}
+\begin{itemize}
+	\item Describe the determinization, or explain
 \end{itemize}
@@
 
+\subsubsection{Probabilistic planning vs Replanning}
+Inspired by the FF-Replan entrance in the IPPC competition, this paper described a probabilistic interestingness quality of domains.
+It then compares probabilitsic planners with replanners in the different domains to draw conclusions.
+Classical planning with replanning upon failure when there is so little or so much uncertainty about the world that it is not worth modelling and reasoning about or when goals dynamically change or when the problem is too large to solve at once.
+Probabilistic planners are more appropriate when avoiding irreparable or costly failures.
+Probabilistic planning computes a plan that can handle all foreseeable contingencies and is preferable for quick reactions in closed control loops.
+
+The following structural properties are identified for comparing probabilistic planning with replanning:
+\begin{itemize}
+	\item 'dead' end states
+	\item the degree to which the probability of reaching a deaad end state can be reduced through choice of actions
+	\item number of distinct trajectories
+	\item presence of mutual exclusion
+\end{itemize}
+
+If there are no dead ends, a replanner will always succeed.
+It is impossible to improve on the unavoidable dead ends (positive probability of reaching when executing which cannot be reduced without reucing the probability of reaching the goal).
+
+A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties:
+\begin{itemize}
+	\item there are multiple goal trajectories;
+	\item there is at least on pair of distinct goal trajectories, $\tau$ and $\tau$ ', that share a common sequence of outcomes for the first n-1 outcomes, and where $\tau$\textsubscript{n} and $\tau$'\textsubscript{n} are distinct outcomes of the same action; and
+	\item there exist two distinct goal trajectories $\tau$ and $\tau$' and outcome o $\in$ $\tau$ and o' $\in$ $\tau$' of two distinct actions a = act(o) and a'= act(o') such that executing a strictly decreases the maximum probability of reaching a state where a' can be executed.
+\end{itemize}
+
+Problems that fail to be \emph{probabilistically interesting} are actually classical planning problems in disguise and for those replanners are more appropriate.
+A replanner can also perform optimally for probabilistically interesting planning problems whenever the 'most promising' goal trajectory is the correct thing to do.
+They create several domains to explore the issue of replanning vs.
+probabilistic planning.
+
+Following existing domains were said to be probabilistically interesting:
+\begin{itemize}
+	\item Drive
+	\item Exploding blocksworld
+	\item Pitchcatch
+	\item Schedule
+	\item Tireworld
+\end{itemize}
+
+They conclude by stating that the negative perception of probabilistic planning by the ICAPS community was inaccurate.
+They state that a synthesis of planning and replanning techniques could make a larger number of probabilistic planning problems pacticably solvable than is currently possible.
+
+\section{Domain description}
+% Stukje voor domein
+Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thiébauw a baseline test for \emph{probabilistically interesting} domains is proposed.
+Problems that fail this test were deemed to be classical planning problems in disguise \cite{little2007probvsreplan}.
+To validate our planners in a real-world domain we will analyze previous and current domain description for the 'probabilistically interestingness' using this baseline test, adjust them to what we consider as being a real-world domain and test it again.
+Using these
+
+FF-Replan participated in IPPC-04 (and IPPC-06) solving problems that had been specified in the Probabilstic Planning Domain Description Language (PPDDL) whereas Gourmand has been tested on the set of IPPC-11 problems specified in Relational Dynamic Influence Diagram Language (RDDL)\cite{sanner2008rddl}.
+
+\subsection{Planning problem definition}
+
 %---------------------------------------------------------------------
@@
 	\item \cite{kolobov2012glutton}
+	\item \cite{sanner2008rddl}
 \end{itemize}

### 2014-03-28 FinalPaper/paper.tex
added initial part gourmand, piece of intro

@@
 % first the title is needed
-\title{Validating FF-Replan vs. a state-of-the-art propabilistic planner in a real world domain}
+\title{Validating FF-Replan vs. a state-of-the-art propabilistic planner in translated real world domains}
 
@@
 
+The baseline test in \cite{little2007probvsreplan} evaluates the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.
+probabilistic planners.
+We would like to carefully analyze the credibility of these domains in the real world and evaluate the worth of FF-Replan vs a state of the art probabilistic planner: Gourmand \cite{kolobov2012gourmand}.
+
 \begin{itemize}
@@
 \section{Domain description}
+Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thiébauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
+Problems that fail this test were deemed to be classical planning problems in disguise, favouring using replanners\cite{little2007probvsreplan}.
+This section describes interesting domains in which either FF-Replan or Gourmand prevailed during the International Probabilistic Planning Compeitions.
+We will then translate the most interesting domains to a complete "real-world" domain and evaluate them using the probabilistically interesting baseline test.
+This paper concludes on evaluation both planners using the translated domains.
 
+\subsection{Interesting domains}
+The competitor FF-Replan\cite{FFReplan} remembered the committee of the IPPC in 2004 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
+The baseline test evaluates the competition problems of the IPPC described in PPDDLto correct the possible inaccurate perception of replanners vs.
+probabilistic planners.
+
+Following existing domains were said to be probabilistically interesting:
 \begin{itemize}
-	\item Describe domains from IPPC
-	\item Explain shortcomings
-	\item Evaluate a valuable real-world domain in which we can test 2 papers
-	\item Show PPDDL or RDDL of domain (probabilistic extension of PDDL)
+	\item Drive
+	\item Exploding blocksworld
+	\item Pitchcatch
+	\item Schedule
+	\item Tireworld
 \end{itemize}
+
+\subsection{Real world evaluation}
+Explain shortcomings
+
+\subsection{Probabilistically interesting domains}
+A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties:
+\begin{itemize}
+	\item there are multiple goal trajectories;
+	\item there is at least on pair of distinct goal trajectories, $\tau$ and $\tau$ ', that share a common sequence of outcomes for the first n-1 outcomes, and where $\tau$\textsubscript{n} and $\tau$'\textsubscript{n} are distinct outcomes of the same action; and
+	\item there exist two distinct goal trajectories $\tau$ and $\tau$' and outcome o $\in$ $\tau$ and o' $\in$ $\tau$' of two distinct actions a = act(o) and a'= act(o') such that executing a strictly decreases the maximum probability of reaching a state where a' can be executed.
+\end{itemize}
+
+\subsection{Evaluating the domains}
+FF-Replan participated in IPPC-04 (and IPPC-06) solving problems that had been specified in the Probabilstic Planning Domain Description Language (PPDDL) whereas Gourmand has been tested on the set of IPPC-11 problems specified in Relational Dynamic Influence Diagram Language (RDDL)\cite{sanner2008rddl}.
 
@@
 
-\section{Domain description}
-% Stukje voor domein
-Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thiébauw a baseline test for \emph{probabilistically interesting} domains is proposed.
-Problems that fail this test were deemed to be classical planning problems in disguise \cite{little2007probvsreplan}.
-To validate our planners in a real-world domain we will analyze previous and current domain description for the 'probabilistically interestingness' using this baseline test, adjust them to what we consider as being a real-world domain and test it again.
-Using these
-
-FF-Replan participated in IPPC-04 (and IPPC-06) solving problems that had been specified in the Probabilstic Planning Domain Description Language (PPDDL) whereas Gourmand has been tested on the set of IPPC-11 problems specified in Relational Dynamic Influence Diagram Language (RDDL)\cite{sanner2008rddl}.
-
-\subsection{Planning problem definition}
-
 %---------------------------------------------------------------------
@@
 	\item \cite{sanner2008rddl}
+	\item \cite{kolobov2012gourmand}
 \end{itemize}

### 2014-03-29 FinalPaper/paper.tex
Fixing typos, adding pdf to gitignore

@@
 % first the title is needed
-\title{Validating FF-Replan vs. a state-of-the-art propabilistic planner in translated real world domains}
+\title{Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains}
 
 % a short form should be given in case it is too long for the running head
-\titlerunning{Presentation Plan}
+\titlerunning{FF-Replan vs Probabilistic Planner in Real World Domains}
 
@@
 %
-\authorrunning{Validating planners in a real world domain}
+\authorrunning{Validating Planners in a Real World Domain}
 % (feature abused for this document to repeat the title also on left hand pages)
@@
 \institute{Seminar Algorithms, Embedded Software,
-Msc Embedded Systems,\\
+MSc Embedded Systems,\\
 Delft University of Technology\\
@@
 
-The baseline test in \cite{little2007probvsreplan} evaluates the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.
-probabilistic planners.
+The baseline test in \cite{little2007probvsreplan} evaluates the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
 We would like to carefully analyze the credibility of these domains in the real world and evaluate the worth of FF-Replan vs a state of the art probabilistic planner: Gourmand \cite{kolobov2012gourmand}.
@@
 \section{Domain description}
-Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thiébauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
+Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
 Problems that fail this test were deemed to be classical planning problems in disguise, favouring using replanners\cite{little2007probvsreplan}.
@@
 The competitor FF-Replan\cite{FFReplan} remembered the committee of the IPPC in 2004 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
-The baseline test evaluates the competition problems of the IPPC described in PPDDLto correct the possible inaccurate perception of replanners vs.
-probabilistic planners.
+The baseline test evaluates the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
 
@@
 \subsection{Real world evaluation}
+
 Explain shortcomings
@@
 A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties:
+
+% reference little & thiebauw again. Maybe also shortly define what all o, n, act etc. are.
+
 \begin{itemize}
@@
 	\item Discuss the other domains and why our domain adds anything to the community
-	\item Introduce the current state of the art papers that use deterministic approaches for probablistic domains deadling with uncertainty
+	\item Introduce the current state of the art papers that use deterministic approaches for probablistic domains dealing with uncertainty
 \end{itemize}
@@
 \subsubsection{Reverse Iterative Deepening for Finite-Horizon MDPs with Large Branching Factors (2012)~\cite{kolobov2012glutton}}
-The IPPC-2011 introduces more realistic MDPs to accomodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
+The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
 For this reason planners needed to be scalable and sensitive to the expected reward maximization.
-Glutton introduces an offline algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a succesfull policy can be produced by solving an MDP M(H) for a smaller horizon h.
+Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP M(H) for a smaller horizon h.
 Incrementally solving the sequence M(1), M(2) forms the basis of LR\textsuperscript{2}TDP.
-By iterating on the distance from the horizon, data can be reused (and is stored in the cache untill the hash-table is full).
+By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full).
 The max-reward heuristic finds the largest horizon value h' for which already a heuristic value V is estimated.
-The  cmputation time remains much lower because it runs quickly into states that converged while solving M(h-1).
+The  computation time remains much lower because it runs quickly into states that converged while solving M(h-1).
 The max-reward computation relies on knowing the maximum reward any action can yield in any state or an upper bound on it.
@@
 Inspired by the FF-Replan entrance in the IPPC competition, this paper described a probabilistic interestingness quality of domains.
-It then compares probabilitsic planners with replanners in the different domains to draw conclusions.
+It then compares probabilistic planners with replanners in the different domains to draw conclusions.
 Classical planning with replanning upon failure when there is so little or so much uncertainty about the world that it is not worth modelling and reasoning about or when goals dynamically change or when the problem is too large to solve at once.
@@
 	\item 'dead' end states
-	\item the degree to which the probability of reaching a deaad end state can be reduced through choice of actions
+	\item the degree to which the probability of reaching a dead end state can be reduced through choice of actions
 	\item number of distinct trajectories
@@
 If there are no dead ends, a replanner will always succeed.
-It is impossible to improve on the unavoidable dead ends (positive probability of reaching when executing which cannot be reduced without reucing the probability of reaching the goal).
+It is impossible to improve on the unavoidable dead ends (positive probability of reaching when executing which cannot be reduced without reducing the probability of reaching the goal).
+
+% repetition of what's already stated earlier
 
 A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties:
+
 \begin{itemize}
@@
 They conclude by stating that the negative perception of probabilistic planning by the ICAPS community was inaccurate.
-They state that a synthesis of planning and replanning techniques could make a larger number of probabilistic planning problems pacticably solvable than is currently possible.
+They state that a synthesis of planning and replanning techniques could make a larger number of probabilistic planning problems practicably solvable than is currently possible.
 

### 2014-03-29 FinalPaper/paper.tex
more about glutton, points added to problem definition

@@
 
+\subsection{Planning problem}
+\begin{itemize}
+	\item Describe the MDP finite horizon planning problem
+	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
+	\item Describe reward heuristic
+	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest exected reward over H steps time
+	\item The challenge or large branching factors
+\end{itemize}
+
 %---------------------------------------------------------------------
@@
 
-\subsubsection{Probabilistic Planning via Determinization in Hindsight (2008)~\cite{yoon2008probabilistic}}
+\subsection{Probabilistic Planning via Determinization in Hindsight (2008)~\cite{yoon2008probabilistic}}
 
@@
 
-\subsubsection{Improving Determinization in Hindsight for Online Probabilistic Planning (2010)~\cite{yoon2010improving}}
-
+\subsection{Improving Determinization in Hindsight for Online Probabilistic Planning (2010)~\cite{yoon2010improving}}
 Hindsight optimization has enjoyed some success for online probabilistic
@@
 
-\subsubsection{Probabilistic Planning in the Graphplan Framework (1999)~\cite{Blum99probabilisticplanning}}
-
+\subsection{Probabilistic Planning in the Graphplan Framework (1999)~\cite{Blum99probabilisticplanning}}
+% might not be necessary?
 Graphplan is a successful planning algorithm for classical STRIPS domains. This
@@
 
-\subsubsection{Compiling Conformant Probabilistic Planning Problems into Classical Planning (2013)~\cite{taig2013conformant}}
+%\subsection{Compiling Conformant Probabilistic Planning Problems into Classical Planning (2013)~\cite{taig2013conformant}}
+% not necessary?
 
-\subsubsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}
+\subsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}
 
@@
 
-\subsubsection{Progressive heuristic search for probabilistic planning based on interaction estimates (2013)~\cite{martin2013progressive}}
+\subsection{Progressive heuristic search for probabilistic planning based on interaction estimates (2013)~\cite{martin2013progressive}}
 
@@
 
-\subsubsection{Translation based approaches to probabilistic planning (2013)~\cite{taig2013translation}}
+%\subsection{Translation based approaches to probabilistic planning (2013)~\cite{taig2013translation}}
+% I don't think one is valuable
 
-\subsubsection{Reverse Iterative Deepening for Finite-Horizon MDPs with Large Branching Factors (2012)~\cite{kolobov2012glutton}}
+\subsection{Reverse Iterative Deepening for Finite-Horizon MDPs with Large Branching Factors (2012)~\cite{kolobov2012glutton}}
 The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
@@
 The  computation time remains much lower because it runs quickly into states that converged while solving M(h-1).
-The max-reward computation relies on knowing the maximum reward any action can yield in any state or an upper bound on it.
+The max-reward computation relies on knowing the maximum \textsubscriptreward any action can yield in any state or an upper bound on it.
 
-%TODO still have to describe the Glutton variation on LR2TDP
+\subsubsection{LRTDP}
+Using goal oriented MDPs, the \emph{Labelled Real-Time Dynamic Programmer} (LRTDP) operates a series of trials starting from s\textsubscript{0}. 
+\begin{itemize}
+	\item Trials start at s\textsubscript{0}
+	\item Choose best action greedily in the current state based on current \emph(V)
+	\item Perform  Bellman backup on the current state
+	\item Sample the outcome as the chosen action
+	\item Transition to the new state
+	\item Repeat untill a goal, dead end or converged state is reached
+	\item After trial, special convergence check on all states in the trial is performed to prove the convergence of these values
+\end{itemize}
 
-\subsubsection{Probabilistic planning vs Replanning}
+\subsubsection{LRTDP-FH}
+Adapting LRTDP to a finite horizon MDP \emph{M(H)} requires to let each trial start at (\emph{s\textsubscript{0}, H}) and run for at most H time steps.
+A steps H steps away from s\textsubscript{0} would translate to goals in a goal-oriented MDP.
+However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.
+
+\subsubsection{LR\textsuperscript{2}TDP}
+LR\textsuperscript{2}TDP uses \emph{reverse iterative deepening} and LRTDP-FH to solve a sequence of MDPs \emph{M(1), M(2), ...
+, M(H)}, in that order.
+It first decides how to act optimally in (s\textsubscript{0}, 1), equavalent to solving M(1) , then (s\textsubscript{0}, 2), equavalent to solving M(2), eventually solvin M(H) or running out of time halting a M(h') where h' < H.
+This incremental effort allows for reusing state values computed in previous states, so it memorizes all vaues and solves for smaller horizons by backchaining from the goal LRTDP-FH iterates over search depth while LR\textsuperscript{2}TDP iterates over the distance from the horizon and is likely to be better because:
+ \begin{itemize}
+	\item In many MDPs, the optimal policy M(h) for some h < H is near optimal for M(H), it thus may have a solution when stopped prematurely
+	\item it's trials are very short because backchaining from the goal leads to a lots of convergence
+	\item It optimally memorizes a large fraction of augmented states to save memory
+	\item a large fraction of state space may be unreachable from s\textsubscript{0} and it avoid storing information it does not need
+
+	\item it should however use a heuristic to treat states that has never been encountered when stopped prematurely, could be a fall back or a default action.  
+\end{itemize}
+
+\subsection{Probabilistic planning vs Replanning}
 Inspired by the FF-Replan entrance in the IPPC competition, this paper described a probabilistic interestingness quality of domains.

### 2014-03-29 FinalPaper/paper.tex
glutton added, stating on gourmand summary now

@@
 	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest exected reward over H steps time
-	\item The challenge or large branching factors
+	\item The challenge or large branching factors (induced by natural dynamic)
 \end{itemize}
@@
 
+%---------------------------------------------------------------------------------------------------------------------------
+
 \subsection{Reverse Iterative Deepening for Finite-Horizon MDPs with Large Branching Factors (2012)~\cite{kolobov2012glutton}}
@@
 \end{itemize}
+
+\subsubsection{GLUTTON}
+Glutton uses the \emph{Max-Reward} heuristic that relies on knowing the maximum reward \emph{R\textsubscript{max}} any action can yield in a state or an upper bound on it.
+Large branching factors induce that the computation of the Bellman Backups becomes prohibitively expensive.
+Glutton uses the following mechanisms to optimize for large branching factors:
+\begin{itemize}
+	\item Subsampling the transition function, is not enough to decrease the amount of computations yet
+	\item Seperating out Natural Dynamics: to reuse variable samples when generator succesors for multiple actions, by seperating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both.
+	\item Caching the transition function samples: as LR\textsuperscript{2}TDP populates the state-value hash table lazily, Glutton uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same (s, h) pair.
+When full, it chooses state-action pars for eviction ans replacement randomly.
+	\item Default policies: Glutton uses 3 tricks to determine a policy when stopped prematurely.
+It compares the optimal action from a h' with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.
+\end{itemize}
+
+%---------------------------------------------------------------------------------------------------------------------------
 

### 2014-03-29 FinalPaper/paper.tex
small compilation error

@@
 The  computation time remains much lower because it runs quickly into states that converged while solving M(h-1).
-The max-reward computation relies on knowing the maximum \textsubscriptreward any action can yield in any state or an upper bound on it.
+The max-reward computation relies on knowing the maximum R\textsubscript{max} any action can yield in any state or an upper bound on it.
 
@@
 \end{itemize}
+
+%---------------------------------------------------------------------------------------------------------------------------
+
+\subsection{LRTDP vs. UCT for Online Probabilistic Planning\cite{kolobov2012gourmand}}
 

### 2014-03-29 FinalPaper/paper.tex
Describe classical/probabilistic/replanning planners

--- 2014-03-29 FinalPaper/paper.tex
@@
 
+\subsubsection{Classical Planners}
+
+A planner tries to find a sequence of actions such that a goal or maximum
+reward is achieved. A classical planning problem consists out of states,
+actions, conditions and a goal state.
+
+\subsubsection{Probabilistic Planning} Classical Planners expect a
+deterministic world. For many Real World applications actions happen with a
+certain probability. This kind of Probabilistic Planning Problems can be
+described with Markov Decision Processes (MDPs). For the purpose of our
+analysis we define the problem as:
+
+\begin{itemize}
+	\item finite set of states $S$
+	\item an initial state $s_o \in S$
+	\item a $G \subseteq S$ of (absorbing) goal states
+	\item a set $O$ of outcomes; probability of $o \in O$ is $\Pr(o)$
+	\item a (total) deterministic transition function $T(o,s) \in S$ for all
+		outcomes $o \in O$ and states $s \in S$
+	\item sets $A(s)$ of applicable actions for each $s \in S$, together with
+		function $out(a) \subseteq O$ mapping each action to a set of outcomes
+		such that each outcome $o \in O$ belongs exactly to one action $act(o)$
+		and $\sum_{o \in out(a)} \Pr(o) = 1$ for all $a$
+\end{itemize}
+
+% depends if we should include this, what we tell about Gourmand / RDDL...
+
+Besides a single or multiple goals, some planning problems also include a
+reward function: For every $s \in S$, $s' \in S$, and $a \in A(s)$,
+$R(s,a,s')$ is the reward function. The goal if the problem is to maximize
+the reward until a goal is reached. If a Finite Horizon (number of steps of the
+plan) is used, the goal of the problem is to achieve the highest reward within
+the horizon.
+
+A probabilistic planner takes the probabilistic planning problem as input and
+builds and outputs a plan for the problem.
+
+In this paper we use Gourmand as a representative probabilistic planner, as
+it's the improved version of Glutton, the runner-up of the IPPC-11 competition.
+
+\subsubsection{Replanning}
+
+An Replanning Planner takes a probabilistic problem and tries to solve it with
+replanning. First the problem is determinized, a compilation from a
+probabilistic problem to a deterministic problem. This deterministic problem
+be solved by a classical planner which returns a plan. The Replanner then
+executes the plan. If it ends up in a state which is different from the plan,
+it executes the classical planner to get a new plan.
+
 \begin{itemize}
@@
 	\item Describe the determinization, or explain
-\end{itemize}
-
-\subsection{Planning problem}
-\begin{itemize}
-	\item Describe the MDP finite horizon planning problem
-	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
-	\item Describe reward heuristic
-	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest exected reward over H steps time
-	\item The challenge or large branching factors
 \end{itemize}
@@
 
-\subsection{Improving Determinization in Hindsight for Online Probabilistic Planning (2010)~\cite{yoon2010improving}}
+\subsubsection{Improving Determinization in Hindsight for Online Probabilistic Planning (2010)~\cite{yoon2010improving}}
+
 Hindsight optimization has enjoyed some success for online probabilistic
@@
 
-\subsection{Probabilistic Planning in the Graphplan Framework (1999)~\cite{Blum99probabilisticplanning}}
-% might not be necessary?
+\subsubsection{Probabilistic Planning in the Graphplan Framework (1999)~\cite{Blum99probabilisticplanning}}
+
 Graphplan is a successful planning algorithm for classical STRIPS domains. This
@@
 
-%\subsection{Compiling Conformant Probabilistic Planning Problems into Classical Planning (2013)~\cite{taig2013conformant}}
-% not necessary?
+\subsubsection{Compiling Conformant Probabilistic Planning Problems into Classical Planning (2013)~\cite{taig2013conformant}}
 
-\subsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}
+\subsubsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}
 
@@
 
-\subsection{Progressive heuristic search for probabilistic planning based on interaction estimates (2013)~\cite{martin2013progressive}}
+\subsubsection{Progressive heuristic search for probabilistic planning based on interaction estimates (2013)~\cite{martin2013progressive}}
 
@@
 
-%\subsection{Translation based approaches to probabilistic planning (2013)~\cite{taig2013translation}}
-% I don't think one is valuable
+\subsubsection{Translation based approaches to probabilistic planning (2013)~\cite{taig2013translation}}
 
-\subsection{Reverse Iterative Deepening for Finite-Horizon MDPs with Large Branching Factors (2012)~\cite{kolobov2012glutton}}
+\subsubsection{Reverse Iterative Deepening for Finite-Horizon MDPs with Large Branching Factors (2012)~\cite{kolobov2012glutton}}
 The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
@@
 The  computation time remains much lower because it runs quickly into states that converged while solving M(h-1).
-The max-reward computation relies on knowing the maximum \textsubscriptreward any action can yield in any state or an upper bound on it.
+The max-reward computation relies on knowing the maximum reward any action can yield in any state or an upper bound on it.
 
-\subsubsection{LRTDP}
-Using goal oriented MDPs, the \emph{Labelled Real-Time Dynamic Programmer} (LRTDP) operates a series of trials starting from s\textsubscript{0}. 
-\begin{itemize}
-	\item Trials start at s\textsubscript{0}
-	\item Choose best action greedily in the current state based on current \emph(V)
-	\item Perform  Bellman backup on the current state
-	\item Sample the outcome as the chosen action
-	\item Transition to the new state
-	\item Repeat untill a goal, dead end or converged state is reached
-	\item After trial, special convergence check on all states in the trial is performed to prove the convergence of these values
-\end{itemize}
+%TODO still have to describe the Glutton variation on LR2TDP
 
-\subsubsection{LRTDP-FH}
-Adapting LRTDP to a finite horizon MDP \emph{M(H)} requires to let each trial start at (\emph{s\textsubscript{0}, H}) and run for at most H time steps.
-A steps H steps away from s\textsubscript{0} would translate to goals in a goal-oriented MDP.
-However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.
-
-\subsubsection{LR\textsuperscript{2}TDP}
-LR\textsuperscript{2}TDP uses \emph{reverse iterative deepening} and LRTDP-FH to solve a sequence of MDPs \emph{M(1), M(2), ...
-, M(H)}, in that order.
-It first decides how to act optimally in (s\textsubscript{0}, 1), equavalent to solving M(1) , then (s\textsubscript{0}, 2), equavalent to solving M(2), eventually solvin M(H) or running out of time halting a M(h') where h' < H.
-This incremental effort allows for reusing state values computed in previous states, so it memorizes all vaues and solves for smaller horizons by backchaining from the goal LRTDP-FH iterates over search depth while LR\textsuperscript{2}TDP iterates over the distance from the horizon and is likely to be better because:
- \begin{itemize}
-	\item In many MDPs, the optimal policy M(h) for some h < H is near optimal for M(H), it thus may have a solution when stopped prematurely
-	\item it's trials are very short because backchaining from the goal leads to a lots of convergence
-	\item It optimally memorizes a large fraction of augmented states to save memory
-	\item a large fraction of state space may be unreachable from s\textsubscript{0} and it avoid storing information it does not need
-
-	\item it should however use a heuristic to treat states that has never been encountered when stopped prematurely, could be a fall back or a default action.  
-\end{itemize}
-
-\subsection{Probabilistic planning vs Replanning}
+\subsubsection{Probabilistic planning vs Replanning}
 Inspired by the FF-Replan entrance in the IPPC competition, this paper described a probabilistic interestingness quality of domains.

### 2014-03-29 FinalPaper/paper.tex
Small addition to the problem definition of replanners
gourmand added

--- 2014-03-29 FinalPaper/paper.tex
@@
 \begin{itemize}
-	\item Describe the MDP finite horizon planning problem
+	\item Describe the MDP finite horizon planning problem (usefull for modelling nearly inifinite processes)
 	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
@@
 \subsection{LRTDP vs. UCT for Online Probabilistic Planning\cite{kolobov2012gourmand}}
+During IPPC-2011 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT.
+This caused to wonder whether LRTDP planners could outperform UCT based systems.
+UCT forces an expert to guess a non-shortsighted lookahead value for which it should be able to converge on encountered states.
+Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity.
+At the IPPC-2011 GLUTTON was an offline LRTDP based planner that came second.
+As PROST employed UCT in an online manner, GOURMAND is an online adaptation of the GLUTTON algorithm to test whether LRTDP performs better if it is employed online.
+
+UCT picks an action based on it current quality estimate and an \emph{exploration term} which forces the planner to choose actions that have rarely been tried in the past.
+This makes UCT suitable for a wider scale of scenarios but also implies an unreliable termination condition.
+
+Because real world domains contain Natural Dynamics that introduce large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of state the planner may never reach in a lifetime.
+Such problems are far better solved using online planners by finding a $\tau$* or an approximation for the current state, executing it and repeating.
+This is done by choosing a certain lookahead  L and solving MDP \emph{M\textsubscript{s}(L)} to solve \emph{M\textsubscript{0}(H)} where L $<$ H and then select \emph{$\pi$*\textsubscript{L}(s, L)} recommended by the optimal policy.
+This lookahead value is determined using the per-process time constraint.
+
+\subsubsection{GOURMAND}
+In contrast to GLUTTON, GOURMAND always makes an informed choice in any state where it ends up when the time T allocated for solving the MDP runs out because of the online fashion it uses LRTDP.
+GOURMAND first divides the time among all remaining epochs, determines the largest lookahead L for which it can almost certainly solve any remaining epoch if T is assigned.
+It then checks if it can solve even for a larger lookahead L by taking away a small configuration time from future epochs  while still guaranteeing that it can solve for Lookahead L in each of them.
+This was GOURMAND adaptively picks a good lookahead value at each desicion epoch given the per-process constraint T.
+This can only be achieved by knowing how long it takes for LRTDP to solve a state for certain lookahead values.
+It uses LR\textsuperscript{2}TDP to collect this data.
+This version of LRTDP is more efficient because of the early convergences and it allows measuring how long on average the solving of a task takes.
+GOURMAND uses the same engineering optimizations to to handle evaluate actions, iterating over the successors of s under a by the Bellman Backups.
+GOURMAND eventually outperforms both GLUTTON and PROST, the winner of the IPPC-11\cite{keller2012prost}.
 

### 2014-03-30 FinalPaper/paper.tex

@@
 For this reason planners needed to be scalable and sensitive to the expected reward maximization.
-Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP M(H) for a smaller horizon h.
-Incrementally solving the sequence M(1), M(2) forms the basis of LR\textsuperscript{2}TDP.
+Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP $M(H)$ for a smaller horizon $h$.
+Incrementally solving the sequence $M(1)$, $M(2)$ forms the basis of LR\textsuperscript{2}TDP\@.
 By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full).
-The max-reward heuristic finds the largest horizon value h' for which already a heuristic value V is estimated.
-The  computation time remains much lower because it runs quickly into states that converged while solving M(h-1).
-The max-reward computation relies on knowing the maximum R\textsubscript{max} any action can yield in any state or an upper bound on it.
+The max-reward heuristic finds the largest horizon value $h'$ for which already a heuristic value $V$ is estimated.
+The  computation time remains much lower because it runs quickly into states that converged while solving $M(h-1)$.
+The max-reward computation relies on knowing the maximum $R_{max}$ any action can yield in any state or an upper bound on it.
 
 \subsubsection{LRTDP}
-Using goal oriented MDPs, the \emph{Labelled Real-Time Dynamic Programmer} (LRTDP) operates a series of trials starting from s\textsubscript{0}. 
+Using goal oriented MDPs, the \emph{Labelled Real-Time Dynamic Programmer} (LRTDP) operates a series of trials starting from $s_0$.
+
 \begin{itemize}
-	\item Trials start at s\textsubscript{0}
-	\item Choose best action greedily in the current state based on current \emph(V)
+	\item Trials start at $s_0$
+	\item Choose best action greedily in the current state based on current $V$
 	\item Perform  Bellman backup on the current state
@@
 	\item Transition to the new state
-	\item Repeat untill a goal, dead end or converged state is reached
+	\item Repeat until a goal, dead end or converged state is reached
 	\item After trial, special convergence check on all states in the trial is performed to prove the convergence of these values
@@
 \subsubsection{LRTDP-FH}
-Adapting LRTDP to a finite horizon MDP \emph{M(H)} requires to let each trial start at (\emph{s\textsubscript{0}, H}) and run for at most H time steps.
-A steps H steps away from s\textsubscript{0} would translate to goals in a goal-oriented MDP.
+
+Adapting LRTDP to a finite horizon MDP \emph{M(H)} requires to let each trial start at ($s_0$) and run for at most H time steps.
+A steps $H$ steps away from $s_0$ would translate to goals in a goal-oriented MDP.
 However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.
@@
 \subsubsection{LR\textsuperscript{2}TDP}
-LR\textsuperscript{2}TDP uses \emph{reverse iterative deepening} and LRTDP-FH to solve a sequence of MDPs \emph{M(1), M(2), ...
-, M(H)}, in that order.
-It first decides how to act optimally in (s\textsubscript{0}, 1), equavalent to solving M(1) , then (s\textsubscript{0}, 2), equavalent to solving M(2), eventually solvin M(H) or running out of time halting a M(h') where h' < H.
-This incremental effort allows for reusing state values computed in previous states, so it memorizes all vaues and solves for smaller horizons by backchaining from the goal LRTDP-FH iterates over search depth while LR\textsuperscript{2}TDP iterates over the distance from the horizon and is likely to be better because:
+
+LR\textsuperscript{2}TDP uses \emph{reverse iterative deepening} and LRTDP-FH to solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$, in that order.
+It first decides how to act optimally in ($s_0$, 1), equivalent to solving M(1) , then ($s_0$, 2), equivalent to solving $M(2)$, eventually solving $M(H)$ or running out of time halting a $M(h')$ where $h' < H$.
+This incremental effort allows for reusing state values computed in previous states, so it memorizes all values and solves for smaller horizons by backchaining from the goal LRTDP-FH iterates over search depth while LR\textsuperscript{2}TDP iterates over the distance from the horizon and is likely to be better because:
+
  \begin{itemize}
-	\item In many MDPs, the optimal policy M(h) for some h < H is near optimal for M(H), it thus may have a solution when stopped prematurely
+	\item In many MDPs, the optimal policy $M(h)$ for some $h < H$ is near optimal for M(H), it thus may have a solution when stopped prematurely
 	\item it's trials are very short because backchaining from the goal leads to a lots of convergence
 	\item It optimally memorizes a large fraction of augmented states to save memory
-	\item a large fraction of state space may be unreachable from s\textsubscript{0} and it avoid storing information it does not need
-
+	\item a large fraction of state space may be unreachable from $s_0$ and it avoid storing information it does not need
 	\item it should however use a heuristic to treat states that has never been encountered when stopped prematurely, could be a fall back or a default action.
@@
 \subsubsection{GLUTTON}
-Glutton uses the \emph{Max-Reward} heuristic that relies on knowing the maximum reward \emph{R\textsubscript{max}} any action can yield in a state or an upper bound on it.
+
+Glutton uses the \emph{Max-Reward} heuristic that relies on knowing the maximum reward $R_{max}$ any action can yield in a state or an upper bound on it.
 Large branching factors induce that the computation of the Bellman Backups becomes prohibitively expensive.
 Glutton uses the following mechanisms to optimize for large branching factors:
+
 \begin{itemize}
 	\item Subsampling the transition function, is not enough to decrease the amount of computations yet
-	\item Seperating out Natural Dynamics: to reuse variable samples when generator succesors for multiple actions, by seperating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both.
-	\item Caching the transition function samples: as LR\textsuperscript{2}TDP populates the state-value hash table lazily, Glutton uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same (s, h) pair.
+	\item Separating out Natural Dynamics: to reuse variable samples when generator successors for multiple actions, by separating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both.
+	\item Caching the transition function samples: as LR\textsuperscript{2}TDP populates the state-value hash table lazily, Glutton uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same $(s,h)$ pair.
 When full, it chooses state-action pars for eviction ans replacement randomly.
 	\item Default policies: Glutton uses 3 tricks to determine a policy when stopped prematurely.
-It compares the optimal action from a h' with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.
+It compares the optimal action from a $h'$ with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.
 \end{itemize}

### 2014-03-30 FinalPaper/paper.tex

@@
 \section{Problem formulation}
+
+\subsubsection{Classical Planners}
+
+A planner tries to find a sequence of actions such that a goal or maximum
+reward is achieved. A classical planning problem consists out of states,
+actions, conditions and a goal state.
+
+\subsubsection{Probabilistic Planning} Classical Planners expect a
+deterministic world. For many Real World applications actions happen with a
+certain probability. This kind of Probabilistic Planning Problems can be
+described with Markov Decision Processes (MDPs). For the purpose of our
+analysis we define the problem as:
+
+\begin{itemize}
+	\item finite set of states $S$
+	\item an initial state $s_o \in S$
+	\item a $G \subseteq S$ of (absorbing) goal states
+	\item a set $O$ of outcomes; probability of $o \in O$ is $\Pr(o)$
+	\item a (total) deterministic transition function $T(o,s) \in S$ for all
+		outcomes $o \in O$ and states $s \in S$
+	\item sets $A(s)$ of applicable actions for each $s \in S$, together with
+		function $out(a) \subseteq O$ mapping each action to a set of outcomes
+		such that each outcome $o \in O$ belongs exactly to one action $act(o)$
+		and $\sum_{o \in out(a)} \Pr(o) = 1$ for all $a$
+\end{itemize}
+
+% depends if we should include this, what we tell about Gourmand / RDDL...
+
+Besides a single or multiple goals, some planning problems also include a
+reward function: For every $s \in S$, $s' \in S$, and $a \in A(s)$,
+$R(s,a,s')$ is the reward function. The goal if the problem is to maximize
+the reward until a goal is reached. If a Finite Horizon (number of steps of the
+plan) is used, the goal of the problem is to achieve the highest reward within
+the horizon.
+
+A probabilistic planner takes the probabilistic planning problem as input and
+builds and outputs a plan for the problem.
+
+In this paper we use Gourmand as a representative probabilistic planner, as
+it's the improved version of Glutton, the runner-up of the IPPC-11 competition.
+
+\subsubsection{Replanning}
+
+An Replanning Planner takes a probabilistic problem and tries to solve it with
+replanning. First the problem is determinized, a compilation from a
+probabilistic problem to a deterministic problem. This deterministic problem
+be solved by a classical planner which returns a plan. The Replanner then
+executes the plan. If it ends up in a state which is different from the plan,
+it executes the classical planner to get a new plan. This is repeated until a
+goal is reached.
+
+In this paper we use FF-Replan as a representative replanning planner.
 

### 2014-03-30 FinalPaper/paper.tex
Begin of introduction

@@
 
+Since the first incorporation of the International Probabilistic Planning
+Competition (IPPC), it has undergone radical changes. Dominating planners
+of previous incorporations had a strong focus on goal-oriented MDPs,
+determinizing and using powerful classical planners (e.g. FF
+\cite{Hoffmann01theff}).New benchmarks have demonstrated weaknesses in existing
+solution techniques.
+
 The baseline test in \cite{little2007probvsreplan} evaluates the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
@@
 
-\section{Problem formulation}
+\section{Problem Formulation}
+
+\subsection{Markov Decision Process}
+
+\subsubsection{Goal-oriented MDPs}
+
+\subsubsection{MDP with Finite Horizon}
+
+\subsection{Planners}
 
@@
 
-\subsection{Probabilistic planning}
-
-\subsection{Replanning}
-\begin{itemize}
-	\item Describe the determinization, or explain
-\end{itemize}
-
 \subsection{Planning problem}
 \begin{itemize}
-	\item Describe the MDP finite horizon planning problem (usefull for modelling nearly inifinite processes)
+	\item Describe the MDP finite horizon planning problem (useful for modelling nearly infinite processes)
 	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
 	\item Describe reward heuristic
-	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest exected reward over H steps time
+	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest expected reward over H steps time
 	\item The challenge or large branching factors (induced by natural dynamic)
@@
 
-%---------------------------------------------------------------------
+\subsection{Probabilistic Interestingness}
 
-\section{Domain description}
 Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
@@
 
-\subsection{Interesting domains}
 The competitor FF-Replan\cite{FFReplan} remembered the committee of the IPPC in 2004 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
@@
 Following existing domains were said to be probabilistically interesting:
+
 \begin{itemize}
@@
 
-\subsection{Real world evaluation}
-
-Explain shortcomings
-
-\subsection{Probabilistically interesting domains}
 A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties:
@@
 
+%---------------------------------------------------------------------
+
+\section{Domain Descriptions}
+
+\subsection{IPPC-2011 Domains}
+
+\subsection{Real-World Domains}
+
+\subsection{Baseline test for Probabilistic Interesting domains}
+
 \subsection{Evaluating the domains}
@@
 
-\section{Theoretical approach}
+\section{Planners}
 
-\begin{itemize}
-	\item Describe how we are using the created domain
-	\item show pseudo code for the 2 papers
-	\item Introduce the improvements (or combination) of the approaches of the papers fitted for the domain
-\end{itemize}
+\subsection{FF-Replan}
+
+\subsection{Gourmand}
 
@@
 
-\section{Empirical evaluation}
+\section{Future Experiment}
+
+\subsection{Setup}
+
+\subsection{FF-Replan}
+
+\subsubsection{FF-Replan with Finite Horizon}
+
+\subsection{Hypothesis}
 
@@
 \section{Related Work}
+
+\subsection{RFF}
+
+\subsection{PROST}
+
+\subsection{FF-H+}
+
 % Use related work to display the differences with own work
@@
 
-%---------------------------------------------------------------------------------------------------------------------------
-
 \subsection{Reverse Iterative Deepening for Finite-Horizon MDPs with Large Branching Factors (2012)~\cite{kolobov2012glutton}}
@@
 
-%---------------------------------------------------------------------------------------------------------------------------
-
 \subsection{LRTDP vs. UCT for Online Probabilistic Planning\cite{kolobov2012gourmand}}
@@
 
-%---------------------------------------------------------------------------------------------------------------------------
-
 \subsection{Probabilistic planning vs Replanning}
@@
 \begin{itemize}
-	\item 'dead' end states
+	\item `dead' end states
 	\item the degree to which the probability of reaching a dead end state can be reduced through choice of actions
@@
 Problems that fail to be \emph{probabilistically interesting} are actually classical planning problems in disguise and for those replanners are more appropriate.
-A replanner can also perform optimally for probabilistically interesting planning problems whenever the 'most promising' goal trajectory is the correct thing to do.
-They create several domains to explore the issue of replanning vs.
+A replanner can also perform optimally for probabilistically interesting planning problems whenever the `most promising' goal trajectory is the correct thing to do.
+They create several domains to explore the issue of replanning vs\@.
 probabilistic planning.

### 2014-03-30 FinalPaper/paper.tex

@@
 \section{Introduction}
-
-Since the first incorporation of the International Probabilistic Planning
-Competition (IPPC), it has undergone radical changes. Dominating planners
-of previous incorporations had a strong focus on goal-oriented MDPs,
-determinizing and using powerful classical planners (e.g. FF
-\cite{Hoffmann01theff}).New benchmarks have demonstrated weaknesses in existing
-solution techniques.
 

### 2014-03-30 FinalPaper/paper.tex
chips ik was dit vergeten te committen vooraf, kan jij het mergen somehow?

--- 2014-03-30 FinalPaper/paper.tex
@@
 Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
-Problems that fail this test were deemed to be classical planning problems in disguise, favouring using replanners\cite{little2007probvsreplan}.
+Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners\cite{little2007probvsreplan}.
 This section describes interesting domains in which either FF-Replan or Gourmand prevailed during the International Probabilistic Planning Compeitions.
-We will then translate the most interesting domains to a complete "real-world" domain and evaluate them using the probabilistically interesting baseline test.
-This paper concludes on evaluation both planners using the translated domains.
+These domains are evaluated for how well they portray real-world scenarios.
+The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario.
+Little et all's baseline test helps us to predict which planner would perform well on these domains.
+We will then conclude our evaluation by comparing these results to the result of our experiments described in Section \ref{sec:experiment}.
 
 \subsection{Interesting domains}
-The competitor FF-Replan\cite{FFReplan} remembered the committee of the IPPC in 2004 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
+The competitor FF-Replan\cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
 The baseline test evaluates the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
@@
 \section{Empirical evaluation}
+\label{sec:experiment}
 

### 2014-03-30 FinalPaper/paper.tex
first part of domains

--- 2014-03-30 FinalPaper/paper.tex
@@
 
+\section{Planners}
+
+\subsection{FF-Replan}
+
+\subsection{Gourmand}
+The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
+For this reason planners needed to be scalable and sensitive to the expected reward maximization.
+Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP $M(H)$ for a smaller horizon $h$.
+Incrementally solving the sequence $M(1)$, $M(2)$ forms the basis of LR\textsuperscript{2}TDP\@.
+By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full).
+The max-reward heuristic finds the largest horizon value $h'$ for which already a heuristic value $V$ is estimated.
+The  computation time remains much lower because it runs quickly into states that converged while solving $M(h-1)$.
+The max-reward computation relies on knowing the maximum $R_{max}$ any action can yield in any state or an upper bound on it.
+
+\subsubsection{LRTDP}
+Using goal oriented MDPs, the \emph{Labelled Real-Time Dynamic Programmer} (LRTDP) operates a series of trials starting from $s_0$.
+
+\begin{itemize}
+	\item Trials start at $s_0$
+	\item Choose best action greedily in the current state based on current $V$
+	\item Perform  Bellman backup on the current state
+	\item Sample the outcome as the chosen action
+	\item Transition to the new state
+	\item Repeat until a goal, dead end or converged state is reached
+	\item After trial, special convergence check on all states in the trial is performed to prove the convergence of these values
+\end{itemize}
+
+\subsubsection{LRTDP-FH}
+
+Adapting LRTDP to a finite horizon MDP \emph{M(H)} requires to let each trial start at ($s_0$) and run for at most H time steps.
+A steps $H$ steps away from $s_0$ would translate to goals in a goal-oriented MDP.
+However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.
+
+\subsubsection{LR\textsuperscript{2}TDP}
+
+LR\textsuperscript{2}TDP uses \emph{reverse iterative deepening} and LRTDP-FH to solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$, in that order.
+It first decides how to act optimally in ($s_0$, 1), equivalent to solving M(1) , then ($s_0$, 2), equivalent to solving $M(2)$, eventually solving $M(H)$ or running out of time halting a $M(h')$ where $h' < H$.
+This incremental effort allows for reusing state values computed in previous states, so it memorizes all values and solves for smaller horizons by backchaining from the goal LRTDP-FH iterates over search depth while LR\textsuperscript{2}TDP iterates over the distance from the horizon and is likely to be better because:
+
+\begin{itemize}
+	\item In many MDPs, the optimal policy $M(h)$ for some $h < H$ is near optimal for M(H), it thus may have a solution when stopped prematurely
+	\item it's trials are very short because backchaining from the goal leads to a lots of convergence
+	\item It optimally memorizes a large fraction of augmented states to save memory
+	\item a large fraction of state space may be unreachable from $s_0$ and it avoid storing information it does not need
+	\item it should however use a heuristic to treat states that has never been encountered when stopped prematurely, could be a fall back or a default action.
+\end{itemize}
+
+\subsubsection{GLUTTON}
+
+Glutton uses the \emph{Max-Reward} heuristic that relies on knowing the maximum reward $R_{max}$ any action can yield in a state or an upper bound on it.
+Large branching factors induce that the computation of the Bellman Backups becomes prohibitively expensive.
+Glutton uses the following mechanisms to optimize for large branching factors:
+
+\begin{itemize}
+	\item Subsampling the transition function, is not enough to decrease the amount of computations yet
+	\item Separating out Natural Dynamics: to reuse variable samples when generator successors for multiple actions, by separating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both.
+	\item Caching the transition function samples: as LR\textsuperscript{2}TDP populates the state-value hash table lazily, Glutton uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same $(s,h)$ pair.
+When full, it chooses state-action pars for eviction ans replacement randomly.
+	\item Default policies: Glutton uses 3 tricks to determine a policy when stopped prematurely.
+It compares the optimal action from a $h'$ with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.
+\end{itemize}
+
+During IPPC-2011 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT.
+This caused to wonder whether LRTDP planners could outperform UCT based systems.
+UCT forces an expert to guess a non-shortsighted lookahead value for which it should be able to converge on encountered states.
+Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity.
+At the IPPC-2011 GLUTTON was an offline LRTDP based planner that came second.
+As PROST employed UCT in an online manner, GOURMAND is an online adaptation of the GLUTTON algorithm to test whether LRTDP performs better if it is employed online.
+
+UCT picks an action based on it current quality estimate and an \emph{exploration term} which forces the planner to choose actions that have rarely been tried in the past.
+This makes UCT suitable for a wider scale of scenarios but also implies an unreliable termination condition.
+
+Because real world domains contain Natural Dynamics that introduce large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of state the planner may never reach in a lifetime.
+Such problems are far better solved using online planners by finding a $\tau$* or an approximation for the current state, executing it and repeating.
+This is done by choosing a certain lookahead  L and solving MDP \emph{M\textsubscript{s}(L)} to solve \emph{M\textsubscript{0}(H)} where L $<$ H and then select \emph{$\pi$*\textsubscript{L}(s, L)} recommended by the optimal policy.
+This lookahead value is determined using the per-process time constraint.
+
+\subsubsection{GOURMAND}
+In contrast to GLUTTON, GOURMAND always makes an informed choice in any state where it ends up when the time T allocated for solving the MDP runs out because of the online fashion it uses LRTDP.
+GOURMAND first divides the time among all remaining epochs, determines the largest lookahead L for which it can almost certainly solve any remaining epoch if T is assigned.
+It then checks if it can solve even for a larger lookahead L by taking away a small configuration time from future epochs  while still guaranteeing that it can solve for Lookahead L in each of them.
+This was GOURMAND adaptively picks a good lookahead value at each desicion epoch given the per-process constraint T.
+This can only be achieved by knowing how long it takes for LRTDP to solve a state for certain lookahead values.
+It uses LR\textsuperscript{2}TDP to collect this data.
+This version of LRTDP is more efficient because of the early convergences and it allows measuring how long on average the solving of a task takes.
+GOURMAND uses the same engineering optimizations to to handle evaluate actions, iterating over the successors of s under a by the Bellman Backups.
+GOURMAND eventually outperforms both GLUTTON and PROST, the winner of the IPPC-11\cite{keller2012prost}.
+
+%---------------------------------------------------------------------
+
 \section{Domain Descriptions}
+Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
+Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}.
+This section describes interesting domains in which either FF-Replan or Gourmand prevailed during the International Probabilistic Planning Compeitions.
+These domains are evaluated for how well they portray real-world scenarios.
+The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario.
+Little et all's baseline test helps us to predict which planner would perform well on these domains.
+We will then conclude our evaluation by comparing these results to the result of our experiments described in Section \ref{sec:experiment}.
 
 \subsection{IPPC-2011 Domains}
+The competitor FF-Replan \cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
+The baseline test of Little et.
+all evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
+IPPC-2011 responded by introducing more realistic MDPs and evluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
+
+GOURMAND vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}.
+Prost however midly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
+
+\subsubsection{Navigation domain}
+
+\subsubsection{Traffic domain}
 
@@
 FF-Replan participated in IPPC-04 (and IPPC-06) solving problems that had been specified in the Probabilstic Planning Domain Description Language (PPDDL) whereas Gourmand has been tested on the set of IPPC-11 problems specified in Relational Dynamic Influence Diagram Language (RDDL)\cite{sanner2008rddl}.
-
-%---------------------------------------------------------------------
-
-\section{Planners}
-
-\subsection{FF-Replan}
-
-\subsection{Gourmand}
 
@@
 
-\subsection{Reverse Iterative Deepening for Finite-Horizon MDPs with Large Branching Factors (2012)~\cite{kolobov2012glutton}}
-The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
-For this reason planners needed to be scalable and sensitive to the expected reward maximization.
-Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP $M(H)$ for a smaller horizon $h$.
-Incrementally solving the sequence $M(1)$, $M(2)$ forms the basis of LR\textsuperscript{2}TDP\@.
-By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full).
-The max-reward heuristic finds the largest horizon value $h'$ for which already a heuristic value $V$ is estimated.
-The  computation time remains much lower because it runs quickly into states that converged while solving $M(h-1)$.
-The max-reward computation relies on knowing the maximum $R_{max}$ any action can yield in any state or an upper bound on it.
-
-\subsubsection{LRTDP}
-Using goal oriented MDPs, the \emph{Labelled Real-Time Dynamic Programmer} (LRTDP) operates a series of trials starting from $s_0$.
-
-\begin{itemize}
-	\item Trials start at $s_0$
-	\item Choose best action greedily in the current state based on current $V$
-	\item Perform  Bellman backup on the current state
-	\item Sample the outcome as the chosen action
-	\item Transition to the new state
-	\item Repeat until a goal, dead end or converged state is reached
-	\item After trial, special convergence check on all states in the trial is performed to prove the convergence of these values
-\end{itemize}
-
-\subsubsection{LRTDP-FH}
-
-Adapting LRTDP to a finite horizon MDP \emph{M(H)} requires to let each trial start at ($s_0$) and run for at most H time steps.
-A steps $H$ steps away from $s_0$ would translate to goals in a goal-oriented MDP.
-However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.
-
-\subsubsection{LR\textsuperscript{2}TDP}
-
-LR\textsuperscript{2}TDP uses \emph{reverse iterative deepening} and LRTDP-FH to solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$, in that order.
-It first decides how to act optimally in ($s_0$, 1), equivalent to solving M(1) , then ($s_0$, 2), equivalent to solving $M(2)$, eventually solving $M(H)$ or running out of time halting a $M(h')$ where $h' < H$.
-This incremental effort allows for reusing state values computed in previous states, so it memorizes all values and solves for smaller horizons by backchaining from the goal LRTDP-FH iterates over search depth while LR\textsuperscript{2}TDP iterates over the distance from the horizon and is likely to be better because:
-
-\begin{itemize}
-	\item In many MDPs, the optimal policy $M(h)$ for some $h < H$ is near optimal for M(H), it thus may have a solution when stopped prematurely
-	\item it's trials are very short because backchaining from the goal leads to a lots of convergence
-	\item It optimally memorizes a large fraction of augmented states to save memory
-	\item a large fraction of state space may be unreachable from $s_0$ and it avoid storing information it does not need
-	\item it should however use a heuristic to treat states that has never been encountered when stopped prematurely, could be a fall back or a default action.
-\end{itemize}
-
-\subsubsection{GLUTTON}
-
-Glutton uses the \emph{Max-Reward} heuristic that relies on knowing the maximum reward $R_{max}$ any action can yield in a state or an upper bound on it.
-Large branching factors induce that the computation of the Bellman Backups becomes prohibitively expensive.
-Glutton uses the following mechanisms to optimize for large branching factors:
-
-\begin{itemize}
-	\item Subsampling the transition function, is not enough to decrease the amount of computations yet
-	\item Separating out Natural Dynamics: to reuse variable samples when generator successors for multiple actions, by separating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both.
-	\item Caching the transition function samples: as LR\textsuperscript{2}TDP populates the state-value hash table lazily, Glutton uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same $(s,h)$ pair.
-When full, it chooses state-action pars for eviction ans replacement randomly.
-	\item Default policies: Glutton uses 3 tricks to determine a policy when stopped prematurely.
-It compares the optimal action from a $h'$ with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.
-\end{itemize}
-
-\subsection{LRTDP vs. UCT for Online Probabilistic Planning\cite{kolobov2012gourmand}}
-During IPPC-2011 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT.
-This caused to wonder whether LRTDP planners could outperform UCT based systems.
-UCT forces an expert to guess a non-shortsighted lookahead value for which it should be able to converge on encountered states.
-Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity.
-At the IPPC-2011 GLUTTON was an offline LRTDP based planner that came second.
-As PROST employed UCT in an online manner, GOURMAND is an online adaptation of the GLUTTON algorithm to test whether LRTDP performs better if it is employed online.
-
-UCT picks an action based on it current quality estimate and an \emph{exploration term} which forces the planner to choose actions that have rarely been tried in the past.
-This makes UCT suitable for a wider scale of scenarios but also implies an unreliable termination condition.
-
-Because real world domains contain Natural Dynamics that introduce large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of state the planner may never reach in a lifetime.
-Such problems are far better solved using online planners by finding a $\tau$* or an approximation for the current state, executing it and repeating.
-This is done by choosing a certain lookahead  L and solving MDP \emph{M\textsubscript{s}(L)} to solve \emph{M\textsubscript{0}(H)} where L $<$ H and then select \emph{$\pi$*\textsubscript{L}(s, L)} recommended by the optimal policy.
-This lookahead value is determined using the per-process time constraint.
-
-\subsubsection{GOURMAND}
-In contrast to GLUTTON, GOURMAND always makes an informed choice in any state where it ends up when the time T allocated for solving the MDP runs out because of the online fashion it uses LRTDP.
-GOURMAND first divides the time among all remaining epochs, determines the largest lookahead L for which it can almost certainly solve any remaining epoch if T is assigned.
-It then checks if it can solve even for a larger lookahead L by taking away a small configuration time from future epochs  while still guaranteeing that it can solve for Lookahead L in each of them.
-This was GOURMAND adaptively picks a good lookahead value at each desicion epoch given the per-process constraint T.
-This can only be achieved by knowing how long it takes for LRTDP to solve a state for certain lookahead values.
-It uses LR\textsuperscript{2}TDP to collect this data.
-This version of LRTDP is more efficient because of the early convergences and it allows measuring how long on average the solving of a task takes.
-GOURMAND uses the same engineering optimizations to to handle evaluate actions, iterating over the successors of s under a by the Bellman Backups.
-GOURMAND eventually outperforms both GLUTTON and PROST, the winner of the IPPC-11\cite{keller2012prost}.
-
 \subsection{Probabilistic planning vs Replanning}

### 2014-03-30 FinalPaper/paper.tex
Improve introduction

--- 2014-03-30 FinalPaper/paper.tex
@@
 
-The baseline test in \cite{little2007probvsreplan} evaluates the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
-We would like to carefully analyze the credibility of these domains in the real world and evaluate the worth of FF-Replan vs a state of the art probabilistic planner: Gourmand \cite{kolobov2012gourmand}.
+Since the first incorporation of the International Probabilistic Planning
+Competition (IPPC), it has undergone radical changes. Dominating planners
+of previous incorporations had a strong focus on goal-oriented MDPs,
+determinizing and using powerful classical planners (e.g. FF
+\cite{Hoffmann01theff}) and replanning. New benchmarks have demonstrated
+weaknesses in existing solution techniques.
+
+Little and Thi\'ebaux have developed a baseline test in
+\cite{little2007probvsreplan} to evaluate the IPC-5 problems. This
+test determines if a planning problem is `probabilistically interesting'.
+Problems that fail this test are classical planning problems in disguise.
+Knowing this it is easy to design a problem where a replanner performs badly
+or incredibly well.
+
+The IPPC-11 introduced Relation Dynamic Influence Diagram Language (RDDL),
+which can design domains that are more probabilistically interesting. The top
+performers were PROST \cite{keller2012prost} and Glutton
+\cite{kolobov2012glutton}.
+
+While it is interesting to make problems harder and invent better planning
+algorithms to solve those probabilistic complex problems, one must not forget
+if the problem makes sense in the real world.
+
+The main contribution of this paper is an evaluation of the domains used in
+IPPC-11 and see if they can be adjusted so they fail the baseline test for
+probabilistic interestingness, which might make them more suitable for
+replanning planners.
 

### 2014-03-30 FinalPaper/paper.tex
First part of future experiments

--- 2014-03-30 FinalPaper/paper.tex
@@
 
-The baseline test in \cite{little2007probvsreplan} evaluates the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
-We would like to carefully analyze the credibility of these domains in the real world and evaluate the worth of FF-Replan vs a state of the art probabilistic planner: Gourmand \cite{kolobov2012gourmand}.
+Since the first the International Probabilistic Planning Competition (IPPC),
+problems have undergone radical changes. Dominating planners of previous
+incorporations had a strong focus on goal-oriented MDPs, determinizing and
+using powerful classical planners (e.g. FF \cite{Hoffmann01theff}) and
+replanning. New benchmark problems have demonstrated weaknesses in existing
+solution techniques.
+
+Little and Thi\'ebaux have developed a baseline test in
+\cite{little2007probvsreplan} to evaluate the problems of the fifth International
+Planning Competition (IPC-5). This test determines if a planning problem is
+`probabilistically interesting'. Problems that fail this test are classical
+planning problems in disguise. Knowing this it is easy to design a problem
+where a replanner performs badly or incredibly well.
+
+The IPPC-11 introduced Relation Dynamic Influence Diagram Language (RDDL),
+which can design domains that are more probabilistically interesting. The top
+performers were PROST \cite{keller2012prost} and Glutton
+\cite{kolobov2012glutton}.
+
+While it is interesting to make problems harder and invent better planning
+algorithms to solve those probabilistic complex problems, we evaluate whether
+or not these problems are coherent with real-world situations.
+
+The main contribution of this paper is an evaluation of FF-Replan versus a
+probabilistically state of the art planner GOURMAND in the realistically
+augmented domains of IPPC-11. If these domains fail the baseline test proposed
+by Little et\@. all, they would translate to classical planning problems in
+disguise and could be easily solved by FF-Replan.
 
@@
 
-\section{Problem Formulation}
+\section{Problem formulation}
+To evaluate FF-Replan and GOURMAND in a real world domain a finite horizon MDP is used to represent the realistic \emph{natural dynamics} such as external forces or forces of nature.
+These dynamics introduce large branching factors emphasizing the need for a planner to be scalable.
+To evaluate the model, the planner should also be sensitive to an expected reward maximization criterion.
+Current finite horizon MDP problems as introduced in IPPC-11 are simplified and therefor do not account for the rich set of state-actions as would be available in a real-world planning problem.
+We will reason about the most interesting domains for our evaluation and adjust them to match their real-world equivalent.
+Using the baseline test introduced by Little et.
+all \cite{little2007probvsreplan}, we can evaluate the probabilistically interestingness of these domains and evaluate the performance of FF-Replan vs.
+a state of the art probabilistic planner: GOURMAND.
 
-\subsection{Markov Decision Process}
+%---------------------------------------------------------------------
 
-\subsubsection{Goal-oriented MDPs}
+\section{Background}
 
-\subsubsection{MDP with Finite Horizon}
+\subsection{Planning problems}
+\subsubsection{Classical Planning problems.
+} Planning is the process of computing several steps of a problem-solving procedure before executing any of them.
+In classical planning problems the environment is assumed to \emph{deterministic, observable and state}.
+Classical planning problems consists out of states, actions, conditions and a goal state and are solved using search and can be aided using heuristics.
+The planner tries to find a sequence of actions such that a goal or maximum reward is achieved.
 
-\subsection{Planners}
+\subsubsection{Probabilistic Planning problems}
+Real-World applications are far from deterministic, induced by natural dynamics and chance.
+To accommodate for Real-World domains probabilistic planning problems were introduced.
+These systems can be described using \emph{Markov Decision Processes} (MDPs) and can account for observable uncertainty.
+Probabilistic planning problems can be solved by evaluating iterations and creating policies to reach a goal state, either online or offline.
 
-\subsubsection{Classical Planners}
+\subsection{Problem domains}
+\subsubsection{Goal-oriented MDPs.
+}The problems in IPPC-04 were specified using the Planning Domain Description Language (PPDLL).
+PPDDL specifies a probabistic planning problem as a set of probabilistic action sets and an initial and goal state description in which every action has a certain probability assigned to it \cite{FFReplan}.
+These MDPs are of the form $\mathit{M = (S, A, app, Pr, R)}$ where $\mathit{S}$ and $\mathit{A}$ are a finite set of states and actions, $\mathit{app(s)}$ is the set of all actions applicable in $\mathit{s}$.
+$\mathit{Pr}$ represents the probability of a state transaction $\mathit{(s, a, s')}$ for $\mathit{a}$ and $\mathit{R(s, a, s')}$ is the reward of applying $\mathit{a}$ to $\mathit{s}$ and generating $\mathit{s'}$ The planning problem is defined as a triple $\mathit{P = (M, s\textsubscript{0}, G, \rho)}$ where $\mathit{M = (S, A, app, Pr, R)}$ is an MDP, $\mathit{s\textsubscript{0} \in S}$ is the initial state, $\mathit{G \subseteq S}$ is the set of goal states and $\mathit{0 < \rho < 1}$ is a probability threshold \cite{teichteil2010incremental}.
 
-A planner tries to find a sequence of actions such that a goal or maximum
-reward is achieved. A classical planning problem consists out of states,
-actions, conditions and a goal state.
+ The planners from IPPC-04 were evaluated on how many trials reached the goal per problem and the average number of actions selected when successful.
+These planning problems were however relatively easy to solve as they did not account for \emph{natural dynamics} and/or large branching factors that occur in more realistic systems \cite{kolobov2012glutton}.
+FF-Replan \cite{FFReplan}, as specified in Section \ref{sec:planners} kindly remembered the committee of the IPPC-04 that the specified planning problems that contained no dead-ends were fairly easy to solve using relatively simple tools to handle with uncertainty.
 
-\subsubsection{Probabilistic Planning} Classical Planners expect a
-deterministic world. For many Real World applications actions happen with a
-certain probability. This kind of Probabilistic Planning Problems can be
-described with Markov Decision Processes (MDPs). For the purpose of our
-analysis we define the problem as:
+\subsubsection{MDPs with Finite Horizon.
+}IPPC-11 decided to respond by introducing more realistic MDPs and their evaluation criteria by using MDPs with finite horizons.
+The planning problems are defined as tuples of the form \\ $\mathit{M\textsubscript{s0}(H) = \langle \langle S, A, T, R, s\textsubscript{0} \rangle , H \rangle }$ where $\mathit{S}$ s a finite set of states, $\mathit{A}$ a finite set of actions, $\mathit{T}$ is the transition function, similar to $\mathit{Pr}$ in the goal oriented MDP.
+$\mathit{R}$ represents the transitioning reward, $\mathit{s\textsubscript{0}}$ and $\mathit{H}$ is the number of decision epochs after which the process stops.
+Solving $\mathit{M(H)}$ means finding a policy for executing recommended state from the initial state over $\mathit{H}$ decision epochs \cite{kolobov2012gourmand}.
 
-\begin{itemize}
-	\item finite set of states $S$
-	\item an initial state $s_o \in S$
-	\item a $G \subseteq S$ of (absorbing) goal states
-	\item a set $O$ of outcomes; probability of $o \in O$ is $\Pr(o)$
-	\item a (total) deterministic transition function $T(o,s) \in S$ for all
-		outcomes $o \in O$ and states $s \in S$
-	\item sets $A(s)$ of applicable actions for each $s \in S$, together with
-		function $out(a) \subseteq O$ mapping each action to a set of outcomes
-		such that each outcome $o \in O$ belongs exactly to one action $act(o)$
-		and $\sum_{o \in out(a)} \Pr(o) = 1$ for all $a$
-\end{itemize}
+Translating finite horizon MDPs to goal-oriented domains results ends up in all state $H$ steps away from $s\textsubscript{0}$ are goal states.
+The evaluation criteria in finite horizon MDPs is the \emph{expected reward} and not the probability of the policy reaching the goal states.
 
-% depends if we should include this, what we tell about Gourmand / RDDL...
+\subsection{Planning algorithms}
+\subsubsection{Replanning}
+A replanner is a planner that takes a problem as input, plans a state-action policy, executes it online and whenever it encounters a state that was not in its state-action policy, it takes the current state as starting state and plans again until it has reached a goal or dead-end state.
+For our paper have chosen to evaluate FF-Replan \cite{FFReplan}, the winner of IPPC-04 and unenrolled winner of IPPC-06 as an inspiring, fairly simple planner that in our opinion is capable of employment in real-world domains.
 
-Besides a single or multiple goals, some planning problems also include a
-reward function: For every $s \in S$, $s' \in S$, and $a \in A(s)$,
-$R(s,a,s')$ is the reward function. The goal if the problem is to maximize
-the reward until a goal is reached. If a Finite Horizon (number of steps of the
-plan) is used, the goal of the problem is to achieve the highest reward within
-the horizon.
-
-A probabilistic planner takes the probabilistic planning problem as input and
-builds and outputs a plan for the problem.
-
-In this paper we use Gourmand as a representative probabilistic planner, as
-it's the improved version of Glutton, the runner-up of the IPPC-11 competition.
-
-\subsubsection{Replanning}
-
-An Replanning Planner takes a probabilistic problem and tries to solve it with
-replanning. First the problem is determinized, a compilation from a
-probabilistic problem to a deterministic problem. This deterministic problem
-be solved by a classical planner which returns a plan. The Replanner then
-executes the plan. If it ends up in a state which is different from the plan,
-it executes the classical planner to get a new plan. This is repeated until a
-goal is reached.
-
-In this paper we use FF-Replan as a representative replanning planner.
-
-\begin{itemize}
-	\item Summarize shortcomings of the previous solutions
-	\item Describe the planning problem
-	\item Argument the choice for 2 current papers to analyze
-	\item Define how we would like to test the planning algorithms in a domain by our choice
-\end{itemize}
-
-\subsection{Planning problem}
-\begin{itemize}
-	\item Describe the MDP finite horizon planning problem (useful for modelling nearly infinite processes)
-	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
-	\item Describe reward heuristic
-	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest expected reward over H steps time
-	\item The challenge or large branching factors (induced by natural dynamic)
-\end{itemize}
+\subsubsection{Probabilistic planning}
+Probabilistic planners are used to solve probabilistic planning problems and should be able to account for uncertainty as opposed to classical planners.
+For our evaluation we have chosen to compare FF-Replan to a state-of-the-art probabilistic planner: GOURMAND.
+GOURMAND is the online successor of the GLUTTON plan, a Labelled Real-Time Dynamic Programming (LRTDP) based planner and the runner up of IPPC-11.
 
 \subsection{Probabilistic Interestingness}
-
-Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
-Problems that fail this test were deemed to be classical planning problems in disguise, favouring using replanners\cite{little2007probvsreplan}.
-This section describes interesting domains in which either FF-Replan or Gourmand prevailed during the International Probabilistic Planning Compeitions.
-We will then translate the most interesting domains to a complete "real-world" domain and evaluate them using the probabilistically interesting baseline test.
-This paper concludes on evaluation both planners using the translated domains.
-
-The competitor FF-Replan\cite{FFReplan} remembered the committee of the IPPC in 2004 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
-The baseline test evaluates the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
-
-Following existing domains were said to be probabilistically interesting:
-
-\begin{itemize}
-	\item Drive
-	\item Exploding blocksworld
-	\item Pitchcatch
-	\item Schedule
-	\item Tireworld
-\end{itemize}
-
-A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties:
-
+After IPPC-06, a baseline test for \emph{probabilistically interesting} planning domains was proposed by Little and Thi\'ebauw \cite{little2007probvsreplan}.
+Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners.
+A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties \cite{little2007probvsreplan}:
 % reference little & thiebauw again. Maybe also shortly define what all o, n, act etc. are.
@@
 
+%Following existing domains were said to be probabilistically interesting:
+%
+%\begin{itemize}
+%	\item Drive
+%	\item Exploding blocksworld
+%	\item Pitchcatch
+%	\item Schedule
+%	\item Tireworld
+%\end{itemize}
+
 %---------------------------------------------------------------------
@@
 \section{Planners}
+\label{sec:planners}
 
@@
 
-\subsection{Gourmand}
+\subsection{GOURMAND}
+
 The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
@@
 \end{itemize}
-
+%---------------------------------------------------------------------
 During IPPC-2011 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT.
@@
 \section{Domain Descriptions}
+
 Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
 Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}.
-This section describes interesting domains in which either FF-Replan or Gourmand prevailed during the International Probabilistic Planning Compeitions.
+This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Competitions.
 These domains are evaluated for how well they portray real-world scenarios.
 The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario.
-Little et all's baseline test helps us to predict which planner would perform well on these domains.
+Little et.
+all's baseline test helps us to predict which planner would perform well on these domains.
 We will then conclude our evaluation by comparing these results to the result of our experiments described in Section \ref{sec:experiment}.
@@
 \subsection{IPPC-2011 Domains}
+
 The competitor FF-Replan \cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
@@
 all evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
-IPPC-2011 responded by introducing more realistic MDPs and evluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
+IPPC-2011 responded by introducing more realistic MDPs and evaluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
 
 GOURMAND vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}.
-Prost however midly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
+PROST however mildly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
 
@@
 
+The navigation domain represents a grid in which a robot must reach a goal.
+Every cell offers the robot a different chance of disappearing.
+The robot needs to choose a path which gets it to the goal most reliably within the finite horizon time \cite{sanner2011navigation}.
+Because GOURMAND uses a dynamic lookahead, it performs quite well in this domain.
+
+%ADD IMAGE HERE
+
 \subsubsection{Traffic domain}
+This domain represents a simple binary version of the cell transition model (CTM) for modelling traffic based on the original CTM Tech Report \cite{sanner2011traffic}.
+Because of the binary variables and no intermediate variable restrictions, this model is simplified and ignores traffic aspects such as turns and turn probabilities.
+This model also uses concurrent actions and the total actions has an upperbound of 2\textsuperscript{ (\# of intersections)}.
 
-\subsection{Real-World Domains}
+%ADD IMAGE HERE
+
+%\subsection{IPPC-04 Domains}
+%Duing IPPC-04, the domains were written in the Probabilistic PLanning Domain Description Language (PPDDL). 30 trials per problem were to be solved in 15 minutes.
+%
+%\subsubsection{}
+%
+%\subsubsection{}
+
+\subsection{Real-World evaluation}
+
+\subsubsection{Navigation domain}
+
+In the navigation problem there is a chance that the robot disappears after
+entering a cell. The disappearing action is a dead end. Disappearing here is a
+metaphor for the robot breaking down, or that it disappears from the radar with
+the base station. In many of such cases it's a big problem, but can be repaired
+with a high cost. In the navigation domain a step to another cell has a cost of
+1. If instead of a dead end the cost is $n$ (e.g. 5) instead of 1, which
+represents the cost of repairing the robot, dead ends are removed. Without dead
+ends the problem becomes probabilistic uninteresting, which makes it suitable for
+replanning planners.
 
 \subsection{Baseline test for Probabilistic Interesting domains}
-
-\subsection{Evaluating the domains}
-FF-Replan participated in IPPC-04 (and IPPC-06) solving problems that had been specified in the Probabilstic Planning Domain Description Language (PPDDL) whereas Gourmand has been tested on the set of IPPC-11 problems specified in Relational Dynamic Influence Diagram Language (RDDL)\cite{sanner2008rddl}.
 
@@
 
+Experiments can empirically evaluate the performance of the adjusted domains.
+
 \subsection{Setup}
+
+The planning problems are taken from the IPPC-11 suite and are written in RDDL,
+which are publicity available. A domain consists of the domain description and
+instances of a domain problem. The domain description is read by RDDLSim, which
+is a server a planner can communicate with, and simulates the real world after
+the planner sends an action.
 
@@
 
-\begin{itemize}
-	\item Describe the experiment setup
-	\item Show results for the experiment
-	\item Critically analyze the results
-	\item Compare with results from the original papers
-\end{itemize}
-
 %---------------------------------------------------------------------
@@
 
-\subsection{RFF}
+\subsubsection{RFF}. Also uses an incremental plan aggregation, but offline similar to GLUTTON.
 
-\subsection{PROST}
+\subsubsection{PROST}
 
-\subsection{FF-H+}
-
-% Use related work to display the differences with own work
-
-\begin{itemize}
-	\item Discuss the related work and how their approaches are different
-	\item Discuss the other domains and why our domain adds anything to the community
-	\item Introduce the current state of the art papers that use deterministic approaches for probablistic domains dealing with uncertainty
-\end{itemize}
+\subsubsection{FF-H+}
 
@@
 
-\section{Some papers}
-
-\begin{itemize}
-	\item \cite{Hoffmann01theff}
-	\item \cite{FFReplan}
-	\item \cite{teichteil2010incremental}
-	\item \cite{yoon2008probabilistic}
-	\item \cite{teichteil2012fast}
-	\item \cite{bonet2011planning}
-	\item \cite{taig2013translation}
-	\item \cite{martin2013progressive}
-	\item \cite{taig2013conformant}
-	\item \cite{2013workshop}
-	\item \cite{nebel2013much}
-	\item \cite{little2007probvsreplan}
-	\item \cite{keller2012prost}
-	\item \cite{kolobov2012glutton}
-	\item \cite{sanner2008rddl}
-	\item \cite{kolobov2012gourmand}
-\end{itemize}
+%\section{Some papers}
+%
+%\begin{itemize}
+%	\item \cite{Hoffmann01theff}
+%	\item \cite{FFReplan}
+%	\item \cite{teichteil2010incremental}
+%	\item \cite{yoon2008probabilistic}
+%	\item \cite{teichteil2012fast}
+%	\item \cite{bonet2011planning}
+%	\item \cite{taig2013translation}
+%	\item \cite{martin2013progressive}
+%	\item \cite{taig2013conformant}
+%	\item \cite{2013workshop}
+%	\item \cite{nebel2013much}
+%	\item \cite{little2007probvsreplan}
+%	\item \cite{keller2012prost}
+%	\item \cite{kolobov2012glutton}
+%	\item \cite{sanner2008rddl}
+%	\item \cite{kolobov2012gourmand}
+%\end{itemize}
 

### 2014-03-30 FinalPaper/paper.tex
Experiment strategy for implementing FF-Replan for MDP-FH and RDDLSim

@@
 
-\subsection{FF-Replan}
+\subsection{FF-Replan with Finite Horizon}
 
-\subsubsection{FF-Replan with Finite Horizon}
+Gourmand already works with RDDLSim and MDPs with finite horizon. The original
+FF-Replan is a Goal-Oriented MDP planner. For a Finite-Horizon each state at
+the horizon is a goal. To compare Gourmand, that works with MDP-FH, with
+FF-Replan, FF-Replan needs a slight update. It should not only execute FF for
+one goal, but for all goals at the horizon. It could then start executing the
+plan with the highest reward. Depending on the determinization method,
+\emph{single-outcomes} or \emph{all-outcomes}, not all goals might be
+reachable. Of course the performance decreases with an increase of goal states
+at the horizon. A hash-table cache, as FF-Replan already uses can still be used
+to store plans generated by FF from a state to goal states, however not only
+the plan should be stored, but also the reward for this plan should be stored
+to pick the plan with the highest expected reward.
+
+Using the framework of Glutton and Gourmand, and the FF heuristic found in mGPT
+\cite{bonet2011mgpt}, the updated FF-Replan can be implemented. The first step
+of Gourmand is parsing the problem and creating a structure of the problem.
+Instead of executing the Gourmand algorithm, this structure can be used to
+determinize the problem by setting all probabilities of each action to 1
+(\emph{all-outcome}) or all but one to 0 (\emph{single-outcome}). Using the
+FF heuristic it can find plans for each goal and calculate the expected reward.
+Then it can reuse the Gourmand framework to execute the plan by sending the
+action to the RDDLSim server. Like FF-Replan if the server returns with a state
+that is not in the plan the algorithm will replan. If a goal is reached it will
+output the achieved reward.
 

### 2014-03-30 FinalPaper/paper.tex
describing domain

--- 2014-03-30 FinalPaper/paper.tex
@@
 
-Since the first incorporation of the International Probabilistic Planning
-Competition (IPPC), it has undergone radical changes. Dominating planners
-of previous incorporations had a strong focus on goal-oriented MDPs,
-determinizing and using powerful classical planners (e.g. FF
-\cite{Hoffmann01theff}) and replanning. New benchmarks have demonstrated
-weaknesses in existing solution techniques.
-
-Little and Thi\'ebaux have developed a baseline test in
-\cite{little2007probvsreplan} to evaluate the IPC-5 problems. This
-test determines if a planning problem is `probabilistically interesting'.
-Problems that fail this test are classical planning problems in disguise.
-Knowing this it is easy to design a problem where a replanner performs badly
-or incredibly well.
-
-The IPPC-11 introduced Relation Dynamic Influence Diagram Language (RDDL),
-which can design domains that are more probabilistically interesting. The top
-performers were PROST \cite{keller2012prost} and Glutton
-\cite{kolobov2012glutton}.
-
-While it is interesting to make problems harder and invent better planning
-algorithms to solve those probabilistic complex problems, one must not forget
-if the problem makes sense in the real world.
-
-The main contribution of this paper is an evaluation of the domains used in
-IPPC-11 and see if they can be adjusted so they fail the baseline test for
-probabilistic interestingness, which might make them more suitable for
-replanning planners.
+The baseline test in \cite{little2007probvsreplan} evaluates the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
+We would like to carefully analyze the credibility of these domains in the real world and evaluate the worth of FF-Replan vs a state of the art probabilistic planner: Gourmand \cite{kolobov2012gourmand}.
 
@@
 
+\section{Planners}
+
+\subsection{FF-Replan}
+
+\subsection{Gourmand}
+The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
+For this reason planners needed to be scalable and sensitive to the expected reward maximization.
+Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP $M(H)$ for a smaller horizon $h$.
+Incrementally solving the sequence $M(1)$, $M(2)$ forms the basis of LR\textsuperscript{2}TDP\@.
+By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full).
+The max-reward heuristic finds the largest horizon value $h'$ for which already a heuristic value $V$ is estimated.
+The  computation time remains much lower because it runs quickly into states that converged while solving $M(h-1)$.
+The max-reward computation relies on knowing the maximum $R_{max}$ any action can yield in any state or an upper bound on it.
+
+\subsubsection{LRTDP}
+Using goal oriented MDPs, the \emph{Labelled Real-Time Dynamic Programmer} (LRTDP) operates a series of trials starting from $s_0$.
+
+\begin{itemize}
+	\item Trials start at $s_0$
+	\item Choose best action greedily in the current state based on current $V$
+	\item Perform  Bellman backup on the current state
+	\item Sample the outcome as the chosen action
+	\item Transition to the new state
+	\item Repeat until a goal, dead end or converged state is reached
+	\item After trial, special convergence check on all states in the trial is performed to prove the convergence of these values
+\end{itemize}
+
+\subsubsection{LRTDP-FH}
+
+Adapting LRTDP to a finite horizon MDP \emph{M(H)} requires to let each trial start at ($s_0$) and run for at most H time steps.
+A steps $H$ steps away from $s_0$ would translate to goals in a goal-oriented MDP.
+However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.
+
+\subsubsection{LR\textsuperscript{2}TDP}
+
+LR\textsuperscript{2}TDP uses \emph{reverse iterative deepening} and LRTDP-FH to solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$, in that order.
+It first decides how to act optimally in ($s_0$, 1), equivalent to solving M(1) , then ($s_0$, 2), equivalent to solving $M(2)$, eventually solving $M(H)$ or running out of time halting a $M(h')$ where $h' < H$.
+This incremental effort allows for reusing state values computed in previous states, so it memorizes all values and solves for smaller horizons by backchaining from the goal LRTDP-FH iterates over search depth while LR\textsuperscript{2}TDP iterates over the distance from the horizon and is likely to be better because:
+
+\begin{itemize}
+	\item In many MDPs, the optimal policy $M(h)$ for some $h < H$ is near optimal for M(H), it thus may have a solution when stopped prematurely
+	\item it's trials are very short because backchaining from the goal leads to a lots of convergence
+	\item It optimally memorizes a large fraction of augmented states to save memory
+	\item a large fraction of state space may be unreachable from $s_0$ and it avoid storing information it does not need
+	\item it should however use a heuristic to treat states that has never been encountered when stopped prematurely, could be a fall back or a default action.
+\end{itemize}
+
+\subsubsection{GLUTTON}
+
+Glutton uses the \emph{Max-Reward} heuristic that relies on knowing the maximum reward $R_{max}$ any action can yield in a state or an upper bound on it.
+Large branching factors induce that the computation of the Bellman Backups becomes prohibitively expensive.
+Glutton uses the following mechanisms to optimize for large branching factors:
+
+\begin{itemize}
+	\item Subsampling the transition function, is not enough to decrease the amount of computations yet
+	\item Separating out Natural Dynamics: to reuse variable samples when generator successors for multiple actions, by separating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both.
+	\item Caching the transition function samples: as LR\textsuperscript{2}TDP populates the state-value hash table lazily, Glutton uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same $(s,h)$ pair.
+When full, it chooses state-action pars for eviction ans replacement randomly.
+	\item Default policies: Glutton uses 3 tricks to determine a policy when stopped prematurely.
+It compares the optimal action from a $h'$ with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.
+\end{itemize}
+
+During IPPC-2011 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT.
+This caused to wonder whether LRTDP planners could outperform UCT based systems.
+UCT forces an expert to guess a non-shortsighted lookahead value for which it should be able to converge on encountered states.
+Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity.
+At the IPPC-2011 GLUTTON was an offline LRTDP based planner that came second.
+As PROST employed UCT in an online manner, GOURMAND is an online adaptation of the GLUTTON algorithm to test whether LRTDP performs better if it is employed online.
+
+UCT picks an action based on it current quality estimate and an \emph{exploration term} which forces the planner to choose actions that have rarely been tried in the past.
+This makes UCT suitable for a wider scale of scenarios but also implies an unreliable termination condition.
+
+Because real world domains contain Natural Dynamics that introduce large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of state the planner may never reach in a lifetime.
+Such problems are far better solved using online planners by finding a $\tau$* or an approximation for the current state, executing it and repeating.
+This is done by choosing a certain lookahead  L and solving MDP \emph{M\textsubscript{s}(L)} to solve \emph{M\textsubscript{0}(H)} where L $<$ H and then select \emph{$\pi$*\textsubscript{L}(s, L)} recommended by the optimal policy.
+This lookahead value is determined using the per-process time constraint.
+
+\subsubsection{GOURMAND}
+In contrast to GLUTTON, GOURMAND always makes an informed choice in any state where it ends up when the time T allocated for solving the MDP runs out because of the online fashion it uses LRTDP.
+GOURMAND first divides the time among all remaining epochs, determines the largest lookahead L for which it can almost certainly solve any remaining epoch if T is assigned.
+It then checks if it can solve even for a larger lookahead L by taking away a small configuration time from future epochs  while still guaranteeing that it can solve for Lookahead L in each of them.
+This was GOURMAND adaptively picks a good lookahead value at each desicion epoch given the per-process constraint T.
+This can only be achieved by knowing how long it takes for LRTDP to solve a state for certain lookahead values.
+It uses LR\textsuperscript{2}TDP to collect this data.
+This version of LRTDP is more efficient because of the early convergences and it allows measuring how long on average the solving of a task takes.
+GOURMAND uses the same engineering optimizations to to handle evaluate actions, iterating over the successors of s under a by the Bellman Backups.
+GOURMAND eventually outperforms both GLUTTON and PROST, the winner of the IPPC-11\cite{keller2012prost}.
+
+%---------------------------------------------------------------------
+
 \section{Domain Descriptions}
+Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
+Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}.
+This section describes interesting domains in which either FF-Replan or Gourmand prevailed during the International Probabilistic Planning Compeitions.
+These domains are evaluated for how well they portray real-world scenarios.
+The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario.
+Little et all's baseline test helps us to predict which planner would perform well on these domains.
+We will then conclude our evaluation by comparing these results to the result of our experiments described in Section \ref{sec:experiment}.
 
 \subsection{IPPC-2011 Domains}
+The competitor FF-Replan \cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
+The baseline test of Little et.
+all evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
+IPPC-2011 responded by introducing more realistic MDPs and evluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
+
+GOURMAND vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}.
+Prost however midly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
+
+\subsubsection{Navigation domain}
+The navigation domain represents a grid in which a robot must reach a goal.
+Every cell offers the robot a different chance of dissapearinng.
+The robot needs to choose a path which gets it to the goal most reliably within the finite horizon time \cite{sanner2011navigation}.
+Because GOURMAND uses a dynamic lookahead, it performs quite well in this domain.
+
+%ADD IMAGE HERE
+
+\subsubsection{Traffic domain}
+This domain represents a simple binary version of the cell transition model (CTM) for modelling traffic based on the original CTM Tech Report \cite{sanner2011traffic}.
+Because of the binary variables and no intermediate variable restrictions, this model is simplified and ignores traffic aspects such as turns and turn probabilities.
+This model also uses concurrent actions and the total actions has an upperbound of 2\^ (\# of intersections).
+
+\subsection{IPPC-04 Domains}
+Duing IPPC-04, the domains were written in the Probabilistic PLanning Domain Description Language (PPDDL). 30 trials per problem were to be solved in 15 minutes.
+
+\subsubsection{}
+
+\subsubsection{}
 

### 2014-03-30 FinalPaper/paper.tex
kom er even niet meer uit

@@
 
-\subsection{IPPC-04 Domains}
-Duing IPPC-04, the domains were written in the Probabilistic PLanning Domain Description Language (PPDDL). 30 trials per problem were to be solved in 15 minutes.
+%ADD IMAGE HERE
 
-\subsubsection{}
+%\subsection{IPPC-04 Domains}
+%Duing IPPC-04, the domains were written in the Probabilistic PLanning Domain Description Language (PPDDL). 30 trials per problem were to be solved in 15 minutes. 
+%
+%\subsubsection{}
+%
+%\subsubsection{}
 
-\subsubsection{}
-
-\subsection{Real-World Domains}
+\subsection{Real-World evaluation}
 
 \subsection{Baseline test for Probabilistic Interesting domains}
-
-\subsection{Evaluating the domains}
-FF-Replan participated in IPPC-04 (and IPPC-06) solving problems that had been specified in the Probabilstic Planning Domain Description Language (PPDDL) whereas Gourmand has been tested on the set of IPPC-11 problems specified in Relational Dynamic Influence Diagram Language (RDDL)\cite{sanner2008rddl}.
 

### 2014-03-30 FinalPaper/paper.tex
problem def

@@
 
-\section{Problem Formulation}
+\section{Background}
 
-\subsection{Markov Decision Process}
+\subsubsection{Goal-oriented MDPs.
+}The problems in IPPC-04 were specified using the Planning Domain Description Language (PPDLL).
+PPDDL specifies a probabistic planning problem as a set of probabilistic action sets and an initial and goal state description in which every action has a certain probability assigned to it \cite{FFReplan}.
+The planners from IPPC-04 were evaluated on how many trials reached the goal per problem and the average number of actions selected when succesfull.
+These planning problems were however relatively easy to solve as they did not account for \emph{natural dynamics} and/or large branching factors that occur in more realtistic systems \cite{kolobov2012glutton}.
+FF-Replan \cite{FFReplan}, as specified in Section  kindly remembered the committee of the IPPC-04 that the specified planning problems that contained no dead-ends were fairly easy to solve using relatively simple tools to handle with uncertainty.
 
-\subsubsection{Goal-oriented MDPs}
-
-\subsubsection{MDP with Finite Horizon}
-
-\subsection{Planners}
+\subsubsection{MDP with Finite Horizon. }IPPC
 
@@
 
-\subsubsection{Probabilistic Planning} Classical Planners expect a
-deterministic world. For many Real World applications actions happen with a
+\subsubsection{Probabilistic Planning} 
+Classical Planners expect a deterministic world. For many Real World applications actions happen with a
 certain probability. This kind of Probabilistic Planning Problems can be
@@
 
-% depends if we should include this, what we tell about Gourmand / RDDL...
+% depends if we should include this, what we tell about GOURMAND / RDDL...
 
@@
 
-In this paper we use Gourmand as a representative probabilistic planner, as
+In this paper we use GOURMAND as a representative probabilistic planner, as
 it's the improved version of Glutton, the runner-up of the IPPC-11 competition.
@@
 \subsection{Planning problem}
+
 \begin{itemize}
@@
 Problems that fail this test were deemed to be classical planning problems in disguise, favouring using replanners\cite{little2007probvsreplan}.
-This section describes interesting domains in which either FF-Replan or Gourmand prevailed during the International Probabilistic Planning Compeitions.
+This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Compeitions.
 We will then translate the most interesting domains to a complete "real-world" domain and evaluate them using the probabilistically interesting baseline test.
@@
 Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}.
-This section describes interesting domains in which either FF-Replan or Gourmand prevailed during the International Probabilistic Planning Compeitions.
+This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Compeitions.
 These domains are evaluated for how well they portray real-world scenarios.

### 2014-03-30 FinalPaper/paper.tex
Fixing some introduction stuff

--- 2014-03-30 FinalPaper/paper.tex
@@
 
-The baseline test in \cite{little2007probvsreplan} evaluates the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
-We would like to carefully analyze the credibility of these domains in the real world and evaluate the worth of FF-Replan vs a state of the art probabilistic planner: Gourmand \cite{kolobov2012gourmand}.
+Since the first incorporation of the International Probabilistic Planning
+Competition (IPPC), it has undergone radical changes. Dominating planners
+of previous incorporations had a strong focus on goal-oriented MDPs,
+determinizing and using powerful classical planners (e.g. FF
+\cite{Hoffmann01theff}) and replanning. New benchmarks have demonstrated
+weaknesses in existing solution techniques.
+
+Little and Thi\'ebaux have developed a baseline test in
+\cite{little2007probvsreplan} to evaluate the problems of the fifth International
+Planning Competition (IPC-5). This test determines if a planning problem is
+`probabilistically interesting'. Problems that fail this test are classical
+planning problems in disguise. Knowing this it is easy to design a problem
+where a replanner performs badly or incredibly well.
+
+The IPPC-11 introduced Relation Dynamic Influence Diagram Language (RDDL),
+which can design domains that are more probabilistically interesting. The top
+performers were PROST \cite{keller2012prost} and Glutton
+\cite{kolobov2012glutton}.
+
+While it is interesting to make problems harder and invent better planning
+algorithms to solve those probabilistic complex problems, one must not forget
+if the problem makes sense in the real world.
+
+The main contribution of this paper is an evaluation of FF-Replan versus a
+probabilistically state of the art planner GOURMAND in the realistically
+augmented domains of IPPC-11. If these domains fail the baseline test proposed
+by Little et\@. all, they would translate to classical planning problems in
+disguise and could be easily solved by FF-Replan.
 
@@
 
-\section{Planners}
-
-\subsection{FF-Replan}
-
-\subsection{Gourmand}
-The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
-For this reason planners needed to be scalable and sensitive to the expected reward maximization.
-Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP $M(H)$ for a smaller horizon $h$.
-Incrementally solving the sequence $M(1)$, $M(2)$ forms the basis of LR\textsuperscript{2}TDP\@.
-By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full).
-The max-reward heuristic finds the largest horizon value $h'$ for which already a heuristic value $V$ is estimated.
-The  computation time remains much lower because it runs quickly into states that converged while solving $M(h-1)$.
-The max-reward computation relies on knowing the maximum $R_{max}$ any action can yield in any state or an upper bound on it.
-
-\subsubsection{LRTDP}
-Using goal oriented MDPs, the \emph{Labelled Real-Time Dynamic Programmer} (LRTDP) operates a series of trials starting from $s_0$.
-
-\begin{itemize}
-	\item Trials start at $s_0$
-	\item Choose best action greedily in the current state based on current $V$
-	\item Perform  Bellman backup on the current state
-	\item Sample the outcome as the chosen action
-	\item Transition to the new state
-	\item Repeat until a goal, dead end or converged state is reached
-	\item After trial, special convergence check on all states in the trial is performed to prove the convergence of these values
-\end{itemize}
-
-\subsubsection{LRTDP-FH}
-
-Adapting LRTDP to a finite horizon MDP \emph{M(H)} requires to let each trial start at ($s_0$) and run for at most H time steps.
-A steps $H$ steps away from $s_0$ would translate to goals in a goal-oriented MDP.
-However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.
-
-\subsubsection{LR\textsuperscript{2}TDP}
-
-LR\textsuperscript{2}TDP uses \emph{reverse iterative deepening} and LRTDP-FH to solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$, in that order.
-It first decides how to act optimally in ($s_0$, 1), equivalent to solving M(1) , then ($s_0$, 2), equivalent to solving $M(2)$, eventually solving $M(H)$ or running out of time halting a $M(h')$ where $h' < H$.
-This incremental effort allows for reusing state values computed in previous states, so it memorizes all values and solves for smaller horizons by backchaining from the goal LRTDP-FH iterates over search depth while LR\textsuperscript{2}TDP iterates over the distance from the horizon and is likely to be better because:
-
-\begin{itemize}
-	\item In many MDPs, the optimal policy $M(h)$ for some $h < H$ is near optimal for M(H), it thus may have a solution when stopped prematurely
-	\item it's trials are very short because backchaining from the goal leads to a lots of convergence
-	\item It optimally memorizes a large fraction of augmented states to save memory
-	\item a large fraction of state space may be unreachable from $s_0$ and it avoid storing information it does not need
-	\item it should however use a heuristic to treat states that has never been encountered when stopped prematurely, could be a fall back or a default action.
-\end{itemize}
-
-\subsubsection{GLUTTON}
-
-Glutton uses the \emph{Max-Reward} heuristic that relies on knowing the maximum reward $R_{max}$ any action can yield in a state or an upper bound on it.
-Large branching factors induce that the computation of the Bellman Backups becomes prohibitively expensive.
-Glutton uses the following mechanisms to optimize for large branching factors:
-
-\begin{itemize}
-	\item Subsampling the transition function, is not enough to decrease the amount of computations yet
-	\item Separating out Natural Dynamics: to reuse variable samples when generator successors for multiple actions, by separating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both.
-	\item Caching the transition function samples: as LR\textsuperscript{2}TDP populates the state-value hash table lazily, Glutton uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same $(s,h)$ pair.
-When full, it chooses state-action pars for eviction ans replacement randomly.
-	\item Default policies: Glutton uses 3 tricks to determine a policy when stopped prematurely.
-It compares the optimal action from a $h'$ with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.
-\end{itemize}
-
-During IPPC-2011 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT.
-This caused to wonder whether LRTDP planners could outperform UCT based systems.
-UCT forces an expert to guess a non-shortsighted lookahead value for which it should be able to converge on encountered states.
-Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity.
-At the IPPC-2011 GLUTTON was an offline LRTDP based planner that came second.
-As PROST employed UCT in an online manner, GOURMAND is an online adaptation of the GLUTTON algorithm to test whether LRTDP performs better if it is employed online.
-
-UCT picks an action based on it current quality estimate and an \emph{exploration term} which forces the planner to choose actions that have rarely been tried in the past.
-This makes UCT suitable for a wider scale of scenarios but also implies an unreliable termination condition.
-
-Because real world domains contain Natural Dynamics that introduce large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of state the planner may never reach in a lifetime.
-Such problems are far better solved using online planners by finding a $\tau$* or an approximation for the current state, executing it and repeating.
-This is done by choosing a certain lookahead  L and solving MDP \emph{M\textsubscript{s}(L)} to solve \emph{M\textsubscript{0}(H)} where L $<$ H and then select \emph{$\pi$*\textsubscript{L}(s, L)} recommended by the optimal policy.
-This lookahead value is determined using the per-process time constraint.
-
-\subsubsection{GOURMAND}
-In contrast to GLUTTON, GOURMAND always makes an informed choice in any state where it ends up when the time T allocated for solving the MDP runs out because of the online fashion it uses LRTDP.
-GOURMAND first divides the time among all remaining epochs, determines the largest lookahead L for which it can almost certainly solve any remaining epoch if T is assigned.
-It then checks if it can solve even for a larger lookahead L by taking away a small configuration time from future epochs  while still guaranteeing that it can solve for Lookahead L in each of them.
-This was GOURMAND adaptively picks a good lookahead value at each desicion epoch given the per-process constraint T.
-This can only be achieved by knowing how long it takes for LRTDP to solve a state for certain lookahead values.
-It uses LR\textsuperscript{2}TDP to collect this data.
-This version of LRTDP is more efficient because of the early convergences and it allows measuring how long on average the solving of a task takes.
-GOURMAND uses the same engineering optimizations to to handle evaluate actions, iterating over the successors of s under a by the Bellman Backups.
-GOURMAND eventually outperforms both GLUTTON and PROST, the winner of the IPPC-11\cite{keller2012prost}.
-
-%---------------------------------------------------------------------
-
 \section{Domain Descriptions}
-Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
-Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}.
-This section describes interesting domains in which either FF-Replan or Gourmand prevailed during the International Probabilistic Planning Compeitions.
-These domains are evaluated for how well they portray real-world scenarios.
-The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario.
-Little et all's baseline test helps us to predict which planner would perform well on these domains.
-We will then conclude our evaluation by comparing these results to the result of our experiments described in Section \ref{sec:experiment}.
 
 \subsection{IPPC-2011 Domains}
-The competitor FF-Replan \cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
-The baseline test of Little et.
-all evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
-IPPC-2011 responded by introducing more realistic MDPs and evluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
-
-GOURMAND vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}.
-Prost however midly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
-
-\subsubsection{Navigation domain}
-The navigation domain represents a grid in which a robot must reach a goal.
-Every cell offers the robot a different chance of dissapearinng.
-The robot needs to choose a path which gets it to the goal most reliably within the finite horizon time \cite{sanner2011navigation}.
-Because GOURMAND uses a dynamic lookahead, it performs quite well in this domain.
-
-%ADD IMAGE HERE
-
-\subsubsection{Traffic domain}
-This domain represents a simple binary version of the cell transition model (CTM) for modelling traffic based on the original CTM Tech Report \cite{sanner2011traffic}.
-Because of the binary variables and no intermediate variable restrictions, this model is simplified and ignores traffic aspects such as turns and turn probabilities.
-This model also uses concurrent actions and the total actions has an upperbound of 2\^ (\# of intersections).
-
-\subsection{IPPC-04 Domains}
-Duing IPPC-04, the domains were written in the Probabilistic PLanning Domain Description Language (PPDDL). 30 trials per problem were to be solved in 15 minutes.
-
-\subsubsection{}
-
-\subsubsection{}
 
@@
 FF-Replan participated in IPPC-04 (and IPPC-06) solving problems that had been specified in the Probabilstic Planning Domain Description Language (PPDDL) whereas Gourmand has been tested on the set of IPPC-11 problems specified in Relational Dynamic Influence Diagram Language (RDDL)\cite{sanner2008rddl}.
+
+%---------------------------------------------------------------------
+
+\section{Planners}
+
+\subsection{FF-Replan}
+
+\subsection{Gourmand}
 
@@
 
+\subsection{Reverse Iterative Deepening for Finite-Horizon MDPs with Large Branching Factors (2012)~\cite{kolobov2012glutton}}
+The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
+For this reason planners needed to be scalable and sensitive to the expected reward maximization.
+Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP $M(H)$ for a smaller horizon $h$.
+Incrementally solving the sequence $M(1)$, $M(2)$ forms the basis of LR\textsuperscript{2}TDP\@.
+By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full).
+The max-reward heuristic finds the largest horizon value $h'$ for which already a heuristic value $V$ is estimated.
+The  computation time remains much lower because it runs quickly into states that converged while solving $M(h-1)$.
+The max-reward computation relies on knowing the maximum $R_{max}$ any action can yield in any state or an upper bound on it.
+
+\subsubsection{LRTDP}
+Using goal oriented MDPs, the \emph{Labelled Real-Time Dynamic Programmer} (LRTDP) operates a series of trials starting from $s_0$.
+
+\begin{itemize}
+	\item Trials start at $s_0$
+	\item Choose best action greedily in the current state based on current $V$
+	\item Perform  Bellman backup on the current state
+	\item Sample the outcome as the chosen action
+	\item Transition to the new state
+	\item Repeat until a goal, dead end or converged state is reached
+	\item After trial, special convergence check on all states in the trial is performed to prove the convergence of these values
+\end{itemize}
+
+\subsubsection{LRTDP-FH}
+
+Adapting LRTDP to a finite horizon MDP \emph{M(H)} requires to let each trial start at ($s_0$) and run for at most H time steps.
+A steps $H$ steps away from $s_0$ would translate to goals in a goal-oriented MDP.
+However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.
+
+\subsubsection{LR\textsuperscript{2}TDP}
+
+LR\textsuperscript{2}TDP uses \emph{reverse iterative deepening} and LRTDP-FH to solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$, in that order.
+It first decides how to act optimally in ($s_0$, 1), equivalent to solving M(1) , then ($s_0$, 2), equivalent to solving $M(2)$, eventually solving $M(H)$ or running out of time halting a $M(h')$ where $h' < H$.
+This incremental effort allows for reusing state values computed in previous states, so it memorizes all values and solves for smaller horizons by backchaining from the goal LRTDP-FH iterates over search depth while LR\textsuperscript{2}TDP iterates over the distance from the horizon and is likely to be better because:
+
+\begin{itemize}
+	\item In many MDPs, the optimal policy $M(h)$ for some $h < H$ is near optimal for M(H), it thus may have a solution when stopped prematurely
+	\item it's trials are very short because backchaining from the goal leads to a lots of convergence
+	\item It optimally memorizes a large fraction of augmented states to save memory
+	\item a large fraction of state space may be unreachable from $s_0$ and it avoid storing information it does not need
+	\item it should however use a heuristic to treat states that has never been encountered when stopped prematurely, could be a fall back or a default action.
+\end{itemize}
+
+\subsubsection{GLUTTON}
+
+Glutton uses the \emph{Max-Reward} heuristic that relies on knowing the maximum reward $R_{max}$ any action can yield in a state or an upper bound on it.
+Large branching factors induce that the computation of the Bellman Backups becomes prohibitively expensive.
+Glutton uses the following mechanisms to optimize for large branching factors:
+
+\begin{itemize}
+	\item Subsampling the transition function, is not enough to decrease the amount of computations yet
+	\item Separating out Natural Dynamics: to reuse variable samples when generator successors for multiple actions, by separating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both.
+	\item Caching the transition function samples: as LR\textsuperscript{2}TDP populates the state-value hash table lazily, Glutton uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same $(s,h)$ pair.
+When full, it chooses state-action pars for eviction ans replacement randomly.
+	\item Default policies: Glutton uses 3 tricks to determine a policy when stopped prematurely.
+It compares the optimal action from a $h'$ with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.
+\end{itemize}
+
+\subsection{LRTDP vs. UCT for Online Probabilistic Planning\cite{kolobov2012gourmand}}
+During IPPC-2011 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT.
+This caused to wonder whether LRTDP planners could outperform UCT based systems.
+UCT forces an expert to guess a non-shortsighted lookahead value for which it should be able to converge on encountered states.
+Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity.
+At the IPPC-2011 GLUTTON was an offline LRTDP based planner that came second.
+As PROST employed UCT in an online manner, GOURMAND is an online adaptation of the GLUTTON algorithm to test whether LRTDP performs better if it is employed online.
+
+UCT picks an action based on it current quality estimate and an \emph{exploration term} which forces the planner to choose actions that have rarely been tried in the past.
+This makes UCT suitable for a wider scale of scenarios but also implies an unreliable termination condition.
+
+Because real world domains contain Natural Dynamics that introduce large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of state the planner may never reach in a lifetime.
+Such problems are far better solved using online planners by finding a $\tau$* or an approximation for the current state, executing it and repeating.
+This is done by choosing a certain lookahead  L and solving MDP \emph{M\textsubscript{s}(L)} to solve \emph{M\textsubscript{0}(H)} where L $<$ H and then select \emph{$\pi$*\textsubscript{L}(s, L)} recommended by the optimal policy.
+This lookahead value is determined using the per-process time constraint.
+
+\subsubsection{GOURMAND}
+In contrast to GLUTTON, GOURMAND always makes an informed choice in any state where it ends up when the time T allocated for solving the MDP runs out because of the online fashion it uses LRTDP.
+GOURMAND first divides the time among all remaining epochs, determines the largest lookahead L for which it can almost certainly solve any remaining epoch if T is assigned.
+It then checks if it can solve even for a larger lookahead L by taking away a small configuration time from future epochs  while still guaranteeing that it can solve for Lookahead L in each of them.
+This was GOURMAND adaptively picks a good lookahead value at each desicion epoch given the per-process constraint T.
+This can only be achieved by knowing how long it takes for LRTDP to solve a state for certain lookahead values.
+It uses LR\textsuperscript{2}TDP to collect this data.
+This version of LRTDP is more efficient because of the early convergences and it allows measuring how long on average the solving of a task takes.
+GOURMAND uses the same engineering optimizations to to handle evaluate actions, iterating over the successors of s under a by the Bellman Backups.
+GOURMAND eventually outperforms both GLUTTON and PROST, the winner of the IPPC-11\cite{keller2012prost}.
+
 \subsection{Probabilistic planning vs Replanning}
@@
 
-%\section{Some papers}
-%
-%\begin{itemize}
-%	\item \cite{Hoffmann01theff}
-%	\item \cite{FFReplan}
-%	\item \cite{teichteil2010incremental}
-%	\item \cite{yoon2008probabilistic}
-%	\item \cite{teichteil2012fast}
-%	\item \cite{bonet2011planning}
-%	\item \cite{taig2013translation}
-%	\item \cite{martin2013progressive}
-%	\item \cite{taig2013conformant}
-%	\item \cite{2013workshop}
-%	\item \cite{nebel2013much}
-%	\item \cite{little2007probvsreplan}
-%	\item \cite{keller2012prost}
-%	\item \cite{kolobov2012glutton}
-%	\item \cite{sanner2008rddl}
-%	\item \cite{kolobov2012gourmand}
-%\end{itemize}
+\section{Some papers}
+
+\begin{itemize}
+	\item \cite{Hoffmann01theff}
+	\item \cite{FFReplan}
+	\item \cite{teichteil2010incremental}
+	\item \cite{yoon2008probabilistic}
+	\item \cite{teichteil2012fast}
+	\item \cite{bonet2011planning}
+	\item \cite{taig2013translation}
+	\item \cite{martin2013progressive}
+	\item \cite{taig2013conformant}
+	\item \cite{2013workshop}
+	\item \cite{nebel2013much}
+	\item \cite{little2007probvsreplan}
+	\item \cite{keller2012prost}
+	\item \cite{kolobov2012glutton}
+	\item \cite{sanner2008rddl}
+	\item \cite{kolobov2012gourmand}
+\end{itemize}
 

### 2014-03-30 FinalPaper/paper.tex
Fixing sentence in the introduction, consistent use of GOURMAND

@@
 While it is interesting to make problems harder and invent better planning
-algorithms to solve those probabilistic complex problems, one must not forget
-if the problem makes sense in the real world.
+algorithms to solve those probabilistic complex problems, we evaluate whether
+or not these problems are coherent with real-world situations.
 

### 2014-03-30 FinalPaper/paper.tex
Improve first sentence of the introduction, remove incorporate.

@@
 
-Since the first incorporation of the International Probabilistic Planning
-Competition (IPPC), it has undergone radical changes. Dominating planners
-of previous incorporations had a strong focus on goal-oriented MDPs,
-determinizing and using powerful classical planners (e.g. FF
-\cite{Hoffmann01theff}) and replanning. New benchmarks have demonstrated
-weaknesses in existing solution techniques.
+Since the first the International Probabilistic Planning Competition (IPPC),
+problems have undergone radical changes. Dominating planners of previous
+incorporations had a strong focus on goal-oriented MDPs, determinizing and
+using powerful classical planners (e.g. FF \cite{Hoffmann01theff}) and
+replanning. New benchmark problems have demonstrated weaknesses in existing
+solution techniques.
 

### 2014-03-30 FinalPaper/paper.tex
Fixing typos

@@
 
-\section{Problem Formulation}
+\section{Problem formulation}
+To evaluate FF-Replan and GOURMAND in a real world domain a finite horizon MDP is used to represent the realistic \emph{natural dynamics} such as external forces or forces of nature.
+These dynamics introduce large branching factors emphasizing the need for a planner to be scalable.
+To evaluate the model, the planner should also be sensitive to an expected reward maximization criterion.
+Current finite horizon MDP problems as introduced in IPPC-11 are simplified and therefor do not account for the rich set of state-actions as would be available in a real-world planning problem.
+We will reason about the most interesting domains for our evaluation and adjust them to match their real-world equivalent.
+Using the basline test introduced by Little et.
+all \cite{little2007probvsreplan}, we can evaluate the probabilistically interestingness of these domains and evaluate the performance of FF-Replan vs.
+a state of the art probabilistic planner: GOURMAND.
 
-\subsection{Markov Decision Process}
+%---------------------------------------------------------------------
 
-\subsubsection{Goal-oriented MDPs}
+\section{Background}
 
-\subsubsection{MDP with Finite Horizon}
+\subsection{Planning problems}
+\subsubsection{Classical Planning problems.
+} Planning is the process of computing several steps of a problem-solving procedure before executing any of them.
+In classical planning problems the environment is assumed to \emph{deterministic, observable and state}.
+Classical planning problems consists out of states, actions, conditions and a goal state and are solved using search and can be aided using heuristics.
+The planner tries to find a sequence of actions such that a goal or maximum reward is achieved.
 
-\subsection{Planners}
+\subsubsection{Probabilistic Planning problems}
+Real-World applications are far from deterministic, induced by natural dynamics and chance.
+To accomodate for Real-World domains probabilistic planning problems were introduced.
+These systems can be described using \emph{Markov Decision Processes} (MDPs) and can account for observable uncertainty.
+Probabilistic planning problems can be solved by evaluating iterations and creating policies to reach a goal state, either online or offline.
 
-\subsubsection{Classical Planners}
+\subsection{Problem domains}
+\subsubsection{Goal-oriented MDPs.
+}The problems in IPPC-04 were specified using the Planning Domain Description Language (PPDLL).
+PPDDL specifies a probabistic planning problem as a set of probabilistic action sets and an initial and goal state description in which every action has a certain probability assigned to it \cite{FFReplan}.
+These MDPs are of the form $\mathit{M = (S, A, app, Pr, R)}$ where $\mathit{S}$ and $\mathit{A}$ are a finite set of states and actions, $\mathit{app(s)}$ is the set of all actions applicable in $\mathit{s}$.
+$\mathit{Pr}$ represents the probability of a state transaction $\mathit{(s, a, s')}$ for $\mathit{a}$ and $\mathit{R(s, a, s')}$ is the reward of applying $\mathit{a}$ to $\mathit{s}$ and generating $\mathit{s'}$ The planning problem is defined as a triple $\mathit{P = (M, s\textsubscript{0}, G, \rho)}$ where $\mathit{M = (S, A, app, Pr, R)}$ is an MDP, $\mathit{s\textsubscript{0} \in S}$ is the initial state, $\mathit{G \subseteq S}$ is the set of goal states and $\mathit{0 < \rho < 1}$ is a probability threshold \cite{teichteil2010incremental}.
 
-A planner tries to find a sequence of actions such that a goal or maximum
-reward is achieved. A classical planning problem consists out of states,
-actions, conditions and a goal state.
+ The planners from IPPC-04 were evaluated on how many trials reached the goal per problem and the average number of actions selected when succesfull.
+These planning problems were however relatively easy to solve as they did not account for \emph{natural dynamics} and/or large branching factors that occur in more realtistic systems \cite{kolobov2012glutton}.
+FF-Replan \cite{FFReplan}, as specified in Section \ref{sec:planners} kindly remembered the committee of the IPPC-04 that the specified planning problems that contained no dead-ends were fairly easy to solve using relatively simple tools to handle with uncertainty.
 
-\subsubsection{Probabilistic Planning} Classical Planners expect a
-deterministic world. For many Real World applications actions happen with a
-certain probability. This kind of Probabilistic Planning Problems can be
-described with Markov Decision Processes (MDPs). For the purpose of our
-analysis we define the problem as:
+\subsubsection{MDPs with Finite Horizon.
+}IPPC-11 decided to respond by introducing more realistic MDPs and their evaluation criteria by using MDPs with finite horizons.
+The planning problems are defined as tuples of the form \\ $\mathit{M\textsubscript{s0}(H) = \langle \langle S, A, T, R, s\textsubscript{0} \rangle , H \rangle }$ where $\mathit{S}$ s a finite set of states, $\mathit{A}$ a finite set of actions, $\mathit{T}$ is the transition function, similar to $\mathit{Pr}$ in the goal oriented MDP.
+$\mathit{R}$ represents the transitioning reward, $\mathit{s\textsubscript{0}}$ and $\mathit{H}$ is the number of decision epochs after which the process stops.
+Solving $\mathit{M(H)}$ means finding a policy for executing recommended state from the initial state over $\mathit{H}$ decision epochs \cite{kolobov2012gourmand}.
 
-\begin{itemize}
-	\item finite set of states $S$
-	\item an initial state $s_o \in S$
-	\item a $G \subseteq S$ of (absorbing) goal states
-	\item a set $O$ of outcomes; probability of $o \in O$ is $\Pr(o)$
-	\item a (total) deterministic transition function $T(o,s) \in S$ for all
-		outcomes $o \in O$ and states $s \in S$
-	\item sets $A(s)$ of applicable actions for each $s \in S$, together with
-		function $out(a) \subseteq O$ mapping each action to a set of outcomes
-		such that each outcome $o \in O$ belongs exactly to one action $act(o)$
-		and $\sum_{o \in out(a)} \Pr(o) = 1$ for all $a$
-\end{itemize}
+Translating finite horizon MDPs to goal-oriented domains results ends up in all state $H$ steps away from $s\textsubscript{0}$ are goal states.
+The evaluation criteria in finite horizon MDPs is the \emph{expected reward} and not the probability of the policy reaching the goal states.
 
-% depends if we should include this, what we tell about GOURMAND / RDDL...
+\subsection{Planning algorithms}
+\subsubsection{Replanning}
+A replanner is a planner that takes a problem as input, plans a state-action policy, executes it online and whenever it encounters a state that was not in its state-action policy, it takes the current state as starting state and plans again until it has reached a goal or dead-end state.
+For our paper have chosen to evaluate FF-Replan \cite{FFReplan}, the winner of IPPC-04 and unenrolled winner of IPPC-06 as an inspiring, fairly simple planner that in our opinion is capable of employment in real-world domains.
 
-Besides a single or multiple goals, some planning problems also include a
-reward function: For every $s \in S$, $s' \in S$, and $a \in A(s)$,
-$R(s,a,s')$ is the reward function. The goal if the problem is to maximize
-the reward until a goal is reached. If a Finite Horizon (number of steps of the
-plan) is used, the goal of the problem is to achieve the highest reward within
-the horizon.
-
-A probabilistic planner takes the probabilistic planning problem as input and
-builds and outputs a plan for the problem.
-
-In this paper we use GOURMAND as a representative probabilistic planner, as
-it's the improved version of Glutton, the runner-up of the IPPC-11 competition.
-
-\subsubsection{Replanning}
-
-An Replanning Planner takes a probabilistic problem and tries to solve it with
-replanning. First the problem is determinized, a compilation from a
-probabilistic problem to a deterministic problem. This deterministic problem
-be solved by a classical planner which returns a plan. The Replanner then
-executes the plan. If it ends up in a state which is different from the plan,
-it executes the classical planner to get a new plan. This is repeated until a
-goal is reached.
-
-In this paper we use FF-Replan as a representative replanning planner.
-
-\begin{itemize}
-	\item Summarize shortcomings of the previous solutions
-	\item Describe the planning problem
-	\item Argument the choice for 2 current papers to analyze
-	\item Define how we would like to test the planning algorithms in a domain by our choice
-\end{itemize}
-
-\subsection{Planning problem}
-
-\begin{itemize}
-	\item Describe the MDP finite horizon planning problem (useful for modelling nearly infinite processes)
-	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
-	\item Describe reward heuristic
-	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest expected reward over H steps time
-	\item The challenge or large branching factors (induced by natural dynamic)
-\end{itemize}
+\subsubsection{Probabilistic planning}
+Probabilistic planners are used to solve probabilistic planning problems and should be able to account for uncertainty as opposed to classical planners.
+For our evaluation we have choosen to compare FF-Replan to a state-of-the-art probabilistic planner: GOURMAND.
+GOURMAND is the online successor of the GLUTTON plan, a Labelled Real-Time Dynamic Programming (LRTDP) based planner and the runner up of IPPC-11.
 
 \subsection{Probabilistic Interestingness}
-
-Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
-Problems that fail this test were deemed to be classical planning problems in disguise, favouring using replanners\cite{little2007probvsreplan}.
-This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Compeitions.
-We will then translate the most interesting domains to a complete "real-world" domain and evaluate them using the probabilistically interesting baseline test.
-This paper concludes on evaluation both planners using the translated domains.
-
-The competitor FF-Replan\cite{FFReplan} remembered the committee of the IPPC in 2004 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
-The baseline test evaluates the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
-
-Following existing domains were said to be probabilistically interesting:
-
-\begin{itemize}
-	\item Drive
-	\item Exploding blocksworld
-	\item Pitchcatch
-	\item Schedule
-	\item Tireworld
-\end{itemize}
-
-A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties:
-
+After IPPC-06, a baseline test for \emph{probabilistically interesting} planning domains was proposed by Little and Thi\'ebauw \cite{little2007probvsreplan}.
+Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners.
+A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties \cite{little2007probvsreplan}:
 % reference little & thiebauw again. Maybe also shortly define what all o, n, act etc. are.
@@
 \section{Domain Descriptions}
+
 Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
 Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}.
-This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Compeitions.
+This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Competitions.
 These domains are evaluated for how well they portray real-world scenarios.
 The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario.
-Little et all's baseline test helps us to predict which planner would perform well on these domains.
+Little et.
+all's baseline test helps us to predict which planner would perform well on these domains.
 We will then conclude our evaluation by comparing these results to the result of our experiments described in Section \ref{sec:experiment}.
@@
 all evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
-IPPC-2011 responded by introducing more realistic MDPs and evluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
+IPPC-2011 responded by introducing more realistic MDPs and evaluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
 
 GOURMAND vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}.
-Prost however midly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
+PROST however mildly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
 
 \subsubsection{Navigation domain}
+
 The navigation domain represents a grid in which a robot must reach a goal.
-Every cell offers the robot a different chance of dissapearinng.
+Every cell offers the robot a different chance of disappearing.
 The robot needs to choose a path which gets it to the goal most reliably within the finite horizon time \cite{sanner2011navigation}.
@@
 Because of the binary variables and no intermediate variable restrictions, this model is simplified and ignores traffic aspects such as turns and turn probabilities.
-This model also uses concurrent actions and the total actions has an upperbound of 2\^ (\# of intersections).
+This model also uses concurrent actions and the total actions has an upperbound of 2\textsuperscript{ (\# of intersections)}.
 
@@
 \subsection{Real-World evaluation}
+
+\subsubsection{Navigation domain}
+
+In the navigation problem there is a chance that the robot disappears after
+entering a cell. The disappearing action is a dead end. Disappearing here is a
+metaphor for the robot breaking down, or that it disappears from the radar with
+the base station. In many of such cases it's a big problem, but can be repaired
+with a high cost. In the navigation domain a step to another cell has a cost of
+1. If instead of a dead end the cost is $n$ (e.g. 5) instead of 1, which
+represents the cost of repairing the robot, dead ends are removed. Without dead
+ends the problem becomes probabilistic uninteresting, which makes it suitable for
+replanning planners.
 

### 2014-03-30 FinalPaper/paper.tex
added initial part background

--- 2014-03-30 FinalPaper/paper.tex
@@
 
-\section{Problem Formulation}
+\section{Background}
 
-\subsection{Markov Decision Process}
+\subsection{Planning problems}
+\subsubsection{Classical Planning problems.
+} Planning is the process of computing several steps of a problem-solving procedure before executing any of them.
+In classical planning problems the environment is assumed to \emph{deterministic, observable and state}.
+Classical planning problems consists out of states, actions, conditions and a goal state and are solved using search and can be aided using heuristics.
+The planner tries to find a sequence of actions such that a goal or maximum reward is achieved.
 
-\subsubsection{Goal-oriented MDPs}
+\subsubsection{Probabilistic Planning problems} 
+Real-World applications are far from deterministic, induced by natural dynamics and chance.
+To accomodate for Real-World domains probabilistic planning problems were introduced.
+These systems can be described using \emph{Markov Decision Processes} (MDPs) and can account for observable uncertainty.
+Probabilistic planning problems can be solved by evaluating iterations and creating policies to reach a goal state, either online or offline.
 
-\subsubsection{MDP with Finite Horizon}
+\subsection{Problem domains}
+\subsubsection{Goal-oriented MDPs.
+}The problems in IPPC-04 were specified using the Planning Domain Description Language (PPDLL).
+PPDDL specifies a probabistic planning problem as a set of probabilistic action sets and an initial and goal state description in which every action has a certain probability assigned to it \cite{FFReplan}.
+These MDPs are of the form $\mathit{M = (S, A, app, Pr, R)}$ where $\mathit{S}$ and $\mathit{A}$ are a finite set of states and actions, $\mathit{app(s)}$ is the set of all actions applicable in $\mathit{s}$.
+$\mathit{Pr}$ represents the probability of a state transaction $\mathit{(s, a, s')}$ for $\mathit{a}$ and $\mathit{R(s, a, s')}$ is the reward of applying $\mathit{a}$ to $\mathit{s}$ and generating $\mathit{s'}$ The planning problem is defined as a triple $\mathit{P = (M, s\textsubscript{0}, G, \rho)}$ where $\mathit{M = (S, A, app, Pr, R)}$ is an MDP, $\mathit{s\textsubscript{0} \in S}$ is the initial state, $\mathit{G \subseteq S}$ is the set of goal states and $\mathit{0 < \rho < 1}$ is a probability threshold \cite{teichteil2010incremental}.
 
-\subsection{Planners}
+ The planners from IPPC-04 were evaluated on how many trials reached the goal per problem and the average number of actions selected when succesfull.
+These planning problems were however relatively easy to solve as they did not account for \emph{natural dynamics} and/or large branching factors that occur in more realtistic systems \cite{kolobov2012glutton}.
+FF-Replan \cite{FFReplan}, as specified in Section \ref{sec:planners} kindly remembered the committee of the IPPC-04 that the specified planning problems that contained no dead-ends were fairly easy to solve using relatively simple tools to handle with uncertainty.
 
-\subsubsection{Classical Planners}
+\subsubsection{MDPs with Finite Horizon.
+}IPPC-11 decided to respond by introducing more realistic MDPs and their evaluation criteria by using MDPs with finite horizons.
+The planning problems are defined as tuples of the form \\ $\mathit{M\textsubscript{s0}(H) = \langle \langle S, A, T, R, s\textsubscript{0} \rangle , H \rangle }$ where $\mathit{S}$ s a finite set of states, $\mathit{A}$ a finite set of actions, $\mathit{T}$ is the transition function, similar to $\mathit{Pr}$ in the goal oriented MDP.
+$\mathit{R}$ represents the transitioning reward, $\mathit{s\textsubscript{0}}$ and $\mathit{H}$ is the number of decision epochs after which the process stops.
+Solving $\mathit{M(H)}$ means finding a policy for executing recommended state from the initial state over $\mathit{H}$ decision epochs \cite{kolobov2012gourmand}.
 
-A planner tries to find a sequence of actions such that a goal or maximum
-reward is achieved. A classical planning problem consists out of states,
-actions, conditions and a goal state.
+Translating finite horizon MDPs to goal-oriented domains results ends up in all state $H$ steps away from $s\textsubscript{0}$ are goal states.
+The evaluation criteria in finite horizon MDPs is the \emph{expected reward} and not the probability of the policy reaching the goal states.
 
-\subsubsection{Probabilistic Planning} Classical Planners expect a
-deterministic world. For many Real World applications actions happen with a
-certain probability. This kind of Probabilistic Planning Problems can be
-described with Markov Decision Processes (MDPs). For the purpose of our
-analysis we define the problem as:
-
-\begin{itemize}
-	\item finite set of states $S$
-	\item an initial state $s_o \in S$
-	\item a $G \subseteq S$ of (absorbing) goal states
-	\item a set $O$ of outcomes; probability of $o \in O$ is $\Pr(o)$
-	\item a (total) deterministic transition function $T(o,s) \in S$ for all
-		outcomes $o \in O$ and states $s \in S$
-	\item sets $A(s)$ of applicable actions for each $s \in S$, together with
-		function $out(a) \subseteq O$ mapping each action to a set of outcomes
-		such that each outcome $o \in O$ belongs exactly to one action $act(o)$
-		and $\sum_{o \in out(a)} \Pr(o) = 1$ for all $a$
-\end{itemize}
-
-% depends if we should include this, what we tell about GOURMAND / RDDL...
-
-Besides a single or multiple goals, some planning problems also include a
-reward function: For every $s \in S$, $s' \in S$, and $a \in A(s)$,
-$R(s,a,s')$ is the reward function. The goal if the problem is to maximize
-the reward until a goal is reached. If a Finite Horizon (number of steps of the
-plan) is used, the goal of the problem is to achieve the highest reward within
-the horizon.
-
-A probabilistic planner takes the probabilistic planning problem as input and
-builds and outputs a plan for the problem.
-
-In this paper we use GOURMAND as a representative probabilistic planner, as
-it's the improved version of Glutton, the runner-up of the IPPC-11 competition.
-
+\subsection{Planning algorithms}
 \subsubsection{Replanning}
@@
 
-\begin{itemize}
-	\item Summarize shortcomings of the previous solutions
-	\item Describe the planning problem
-	\item Argument the choice for 2 current papers to analyze
-	\item Define how we would like to test the planning algorithms in a domain by our choice
-\end{itemize}
-
-\subsection{Planning problem}
-
-\begin{itemize}
-	\item Describe the MDP finite horizon planning problem (useful for modelling nearly infinite processes)
-	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
-	\item Describe reward heuristic
-	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest expected reward over H steps time
-	\item The challenge or large branching factors (induced by natural dynamic)
-\end{itemize}
+\subsubsection{Probabilstic planning}
+In this paper we use Gourmand as a representative probabilistic planner, as
+it's the improved version of Glutton, the runner-up of the IPPC-11 competition.
 
@@
 
+\section{Problem formulation}
+\begin{itemize}
+	\item Describe the MDP finite horizon planning problem (useful for modelling nearly infinite processes)
+	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
+	\item Describe reward heuristic
+	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest expected reward over H steps time
+	\item The challenge or large branching factors (induced by natural dynamic)
+	\item Summarize shortcomings of the previous solutions
+	\item Describe the planning problem
+	\item Argument the choice for 2 current papers to analyze
+	\item Define how we would like to test the planning algorithms in a domain by our choice
+\end{itemize}
+
+%---------------------------------------------------------------------
+
 \section{Planners}
+\label{sec:planners}
 

### 2014-03-30 FinalPaper/paper.tex
fixed mentioned typos

@@
 GOURMAND vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}.
-Prost however midly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
+Prost however mildly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
 

### 2014-03-30 FinalPaper/paper.tex
fixed typos
Real world for navigation

--- 2014-03-30 FinalPaper/paper.tex
@@
 
-\section{Background}
+\section{Problem Formulation}
 
-\subsection{Planning problems}
-\subsubsection{Classical Planning problems.
-} Planning is the process of computing several steps of a problem-solving procedure before executing any of them.
-In classical planning problems the environment is assumed to \emph{deterministic, observable and state}.
-Classical planning problems consists out of states, actions, conditions and a goal state and are solved using search and can be aided using heuristics.
-The planner tries to find a sequence of actions such that a goal or maximum reward is achieved.
+\subsection{Markov Decision Process}
 
-\subsubsection{Probabilistic Planning problems} 
-Real-World applications are far from deterministic, induced by natural dynamics and chance.
-To accomodate for Real-World domains probabilistic planning problems were introduced.
-These systems can be described using \emph{Markov Decision Processes} (MDPs) and can account for observable uncertainty.
-Probabilistic planning problems can be solved by evaluating iterations and creating policies to reach a goal state, either online or offline.
+\subsubsection{Goal-oriented MDPs}
 
-\subsection{Problem domains}
-\subsubsection{Goal-oriented MDPs.
-}The problems in IPPC-04 were specified using the Planning Domain Description Language (PPDLL).
-PPDDL specifies a probabistic planning problem as a set of probabilistic action sets and an initial and goal state description in which every action has a certain probability assigned to it \cite{FFReplan}.
-These MDPs are of the form $\mathit{M = (S, A, app, Pr, R)}$ where $\mathit{S}$ and $\mathit{A}$ are a finite set of states and actions, $\mathit{app(s)}$ is the set of all actions applicable in $\mathit{s}$.
-$\mathit{Pr}$ represents the probability of a state transaction $\mathit{(s, a, s')}$ for $\mathit{a}$ and $\mathit{R(s, a, s')}$ is the reward of applying $\mathit{a}$ to $\mathit{s}$ and generating $\mathit{s'}$ The planning problem is defined as a triple $\mathit{P = (M, s\textsubscript{0}, G, \rho)}$ where $\mathit{M = (S, A, app, Pr, R)}$ is an MDP, $\mathit{s\textsubscript{0} \in S}$ is the initial state, $\mathit{G \subseteq S}$ is the set of goal states and $\mathit{0 < \rho < 1}$ is a probability threshold \cite{teichteil2010incremental}.
+\subsubsection{MDP with Finite Horizon}
 
- The planners from IPPC-04 were evaluated on how many trials reached the goal per problem and the average number of actions selected when succesfull.
-These planning problems were however relatively easy to solve as they did not account for \emph{natural dynamics} and/or large branching factors that occur in more realtistic systems \cite{kolobov2012glutton}.
-FF-Replan \cite{FFReplan}, as specified in Section \ref{sec:planners} kindly remembered the committee of the IPPC-04 that the specified planning problems that contained no dead-ends were fairly easy to solve using relatively simple tools to handle with uncertainty.
+\subsection{Planners}
 
-\subsubsection{MDPs with Finite Horizon.
-}IPPC-11 decided to respond by introducing more realistic MDPs and their evaluation criteria by using MDPs with finite horizons.
-The planning problems are defined as tuples of the form \\ $\mathit{M\textsubscript{s0}(H) = \langle \langle S, A, T, R, s\textsubscript{0} \rangle , H \rangle }$ where $\mathit{S}$ s a finite set of states, $\mathit{A}$ a finite set of actions, $\mathit{T}$ is the transition function, similar to $\mathit{Pr}$ in the goal oriented MDP.
-$\mathit{R}$ represents the transitioning reward, $\mathit{s\textsubscript{0}}$ and $\mathit{H}$ is the number of decision epochs after which the process stops.
-Solving $\mathit{M(H)}$ means finding a policy for executing recommended state from the initial state over $\mathit{H}$ decision epochs \cite{kolobov2012gourmand}.
+\subsubsection{Classical Planners}
 
-Translating finite horizon MDPs to goal-oriented domains results ends up in all state $H$ steps away from $s\textsubscript{0}$ are goal states.
-The evaluation criteria in finite horizon MDPs is the \emph{expected reward} and not the probability of the policy reaching the goal states.
+A planner tries to find a sequence of actions such that a goal or maximum
+reward is achieved. A classical planning problem consists out of states,
+actions, conditions and a goal state.
 
-\subsection{Planning algorithms}
+\subsubsection{Probabilistic Planning} Classical Planners expect a
+deterministic world. For many Real World applications actions happen with a
+certain probability. This kind of Probabilistic Planning Problems can be
+described with Markov Decision Processes (MDPs). For the purpose of our
+analysis we define the problem as:
+
+\begin{itemize}
+	\item finite set of states $S$
+	\item an initial state $s_o \in S$
+	\item a $G \subseteq S$ of (absorbing) goal states
+	\item a set $O$ of outcomes; probability of $o \in O$ is $\Pr(o)$
+	\item a (total) deterministic transition function $T(o,s) \in S$ for all
+		outcomes $o \in O$ and states $s \in S$
+	\item sets $A(s)$ of applicable actions for each $s \in S$, together with
+		function $out(a) \subseteq O$ mapping each action to a set of outcomes
+		such that each outcome $o \in O$ belongs exactly to one action $act(o)$
+		and $\sum_{o \in out(a)} \Pr(o) = 1$ for all $a$
+\end{itemize}
+
+% depends if we should include this, what we tell about GOURMAND / RDDL...
+
+Besides a single or multiple goals, some planning problems also include a
+reward function: For every $s \in S$, $s' \in S$, and $a \in A(s)$,
+$R(s,a,s')$ is the reward function. The goal if the problem is to maximize
+the reward until a goal is reached. If a Finite Horizon (number of steps of the
+plan) is used, the goal of the problem is to achieve the highest reward within
+the horizon.
+
+A probabilistic planner takes the probabilistic planning problem as input and
+builds and outputs a plan for the problem.
+
+In this paper we use GOURMAND as a representative probabilistic planner, as
+it's the improved version of Glutton, the runner-up of the IPPC-11 competition.
+
 \subsubsection{Replanning}
@@
 
-\subsubsection{Probabilstic planning}
-In this paper we use Gourmand as a representative probabilistic planner, as
-it's the improved version of Glutton, the runner-up of the IPPC-11 competition.
+\begin{itemize}
+	\item Summarize shortcomings of the previous solutions
+	\item Describe the planning problem
+	\item Argument the choice for 2 current papers to analyze
+	\item Define how we would like to test the planning algorithms in a domain by our choice
+\end{itemize}
+
+\subsection{Planning problem}
+
+\begin{itemize}
+	\item Describe the MDP finite horizon planning problem (useful for modelling nearly infinite processes)
+	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
+	\item Describe reward heuristic
+	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest expected reward over H steps time
+	\item The challenge or large branching factors (induced by natural dynamic)
+\end{itemize}
 
@@
 
-\section{Problem formulation}
-\begin{itemize}
-	\item Describe the MDP finite horizon planning problem (useful for modelling nearly infinite processes)
-	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
-	\item Describe reward heuristic
-	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest expected reward over H steps time
-	\item The challenge or large branching factors (induced by natural dynamic)
-	\item Summarize shortcomings of the previous solutions
-	\item Describe the planning problem
-	\item Argument the choice for 2 current papers to analyze
-	\item Define how we would like to test the planning algorithms in a domain by our choice
-\end{itemize}
-
-%---------------------------------------------------------------------
-
 \section{Planners}
-\label{sec:planners}
 
@@
 
+\subsubsection{Navigation domain}
+
+In the navigation problem there can be a probability that the robot disappears
+after entering a cell. The disappearing action is a dead end. Disappearing here
+is a metaphor for the robot breaking down, or that it disappears from the radar
+with a base station. In many of such cases it's a big problem, but can be
+repaired with a high cost. In the navigation domain a step to another cell has
+a cost of 1. If instead of a dead end the cost is $n$ (e.g. 5) instead of 1,
+which represents the cost of repairing the robot, we remove dead ens, which
+makes it better for replanning planners.
+
 \subsection{Baseline test for Probabilistic Interesting domains}
@@
 
+\begin{itemize}
+	\item Describe the experiment setup
+	\item Show results for the experiment
+	\item Critically analyze the results
+	\item Compare with results from the original papers
+\end{itemize}
+
 %---------------------------------------------------------------------
@@
 
-\subsubsection{RFF}. Also uses an incremental plan aggregation, but offline similar to GLUTTON.
+\subsection{RFF}
 
-\subsubsection{PROST}
+\subsection{PROST}
 
-\subsubsection{FF-H+}
+\subsection{FF-H+}
+
+% Use related work to display the differences with own work
+
+\begin{itemize}
+	\item Discuss the related work and how their approaches are different
+	\item Discuss the other domains and why our domain adds anything to the community
+	\item Introduce the current state of the art papers that use deterministic approaches for probablistic domains dealing with uncertainty
+\end{itemize}
 

### 2014-03-30 FinalPaper/paper.tex
Improving navigation in real world

@@
 
-In the navigation problem there can be a probability that the robot disappears
-after entering a cell. The disappearing action is a dead end. Disappearing here
-is a metaphor for the robot breaking down, or that it disappears from the radar
-with a base station. In many of such cases it's a big problem, but can be
-repaired with a high cost. In the navigation domain a step to another cell has
-a cost of 1. If instead of a dead end the cost is $n$ (e.g. 5) instead of 1,
-which represents the cost of repairing the robot, we remove dead ens, which
-makes it better for replanning planners.
+In the navigation problem there is a chance that the robot disappears after
+entering a cell. The disappearing action is a dead end. Disappearing here is a
+metaphor for the robot breaking down, or that it disappears from the radar with
+the base station. In many of such cases it's a big problem, but can be repaired
+with a high cost. In the navigation domain a step to another cell has a cost of
+1. If instead of a dead end the cost is $n$ (e.g. 5) instead of 1, which
+represents the cost of repairing the robot, dead ends are removed. Without dead
+ends the problem becomes probabilistic uninteresting, which makes it suitable for
+replanning planners.
 

### 2014-03-30 FinalPaper/paper.tex
probabilistically interestingness

--- 2014-03-30 FinalPaper/paper.tex
@@
 \subsubsection{Replanning}
-
-An Replanning Planner takes a probabilistic problem and tries to solve it with
-replanning. First the problem is determinized, a compilation from a
-probabilistic problem to a deterministic problem. This deterministic problem
-be solved by a classical planner which returns a plan. The Replanner then
-executes the plan. If it ends up in a state which is different from the plan,
-it executes the classical planner to get a new plan. This is repeated until a
-goal is reached.
-
-In this paper we use FF-Replan as a representative replanning planner.
+A replanner is a planner that takes a problem as input, plans a state-action policy, executes it online and whenever it encounters a state that was not in its state-action policy, it takes the current state as starting state and plans again untill it has reached a goal or dead-end state.
+For our paper have chosen to evaluate FF-Replan \cite{FFReplan}, the winner of IPPC-04 and unenrolled winner of IPPC-06 as an inspiring, fairly simple planner that in our opinion is capable of employment in real-world domains.
 
 \subsubsection{Probabilstic planning}
-In this paper we use Gourmand as a representative probabilistic planner, as
-it's the improved version of Glutton, the runner-up of the IPPC-11 competition.
+Probabilistic planners are used to solve probabilistic planning problems and should be able to account for uncertainty as opposed to classical planners.
+For our evaluation we have choosen to compare FF-Replan to a state-of-the-art probabilistic planner: GOURMAND.
+GOURMAND is the online successor of the GLUTTON plan, a Labelled Real-Time Dynamic Programming (LRTDP) based planner and the runner up of IPPC-11.
 
 \subsection{Probabilistic Interestingness}
-
-Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
-Problems that fail this test were deemed to be classical planning problems in disguise, favouring using replanners\cite{little2007probvsreplan}.
-This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Compeitions.
-We will then translate the most interesting domains to a complete "real-world" domain and evaluate them using the probabilistically interesting baseline test.
-This paper concludes on evaluation both planners using the translated domains.
-
-The competitor FF-Replan\cite{FFReplan} remembered the committee of the IPPC in 2004 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
-The baseline test evaluates the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
-
-Following existing domains were said to be probabilistically interesting:
-
-\begin{itemize}
-	\item Drive
-	\item Exploding blocksworld
-	\item Pitchcatch
-	\item Schedule
-	\item Tireworld
-\end{itemize}
-
-A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties:
-
+After IPPC-06, a baseline test for \emph{probabilistically interesting} planning domains was proposed by Little and Thi\'ebauw \cite{little2007probvsreplan}.
+Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners.
+A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties \cite{little2007probvsreplan}:
 % reference little & thiebauw again. Maybe also shortly define what all o, n, act etc. are.
@@
 \end{itemize}
+
+%Following existing domains were said to be probabilistically interesting:
+%
+%\begin{itemize}
+%	\item Drive
+%	\item Exploding blocksworld
+%	\item Pitchcatch
+%	\item Schedule
+%	\item Tireworld
+%\end{itemize}
 

### 2014-03-30 FinalPaper/paper.tex

@@
 
+\section{Problem formulation}
+To evaluate FF-Replan and GOURMAND in a real world domain a finite horizon MDP is used to represent the realistic \emph{natural dynamics} such as external forces or forces of nature.
+These dynamics introduce large branching factors emphasizing the need for a planner to be scalable.
+To evaluate the model, the planner should also be sensitive to an expected reward maximization criterion.
+Current finite horizon MDP problems as introduced in IPPC-11 are simplified and therefor do not account for the rich set of state-actions as would be available in a real-world planning problem.
+We will reason about the most interesting domains for our evaluation and adjust them to match their real-world equivalent.
+Using the basline test introduced by Little et.
+all \cite{little2007probvsreplan}, we can evaluate the probabilistically interestingness of these domains and evaluate the performance of FF-Replan vs.
+a state of the art probabilistic planner: GOURMAND.
+
+%---------------------------------------------------------------------
+
 \section{Background}
@@
 %\end{itemize}
-
-%---------------------------------------------------------------------
-
-\section{Problem formulation}
-\begin{itemize}
-	\item Describe the MDP finite horizon planning problem (useful for modelling nearly infinite processes)
-	\item reason about the \emph{augmented state space} of M(H), which is a set \emph{S x (0, ... , H)} of state number of steps-to-go pairs
-	\item Describe reward heuristic
-	\item Solving M(H) means finding a policy: a rule for selecting actions in augmented states so that executing the actions recommended by the policy starting in the initial state will accumulate the largest expected reward over H steps time
-	\item The challenge or large branching factors (induced by natural dynamic)
-	\item Summarize shortcomings of the previous solutions
-	\item Describe the planning problem
-	\item Argument the choice for 2 current papers to analyze
-	\item Define how we would like to test the planning algorithms in a domain by our choice
-\end{itemize}
 

### 2014-03-30 FinalPaper/paper.tex

@@
 
+\subsubsection{Navigation domain}
+
+In the navigation problem there is a chance that the robot disappears after
+entering a cell. The disappearing action is a dead end. Disappearing here is a
+metaphor for the robot breaking down, or that it disappears from the radar with
+the base station. In many of such cases it's a big problem, but can be repaired
+with a high cost. In the navigation domain a step to another cell has a cost of
+1. If instead of a dead end the cost is $n$ (e.g. 5) instead of 1, which
+represents the cost of repairing the robot, dead ends are removed. Without dead
+ends the problem becomes probabilistic uninteresting, which makes it suitable for
+replanning planners.
+
 \subsection{Baseline test for Probabilistic Interesting domains}

### 2014-03-30 FinalPaper/paper.tex
Start real world traffic

@@
 \begin{abstract}
-	This paper argues that for many real life domains dead-ends are the end of
-	the world, and by for example human interaction the goal can still be
-	reached. By relaxing the definition of a dead-end, we argue that for many
-	real life domains a simpler planning algorithm, like FF-Replan, can be
-	sufficient, and that it's not needed to have newer and sophisticated
-	probabilistic planners.
+	In contrast to current demand for probabilistically interesting domains in the International Probabilistic Planning Competitions, this papier argues for using real-world appropriate domains.
+By relaxing the definition of a dead-end, we argue that for many
+real life domains a simpler planning algorithm can be sufficient and even better than sophisticated probabilistic planners.
+
+In this paper we evaluate the strength of FF-Replan, winner of IPPC-04 and unenrolled winner of IPPC-06, a replanner that uses the classical planner FF on a determinized probabilistic problem against a state of the art probabilistic planner GOURMAND, the successor of the Labelled Real-Time Dynamic Probabilistic planner Glutton, runner up of the IPPC-11.
+By translating the Navigation and Traffic domain from IPPC-11 to a matching real-world equivalent and evaluating these using the proposed probabilistically interesting baseline test as proposed by Little et.
+all we evaluate whether FF-Replan is in fact capable enough to solve enough of these so called classical planning problems in disguise.
 \end{abstract}
@@
 
-\begin{itemize}
-	\item Describe probabilistic planning problem
-	\item Introduce planning for uncertainty
-	\item Describe how deterministic classical planners can be used in probabilistic domains and motivate why this is interesting
-	\item Introduce the qualities of replanning and the second planning algorithm
-	\item Describe the need for a new domain for real world applications
-	\item Describe the goal and tools used to reach this goal
-\end{itemize}
+%\begin{itemize}
+%	\item Describe probabilistic planning problem
+%	\item Introduce planning for uncertainty
+%	\item Describe how deterministic classical planners can be used in probabilistic domains and motivate why this is interesting
+%	\item Introduce the qualities of replanning and the second planning algorithm
+%	\item Describe the need for a new domain for real world applications
+%	\item Describe the goal and tools used to reach this goal
+%\end{itemize}
 
@@
 We will reason about the most interesting domains for our evaluation and adjust them to match their real-world equivalent.
-Using the basline test introduced by Little et.
+Using the baseline test introduced by Little et.
 all \cite{little2007probvsreplan}, we can evaluate the probabilistically interestingness of these domains and evaluate the performance of FF-Replan vs.
@@
 Real-World applications are far from deterministic, induced by natural dynamics and chance.
-To accomodate for Real-World domains probabilistic planning problems were introduced.
+To accommodate for Real-World domains probabilistic planning problems were introduced.
 These systems can be described using \emph{Markov Decision Processes} (MDPs) and can account for observable uncertainty.
@@
 
- The planners from IPPC-04 were evaluated on how many trials reached the goal per problem and the average number of actions selected when succesfull.
-These planning problems were however relatively easy to solve as they did not account for \emph{natural dynamics} and/or large branching factors that occur in more realtistic systems \cite{kolobov2012glutton}.
+ The planners from IPPC-04 were evaluated on how many trials reached the goal per problem and the average number of actions selected when successful.
+These planning problems were however relatively easy to solve as they did not account for \emph{natural dynamics} and/or large branching factors that occur in more realistic systems \cite{kolobov2012glutton}.
 FF-Replan \cite{FFReplan}, as specified in Section \ref{sec:planners} kindly remembered the committee of the IPPC-04 that the specified planning problems that contained no dead-ends were fairly easy to solve using relatively simple tools to handle with uncertainty.
@@
 \subsubsection{Replanning}
-A replanner is a planner that takes a problem as input, plans a state-action policy, executes it online and whenever it encounters a state that was not in its state-action policy, it takes the current state as starting state and plans again untill it has reached a goal or dead-end state.
+A replanner is a planner that takes a problem as input, plans a state-action policy, executes it online and whenever it encounters a state that was not in its state-action policy, it takes the current state as starting state and plans again until it has reached a goal or dead-end state.
 For our paper have chosen to evaluate FF-Replan \cite{FFReplan}, the winner of IPPC-04 and unenrolled winner of IPPC-06 as an inspiring, fairly simple planner that in our opinion is capable of employment in real-world domains.
 
-\subsubsection{Probabilstic planning}
+\subsubsection{Probabilistic planning}
 Probabilistic planners are used to solve probabilistic planning problems and should be able to account for uncertainty as opposed to classical planners.
-For our evaluation we have choosen to compare FF-Replan to a state-of-the-art probabilistic planner: GOURMAND.
+For our evaluation we have chosen to compare FF-Replan to a state-of-the-art probabilistic planner: GOURMAND.
 GOURMAND is the online successor of the GLUTTON plan, a Labelled Real-Time Dynamic Programming (LRTDP) based planner and the runner up of IPPC-11.
@@
 
+At the first international probabilistic planning competition IPPC-04, most entries were Markov Decision Processes. The winner, FF-Replan, however was based on deterministic planning techniques.
+
+FF-Replan is an action selection algorithm for online planning in probabilistic domains.
+Given a domain description, a goal and an initial state as a probabilistic planning problem, FF-Replan generates a deterministic planning problem.
+It determinizes the input domain at the start of the planning into a deterministic different domain.
+They consider two methods of determinization:
+\begin{enumerate}
+\item \emph{Single-outcome determinization}: selects one outcome for each probabilistic construct using a variety of heuristics.
+The performance strongly depends on the methods for choosing the outcomes.
+\item \emph{All-outcomes determinization}: considers every probabilistic outcome as a distinct deterministic action.
+For each possible outcome FF-Replan generates one seperate action for each effect.
+For nested probabilities, the all-outcomes procedure is applied recursively.
+This implies that FF-Replan will cease selecting actions whenever it enters a dead state.
+However when given no information, all probabilistic effects will be considered as equal which is a potential weakness.
+\end{enumerate}
+
+After determinization FF-Replan then uses the deterministic FF planner to compute an ordered plan for the generated deterministic problem.
+This process is repeated when countering an unexpected state until a goal state is reached.
+It maintains a partial state-action mapping using a hash-table which is initially empty.
+Whenever FF-Replan encounters a state which is not in the table, it determinizes the problem and synthesizes a plan using FF.
+It then simulates the plan according to the deterministic action definitions resulting in a state-action sequence whose pairs are put in the hash table.
+The first action of the plan is then executed in the environment, returning a new state.
+This partial policy is this produces in an online fashion.
+It would be valuable to look into incremental planning approaches that don't create a deterministic plan from scratch whenever an unexpected state is encountered or reusing previous planning effort.
+
+FF-Replan has some obvious shortcomings as it first determinizes the input domain, removing all probabilistic information from the problem and then synthesizes a plan.
+If an unexpected state should occur whilst executing, the planner replans in the same determinization.
+It also does not consider multiple potential effects if an action.
+
+By relying on search, FF-Replan could function with enormous speed and efficiency.
+However when dealing with difficult probabilistic problems attempting to span the spectrum of complexity ranging from deterministic problems to highly stochastic problems, FF-Replan is expected to come short.
+Because FF-Replan is developed hoping to inspire extensions and insight into the approach and planning domains, the authors are hoping to achieve this.
+
 \subsection{GOURMAND}
 
-The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
+The IPPC-11 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
 For this reason planners needed to be scalable and sensitive to the expected reward maximization.
@@
 %---------------------------------------------------------------------
-During IPPC-2011 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT.
+During IPPC-11 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT.
 This caused to wonder whether LRTDP planners could outperform UCT based systems.
@@
 Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity.
-At the IPPC-2011 GLUTTON was an offline LRTDP based planner that came second.
+At the IPPC-11 GLUTTON was an offline LRTDP based planner that came second.
 As PROST employed UCT in an online manner, GOURMAND is an online adaptation of the GLUTTON algorithm to test whether LRTDP performs better if it is employed online.
@@
 It then checks if it can solve even for a larger lookahead L by taking away a small configuration time from future epochs  while still guaranteeing that it can solve for Lookahead L in each of them.
-This was GOURMAND adaptively picks a good lookahead value at each desicion epoch given the per-process constraint T.
+This was GOURMAND adaptively picks a good lookahead value at each decision epoch given the per-process constraint T.
 This can only be achieved by knowing how long it takes for LRTDP to solve a state for certain lookahead values.
@@
 
-\section{Domain Descriptions}
+\section{Domains}
 Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
 Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}.
-This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Compeitions.
+This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Competitions.
 These domains are evaluated for how well they portray real-world scenarios.
@@
 
-\subsection{IPPC-2011 Domains}
+\subsection{IPPC-11 Domains}
+
 The competitor FF-Replan \cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
-The baseline test of Little et.
-all evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
-IPPC-2011 responded by introducing more realistic MDPs and evluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
+The baseline test of Little et.\@ all evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
+IPPC-11 responded by introducing more realistic MDPs and evaluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
 
 GOURMAND vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}.
-Prost however mildly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
+PROST however mildly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
 
 \subsubsection{Navigation domain}
+
 The navigation domain represents a grid in which a robot must reach a goal.
-Every cell offers the robot a different chance of dissapearinng.
+Every cell offers the robot a different chance of disappearing.
 The robot needs to choose a path which gets it to the goal most reliably within the finite horizon time \cite{sanner2011navigation}.
@@
 
+\subsubsection{Traffic Domain}
+
+The traffic domain describes a crossroad with traffic lights, modelled as
+cells. Either the north to south road has a green light, the west to east road
+or all lights are red.
+
 \subsection{Baseline test for Probabilistic Interesting domains}
@@
 \section{Future Experiment}
+\label{sec:experiment}
+
+Experiments can empirically evaluate the performance of the adjusted domains.
 
@@
 
-\subsection{FF-Replan}
+The planning problems are taken from the IPPC-11 suite and are written in RDDL,
+which are publicity available. A domain consists of the domain description and
+instances of a domain problem. The domain description is read by RDDLSim, which
+is a server a planner can communicate with, and simulates the real world after
+the planner sends an action.
 
-\subsubsection{FF-Replan with Finite Horizon}
+\subsection{FF-Replan with Finite Horizon}
+
+Gourmand already works with RDDLSim and MDPs with finite horizon. The original
+FF-Replan is a Goal-Oriented MDP planner. For a Finite-Horizon each state at
+the horizon is a goal. To compare Gourmand, that works with MDP-FH, with
+FF-Replan, FF-Replan needs a slight update. It should not only execute FF for
+one goal, but for all goals at the horizon. It could then start executing the
+plan with the highest reward. Depending on the determinization method,
+\emph{single-outcomes} or \emph{all-outcomes}, not all goals might be
+reachable. Of course the performance decreases with an increase of goal states
+at the horizon. A hash-table cache, as FF-Replan already uses can still be used
+to store plans generated by FF from a state to goal states, however not only
+the plan should be stored, but also the reward for this plan should be stored
+to pick the plan with the highest expected reward.
+
+Using the framework of Glutton and Gourmand, and the FF heuristic found in mGPT
+\cite{bonet2011mgpt}, the updated FF-Replan can be implemented. The first step
+of Gourmand is parsing the problem and creating a structure of the problem.
+Instead of executing the Gourmand algorithm, this structure can be used to
+determinize the problem by setting all probabilities of each action to 1
+(\emph{all-outcome}) or all but one to 0 (\emph{single-outcome}). Using the
+FF heuristic it can find plans for each goal and calculate the expected reward.
+Then it can reuse the Gourmand framework to execute the plan by sending the
+action to the RDDLSim server. Like FF-Replan if the server returns with a state
+that is not in the plan the algorithm will replan. If a goal is reached it will
+output the achieved reward.
 
@@
 
-\subsubsection{RFF}. Also uses an incremental plan aggregation, but offline similar to GLUTTON.
+In sections above we have described the GOURMAND planner and FF-Replan as two
+probabilistic planners of the IPPC competition.
+RFF~\cite{teichteil2010incremental} is an offline planner that generates a
+policy: for each reachable state it determines a plan to the goal. Like
+FF-Replan it uses determinization and FF\. FF returns an initial plan from the
+initial state to a goal state. For each state in the plan the successor states
+are added to the structure, after which Monte-Carlo sampling is used. States
+where the probability that they're reached is too low (below a threshold) are
+removed. The successor states are used as initial states in the next step. If
+FF fails to find a plan to the goal from this new state, the state is removed
+from the structure too. Results showed that RFF outperformed other competitors.
+A higher threshold means that RFF will generate more policies that are prone to
+replanning.
 
@@
 
-\subsection{Probabilistic Planning via Determinization in Hindsight (2008)~\cite{yoon2008probabilistic}}
+%\subsection{Probabilistic Planning via Determinization in Hindsight (2008)~\cite{yoon2008probabilistic}}
+%
+%Hindsight optimization is an online technique that evaluates one-step-reachable
+%states by sampling future outcomes to generate multiple non-stationary planning
+%problems which are deterministic and can be used using search. It re-interprets
+%FF-Replan's~\cite{FFReplan} strategy randomly generating a set of non-stationary
+%determinized problems and combining their solutions.
 
-Hindsight optimization is an online technique that evaluates one-step-reachable
-states by sampling future outcomes to generate multiple non-stationary planning
-problems which are deterministic and can be used using search. It re-interprets
-FF-Replan's~\cite{FFReplan} strategy randomly generating a set of non-stationary
-determinized problems and combining their solutions.
+%\subsection{Improving Determinization in Hindsight for Online Probabilistic Planning (2010)~\cite{yoon2010improving}}
+%Hindsight optimization has enjoyed some success for online probabilistic
+%planning. Although it has proven to be effective for many domains, it is
+%computationally expensive. This paper presents significant improvements.  1) a
+%method for detecting potential useful actions, 2) exploit determinism in the
+%domain by reusing relevant plans, 2) improves action evaluation by increasing
+%the chance that at least one deterministic plan reaches a goal.
 
-\subsection{Improving Determinization in Hindsight for Online Probabilistic Planning (2010)~\cite{yoon2010improving}}
-Hindsight optimization has enjoyed some success for online probabilistic
-planning. Although it has proven to be effective for many domains, it is
-computationally expensive. This paper presents significant improvements.  1) a
-method for detecting potential useful actions, 2) exploit determinism in the
-domain by reusing relevant plans, 2) improves action evaluation by increasing
-the chance that at least one deterministic plan reaches a goal.
-
-\subsection{Probabilistic Planning in the Graphplan Framework (1999)~\cite{Blum99probabilisticplanning}}
-% might not be necessary?
-Graphplan is a successful planning algorithm for classical STRIPS domains. This
-paper explores the extend it can be used in \emph{probabilistic} domains. The
-paper discusses two variations of Graphplan: PGraphplan and TGraphplan.
-PGraphplan produces an optimal plan, while TGraphplan produces a sub-optimal
-plan but it has increased speed. By comparing the speed and quality of the
-two planners the authors are able to estimate how far they are from the ideal.
+%\subsection{Probabilistic Planning in the Graphplan Framework (1999)~\cite{Blum99probabilisticplanning}}
+%% might not be necessary?
+%Graphplan is a successful planning algorithm for classical STRIPS domains. This
+%paper explores the extend it can be used in \emph{probabilistic} domains. The
+%paper discusses two variations of Graphplan: PGraphplan and TGraphplan.
+%PGraphplan produces an optimal plan, while TGraphplan produces a sub-optimal
+%plan but it has increased speed. By comparing the speed and quality of the
+%two planners the authors are able to estimate how far they are from the ideal.
 
@@
 
-\subsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}
+%\subsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}
+%
+%For household robot planning, it appears easy, but actually involves
+%uncertainty. For tidying things up objects might not be there, or sensing
+%operations might tell things wrong. This paper looks into conditions for
+%classical planning in a replanning loop in order to solve nondeterministic
+%partially observable open domains This paper looks into conditions for
+%classical planning in a replanning loop in order to solve nondeterministic
+%partially observable open domains.
 
-For household robot planning, it appears easy, but actually involves
-uncertainty. For tidying things up objects might not be there, or sensing
-operations might tell things wrong. This paper looks into conditions for
-classical planning in a replanning loop in order to solve nondeterministic
-partially observable open domains This paper looks into conditions for
-classical planning in a replanning loop in order to solve nondeterministic
-partially observable open domains.
-
-\subsection{Progressive heuristic search for probabilistic planning based on interaction estimates (2013)~\cite{martin2013progressive}}
-
-In this paper a probabilistic plan graph heuristic is described which computes
-information about the interaction between actions and between propositions.
-This information is used to find better relaxed plans to compute the
-probability of success. This information guides a forward state space search
-for high probability, non-branching seed plans. These plans are then used in
-a planning and scheduling system that handles unexpected outcomes by runtime
-replanning.
+%\subsection{Progressive heuristic search for probabilistic planning based on interaction estimates (2013)~\cite{martin2013progressive}}
+%
+%In this paper a probabilistic plan graph heuristic is described which computes
+%information about the interaction between actions and between propositions.
+%This information is used to find better relaxed plans to compute the
+%probability of success. This information guides a forward state space search
+%for high probability, non-branching seed plans. These plans are then used in
+%a planning and scheduling system that handles unexpected outcomes by runtime
+%replanning.
 
@@
 \begin{itemize}
-	\item Conclude on the success of the 2 approaches
 	\item Conclude the work done in the paper

### 2014-03-30 FinalPaper/paper.tex
abstract changed

--- 2014-03-30 FinalPaper/paper.tex
@@
 \begin{abstract}
-	This paper argues that for many real life domains dead-ends are the end of
-	the world, and by for example human interaction the goal can still be
-	reached. By relaxing the definition of a dead-end, we argue that for many
-	real life domains a simpler planning algorithm, like FF-Replan, can be
-	sufficient, and that it's not needed to have newer and sophisticated
-	probabilistic planners.
+	In contrast to current demand for probabilistically interesting domains in the International Probabilistic Planning Competitions, this papier argues for using real-world appropriate domains.
+By relaxing the definition of a dead-end, we argue that for many
+real life domains a simpler planning algorithm can be sufficient and even better than sophisticated probabilistic planners.
+
+In this paper we evaluate the strength of FF-Replan, winner of IPPC-04 and unenrolled winner of IPPC-06, a replanner that uses the classical planner FF on a determinized probabistic problem against a state of the art probabilistic planner GOURMAND, the successor of the Labelled Real-Time Dynamic Probabilistic planner Glutton, runner up of the IPPC-11.
+By translating the Navigation and Traffic domain from IPPC-11 to a matching real-world equavalent and evaluating these using the proposed probabilistically interesting baseline test as proposed by Little et.
+all we will evaluate whether FF-Replan is in fact capable enough to solve enough of these so called classical planning problems in disguise.
 \end{abstract}

### 2014-03-30 FinalPaper/paper.tex
abstract changed

@@
 all evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
-IPPC-2011 responded by introducing more realistic MDPs and evluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
+IPPC-2011 responded by introducing more realistic MDPs and evaluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
 
 GOURMAND vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}.
-Prost however mildly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
+PROST however mildly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
 
 \subsubsection{Navigation domain}
+
 The navigation domain represents a grid in which a robot must reach a goal.
-Every cell offers the robot a different chance of dissapearinng.
+Every cell offers the robot a different chance of disappearing.
 The robot needs to choose a path which gets it to the goal most reliably within the finite horizon time \cite{sanner2011navigation}.

### 2014-03-30 FinalPaper/paper.tex
Spotted some more

@@
 \begin{abstract}
-	In contrast to current demand for probabilistically interesting domains in the International Probabilistic Planning Competitions, this papier argues for using real-world appropriate domains.
-By relaxing the definition of a dead-end, we argue that for many
-real life domains a simpler planning algorithm can be sufficient and even better than sophisticated probabilistic planners.
-
-In this paper we evaluate the strength of FF-Replan, winner of IPPC-04 and unenrolled winner of IPPC-06, a replanner that uses the classical planner FF on a determinized probabistic problem against a state of the art probabilistic planner GOURMAND, the successor of the Labelled Real-Time Dynamic Probabilistic planner Glutton, runner up of the IPPC-11.
-By translating the Navigation and Traffic domain from IPPC-11 to a matching real-world equavalent and evaluating these using the proposed probabilistically interesting baseline test as proposed by Little et.
-all we will evaluate whether FF-Replan is in fact capable enough to solve enough of these so called classical planning problems in disguise.
+	This paper argues that for many real life domains dead-ends are the end of
+	the world, and by for example human interaction the goal can still be
+	reached. By relaxing the definition of a dead-end, we argue that for many
+	real life domains a simpler planning algorithm, like FF-Replan, can be
+	sufficient, and that it's not needed to have newer and sophisticated
+	probabilistic planners.
 \end{abstract}
@@
 
-%\begin{itemize}
-%	\item Describe probabilistic planning problem
-%	\item Introduce planning for uncertainty
-%	\item Describe how deterministic classical planners can be used in probabilistic domains and motivate why this is interesting
-%	\item Introduce the qualities of replanning and the second planning algorithm
-%	\item Describe the need for a new domain for real world applications
-%	\item Describe the goal and tools used to reach this goal
-%\end{itemize}
+\begin{itemize}
+	\item Describe probabilistic planning problem
+	\item Introduce planning for uncertainty
+	\item Describe how deterministic classical planners can be used in probabilistic domains and motivate why this is interesting
+	\item Introduce the qualities of replanning and the second planning algorithm
+	\item Describe the need for a new domain for real world applications
+	\item Describe the goal and tools used to reach this goal
+\end{itemize}
 

### 2014-03-30 FinalPaper/paper.tex
oude deel ff replan gebruikt, later dan maar inkorten

--- 2014-03-30 FinalPaper/paper.tex
@@
 
+At the first international probabilistic planning competition IPPC-04, most entries were Markov Decision Processes. The winner, FF-Replan, however was based on deterministic planning techniques.
+
+FF-Replan is an action selection algorithm for online planning in probabilistic domains.
+Given a domain description, a goal and an initial state as a probabilistic planning problem, FF-Replan generates a deterministic planning problem.
+It determinizes the input domain at the start of the planning into a deterministic different domain.
+They consider two methods of determinization:
+\begin{enumerate}
+\item \emph{Single-outcome determinization}: selects one outcome for each probabilistic construct using a variety of heuristics.
+The performance strongly depends on the methods for choosing the outcomes.
+\item \emph{All-outcomes determinization}: considers every probabilistic outcome as a distinct deterministic action.
+For each possible outcome FF-Replan generates one seperate action for each effect.
+For nested probabilities, the all-outcomes procedure is applied recursively.
+This implies that FF-Replan will cease selecting actions whenever it enters a dead state.
+However when given no information, all probabilistic effects will be considered as equal which is a potential weakness.
+\end{enumerate}
+
+After determinization FF-Replan then uses the deterministic FF planner to compute an ordered plan for the generated deterministic problem.
+This process is repeated when countering an unexpected state until a goal state is reached.
+It maintains a partial state-action mapping using a hash-table which is initially empty.
+Whenever FF-Replan encounters a state which is not in the table, it determinizes the problem and synthesizes a plan using FF.
+It then simulates the plan according to the deterministic action definitions resulting in a state-action sequence whose pairs are put in the hash table.
+The first action of the plan is then executed in the environment, returning a new state.
+This partial policy is this produces in an online fashion.
+It would be valuable to look into incremental planning approaches that don't create a deterministic plan from scratch whenever an unexpected state is encountered or reusing previous planning effort.
+
+FF-Replan has some obvious shortcomings as it first determinizes the input domain, removing all probabilistic information from the problem and then synthesizes a plan.
+If an unexpected state should occur whilst executing, the planner replans in the same determinization.
+It also does not consider multiple potential effects if an action.
+
+By relying on search, FF-Replan could function with enormous speed and efficiency.
+However when dealing with difficult probabilistic problems attempting to span the spectrum of complexity ranging from deterministic problems to highly stochastic problems, FF-Replan is expected to come short.
+Because FF-Replan is developed hoping to inspire extensions and insight into the approach and planning domains, the authors are hoping to achieve this.
+
 \subsection{GOURMAND}
@@
 
-\section{Domain Descriptions}
+\section{Domains}
 Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
@@
 \section{Future Experiment}
+\label{sec:experiment}
 

### 2014-03-30 FinalPaper/paper.tex
oude deel ff replan gebruikt, later dan maar inkorten

@@
 Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}.
-This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Compeitions.
+This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Competitions.
 These domains are evaluated for how well they portray real-world scenarios.

### 2014-03-30 FinalPaper/paper.tex

@@
 
+Experiments can empirically evaluate the performance of the adjusted domains.
+
 \subsection{Setup}
 
-\subsection{FF-Replan}
+The planning problems are taken from the IPPC-11 suite and are written in RDDL,
+which are publicity available. A domain consists of the domain description and
+instances of a domain problem. The domain description is read by RDDLSim, which
+is a server a planner can communicate with, and simulates the real world after
+the planner sends an action.
 
-\subsubsection{FF-Replan with Finite Horizon}
+\subsection{FF-Replan with Finite Horizon}
+
+Gourmand already works with RDDLSim and MDPs with finite horizon. The original
+FF-Replan is a Goal-Oriented MDP planner. For a Finite-Horizon each state at
+the horizon is a goal. To compare Gourmand, that works with MDP-FH, with
+FF-Replan, FF-Replan needs a slight update. It should not only execute FF for
+one goal, but for all goals at the horizon. It could then start executing the
+plan with the highest reward. Depending on the determinization method,
+\emph{single-outcomes} or \emph{all-outcomes}, not all goals might be
+reachable. Of course the performance decreases with an increase of goal states
+at the horizon. A hash-table cache, as FF-Replan already uses can still be used
+to store plans generated by FF from a state to goal states, however not only
+the plan should be stored, but also the reward for this plan should be stored
+to pick the plan with the highest expected reward.
+
+Using the framework of Glutton and Gourmand, and the FF heuristic found in mGPT
+\cite{bonet2011mgpt}, the updated FF-Replan can be implemented. The first step
+of Gourmand is parsing the problem and creating a structure of the problem.
+Instead of executing the Gourmand algorithm, this structure can be used to
+determinize the problem by setting all probabilities of each action to 1
+(\emph{all-outcome}) or all but one to 0 (\emph{single-outcome}). Using the
+FF heuristic it can find plans for each goal and calculate the expected reward.
+Then it can reuse the Gourmand framework to execute the plan by sending the
+action to the RDDLSim server. Like FF-Replan if the server returns with a state
+that is not in the plan the algorithm will replan. If a goal is reached it will
+output the achieved reward.
 

### 2014-03-30 FinalPaper/paper.tex
Fix small errors

@@
 
-In this paper we evaluate the strength of FF-Replan, winner of IPPC-04 and unenrolled winner of IPPC-06, a replanner that uses the classical planner FF on a determinized probabistic problem against a state of the art probabilistic planner GOURMAND, the successor of the Labelled Real-Time Dynamic Probabilistic planner Glutton, runner up of the IPPC-11.
-By translating the Navigation and Traffic domain from IPPC-11 to a matching real-world equavalent and evaluating these using the proposed probabilistically interesting baseline test as proposed by Little et.
-all we will evaluate whether FF-Replan is in fact capable enough to solve enough of these so called classical planning problems in disguise.
+In this paper we evaluate the strength of FF-Replan, winner of IPPC-04 and unenrolled winner of IPPC-06, a replanner that uses the classical planner FF on a determinized probabilistic problem against a state of the art probabilistic planner GOURMAND, the successor of the Labelled Real-Time Dynamic Probabilistic planner Glutton, runner up of the IPPC-11.
+By translating the Navigation and Traffic domain from IPPC-11 to a matching real-world equivalent and evaluating these using the proposed probabilistically interesting baseline test as proposed by Little et.
+all we evaluate whether FF-Replan is in fact capable enough to solve enough of these so called classical planning problems in disguise.
 \end{abstract}

### 2014-03-30 FinalPaper/paper.tex
Little more about the traffic domain

@@
 
-The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
+The IPPC-11 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
 For this reason planners needed to be scalable and sensitive to the expected reward maximization.
@@
 
-\subsection{IPPC-2011 Domains}
+\subsection{IPPC-11 Domains}
 
 The competitor FF-Replan \cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
-The baseline test of Little et.
-all evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
-IPPC-2011 responded by introducing more realistic MDPs and evaluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
+The baseline test of Little et.\@ all evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
+IPPC-11 responded by introducing more realistic MDPs and evaluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
 
@@
 Because of the binary variables and no intermediate variable restrictions, this model is simplified and ignores traffic aspects such as turns and turn probabilities.
-This model also uses concurrent actions and the total actions has an upperbound of 2\textsuperscript{ (\# of intersections)}.
+This model also uses concurrent actions and the total actions has an upper bound of $2^{\#~of~intersections}$.
 
@@
 replanning planners.
+
+\subsubsection{Traffic Domain}
+
+The traffic domain describes a crossroad with traffic lights, modelled as
+cells. Either the north to south road has a green light, the west to east road
+or all lights are red. The model uses a finite state machine that handles the
+lights so that the lights are never green at the same time. This would be the
+only dangerous situation on the crossroad. The difficulty in this domain is
+the number of states, which grows exponentially with the number of cells.
+Besides that it is an uninteresting probabilistic problem because it does
+not satisfy the probabilistic interesting test.
 

### 2014-04-07 FinalPaper/paper.tex
RFF related work

--- 2014-03-30 FinalPaper/paper.tex
@@
 Because of the binary variables and no intermediate variable restrictions, this model is simplified and ignores traffic aspects such as turns and turn probabilities.
-This model also uses concurrent actions and the total actions has an upper bound of $2^{\#~of~intersections}$.
+This model also uses concurrent actions and the total actions has an upperbound of 2\textsuperscript{ (\# of intersections)}.
 
@@
 replanning planners.
-
-\subsubsection{Traffic Domain}
-
-The traffic domain describes a crossroad with traffic lights, modelled as
-cells. Either the north to south road has a green light, the west to east road
-or all lights are red. The model uses a finite state machine that handles the
-lights so that the lights are never green at the same time. This would be the
-only dangerous situation on the crossroad. The difficulty in this domain is
-the number of states, which grows exponentially with the number of cells.
-Besides that it is an uninteresting probabilistic problem because it does
-not satisfy the probabilistic interesting test.
 

### 2014-04-07 FinalPaper/paper.tex
adjusted ff-replan

--- 2014-03-30 FinalPaper/paper.tex
@@
 % first the title is needed
-\title{Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains}
+\title{Realistically Interesting Domains for Probabilistic Planners}
 
 % a short form should be given in case it is too long for the running head
-\titlerunning{FF-Replan vs Probabilistic Planner in Real World Domains}
+\titlerunning{Real World Domains}
 
@@
 
-\section{Planners}
+\section{FF-Replan}
 \label{sec:planners}
 
-\subsection{FF-Replan}
+At the first international probabilistic planning competition IPPC-04, most entries were probabilistic planner using Markov Decision Processes.
+The winner, FF-Replan \cite{FFReplan}, however was based on deterministic planning techniques.
+FF-Replan is an action selection algorithm for online planning in probabilistic domains which deals with uncertainty by replanning.
+FF-Replan generates a deterministic planning problem by determinizing the input domain at the start of the planning.
+This classical deterministic planning problem allows for the use of the classical FF planner \cite{Hoffmann01theff}.
+The FF planner then returns an ordered state-action plan for the deterministic problem of the current state mapped in an initially empty hash-table.
+This plan is executed until an unexpected state, not available in the hash-table is encountered.
 
-At the first international probabilistic planning competition IPPC-04, most entries were Markov Decision Processes. The winner, FF-Replan, however was based on deterministic planning techniques.
+If an unexpected state is encountered, the current state, the goal and the domain description are again determinized.
+The FF planner will generate an ordered plan which is executed until either a goal state, a dead-end state or an unexpected state is reached.
 
-FF-Replan is an action selection algorithm for online planning in probabilistic domains.
-Given a domain description, a goal and an initial state as a probabilistic planning problem, FF-Replan generates a deterministic planning problem.
-It determinizes the input domain at the start of the planning into a deterministic different domain.
-They consider two methods of determinization:
-\begin{enumerate}
-\item \emph{Single-outcome determinization}: selects one outcome for each probabilistic construct using a variety of heuristics.
-The performance strongly depends on the methods for choosing the outcomes.
-\item \emph{All-outcomes determinization}: considers every probabilistic outcome as a distinct deterministic action.
-For each possible outcome FF-Replan generates one seperate action for each effect.
-For nested probabilities, the all-outcomes procedure is applied recursively.
-This implies that FF-Replan will cease selecting actions whenever it enters a dead state.
-However when given no information, all probabilistic effects will be considered as equal which is a potential weakness.
-\end{enumerate}
-
-After determinization FF-Replan then uses the deterministic FF planner to compute an ordered plan for the generated deterministic problem.
-This process is repeated when countering an unexpected state until a goal state is reached.
-It maintains a partial state-action mapping using a hash-table which is initially empty.
-Whenever FF-Replan encounters a state which is not in the table, it determinizes the problem and synthesizes a plan using FF.
-It then simulates the plan according to the deterministic action definitions resulting in a state-action sequence whose pairs are put in the hash table.
-The first action of the plan is then executed in the environment, returning a new state.
-This partial policy is this produces in an online fashion.
-It would be valuable to look into incremental planning approaches that don't create a deterministic plan from scratch whenever an unexpected state is encountered or reusing previous planning effort.
-
-FF-Replan has some obvious shortcomings as it first determinizes the input domain, removing all probabilistic information from the problem and then synthesizes a plan.
-If an unexpected state should occur whilst executing, the planner replans in the same determinization.
-It also does not consider multiple potential effects if an action.
-
-By relying on search, FF-Replan could function with enormous speed and efficiency.
-However when dealing with difficult probabilistic problems attempting to span the spectrum of complexity ranging from deterministic problems to highly stochastic problems, FF-Replan is expected to come short.
-Because FF-Replan is developed hoping to inspire extensions and insight into the approach and planning domains, the authors are hoping to achieve this.
-
-\subsection{GOURMAND}
-
-The IPPC-11 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
-For this reason planners needed to be scalable and sensitive to the expected reward maximization.
-Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP $M(H)$ for a smaller horizon $h$.
-Incrementally solving the sequence $M(1)$, $M(2)$ forms the basis of LR\textsuperscript{2}TDP\@.
-By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full).
-The max-reward heuristic finds the largest horizon value $h'$ for which already a heuristic value $V$ is estimated.
-The  computation time remains much lower because it runs quickly into states that converged while solving $M(h-1)$.
-The max-reward computation relies on knowing the maximum $R_{max}$ any action can yield in any state or an upper bound on it.
-
-\subsubsection{LRTDP}
-Using goal oriented MDPs, the \emph{Labelled Real-Time Dynamic Programmer} (LRTDP) operates a series of trials starting from $s_0$.
-
-\begin{itemize}
-	\item Trials start at $s_0$
-	\item Choose best action greedily in the current state based on current $V$
-	\item Perform  Bellman backup on the current state
-	\item Sample the outcome as the chosen action
-	\item Transition to the new state
-	\item Repeat until a goal, dead end or converged state is reached
-	\item After trial, special convergence check on all states in the trial is performed to prove the convergence of these values
-\end{itemize}
-
-\subsubsection{LRTDP-FH}
-
-Adapting LRTDP to a finite horizon MDP \emph{M(H)} requires to let each trial start at ($s_0$) and run for at most H time steps.
-A steps $H$ steps away from $s_0$ would translate to goals in a goal-oriented MDP.
-However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.
-
-\subsubsection{LR\textsuperscript{2}TDP}
-
-LR\textsuperscript{2}TDP uses \emph{reverse iterative deepening} and LRTDP-FH to solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$, in that order.
-It first decides how to act optimally in ($s_0$, 1), equivalent to solving M(1) , then ($s_0$, 2), equivalent to solving $M(2)$, eventually solving $M(H)$ or running out of time halting a $M(h')$ where $h' < H$.
-This incremental effort allows for reusing state values computed in previous states, so it memorizes all values and solves for smaller horizons by backchaining from the goal LRTDP-FH iterates over search depth while LR\textsuperscript{2}TDP iterates over the distance from the horizon and is likely to be better because:
-
-\begin{itemize}
-	\item In many MDPs, the optimal policy $M(h)$ for some $h < H$ is near optimal for M(H), it thus may have a solution when stopped prematurely
-	\item it's trials are very short because backchaining from the goal leads to a lots of convergence
-	\item It optimally memorizes a large fraction of augmented states to save memory
-	\item a large fraction of state space may be unreachable from $s_0$ and it avoid storing information it does not need
-	\item it should however use a heuristic to treat states that has never been encountered when stopped prematurely, could be a fall back or a default action.
-\end{itemize}
-
-\subsubsection{GLUTTON}
-
-Glutton uses the \emph{Max-Reward} heuristic that relies on knowing the maximum reward $R_{max}$ any action can yield in a state or an upper bound on it.
-Large branching factors induce that the computation of the Bellman Backups becomes prohibitively expensive.
-Glutton uses the following mechanisms to optimize for large branching factors:
-
-\begin{itemize}
-	\item Subsampling the transition function, is not enough to decrease the amount of computations yet
-	\item Separating out Natural Dynamics: to reuse variable samples when generator successors for multiple actions, by separating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both.
-	\item Caching the transition function samples: as LR\textsuperscript{2}TDP populates the state-value hash table lazily, Glutton uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same $(s,h)$ pair.
-When full, it chooses state-action pars for eviction ans replacement randomly.
-	\item Default policies: Glutton uses 3 tricks to determine a policy when stopped prematurely.
-It compares the optimal action from a $h'$ with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.
-\end{itemize}
-%---------------------------------------------------------------------
-During IPPC-11 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT.
-This caused to wonder whether LRTDP planners could outperform UCT based systems.
-UCT forces an expert to guess a non-shortsighted lookahead value for which it should be able to converge on encountered states.
-Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity.
-At the IPPC-11 GLUTTON was an offline LRTDP based planner that came second.
-As PROST employed UCT in an online manner, GOURMAND is an online adaptation of the GLUTTON algorithm to test whether LRTDP performs better if it is employed online.
-
-UCT picks an action based on it current quality estimate and an \emph{exploration term} which forces the planner to choose actions that have rarely been tried in the past.
-This makes UCT suitable for a wider scale of scenarios but also implies an unreliable termination condition.
-
-Because real world domains contain Natural Dynamics that introduce large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of state the planner may never reach in a lifetime.
-Such problems are far better solved using online planners by finding a $\tau$* or an approximation for the current state, executing it and repeating.
-This is done by choosing a certain lookahead  L and solving MDP \emph{M\textsubscript{s}(L)} to solve \emph{M\textsubscript{0}(H)} where L $<$ H and then select \emph{$\pi$*\textsubscript{L}(s, L)} recommended by the optimal policy.
-This lookahead value is determined using the per-process time constraint.
-
-\subsubsection{GOURMAND}
-In contrast to GLUTTON, GOURMAND always makes an informed choice in any state where it ends up when the time T allocated for solving the MDP runs out because of the online fashion it uses LRTDP.
-GOURMAND first divides the time among all remaining epochs, determines the largest lookahead L for which it can almost certainly solve any remaining epoch if T is assigned.
-It then checks if it can solve even for a larger lookahead L by taking away a small configuration time from future epochs  while still guaranteeing that it can solve for Lookahead L in each of them.
-This was GOURMAND adaptively picks a good lookahead value at each decision epoch given the per-process constraint T.
-This can only be achieved by knowing how long it takes for LRTDP to solve a state for certain lookahead values.
-It uses LR\textsuperscript{2}TDP to collect this data.
-This version of LRTDP is more efficient because of the early convergences and it allows measuring how long on average the solving of a task takes.
-GOURMAND uses the same engineering optimizations to to handle evaluate actions, iterating over the successors of s under a by the Bellman Backups.
-GOURMAND eventually outperforms both GLUTTON and PROST, the winner of the IPPC-11\cite{keller2012prost}.
+FF-Replan has some obvious shortcomings.Iit first determinizes the input domain and thus removes all probabilistic information from the problem.
+The success of the planner is therefore fully reliable on the chose determinization heuristic.
+As FF-replan uses no roll-out policy or future simulation, it has no way of avoiding \emph{avoidable} dead-ends.
+This explains why FF-replan performs poorly in domains containing dead-ends.
+However, by relying on search FF-replan functions with enormous speed and efficiency and caused the International Conference on Automated Planning and Scheduling (ICAPS) to change their benchmarks to increase their \emph{probabilistically interestingness}.
+By evaluating and correcting the IPPC-11 domains on their \emph{realistically interestingness} we will draw conclusions whether or not these adjusted realistic domains are actually classical planning problems in disguise - ideal planning problems for FF-replan.
 
@@
 \section{Domains}
+
+% TODO we only look at IPPC-11 domains
 Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
@@
 
-\subsubsection{Navigation domain}
+\subsubsection{Navigation}
 
@@
 
-\subsubsection{Traffic domain}
+\subsubsection{Traffic}
 This domain represents a simple binary version of the cell transition model (CTM) for modelling traffic based on the original CTM Tech Report \cite{sanner2011traffic}.
@@
 %ADD IMAGE HERE
+
+\subsection{Elevators}
+
+In the elevators domain there are a number of elevators delivering passengers
+to either the top or bottom floor. Potential passengers arrive at any floor at
+a certain rate (depending on which floor). The elevators can only move in the
+direction it is indicating, so passengers know whether to board or not. The
+goal of the elevators is to transport as many as possible passengers to their
+destinations.
+
+\subsection{SysAdmin}
+
+The SysAdmin domain describes a network of connected servers. Each server has
+a probability that it shuts down, and if is not running, it has a probability
+to reboot. The probability that a server shuts down depends on the number of
+running connected servers.
 
@@
 
-\subsection{Real-World evaluation}
+\subsection{Real-World Domain Evaluation}
 
-\subsubsection{Navigation domain}
+\subsubsection{Navigation}
 
@@
 
-\subsubsection{Traffic Domain}
+\subsubsection{Traffic}
 
@@
 not satisfy the probabilistic interesting test.
+
+\subsubsection{Elevators}
 
@@
 
+%----------------------------------------------------------------------------------------
+
+\subsection{GOURMAND}
+
+The IPPC-11 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
+For this reason planners needed to be scalable and sensitive to the expected reward maximization.
+Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP $M(H)$ for a smaller horizon $h$.
+Incrementally solving the sequence $M(1)$, $M(2)$ forms the basis of LR\textsuperscript{2}TDP\@.
+By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full).
+The max-reward heuristic finds the largest horizon value $h'$ for which already a heuristic value $V$ is estimated.
+The  computation time remains much lower because it runs quickly into states that converged while solving $M(h-1)$.
+The max-reward computation relies on knowing the maximum $R_{max}$ any action can yield in any state or an upper bound on it.
+
+\subsubsection{LRTDP}
+Using goal oriented MDPs, the \emph{Labelled Real-Time Dynamic Programmer} (LRTDP) operates a series of trials starting from $s_0$.
+
+\begin{itemize}
+	\item Trials start at $s_0$
+	\item Choose best action greedily in the current state based on current $V$
+	\item Perform  Bellman backup on the current state
+	\item Sample the outcome as the chosen action
+	\item Transition to the new state
+	\item Repeat until a goal, dead end or converged state is reached
+	\item After trial, special convergence check on all states in the trial is performed to prove the convergence of these values
+\end{itemize}
+
+\subsubsection{LRTDP-FH}
+
+Adapting LRTDP to a finite horizon MDP \emph{M(H)} requires to let each trial start at ($s_0$) and run for at most H time steps.
+A steps $H$ steps away from $s_0$ would translate to goals in a goal-oriented MDP.
+However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.
+
+\subsubsection{LR\textsuperscript{2}TDP}
+
+LR\textsuperscript{2}TDP uses \emph{reverse iterative deepening} and LRTDP-FH to solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$, in that order.
+It first decides how to act optimally in ($s_0$, 1), equivalent to solving M(1) , then ($s_0$, 2), equivalent to solving $M(2)$, eventually solving $M(H)$ or running out of time halting a $M(h')$ where $h' < H$.
+This incremental effort allows for reusing state values computed in previous states, so it memorizes all values and solves for smaller horizons by backchaining from the goal LRTDP-FH iterates over search depth while LR\textsuperscript{2}TDP iterates over the distance from the horizon and is likely to be better because:
+
+\begin{itemize}
+	\item In many MDPs, the optimal policy $M(h)$ for some $h < H$ is near optimal for M(H), it thus may have a solution when stopped prematurely
+	\item it's trials are very short because backchaining from the goal leads to a lots of convergence
+	\item It optimally memorizes a large fraction of augmented states to save memory
+	\item a large fraction of state space may be unreachable from $s_0$ and it avoid storing information it does not need
+	\item it should however use a heuristic to treat states that has never been encountered when stopped prematurely, could be a fall back or a default action.
+\end{itemize}
+
+\subsubsection{GLUTTON}
+
+Glutton uses the \emph{Max-Reward} heuristic that relies on knowing the maximum reward $R_{max}$ any action can yield in a state or an upper bound on it.
+Large branching factors induce that the computation of the Bellman Backups becomes prohibitively expensive.
+Glutton uses the following mechanisms to optimize for large branching factors:
+
+\begin{itemize}
+	\item Subsampling the transition function, is not enough to decrease the amount of computations yet
+	\item Separating out Natural Dynamics: to reuse variable samples when generator successors for multiple actions, by separating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both.
+	\item Caching the transition function samples: as LR\textsuperscript{2}TDP populates the state-value hash table lazily, Glutton uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same $(s,h)$ pair.
+When full, it chooses state-action pars for eviction ans replacement randomly.
+	\item Default policies: Glutton uses 3 tricks to determine a policy when stopped prematurely.
+It compares the optimal action from a $h'$ with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.
+\end{itemize}
+%---------------------------------------------------------------------
+During IPPC-11 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT.
+This caused to wonder whether LRTDP planners could outperform UCT based systems.
+UCT forces an expert to guess a non-shortsighted lookahead value for which it should be able to converge on encountered states.
+Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity.
+At the IPPC-11 GLUTTON was an offline LRTDP based planner that came second.
+As PROST employed UCT in an online manner, GOURMAND is an online adaptation of the GLUTTON algorithm to test whether LRTDP performs better if it is employed online.
+
+UCT picks an action based on it current quality estimate and an \emph{exploration term} which forces the planner to choose actions that have rarely been tried in the past.
+This makes UCT suitable for a wider scale of scenarios but also implies an unreliable termination condition.
+
+Because real world domains contain Natural Dynamics that introduce large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of state the planner may never reach in a lifetime.
+Such problems are far better solved using online planners by finding a $\tau$* or an approximation for the current state, executing it and repeating.
+This is done by choosing a certain lookahead  L and solving MDP \emph{M\textsubscript{s}(L)} to solve \emph{M\textsubscript{0}(H)} where L $<$ H and then select \emph{$\pi$*\textsubscript{L}(s, L)} recommended by the optimal policy.
+This lookahead value is determined using the per-process time constraint.
+
+\subsubsection{GOURMAND}
+In contrast to GLUTTON, GOURMAND always makes an informed choice in any state where it ends up when the time T allocated for solving the MDP runs out because of the online fashion it uses LRTDP.
+GOURMAND first divides the time among all remaining epochs, determines the largest lookahead L for which it can almost certainly solve any remaining epoch if T is assigned.
+It then checks if it can solve even for a larger lookahead L by taking away a small configuration time from future epochs  while still guaranteeing that it can solve for Lookahead L in each of them.
+This was GOURMAND adaptively picks a good lookahead value at each decision epoch given the per-process constraint T.
+This can only be achieved by knowing how long it takes for LRTDP to solve a state for certain lookahead values.
+It uses LR\textsuperscript{2}TDP to collect this data.
+This version of LRTDP is more efficient because of the early convergences and it allows measuring how long on average the solving of a task takes.
+GOURMAND uses the same engineering optimizations to to handle evaluate actions, iterating over the successors of s under a by the Bellman Backups.
+GOURMAND eventually outperforms both GLUTTON and PROST, the winner of the IPPC-11\cite{keller2012prost}.
+
 %---------------------------------------------------------------------

### 2014-04-07 FinalPaper/paper.tex
adjusted ff-replan

@@
 \section{Domains}
-
-% TODO we only look at IPPC-11 domains
 Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
@@
 
-\subsubsection{Navigation}
+\subsubsection{Navigation domain}
 
@@
 
-\subsubsection{Traffic}
+\subsubsection{Traffic domain}
 This domain represents a simple binary version of the cell transition model (CTM) for modelling traffic based on the original CTM Tech Report \cite{sanner2011traffic}.
 Because of the binary variables and no intermediate variable restrictions, this model is simplified and ignores traffic aspects such as turns and turn probabilities.
-This model also uses concurrent actions and the total actions has an upper bound of $2^{\#~of~intersections}$.
+This model also uses concurrent actions and the total actions has an upperbound of 2\textsuperscript{ (\# of intersections)}.
 
 %ADD IMAGE HERE
-
-\subsection{Elevators}
-
-In the elevators domain there are a number of elevators delivering passengers
-to either the top or bottom floor. Potential passengers arrive at any floor at
-a certain rate (depending on which floor). The elevators can only move in the
-direction it is indicating, so passengers know whether to board or not. The
-goal of the elevators is to transport as many as possible passengers to their
-destinations.
-
-\subsection{SysAdmin}
-
-The SysAdmin domain describes a network of connected servers. Each server has
-a probability that it shuts down, and if is not running, it has a probability
-to reboot. The probability that a server shuts down depends on the number of
-running connected servers.
 
@@
 
-\subsection{Real-World Domain Evaluation}
+\subsection{Real-World evaluation}
 
-\subsubsection{Navigation}
+\subsubsection{Navigation domain}
 
@@
 replanning planners.
-
-\subsubsection{Traffic}
-
-The traffic domain describes a crossroad with traffic lights, modelled as
-cells. Either the north to south road has a green light, the west to east road
-or all lights are red. The model uses a finite state machine that handles the
-lights so that the lights are never green at the same time. This would be the
-only dangerous situation on the crossroad. The difficulty in this domain is
-the number of states, which grows exponentially with the number of cells.
-Besides that it is an uninteresting probabilistic problem because it does
-not satisfy the probabilistic interesting test.
-
-\subsubsection{Elevators}
 
@@
 
-In sections above we have described the GOURMAND planner and FF-Replan as two
-probabilistic planners of the IPPC competition.
-RFF~\cite{teichteil2010incremental} is an offline planner that generates a
-policy: for each reachable state it determines a plan to the goal. Like
-FF-Replan it uses determinization and FF\. FF returns an initial plan from the
-initial state to a goal state. For each state in the plan the successor states
-are added to the structure, after which Monte-Carlo sampling is used. States
-where the probability that they're reached is too low (below a threshold) are
-removed. The successor states are used as initial states in the next step. If
-FF fails to find a plan to the goal from this new state, the state is removed
-from the structure too. Results showed that RFF outperformed other competitors.
-A higher threshold means that RFF will generate more policies that are prone to
-replanning.
+\subsubsection{RFF}. Also uses an incremental plan aggregation, but offline similar to GLUTTON.
 

### 2014-04-07 FinalPaper/paper.tex
Add description of elevators and sysadmin

--- 2014-04-07 FinalPaper/paper.tex
@@
 
-\subsubsection{Traffic domain}
+\subsubsection{Traffic}
 This domain represents a simple binary version of the cell transition model (CTM) for modelling traffic based on the original CTM Tech Report \cite{sanner2011traffic}.
 Because of the binary variables and no intermediate variable restrictions, this model is simplified and ignores traffic aspects such as turns and turn probabilities.
-This model also uses concurrent actions and the total actions has an upperbound of 2\textsuperscript{ (\# of intersections)}.
+This model also uses concurrent actions and the total actions has an upper bound of $2^{\#~of~intersections}$.
 
 %ADD IMAGE HERE
+
+\subsection{Elevators}
+
+In the elevators domain there are a number of elevators delivering passengers
+to either the top or bottom floor. Potential passengers arrive at any floor at
+a certain rate (depending on which floor). The elevators can only move in the
+direction it is indicating, so passengers know whether to board or not. The
+goal of the elevators is to transport as many as possible passengers to their
+destinations.
+
+\subsection{SysAdmin}
+
+The SysAdmin domain describes a network of connected servers. Each server has
+a probability that it shuts down, and if is not running, it has a probability
+to reboot. The probability that a server shuts down depends on the number of
+running connected servers.
 

### 2014-04-07 FinalPaper/paper.tex
Add section heading for the domain evaluation
rewrote everything excepr gourmand

--- 2014-04-07 FinalPaper/paper.tex
@@
 \usepackage{fixltx2e}
+
+\usepackage{xcolor}
+\newcommand\myworries[1]{\textcolor{red}{#1}}
+\newcommand\todo[1]{\textcolor{blue}{#1}}
 
@@
 
-\section{FF-Replan}
+\section{Planners}
 \label{sec:planners}
 
+\subsection{FF-replan}
 At the first international probabilistic planning competition IPPC-04, most entries were probabilistic planner using Markov Decision Processes.
@@
 This explains why FF-replan performs poorly in domains containing dead-ends.
-However, by relying on search FF-replan functions with enormous speed and efficiency and caused the International Conference on Automated Planning and Scheduling (ICAPS) to change their benchmarks to increase their \emph{probabilistically interestingness}.
-By evaluating and correcting the IPPC-11 domains on their \emph{realistically interestingness} we will draw conclusions whether or not these adjusted realistic domains are actually classical planning problems in disguise - ideal planning problems for FF-replan.
+However, by relying on search FF-replan functions with enormous speed and efficiency and caused the International Conference on Automated Planning and Scheduling (ICAPS) to adapt their domains, increasing their \emph{probabilistically interestingness}.
+Finite horizon MDPs were introduced as an approximation of the infinite optimization problems using a finite horizon.
+These planning problems accounted for large branching factors as would be caused by \emph{natural dynamics} such as environmental factors and decay.
+To be successful in these domains planners need to be scalable and sensitive to an expected reward maximization, the evaluation criteria of finite-horizon MDPs.
+
+%----------------------------------------------------------------------------------------
+
+\subsection{The rise of LRTDP planners}
+
+\myworries{Still need to introduce LRTDPs better and the reason why they emerged}
+
+\emph{Labeled Real-Time Dynamic Programmers} (LRTDPs) operate a series of trials starting from $s_0$.
+
+\todo{Make this list more technical}
+\begin{itemize}
+	\item Trials start at $s_0$
+	\item Choose best action greedily in the current state based on current $V$ value function
+	\item Perform Bellman backup on the current state
+	\item Sample the outcome as the chosen action
+	\item Transition to the new state
+	\item Repeat until a goal, dead end or converged state is reached
+	\item After trial, special convergence check on all states in the trial is performed to prove the convergence of these values
+\end{itemize}
+
+Adapting LRTDP to a finite horizon MDP \emph{M(H)} or \emph{LRTDP-FH} requires for each trial to start at ($s_0$) and run for at most $H$ time steps.
+The resulting states would translate to the goal states in a goal-oriented MDP.
+\\
+
+%However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.
+
+A \emph{Labeled Reverse Real-Time Dynamic Programmer} (LR\textsuperscript{2}TDP) uses \emph{reverse iterative deepening} and LRTDP-FH to incrementally solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$ in order by relying on the fact that a successful policy can be produced by solving an MDP-FH $M(H)$ for a smaller horizon $h < H$.
+A LR\textsuperscript{2}TDP\@ iterates on the distance from the horizon and allows for reusing precomputed state-action plans from converged states.
+However when dealing with large branching factors Bellman computations tend to become prohibitively expensive.
+\todo{nog een lijstje schrijven van hoe het werkt en waarom er verbetering nodig is}
+
+%\begin{itemize}
+%	\item In many MDPs, the optimal policy $M(h)$ for some $h < H$ is near optimal for M(H), it thus may have a solution when stopped prematurely
+%	\item it's trials are very short because backchaining from the goal leads to a lots of convergence
+%	\item It optimally memorizes a large fraction of augmented states to save memory
+%	\item a large fraction of state space may be unreachable from $s_0$ and it avoid storing information it does not need
+%	\item it should however use a heuristic to treat states that has never been encountered when stopped prematurely, could be a fall back or a default action.
+%\end{itemize}
+
+\subsection{GLUTTON}
+
+\textsc{GLUTTON} introduces an off-line algorithm based on LR\textsuperscript{2}TDP.
+The \emph{Max-Reward} heuristic used to evaluate \todo{the what?} relies on knowing the maximum reward $R_{max}$ any action can yield in a state or an upper bound on it.
+In addition to LR\textsuperscript{2}TDP, it introduces the following mechanisms to optimize for large branching factors:
+
+\todo{rewrite this list}
+\myworries{is this really necessary?}
+\begin{itemize}
+	\item Sub sampling the transition function, is not enough to decrease the amount of computations yet
+	\item Separating out Natural Dynamics: to reuse variable samples when generator successors for multiple actions, by separating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both.
+	\item Caching the transition function samples: as LR\textsuperscript{2}TDP populates the state-value hash table lazily, Glutton uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same $(s,h)$ pair.
+When full, it chooses state-action pars for eviction ans replacement randomly.
+	\item Default policies: Glutton uses 3 tricks to determine a policy when stopped prematurely.
+It compares the optimal action from a $h'$ with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.
+\end{itemize}
+
+%---------------------------------------------------------------------
+%During IPPC-11 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT.
+This caused to wonder whether LRTDP planners could outperform UCT based systems.
+UCT forces an expert to guess a non-shortsighted lookahead value for which it should be able to converge on encountered states.
+Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity.
+At the IPPC-11 GLUTTON was an offline LRTDP based planner that came second.
+As PROST employed UCT in an online manner, GOURMAND is an online adaptation of the GLUTTON algorithm to test whether LRTDP performs better if it is employed online.
+%
+%UCT picks an action based on it current quality estimate and an \emph{exploration term} which forces the planner to choose actions that have rarely been tried in the past.
+This makes UCT suitable for a wider scale of scenarios but also implies an unreliable termination condition.
+
+Because real world domains contain Natural Dynamics that introduce large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of states the planner may never reach in a lifetime.
+Such problems are far better solved using online planners by finding an optimal policy $\tau$* or an approximation of this polict for the \emph{current} state, executing it and repeating.
+This is done by choosing a certain lookahead value $L$ and solving the MDP \emph{M\textsubscript{s}(L)} to solve \emph{M\textsubscript{0}(H)} where L $<$ H and then select \emph{$\pi$*\textsubscript{L}(s, L)} using the evaluation criteria.
+This lookahead value is determined using the per-process time constraint.\todo{elaborate on the per-process time constraint}
+
+\subsection{GOURMAND}
+\textsc{GOURMAND}, an online adaptation of the \textsc{GLUTTON} planner answers these remarks by adding a lookahead value $L$. \todo{still finish this}
+
+% always makes an informed choice in any state where it ends up when the time T allocated for solving the MDP runs out because of the online fashion it uses LRTDP.
+GOURMAND first divides the time among all remaining epochs, determines the largest lookahead L for which it can almost certainly solve any remaining epoch if T is assigned.
+It then checks if it can solve even for a larger lookahead L by taking away a small configuration time from future epochs  while still guaranteeing that it can solve for Lookahead L in each of them.
+This was GOURMAND adaptively picks a good lookahead value at each decision epoch given the per-process constraint T.
+This can only be achieved by knowing how long it takes for LRTDP to solve a state for certain lookahead values.
+It uses LR\textsuperscript{2}TDP to collect this data.
+This version of LRTDP is more efficient because of the early convergences and it allows measuring how long on average the solving of a task takes.
+GOURMAND uses the same engineering optimizations to to handle evaluate actions, iterating over the successors of s under a by the Bellman Backups.
+GOURMAND eventually outperforms both GLUTTON and PROST, the winner of the IPPC-11\cite{keller2012prost}.
 
@@
 
-%----------------------------------------------------------------------------------------
-
-\subsection{GOURMAND}
-
-The IPPC-11 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
-For this reason planners needed to be scalable and sensitive to the expected reward maximization.
-Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP $M(H)$ for a smaller horizon $h$.
-Incrementally solving the sequence $M(1)$, $M(2)$ forms the basis of LR\textsuperscript{2}TDP\@.
-By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full).
-The max-reward heuristic finds the largest horizon value $h'$ for which already a heuristic value $V$ is estimated.
-The  computation time remains much lower because it runs quickly into states that converged while solving $M(h-1)$.
-The max-reward computation relies on knowing the maximum $R_{max}$ any action can yield in any state or an upper bound on it.
-
-\subsubsection{LRTDP}
-Using goal oriented MDPs, the \emph{Labelled Real-Time Dynamic Programmer} (LRTDP) operates a series of trials starting from $s_0$.
-
-\begin{itemize}
-	\item Trials start at $s_0$
-	\item Choose best action greedily in the current state based on current $V$
-	\item Perform  Bellman backup on the current state
-	\item Sample the outcome as the chosen action
-	\item Transition to the new state
-	\item Repeat until a goal, dead end or converged state is reached
-	\item After trial, special convergence check on all states in the trial is performed to prove the convergence of these values
-\end{itemize}
-
-\subsubsection{LRTDP-FH}
-
-Adapting LRTDP to a finite horizon MDP \emph{M(H)} requires to let each trial start at ($s_0$) and run for at most H time steps.
-A steps $H$ steps away from $s_0$ would translate to goals in a goal-oriented MDP.
-However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.
-
-\subsubsection{LR\textsuperscript{2}TDP}
-
-LR\textsuperscript{2}TDP uses \emph{reverse iterative deepening} and LRTDP-FH to solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$, in that order.
-It first decides how to act optimally in ($s_0$, 1), equivalent to solving M(1) , then ($s_0$, 2), equivalent to solving $M(2)$, eventually solving $M(H)$ or running out of time halting a $M(h')$ where $h' < H$.
-This incremental effort allows for reusing state values computed in previous states, so it memorizes all values and solves for smaller horizons by backchaining from the goal LRTDP-FH iterates over search depth while LR\textsuperscript{2}TDP iterates over the distance from the horizon and is likely to be better because:
-
-\begin{itemize}
-	\item In many MDPs, the optimal policy $M(h)$ for some $h < H$ is near optimal for M(H), it thus may have a solution when stopped prematurely
-	\item it's trials are very short because backchaining from the goal leads to a lots of convergence
-	\item It optimally memorizes a large fraction of augmented states to save memory
-	\item a large fraction of state space may be unreachable from $s_0$ and it avoid storing information it does not need
-	\item it should however use a heuristic to treat states that has never been encountered when stopped prematurely, could be a fall back or a default action.
-\end{itemize}
-
-\subsubsection{GLUTTON}
-
-Glutton uses the \emph{Max-Reward} heuristic that relies on knowing the maximum reward $R_{max}$ any action can yield in a state or an upper bound on it.
-Large branching factors induce that the computation of the Bellman Backups becomes prohibitively expensive.
-Glutton uses the following mechanisms to optimize for large branching factors:
-
-\begin{itemize}
-	\item Subsampling the transition function, is not enough to decrease the amount of computations yet
-	\item Separating out Natural Dynamics: to reuse variable samples when generator successors for multiple actions, by separating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both.
-	\item Caching the transition function samples: as LR\textsuperscript{2}TDP populates the state-value hash table lazily, Glutton uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same $(s,h)$ pair.
-When full, it chooses state-action pars for eviction ans replacement randomly.
-	\item Default policies: Glutton uses 3 tricks to determine a policy when stopped prematurely.
-It compares the optimal action from a $h'$ with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.
-\end{itemize}
-%---------------------------------------------------------------------
-During IPPC-11 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT.
-This caused to wonder whether LRTDP planners could outperform UCT based systems.
-UCT forces an expert to guess a non-shortsighted lookahead value for which it should be able to converge on encountered states.
-Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity.
-At the IPPC-11 GLUTTON was an offline LRTDP based planner that came second.
-As PROST employed UCT in an online manner, GOURMAND is an online adaptation of the GLUTTON algorithm to test whether LRTDP performs better if it is employed online.
-
-UCT picks an action based on it current quality estimate and an \emph{exploration term} which forces the planner to choose actions that have rarely been tried in the past.
-This makes UCT suitable for a wider scale of scenarios but also implies an unreliable termination condition.
-
-Because real world domains contain Natural Dynamics that introduce large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of state the planner may never reach in a lifetime.
-Such problems are far better solved using online planners by finding a $\tau$* or an approximation for the current state, executing it and repeating.
-This is done by choosing a certain lookahead  L and solving MDP \emph{M\textsubscript{s}(L)} to solve \emph{M\textsubscript{0}(H)} where L $<$ H and then select \emph{$\pi$*\textsubscript{L}(s, L)} recommended by the optimal policy.
-This lookahead value is determined using the per-process time constraint.
-
-\subsubsection{GOURMAND}
-In contrast to GLUTTON, GOURMAND always makes an informed choice in any state where it ends up when the time T allocated for solving the MDP runs out because of the online fashion it uses LRTDP.
-GOURMAND first divides the time among all remaining epochs, determines the largest lookahead L for which it can almost certainly solve any remaining epoch if T is assigned.
-It then checks if it can solve even for a larger lookahead L by taking away a small configuration time from future epochs  while still guaranteeing that it can solve for Lookahead L in each of them.
-This was GOURMAND adaptively picks a good lookahead value at each decision epoch given the per-process constraint T.
-This can only be achieved by knowing how long it takes for LRTDP to solve a state for certain lookahead values.
-It uses LR\textsuperscript{2}TDP to collect this data.
-This version of LRTDP is more efficient because of the early convergences and it allows measuring how long on average the solving of a task takes.
-GOURMAND uses the same engineering optimizations to to handle evaluate actions, iterating over the successors of s under a by the Bellman Backups.
-GOURMAND eventually outperforms both GLUTTON and PROST, the winner of the IPPC-11\cite{keller2012prost}.
-
 %---------------------------------------------------------------------

### 2014-04-07 FinalPaper/paper.tex
rewrote everything excepr gourmand

@@
 replanning planners.
+
+\subsubsection{Traffic}
+
+The traffic domain describes a crossroad with traffic lights, modelled as
+cells. Either the north to south road has a green light, the west to east road
+or all lights are red. The model uses a finite state machine that handles the
+lights so that the lights are never green at the same time. This would be the
+only dangerous situation on the crossroad. The difficulty in this domain is
+the number of states, which grows exponentially with the number of cells.
+Besides that it is an uninteresting probabilistic problem because it does
+not satisfy the probabilistic interesting test.
+
+\subsubsection{Elevators}
 

### 2014-04-07 FinalPaper/paper.tex
Use textsc for glutton and gourmand. Fix errors (et. all) and other typos

--- 2014-04-07 FinalPaper/paper.tex
@@
 
-In this paper we evaluate the strength of FF-Replan, winner of IPPC-04 and unenrolled winner of IPPC-06, a replanner that uses the classical planner FF on a determinized probabilistic problem against a state of the art probabilistic planner GOURMAND, the successor of the Labelled Real-Time Dynamic Probabilistic planner Glutton, runner up of the IPPC-11.
-By translating the Navigation and Traffic domain from IPPC-11 to a matching real-world equivalent and evaluating these using the proposed probabilistically interesting baseline test as proposed by Little et.
-all we evaluate whether FF-Replan is in fact capable enough to solve enough of these so called classical planning problems in disguise.
+In this paper we evaluate the strength of FF-Replan, winner of IPPC-04 and unenrolled winner of IPPC-06, a replanner that uses the classical planner FF on a determinized probabilistic problem against a state of the art probabilistic planner \textsc{Gourmand}, the successor of the Labelled Real-Time Dynamic Probabilistic planner \textsc{Glutton}, runner up of the IPPC-11.
+By translating the Navigation and Traffic domain from IPPC-11 to a matching real-world equivalent and evaluating these using the proposed probabilistically interesting baseline test as proposed by Little et all\.
+we evaluate whether FF-Replan is in fact capable enough to solve enough of these so called classical planning problems in disguise.
 \end{abstract}
@@
 which can design domains that are more probabilistically interesting. The top
-performers were PROST \cite{keller2012prost} and Glutton
+performers were PROST \cite{keller2012prost} and \textsc{Glutton}
 \cite{kolobov2012glutton}.
@@
 The main contribution of this paper is an evaluation of FF-Replan versus a
-probabilistically state of the art planner GOURMAND in the realistically
+probabilistically state of the art planner \textsc{Gourmand} in the realistically
 augmented domains of IPPC-11. If these domains fail the baseline test proposed
-by Little et\@. all, they would translate to classical planning problems in
+by Little et all\., they would translate to classical planning problems in
 disguise and could be easily solved by FF-Replan.
@@
 \section{Problem formulation}
-To evaluate FF-Replan and GOURMAND in a real world domain a finite horizon MDP is used to represent the realistic \emph{natural dynamics} such as external forces or forces of nature.
+
+To evaluate FF-Replan and \textsc{Gourmand} in a real world domain a finite horizon MDP is used to represent the realistic \emph{natural dynamics} such as external forces or forces of nature.
 These dynamics introduce large branching factors emphasizing the need for a planner to be scalable.
@@
 We will reason about the most interesting domains for our evaluation and adjust them to match their real-world equivalent.
-Using the baseline test introduced by Little et.
-all \cite{little2007probvsreplan}, we can evaluate the probabilistically interestingness of these domains and evaluate the performance of FF-Replan vs.
-a state of the art probabilistic planner: GOURMAND.
+Using the baseline test introduced by Little et all.\@ \cite{little2007probvsreplan}, we can evaluate the probabilistically interestingness of these domains and evaluate the performance of FF-Replan vs.\@ a state of the art probabilistic planner: \textsc{Gourmand}.
 
@@
 Probabilistic planners are used to solve probabilistic planning problems and should be able to account for uncertainty as opposed to classical planners.
-For our evaluation we have chosen to compare FF-Replan to a state-of-the-art probabilistic planner: GOURMAND.
-GOURMAND is the online successor of the GLUTTON plan, a Labelled Real-Time Dynamic Programming (LRTDP) based planner and the runner up of IPPC-11.
+For our evaluation we have chosen to compare FF-Replan to a state-of-the-art probabilistic planner: \textsc{Gourmand}.
+\textsc{Gourmand} is the online successor of the \textsc{Glutton} plan, a Labelled Real-Time Dynamic Programming (LRTDP) based planner and the runner up of IPPC-11.
 
@@
 
-\subsection{FF-replan}
+\subsection{FF-Replan}
 At the first international probabilistic planning competition IPPC-04, most entries were probabilistic planner using Markov Decision Processes.
@@
 
-FF-Replan has some obvious shortcomings.Iit first determinizes the input domain and thus removes all probabilistic information from the problem.
+FF-Replan has some obvious shortcomings.
+It first determinizes the input domain and thus removes all probabilistic information from the problem.
 The success of the planner is therefore fully reliable on the chose determinization heuristic.
-As FF-replan uses no roll-out policy or future simulation, it has no way of avoiding \emph{avoidable} dead-ends.
-This explains why FF-replan performs poorly in domains containing dead-ends.
-However, by relying on search FF-replan functions with enormous speed and efficiency and caused the International Conference on Automated Planning and Scheduling (ICAPS) to adapt their domains, increasing their \emph{probabilistically interestingness}.
+As FF-Replan uses no roll-out policy or future simulation, it has no way of avoiding \emph{avoidable} dead-ends.
+This explains why FF-Replan performs poorly in domains containing dead-ends.
+However, by relying on search FF-Replan functions with enormous speed and efficiency.
+This caused the International Conference on Automated Planning and Scheduling (ICAPS) to adapt their domains, increasing their \emph{probabilistically interestingness}.
 Finite horizon MDPs were introduced as an approximation of the infinite optimization problems using a finite horizon.
@@
 \todo{Make this list more technical}
+
 \begin{itemize}
@@
 
-A \emph{Labeled Reverse Real-Time Dynamic Programmer} (LR\textsuperscript{2}TDP) uses \emph{reverse iterative deepening} and LRTDP-FH to incrementally solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$ in order by relying on the fact that a successful policy can be produced by solving an MDP-FH $M(H)$ for a smaller horizon $h < H$.
-A LR\textsuperscript{2}TDP\@ iterates on the distance from the horizon and allows for reusing precomputed state-action plans from converged states.
+A \emph{Labeled Reverse Real-Time Dynamic Programmer} (LR$^2$TDP) uses \emph{reverse iterative deepening} and LRTDP-FH to incrementally solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$ in order by relying on the fact that a successful policy can be produced by solving an MDP-FH $M(H)$ for a smaller horizon $h < H$.
+A LR$^2$TDP\@ iterates on the distance from the horizon and allows for reusing precomputed state-action plans from converged states.
 However when dealing with large branching factors Bellman computations tend to become prohibitively expensive.
+
 \todo{nog een lijstje schrijven van hoe het werkt en waarom er verbetering nodig is}
@@
 
-\subsection{GLUTTON}
+\subsection{\textsc{Glutton}}
 
-\textsc{GLUTTON} introduces an off-line algorithm based on LR\textsuperscript{2}TDP.
+\textsc{Glutton} introduces an off-line algorithm based on LR$^2$TDP.
 The \emph{Max-Reward} heuristic used to evaluate \todo{the what?} relies on knowing the maximum reward $R_{max}$ any action can yield in a state or an upper bound on it.
-In addition to LR\textsuperscript{2}TDP, it introduces the following mechanisms to optimize for large branching factors:
+In addition to LR$^2$TDP, it introduces the following mechanisms to optimize for large branching factors:
 
 \todo{rewrite this list}
+
 \myworries{is this really necessary?}
+
 \begin{itemize}
@@
 	\item Separating out Natural Dynamics: to reuse variable samples when generator successors for multiple actions, by separating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both.
-	\item Caching the transition function samples: as LR\textsuperscript{2}TDP populates the state-value hash table lazily, Glutton uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same $(s,h)$ pair.
+	\item Caching the transition function samples: as LR$^2$TDP populates the state-value hash table lazily, \textsc{Glutton} uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same $(s,h)$ pair.
 When full, it chooses state-action pars for eviction ans replacement randomly.
-	\item Default policies: Glutton uses 3 tricks to determine a policy when stopped prematurely.
+	\item Default policies: \textsc{Glutton} uses 3 tricks to determine a policy when stopped prematurely.
 It compares the optimal action from a $h'$ with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.
@@
 Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity.
-At the IPPC-11 GLUTTON was an offline LRTDP based planner that came second.
-As PROST employed UCT in an online manner, GOURMAND is an online adaptation of the GLUTTON algorithm to test whether LRTDP performs better if it is employed online.
+At the IPPC-11 \textsc{Glutton} was an offline LRTDP based planner that came second.
+As PROST employed UCT in an online manner, \textsc{Gourmand} is an online adaptation of the \textsc{Glutton} algorithm to test whether LRTDP performs better if it is employed online.
 %
@@
 Because real world domains contain Natural Dynamics that introduce large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of states the planner may never reach in a lifetime.
-Such problems are far better solved using online planners by finding an optimal policy $\tau$* or an approximation of this polict for the \emph{current} state, executing it and repeating.
-This is done by choosing a certain lookahead value $L$ and solving the MDP \emph{M\textsubscript{s}(L)} to solve \emph{M\textsubscript{0}(H)} where L $<$ H and then select \emph{$\pi$*\textsubscript{L}(s, L)} using the evaluation criteria.
-This lookahead value is determined using the per-process time constraint.\todo{elaborate on the per-process time constraint}
+Such problems are far better solved using online planners by finding an optimal policy $\tau^*$ or an approximation of this policy for the \emph{current} state, executing it and repeating.
+This is done by choosing a certain lookahead value $L$ and solving the MDP $M_s(L)$ to solve $M_0(H)$ where L $<$ H and then select $\pi^*_L(s,L)$ using the evaluation criteria.
+This lookahead value is determined using the per-process time constraint.
 
-\subsection{GOURMAND}
-\textsc{GOURMAND}, an online adaptation of the \textsc{GLUTTON} planner answers these remarks by adding a lookahead value $L$. \todo{still finish this}
+\todo{elaborate on the per-process time constraint}
+
+\subsection{\textsc{Gourmand}}
+\textsc{Gourmand}, an online adaptation of the \textsc{Glutton} planner answers these remarks by adding a lookahead value $L$. \todo{still finish this}
 
 % always makes an informed choice in any state where it ends up when the time T allocated for solving the MDP runs out because of the online fashion it uses LRTDP.
-GOURMAND first divides the time among all remaining epochs, determines the largest lookahead L for which it can almost certainly solve any remaining epoch if T is assigned.
+\textsc{Gourmand} first divides the time among all remaining epochs, determines the largest lookahead L for which it can almost certainly solve any remaining epoch if T is assigned.
 It then checks if it can solve even for a larger lookahead L by taking away a small configuration time from future epochs  while still guaranteeing that it can solve for Lookahead L in each of them.
-This was GOURMAND adaptively picks a good lookahead value at each decision epoch given the per-process constraint T.
+This was \textsc{Gourmand} adaptively picks a good lookahead value at each decision epoch given the per-process constraint T.
 This can only be achieved by knowing how long it takes for LRTDP to solve a state for certain lookahead values.
@@
 This version of LRTDP is more efficient because of the early convergences and it allows measuring how long on average the solving of a task takes.
-GOURMAND uses the same engineering optimizations to to handle evaluate actions, iterating over the successors of s under a by the Bellman Backups.
-GOURMAND eventually outperforms both GLUTTON and PROST, the winner of the IPPC-11\cite{keller2012prost}.
+\textsc{Gourmand} uses the same engineering optimizations to to handle evaluate actions, iterating over the successors of s under a by the Bellman Backups.
+\textsc{Gourmand} eventually outperforms both \textsc{Glutton} and PROST, the winner of the IPPC-11\cite{keller2012prost}.
 
@@
 Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}.
-This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Competitions.
+This section describes interesting domains in which either FF-Replan or \textsc{Gourmand} prevailed during the International Probabilistic Planning Competitions.
 These domains are evaluated for how well they portray real-world scenarios.
@@
 
-GOURMAND vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}.
-PROST however mildly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
+\textsc{Gourmand} vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}.
+PROST however mildly outperforms \textsc{Gourmand} on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
 
@@
 The robot needs to choose a path which gets it to the goal most reliably within the finite horizon time \cite{sanner2011navigation}.
-Because GOURMAND uses a dynamic lookahead, it performs quite well in this domain.
+Because \textsc{Gourmand} uses a dynamic lookahead, it performs quite well in this domain.
 
@@
 
-Gourmand already works with RDDLSim and MDPs with finite horizon. The original
+\textsc{Gourmand} already works with RDDLSim and MDPs with finite horizon. The original
 FF-Replan is a Goal-Oriented MDP planner. For a Finite-Horizon each state at
-the horizon is a goal. To compare Gourmand, that works with MDP-FH, with
+the horizon is a goal. To compare \textsc{Gourmand}, that works with MDP-FH, with
 FF-Replan, FF-Replan needs a slight update. It should not only execute FF for
@@
 
-Using the framework of Glutton and Gourmand, and the FF heuristic found in mGPT
+Using the framework of \textsc{Glutton} and \textsc{Gourmand}, and the FF heuristic found in mGPT
 \cite{bonet2011mgpt}, the updated FF-Replan can be implemented. The first step
-of Gourmand is parsing the problem and creating a structure of the problem.
-Instead of executing the Gourmand algorithm, this structure can be used to
+of \textsc{Gourmand} is parsing the problem and creating a structure of the problem.
+Instead of executing the \textsc{Gourmand} algorithm, this structure can be used to
 determinize the problem by setting all probabilities of each action to 1
@@
 FF heuristic it can find plans for each goal and calculate the expected reward.
-Then it can reuse the Gourmand framework to execute the plan by sending the
+Then it can reuse the \textsc{Gourmand} framework to execute the plan by sending the
 action to the RDDLSim server. Like FF-Replan if the server returns with a state
@@
 
-\subsubsection{RFF}. Also uses an incremental plan aggregation, but offline similar to GLUTTON.
+\subsubsection{RFF}. Also uses an incremental plan aggregation, but offline similar to \textsc{Glutton}.
 

### 2014-04-07 FinalPaper/paper.tex
Use textsc for glutton and gourmand. Fix errors (et. all) and other typos

@@
 
-\subsubsection{RFF}. Also uses an incremental plan aggregation, but offline similar to \textsc{Glutton}.
+In sections above we have described the GOURMAND planner and FF-Replan as two
+probabilistic planners of the IPPC competition.
+RFF~\cite{teichteil2010incremental} is an offline planner that generates a
+policy: for each reachable state it determines a plan to the goal. Like
+FF-Replan it uses determinization and FF\. FF returns an initial plan from the
+initial state to a goal state. For each state in the plan the successor states
+are added to the structure, after which Monte-Carlo sampling is used. States
+where the probability that they're reached is too low (below a threshold) are
+removed. The successor states are used as initial states in the next step. If
+FF fails to find a plan to the goal from this new state, the state is removed
+from the structure too. Results showed that RFF outperformed other competitors.
+A higher threshold means that RFF will generate more policies that are prone to
+replanning.
 

### 2014-04-07 FinalPaper/paper.tex
Fixing et al.

--- 2014-04-07 FinalPaper/paper.tex
@@
 In this paper we evaluate the strength of FF-Replan, winner of IPPC-04 and unenrolled winner of IPPC-06, a replanner that uses the classical planner FF on a determinized probabilistic problem against a state of the art probabilistic planner \textsc{Gourmand}, the successor of the Labelled Real-Time Dynamic Probabilistic planner \textsc{Glutton}, runner up of the IPPC-11.
-By translating the Navigation and Traffic domain from IPPC-11 to a matching real-world equivalent and evaluating these using the proposed probabilistically interesting baseline test as proposed by Little et all\.
+By translating the Navigation and Traffic domain from IPPC-11 to a matching real-world equivalent and evaluating these using the proposed probabilistically interesting baseline test as proposed by Little et al\.
 we evaluate whether FF-Replan is in fact capable enough to solve enough of these so called classical planning problems in disguise.
@@
 augmented domains of IPPC-11. If these domains fail the baseline test proposed
-by Little et all\., they would translate to classical planning problems in
+by Little et al\., they would translate to classical planning problems in
 disguise and could be easily solved by FF-Replan.
@@
 We will reason about the most interesting domains for our evaluation and adjust them to match their real-world equivalent.
-Using the baseline test introduced by Little et all.\@ \cite{little2007probvsreplan}, we can evaluate the probabilistically interestingness of these domains and evaluate the performance of FF-Replan vs.\@ a state of the art probabilistic planner: \textsc{Gourmand}.
+Using the baseline test introduced by Little et al.\@ \cite{little2007probvsreplan}, we can evaluate the probabilistically interestingness of these domains and evaluate the performance of FF-Replan vs.\@ a state of the art probabilistic planner: \textsc{Gourmand}.
 
@@
 The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario.
-Little et all's baseline test helps us to predict which planner would perform well on these domains.
-We will then conclude our evaluation by comparing these results to the result of our experiments described in Section \ref{sec:experiment}.
+Little et al.'s baseline test helps us to predict which planner would perform well on these domains.
+We will then conclude our evaluation by comparing these results to the result of our experiments described in Section~\ref{sec:experiment}.
 
@@
 The competitor FF-Replan \cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
-The baseline test of Little et.\@ all evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
+The baseline test of Little et al.\@ evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
 IPPC-11 responded by introducing more realistic MDPs and evaluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
@@
 \textsc{Gourmand} vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}.
-PROST however mildly outperforms \textsc{Gourmand} on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
+PROST however mildly outperforms \textsc{Gourmand} on the Game of Life, SysAdmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
 

### 2014-04-08 FinalPaper/paper.tex
rewrote initial part

--- 2014-04-07 FinalPaper/paper.tex
@@
 
-In this paper we evaluate the strength of FF-Replan, winner of IPPC-04 and unenrolled winner of IPPC-06, a replanner that uses the classical planner FF on a determinized probabilistic problem against a state of the art probabilistic planner \textsc{Gourmand}, the successor of the Labelled Real-Time Dynamic Probabilistic planner \textsc{Glutton}, runner up of the IPPC-11.
-By translating the Navigation and Traffic domain from IPPC-11 to a matching real-world equivalent and evaluating these using the proposed probabilistically interesting baseline test as proposed by Little et al\.
-we evaluate whether FF-Replan is in fact capable enough to solve enough of these so called classical planning problems in disguise.
+In this paper we evaluate the strength of FF-Replan, winner of IPPC-04 and unenrolled winner of IPPC-06, a replanner that uses the classical planner FF on a determinized probabilistic problem against a state of the art probabilistic planner GOURMAND, the successor of the Labelled Real-Time Dynamic Probabilistic planner Glutton, runner up of the IPPC-11.
+By translating the Navigation and Traffic domain from IPPC-11 to a matching real-world equivalent and evaluating these using the proposed probabilistically interesting baseline test as proposed by Little et.
+all we evaluate whether FF-Replan is in fact capable enough to solve enough of these so called classical planning problems in disguise.
 \end{abstract}
@@
 which can design domains that are more probabilistically interesting. The top
-performers were PROST \cite{keller2012prost} and \textsc{Glutton}
+performers were PROST \cite{keller2012prost} and Glutton
 \cite{kolobov2012glutton}.
@@
 The main contribution of this paper is an evaluation of FF-Replan versus a
-probabilistically state of the art planner \textsc{Gourmand} in the realistically
+probabilistically state of the art planner GOURMAND in the realistically
 augmented domains of IPPC-11. If these domains fail the baseline test proposed
-by Little et al\., they would translate to classical planning problems in
+by Little et\@. all, they would translate to classical planning problems in
 disguise and could be easily solved by FF-Replan.
@@
 \section{Problem formulation}
-
-To evaluate FF-Replan and \textsc{Gourmand} in a real world domain a finite horizon MDP is used to represent the realistic \emph{natural dynamics} such as external forces or forces of nature.
+To evaluate FF-Replan and GOURMAND in a real world domain a finite horizon MDP is used to represent the realistic \emph{natural dynamics} such as external forces or forces of nature.
 These dynamics introduce large branching factors emphasizing the need for a planner to be scalable.
@@
 We will reason about the most interesting domains for our evaluation and adjust them to match their real-world equivalent.
-Using the baseline test introduced by Little et al.\@ \cite{little2007probvsreplan}, we can evaluate the probabilistically interestingness of these domains and evaluate the performance of FF-Replan vs.\@ a state of the art probabilistic planner: \textsc{Gourmand}.
+Using the baseline test introduced by Little et.
+all \cite{little2007probvsreplan}, we can evaluate the probabilistically interestingness of these domains and evaluate the performance of FF-Replan vs.
+a state of the art probabilistic planner: GOURMAND.
 
@@
 \section{Background}
+\ref{sec:background}
 
@@
 Probabilistic planners are used to solve probabilistic planning problems and should be able to account for uncertainty as opposed to classical planners.
-For our evaluation we have chosen to compare FF-Replan to a state-of-the-art probabilistic planner: \textsc{Gourmand}.
-\textsc{Gourmand} is the online successor of the \textsc{Glutton} plan, a Labelled Real-Time Dynamic Programming (LRTDP) based planner and the runner up of IPPC-11.
+For our evaluation we have chosen to compare FF-Replan to a state-of-the-art probabilistic planner: GOURMAND.
+GOURMAND is the online successor of the GLUTTON plan, a Labelled Real-Time Dynamic Programming (LRTDP) based planner and the runner up of IPPC-11.
 
@@
 
-\subsection{FF-Replan}
-At the first international probabilistic planning competition IPPC-04, most entries were probabilistic planner using Markov Decision Processes.
-The winner, FF-Replan \cite{FFReplan}, however was based on deterministic planning techniques.
-FF-Replan is an action selection algorithm for online planning in probabilistic domains which deals with uncertainty by replanning.
-FF-Replan generates a deterministic planning problem by determinizing the input domain at the start of the planning.
+FF-Replan \cite{FFReplan}, a replanner based on determinization techniques and a classical planner, surprisingly outperformed other participating MDP solvers in the IPPC-04 and by doing so changed the course of the planning competition entirely.
+By relying on search and removing all probabilistic information from the problem, FF-replan functions with enormous speed and efficiency.
+This method has proven to outperform MDP solvers, the state-of-the-art probabilistic planners for uncertainty of that time.
+Since then, Little et al.
+has argued for \emph{probabilistically interesting} domains.
+By introducing finite horizon MDPs in IPPC-11, state of the art planners have been adapted to cope with large branching factors to approximate infinite planning problems.
+Because these "planning problems" can often be solved using a smaller horizon $h < H$ as introduced in Section \ref{sec:background}, they represent optimization problems rather than planning problems, favoring current state of the art planners over replanners.
+This section introduces the shift of the planners towards optimization  by discussing FF-replan and a current state of the art probabilistic planner \textsc{GOURMAND} and its predecessors.
+
+\myworries{misschien moet dat laatste zinnetje ergens anders?}
+
+\subsection{FF-replan}
+\label{sec:ffreplan}
+ FF-Replan generates a deterministic planning problem by determinizing the input domain at the start of each planning iteration.
 This classical deterministic planning problem allows for the use of the classical FF planner \cite{Hoffmann01theff}.
-The FF planner then returns an ordered state-action plan for the deterministic problem of the current state mapped in an initially empty hash-table.
-This plan is executed until an unexpected state, not available in the hash-table is encountered.
+The FF planner then returns an ordered state-action plan for the deterministic problem of the current state.
+This plan is executed until an unexpected state is encountered in the following manner:
 
-If an unexpected state is encountered, the current state, the goal and the domain description are again determinized.
-The FF planner will generate an ordered plan which is executed until either a goal state, a dead-end state or an unexpected state is reached.
+\begin{enumerate}
+	\item Start planning at $s_0$
+	\item Determinizes the input domain
+	\item Use FF on the classical planning problem
+	\item Executes ordered state-action plan until
+	\item Unexpected state is encountered or
+	\begin{itemize}
+		\item Start planning at $s_t$ at time t
+		\item Repeat step 2 - 6
+	\end{itemize}
+	\item Goal state or dead-end is reached
+\end{enumerate}
 
 FF-Replan has some obvious shortcomings.
-It first determinizes the input domain and thus removes all probabilistic information from the problem.
-The success of the planner is therefore fully reliable on the chose determinization heuristic.
-As FF-Replan uses no roll-out policy or future simulation, it has no way of avoiding \emph{avoidable} dead-ends.
-This explains why FF-Replan performs poorly in domains containing dead-ends.
-However, by relying on search FF-Replan functions with enormous speed and efficiency.
-This caused the International Conference on Automated Planning and Scheduling (ICAPS) to adapt their domains, increasing their \emph{probabilistically interestingness}.
-Finite horizon MDPs were introduced as an approximation of the infinite optimization problems using a finite horizon.
-These planning problems accounted for large branching factors as would be caused by \emph{natural dynamics} such as environmental factors and decay.
-To be successful in these domains planners need to be scalable and sensitive to an expected reward maximization, the evaluation criteria of finite-horizon MDPs.
+It removes all probabilistic information from the problem when determinizing the domain.
+The success of the planner is therefore fully reliable on the chosen determinization heuristic.
+As FF-replan uses no roll-out policy or future simulation, it has no way of avoiding \emph{avoidable} dead-ends.
+This explains why FF-replan performs poorly in domains containing dead-ends.
+
+For a planner to be succesfull in finite-horizon MDPs they need to be scalable and sensitive to an expected reward maximization, the evaluation criteria of these domains.
+This caused for  LRTDP planners to emerge.
 
@@
 
-\myworries{Still need to introduce LRTDPs better and the reason why they emerged}
+\myworries{Still need to introduce LRTDPs better and the reason why they emerged, ook UCT introduceren?}
 
@@
 \todo{Make this list more technical}
-
 \begin{itemize}
@@
 
-A \emph{Labeled Reverse Real-Time Dynamic Programmer} (LR$^2$TDP) uses \emph{reverse iterative deepening} and LRTDP-FH to incrementally solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$ in order by relying on the fact that a successful policy can be produced by solving an MDP-FH $M(H)$ for a smaller horizon $h < H$.
-A LR$^2$TDP\@ iterates on the distance from the horizon and allows for reusing precomputed state-action plans from converged states.
+A \emph{Labeled Reverse Real-Time Dynamic Programmer} (LR\textsuperscript{2}TDP) uses \emph{reverse iterative deepening} and LRTDP-FH to incrementally solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$ in order by relying on the fact that a successful policy can be produced by solving an MDP-FH $M(H)$ for a smaller horizon $h < H$.
+A LR\textsuperscript{2}TDP\@ iterates on the distance from the horizon and allows for reusing precomputed state-action plans from converged states.
 However when dealing with large branching factors Bellman computations tend to become prohibitively expensive.
-
 \todo{nog een lijstje schrijven van hoe het werkt en waarom er verbetering nodig is}
@@
 
-\subsection{\textsc{Glutton}}
+\subsection{GLUTTON}
 
-\textsc{Glutton} introduces an off-line algorithm based on LR$^2$TDP.
+\textsc{GLUTTON} introduces an off-line algorithm based on LR\textsuperscript{2}TDP.
 The \emph{Max-Reward} heuristic used to evaluate \todo{the what?} relies on knowing the maximum reward $R_{max}$ any action can yield in a state or an upper bound on it.
-In addition to LR$^2$TDP, it introduces the following mechanisms to optimize for large branching factors:
+In addition to LR\textsuperscript{2}TDP, it introduces the following mechanisms to optimize for large branching factors:
 
 \todo{rewrite this list}
-
 \myworries{is this really necessary?}
-
 \begin{itemize}
@@
 	\item Separating out Natural Dynamics: to reuse variable samples when generator successors for multiple actions, by separating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both.
-	\item Caching the transition function samples: as LR$^2$TDP populates the state-value hash table lazily, \textsc{Glutton} uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same $(s,h)$ pair.
+	\item Caching the transition function samples: as LR\textsuperscript{2}TDP populates the state-value hash table lazily, Glutton uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same $(s,h)$ pair.
 When full, it chooses state-action pars for eviction ans replacement randomly.
-	\item Default policies: \textsc{Glutton} uses 3 tricks to determine a policy when stopped prematurely.
+	\item Default policies: Glutton uses 3 tricks to determine a policy when stopped prematurely.
 It compares the optimal action from a $h'$ with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.
@@
 Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity.
-At the IPPC-11 \textsc{Glutton} was an offline LRTDP based planner that came second.
-As PROST employed UCT in an online manner, \textsc{Gourmand} is an online adaptation of the \textsc{Glutton} algorithm to test whether LRTDP performs better if it is employed online.
+At the IPPC-11 GLUTTON was an offline LRTDP based planner that came second.
+As PROST employed UCT in an online manner, GOURMAND is an online adaptation of the GLUTTON algorithm to test whether LRTDP performs better if it is employed online.
 %
@@
 Because real world domains contain Natural Dynamics that introduce large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of states the planner may never reach in a lifetime.
-Such problems are far better solved using online planners by finding an optimal policy $\tau^*$ or an approximation of this policy for the \emph{current} state, executing it and repeating.
-This is done by choosing a certain lookahead value $L$ and solving the MDP $M_s(L)$ to solve $M_0(H)$ where L $<$ H and then select $\pi^*_L(s,L)$ using the evaluation criteria.
-This lookahead value is determined using the per-process time constraint.
+Such problems are far better solved using online planners by finding an optimal policy $\tau$* or an approximation of this polict for the \emph{current} state, executing it and repeating.
+This is done by choosing a certain lookahead value $L$ and solving the MDP \emph{M\textsubscript{s}(L)} to solve \emph{M\textsubscript{0}(H)} where L $<$ H and then select \emph{$\pi$*\textsubscript{L}(s, L)} using the evaluation criteria.
+This lookahead value is determined using the per-process time constraint.\todo{elaborate on the per-process time constraint}
 
-\todo{elaborate on the per-process time constraint}
-
-\subsection{\textsc{Gourmand}}
-\textsc{Gourmand}, an online adaptation of the \textsc{Glutton} planner answers these remarks by adding a lookahead value $L$. \todo{still finish this}
+\subsection{GOURMAND}
+\textsc{GOURMAND}, an online adaptation of the \textsc{GLUTTON} planner answers these remarks by adding a lookahead value $L$. \todo{still finish this}
 
 % always makes an informed choice in any state where it ends up when the time T allocated for solving the MDP runs out because of the online fashion it uses LRTDP.
-\textsc{Gourmand} first divides the time among all remaining epochs, determines the largest lookahead L for which it can almost certainly solve any remaining epoch if T is assigned.
+GOURMAND first divides the time among all remaining epochs, determines the largest lookahead L for which it can almost certainly solve any remaining epoch if T is assigned.
 It then checks if it can solve even for a larger lookahead L by taking away a small configuration time from future epochs  while still guaranteeing that it can solve for Lookahead L in each of them.
-This was \textsc{Gourmand} adaptively picks a good lookahead value at each decision epoch given the per-process constraint T.
+This was GOURMAND adaptively picks a good lookahead value at each decision epoch given the per-process constraint T.
 This can only be achieved by knowing how long it takes for LRTDP to solve a state for certain lookahead values.
@@
 This version of LRTDP is more efficient because of the early convergences and it allows measuring how long on average the solving of a task takes.
-\textsc{Gourmand} uses the same engineering optimizations to to handle evaluate actions, iterating over the successors of s under a by the Bellman Backups.
-\textsc{Gourmand} eventually outperforms both \textsc{Glutton} and PROST, the winner of the IPPC-11\cite{keller2012prost}.
+GOURMAND uses the same engineering optimizations to to handle evaluate actions, iterating over the successors of s under a by the Bellman Backups.
+GOURMAND eventually outperforms both GLUTTON and PROST, the winner of the IPPC-11\cite{keller2012prost}.
 
@@
 Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}.
-This section describes interesting domains in which either FF-Replan or \textsc{Gourmand} prevailed during the International Probabilistic Planning Competitions.
+This section describes interesting domains in which either FF-Replan or GOURMAND prevailed during the International Probabilistic Planning Competitions.
 These domains are evaluated for how well they portray real-world scenarios.
 The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario.
-Little et al.'s baseline test helps us to predict which planner would perform well on these domains.
-We will then conclude our evaluation by comparing these results to the result of our experiments described in Section~\ref{sec:experiment}.
+Little et all's baseline test helps us to predict which planner would perform well on these domains.
+We will then conclude our evaluation by comparing these results to the result of our experiments described in Section \ref{sec:experiment}.
 
@@
 The competitor FF-Replan \cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
-The baseline test of Little et al.\@ evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
+The baseline test of Little et.\@ all evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
 IPPC-11 responded by introducing more realistic MDPs and evaluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
 
-\textsc{Gourmand} vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}.
-PROST however mildly outperforms \textsc{Gourmand} on the Game of Life, SysAdmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
+GOURMAND vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}.
+PROST however mildly outperforms GOURMAND on the Game of Life, Sysadmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
 
@@
 The robot needs to choose a path which gets it to the goal most reliably within the finite horizon time \cite{sanner2011navigation}.
-Because \textsc{Gourmand} uses a dynamic lookahead, it performs quite well in this domain.
+Because GOURMAND uses a dynamic lookahead, it performs quite well in this domain.
 
@@
 
-\textsc{Gourmand} already works with RDDLSim and MDPs with finite horizon. The original
+Gourmand already works with RDDLSim and MDPs with finite horizon. The original
 FF-Replan is a Goal-Oriented MDP planner. For a Finite-Horizon each state at
-the horizon is a goal. To compare \textsc{Gourmand}, that works with MDP-FH, with
+the horizon is a goal. To compare Gourmand, that works with MDP-FH, with
 FF-Replan, FF-Replan needs a slight update. It should not only execute FF for
@@
 
-Using the framework of \textsc{Glutton} and \textsc{Gourmand}, and the FF heuristic found in mGPT
+Using the framework of Glutton and Gourmand, and the FF heuristic found in mGPT
 \cite{bonet2011mgpt}, the updated FF-Replan can be implemented. The first step
-of \textsc{Gourmand} is parsing the problem and creating a structure of the problem.
-Instead of executing the \textsc{Gourmand} algorithm, this structure can be used to
+of Gourmand is parsing the problem and creating a structure of the problem.
+Instead of executing the Gourmand algorithm, this structure can be used to
 determinize the problem by setting all probabilities of each action to 1
@@
 FF heuristic it can find plans for each goal and calculate the expected reward.
-Then it can reuse the \textsc{Gourmand} framework to execute the plan by sending the
+Then it can reuse the Gourmand framework to execute the plan by sending the
 action to the RDDLSim server. Like FF-Replan if the server returns with a state
@@
 
-\subsubsection{RFF}. Also uses an incremental plan aggregation, but offline similar to \textsc{Glutton}.
+\subsubsection{RFF}. Also uses an incremental plan aggregation, but offline similar to GLUTTON.
 

### 2014-04-08 FinalPaper/paper.tex
rewrote ff replan

@@
 
-For a planner to be succesfull in finite-horizon MDPs they need to be scalable and sensitive to an expected reward maximization, the evaluation criteria of these domains.
+For a planner to be succesfull in finite-horizon MDPs it needs to be scalable and sensitive to an expected reward maximization, the evaluation criteria of these domains.
 This caused for  LRTDP planners to emerge.

### 2014-04-08 FinalPaper/paper.tex

--- 2014-04-08 FinalPaper/paper.tex
@@
 
-In sections above we have described the GOURMAND planner and FF-Replan as two
-probabilistic planners of the IPPC competition.
-RFF~\cite{teichteil2010incremental} is an offline planner that generates a
-policy: for each reachable state it determines a plan to the goal. Like
-FF-Replan it uses determinization and FF\. FF returns an initial plan from the
-initial state to a goal state. For each state in the plan the successor states
-are added to the structure, after which Monte-Carlo sampling is used. States
-where the probability that they're reached is too low (below a threshold) are
-removed. The successor states are used as initial states in the next step. If
-FF fails to find a plan to the goal from this new state, the state is removed
-from the structure too. Results showed that RFF outperformed other competitors.
-A higher threshold means that RFF will generate more policies that are prone to
-replanning.
+\subsubsection{RFF}. Also uses an incremental plan aggregation, but offline similar to \textsc{Glutton}.
 

### 2014-04-08 FinalPaper/paper.tex
ff replan done, fixed a label
New domain description

--- 2014-04-08 FinalPaper/paper.tex
@@
 \usepackage{fixltx2e}
-
-\usepackage{xcolor}
-\newcommand\myworries[1]{\textcolor{red}{#1}}
-\newcommand\todo[1]{\textcolor{blue}{#1}}
 
@@
 % first the title is needed
-\title{Realistically Interesting Domains for Probabilistic Planners}
+\title{Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains}
 
 % a short form should be given in case it is too long for the running head
-\titlerunning{Real World Domains}
+\titlerunning{FF-Replan vs Probabilistic Planner in Real World Domains}
 
@@
 
+\section{Domain Description}
+
+Unmanned Aerial Vehicles (UAVs), or commonly called \emph{Drones} are aircrafts
+without a pilot and often autonomously controlled. Drones are widely used for
+military as well as for civil uses, including inspecting pipelines, counting
+wildlife, agriculture, filming or delivering supplies to inaccessible areas.
+As many uses cases there are, there are many forms of UAVs, bigger fixed wing
+aircrafts, or small helicopter or quad copter like aircrafts that can hover at
+a certain position in the air.
+
+We are particularly interested in monitoring, for example crops or livestock,
+and surveillance UAVs that work together to monitor a large area. Each UAV
+monitors a part of the total area, and if it has monitored something, it has
+to communicate this to a base station. This can't be done directly due to the
+large distance, instead it has to go through neighboring UAVs.
+
+Communicating the message from the sensing UAV to the base station can be
+expressed as a probabilistic planning problem. Initially the sensing UAV
+has the package that has to be sent, and the goal is to bring this package to
+the base station. Each time the package is passed to the neighboring UAV,
+there is a possibility the package is not received correctly. The bigger the
+distance, the higher the probability the delivery failed.
+
+%% TODO maybe UAVs can be on or of too, so it's forced to use a further UAV.
+%% TODO what's also interesting is that Amazon.com uses drones for package deliveries
+
 %---------------------------------------------------------------------
@@
 \section{Background}
-\ref{sec:background}
 
@@
 
-FF-Replan \cite{FFReplan}, a replanner based on determinization techniques and a classical planner, surprisingly outperformed other participating MDP solvers in the IPPC-04 and by doing so changed the course of the planning competition entirely.
-By relying on search and removing all probabilistic information from the problem, FF-replan functions with enormous speed and efficiency.
-This method has proven to outperform MDP solvers, the state-of-the-art probabilistic planners for uncertainty of that time.
-Since then, Little et al.
-has argued for \emph{probabilistically interesting} domains.
-By introducing finite horizon MDPs in IPPC-11, state of the art planners have been adapted to cope with large branching factors to approximate infinite planning problems.
-Because these "planning problems" can often be solved using a smaller horizon $h < H$ as introduced in Section \ref{sec:background}, they represent optimization problems rather than planning problems, favoring current state of the art planners over replanners.
-This section introduces the shift of the planners towards optimization  by discussing FF-replan and a current state of the art probabilistic planner \textsc{GOURMAND} and its predecessors.
+\subsection{FF-Replan}
 
-\myworries{misschien moet dat laatste zinnetje ergens anders?}
+At the first international probabilistic planning competition IPPC-04, most entries were Markov Decision Processes. The winner, FF-Replan, however was based on deterministic planning techniques.
 
-\subsection{FF-replan}
-\label{sec:ffreplan}
- FF-Replan generates a deterministic planning problem by determinizing the input domain at the start of each planning iteration.
-This classical deterministic planning problem allows for the use of the classical FF planner \cite{Hoffmann01theff}.
-The FF planner then returns an ordered state-action plan for the deterministic problem of the current state.
-This plan is executed until an unexpected state is encountered in the following manner:
-
+FF-Replan is an action selection algorithm for online planning in probabilistic domains.
+Given a domain description, a goal and an initial state as a probabilistic planning problem, FF-Replan generates a deterministic planning problem.
+It determinizes the input domain at the start of the planning into a deterministic different domain.
+They consider two methods of determinization:
 \begin{enumerate}
-	\item Start planning at $s_0$
-	\item Determinizes the input domain
-	\item Use FF on the classical planning problem
-	\item Executes ordered state-action plan until
-	\item Unexpected state is encountered or
-	\begin{itemize}
-		\item Start planning at $s_t$ at time t
-		\item Repeat step 2 - 6
-	\end{itemize}
-	\item Goal state or dead-end is reached
+\item \emph{Single-outcome determinization}: selects one outcome for each probabilistic construct using a variety of heuristics.
+The performance strongly depends on the methods for choosing the outcomes.
+\item \emph{All-outcomes determinization}: considers every probabilistic outcome as a distinct deterministic action.
+For each possible outcome FF-Replan generates one seperate action for each effect.
+For nested probabilities, the all-outcomes procedure is applied recursively.
+This implies that FF-Replan will cease selecting actions whenever it enters a dead state.
+However when given no information, all probabilistic effects will be considered as equal which is a potential weakness.
 \end{enumerate}
 
-FF-Replan has some obvious shortcomings.
-It removes all probabilistic information from the problem when determinizing the domain.
-The success of the planner is therefore fully reliable on the chosen determinization heuristic.
-As FF-replan uses no roll-out policy or future simulation, it has no way of avoiding \emph{avoidable} dead-ends.
-This explains why FF-replan performs poorly in domains containing dead-ends.
+After determinization FF-Replan then uses the deterministic FF planner to compute an ordered plan for the generated deterministic problem.
+This process is repeated when countering an unexpected state until a goal state is reached.
+It maintains a partial state-action mapping using a hash-table which is initially empty.
+Whenever FF-Replan encounters a state which is not in the table, it determinizes the problem and synthesizes a plan using FF.
+It then simulates the plan according to the deterministic action definitions resulting in a state-action sequence whose pairs are put in the hash table.
+The first action of the plan is then executed in the environment, returning a new state.
+This partial policy is this produces in an online fashion.
+It would be valuable to look into incremental planning approaches that don't create a deterministic plan from scratch whenever an unexpected state is encountered or reusing previous planning effort.
 
-For a planner to be succesfull in finite-horizon MDPs it needs to be scalable and sensitive to an expected reward maximization, the evaluation criteria of these domains.
-This caused for  LRTDP planners to emerge.
+FF-Replan has some obvious shortcomings as it first determinizes the input domain, removing all probabilistic information from the problem and then synthesizes a plan.
+If an unexpected state should occur whilst executing, the planner replans in the same determinization.
+It also does not consider multiple potential effects if an action.
 
-%----------------------------------------------------------------------------------------
+By relying on search, FF-Replan could function with enormous speed and efficiency.
+However when dealing with difficult probabilistic problems attempting to span the spectrum of complexity ranging from deterministic problems to highly stochastic problems, FF-Replan is expected to come short.
+Because FF-Replan is developed hoping to inspire extensions and insight into the approach and planning domains, the authors are hoping to achieve this.
 
-\subsection{The rise of LRTDP planners}
+\subsection{GOURMAND}
 
-\myworries{Still need to introduce LRTDPs better and the reason why they emerged, ook UCT introduceren?}
+The IPPC-11 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy.
+For this reason planners needed to be scalable and sensitive to the expected reward maximization.
+Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP $M(H)$ for a smaller horizon $h$.
+Incrementally solving the sequence $M(1)$, $M(2)$ forms the basis of LR\textsuperscript{2}TDP\@.
+By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full).
+The max-reward heuristic finds the largest horizon value $h'$ for which already a heuristic value $V$ is estimated.
+The  computation time remains much lower because it runs quickly into states that converged while solving $M(h-1)$.
+The max-reward computation relies on knowing the maximum $R_{max}$ any action can yield in any state or an upper bound on it.
 
-\emph{Labeled Real-Time Dynamic Programmers} (LRTDPs) operate a series of trials starting from $s_0$.
+\subsubsection{LRTDP}
+Using goal oriented MDPs, the \emph{Labelled Real-Time Dynamic Programmer} (LRTDP) operates a series of trials starting from $s_0$.
 
-\todo{Make this list more technical}
 \begin{itemize}
 	\item Trials start at $s_0$
-	\item Choose best action greedily in the current state based on current $V$ value function
+	\item Choose best action greedily in the current state based on current $V$
 	\item Perform  Bellman backup on the current state
@@
 
-Adapting LRTDP to a finite horizon MDP \emph{M(H)} or \emph{LRTDP-FH} requires for each trial to start at ($s_0$) and run for at most $H$ time steps.
-The resulting states would translate to the goal states in a goal-oriented MDP.
-\\
+\subsubsection{LRTDP-FH}
 
-%However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.
+Adapting LRTDP to a finite horizon MDP \emph{M(H)} requires to let each trial start at ($s_0$) and run for at most H time steps.
+A steps $H$ steps away from $s_0$ would translate to goals in a goal-oriented MDP.
+However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.
 
-A \emph{Labeled Reverse Real-Time Dynamic Programmer} (LR\textsuperscript{2}TDP) uses \emph{reverse iterative deepening} and LRTDP-FH to incrementally solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$ in order by relying on the fact that a successful policy can be produced by solving an MDP-FH $M(H)$ for a smaller horizon $h < H$.
-A LR\textsuperscript{2}TDP\@ iterates on the distance from the horizon and allows for reusing precomputed state-action plans from converged states.
-However when dealing with large branching factors Bellman computations tend to become prohibitively expensive.
-\todo{nog een lijstje schrijven van hoe het werkt en waarom er verbetering nodig is}
+\subsubsection{LR\textsuperscript{2}TDP}
 
-%\begin{itemize}
-%	\item In many MDPs, the optimal policy $M(h)$ for some $h < H$ is near optimal for M(H), it thus may have a solution when stopped prematurely
-%	\item it's trials are very short because backchaining from the goal leads to a lots of convergence
-%	\item It optimally memorizes a large fraction of augmented states to save memory
-%	\item a large fraction of state space may be unreachable from $s_0$ and it avoid storing information it does not need
-%	\item it should however use a heuristic to treat states that has never been encountered when stopped prematurely, could be a fall back or a default action.
-%\end{itemize}
+LR\textsuperscript{2}TDP uses \emph{reverse iterative deepening} and LRTDP-FH to solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$, in that order.
+It first decides how to act optimally in ($s_0$, 1), equivalent to solving M(1) , then ($s_0$, 2), equivalent to solving $M(2)$, eventually solving $M(H)$ or running out of time halting a $M(h')$ where $h' < H$.
+This incremental effort allows for reusing state values computed in previous states, so it memorizes all values and solves for smaller horizons by backchaining from the goal LRTDP-FH iterates over search depth while LR\textsuperscript{2}TDP iterates over the distance from the horizon and is likely to be better because:
 
-\subsection{GLUTTON}
+\begin{itemize}
+	\item In many MDPs, the optimal policy $M(h)$ for some $h < H$ is near optimal for M(H), it thus may have a solution when stopped prematurely
+	\item it's trials are very short because backchaining from the goal leads to a lots of convergence
+	\item It optimally memorizes a large fraction of augmented states to save memory
+	\item a large fraction of state space may be unreachable from $s_0$ and it avoid storing information it does not need
+	\item it should however use a heuristic to treat states that has never been encountered when stopped prematurely, could be a fall back or a default action.
+\end{itemize}
 
-\textsc{GLUTTON} introduces an off-line algorithm based on LR\textsuperscript{2}TDP.
-The \emph{Max-Reward} heuristic used to evaluate \todo{the what?} relies on knowing the maximum reward $R_{max}$ any action can yield in a state or an upper bound on it.
-In addition to LR\textsuperscript{2}TDP, it introduces the following mechanisms to optimize for large branching factors:
+\subsubsection{GLUTTON}
 
-\todo{rewrite this list}
-\myworries{is this really necessary?}
+Glutton uses the \emph{Max-Reward} heuristic that relies on knowing the maximum reward $R_{max}$ any action can yield in a state or an upper bound on it.
+Large branching factors induce that the computation of the Bellman Backups becomes prohibitively expensive.
+Glutton uses the following mechanisms to optimize for large branching factors:
+
 \begin{itemize}
-	\item Sub sampling the transition function, is not enough to decrease the amount of computations yet
+	\item Subsampling the transition function, is not enough to decrease the amount of computations yet
 	\item Separating out Natural Dynamics: to reuse variable samples when generator successors for multiple actions, by separating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both.
@@
 \end{itemize}
-
 %---------------------------------------------------------------------
-%During IPPC-11 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT.
+During IPPC-11 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT.
 This caused to wonder whether LRTDP planners could outperform UCT based systems.
@@
 As PROST employed UCT in an online manner, GOURMAND is an online adaptation of the GLUTTON algorithm to test whether LRTDP performs better if it is employed online.
-%
-%UCT picks an action based on it current quality estimate and an \emph{exploration term} which forces the planner to choose actions that have rarely been tried in the past.
+
+UCT picks an action based on it current quality estimate and an \emph{exploration term} which forces the planner to choose actions that have rarely been tried in the past.
 This makes UCT suitable for a wider scale of scenarios but also implies an unreliable termination condition.
 
-Because real world domains contain Natural Dynamics that introduce large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of states the planner may never reach in a lifetime.
-Such problems are far better solved using online planners by finding an optimal policy $\tau$* or an approximation of this polict for the \emph{current} state, executing it and repeating.
-This is done by choosing a certain lookahead value $L$ and solving the MDP \emph{M\textsubscript{s}(L)} to solve \emph{M\textsubscript{0}(H)} where L $<$ H and then select \emph{$\pi$*\textsubscript{L}(s, L)} using the evaluation criteria.
-This lookahead value is determined using the per-process time constraint.\todo{elaborate on the per-process time constraint}
+Because real world domains contain Natural Dynamics that introduce large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of state the planner may never reach in a lifetime.
+Such problems are far better solved using online planners by finding a $\tau$* or an approximation for the current state, executing it and repeating.
+This is done by choosing a certain lookahead  L and solving MDP \emph{M\textsubscript{s}(L)} to solve \emph{M\textsubscript{0}(H)} where L $<$ H and then select \emph{$\pi$*\textsubscript{L}(s, L)} recommended by the optimal policy.
+This lookahead value is determined using the per-process time constraint.
 
-\subsection{GOURMAND}
-\textsc{GOURMAND}, an online adaptation of the \textsc{GLUTTON} planner answers these remarks by adding a lookahead value $L$. \todo{still finish this}
-
-% always makes an informed choice in any state where it ends up when the time T allocated for solving the MDP runs out because of the online fashion it uses LRTDP.
+\subsubsection{GOURMAND}
+In contrast to GLUTTON, GOURMAND always makes an informed choice in any state where it ends up when the time T allocated for solving the MDP runs out because of the online fashion it uses LRTDP.
 GOURMAND first divides the time among all remaining epochs, determines the largest lookahead L for which it can almost certainly solve any remaining epoch if T is assigned.

### 2014-04-08 FinalPaper/paper.tex
changed all lrtdp

--- 2014-04-08 FinalPaper/paper.tex
@@
 \section{Background}
-\ref{sec:background}
+\label{sec:background}
 
@@
 
-For a planner to be succesfull in finite-horizon MDPs it needs to be scalable and sensitive to an expected reward maximization, the evaluation criteria of these domains.
-This caused for  LRTDP planners to emerge.
+For a planner to be successful in finite-horizon MDPs it needs to be scalable and sensitive to an expected reward maximization, the evaluation criteria of these domains.
+To cope with these domains, trial based methods such as \emph{Labelled Real-Time Dynamic Programmers} (LRTDPs) have been introduced and optimized to find an optimal policy in a dynamic programming-based way.
 
@@
 
-\subsection{The rise of LRTDP planners}
+\subsection{LRTDP algorithms}
 
-\myworries{Still need to introduce LRTDPs better and the reason why they emerged, ook UCT introduceren?}
+The LRTDP algorithm tries to reach the goal using a series of trials starting from $s_0$ and is specifically convenient for only memorizing states reachable from $s_0$ and therefore uses and needs less memory space in the following manner:
 
-\emph{Labeled Real-Time Dynamic Programmers} (LRTDPs) operate a series of trials starting from $s_0$.
+\begin{enumerate}
+	\item Start trial at $s_0$
+	\item Take action based on current value function $V$
+	\item Perform Bellman backup
+	\item Sample the outcome and update $V$
+	\item Transition to the next state
+	\item Repeat step 2 - 5 until a goal, dead end or converged state is reached
+	\item Check if all states have converged, otherwise start a new trial (step 2 - 6)
+\end{enumerate}
 
-\todo{Make this list more technical}
-
-\begin{itemize}
-	\item Trials start at $s_0$
-	\item Choose best action greedily in the current state based on current $V$ value function
-	\item Perform Bellman backup on the current state
-	\item Sample the outcome as the chosen action
-	\item Transition to the new state
-	\item Repeat until a goal, dead end or converged state is reached
-	\item After trial, special convergence check on all states in the trial is performed to prove the convergence of these values
-\end{itemize}
-
-Adapting LRTDP to a finite horizon MDP \emph{M(H)} or \emph{LRTDP-FH} requires for each trial to start at ($s_0$) and run for at most $H$ time steps.
-The resulting states would translate to the goal states in a goal-oriented MDP.
+Adapting LRTDP to a finite horizon MDP \emph{M(H)} solver \emph{LRTDP-FH} requires for each trial to start at $s_0$ or $M(s_0, H)$ and run for at most $H$ time steps.
+All states $H$ steps away from $s_0$ would translate to goal states in a goal-oriented MDP.
 \\
@@
 %However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.
+The \emph{Labeled Reverse Real-Time Dynamic Programmer} (LR$^2$TDP) uses \emph{reverse iterative deepening} and LRTDP-FH to incrementally solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$ by relying on the fact that a successful policy can be produced by solving a MDP-FH $M(h)$ for a smaller horizon $h < H$.
+%LR$^2$TDP\@ iterates on the distance from the horizon and allows for reusing precomputed state-action plans from converged states.
 
-A \emph{Labeled Reverse Real-Time Dynamic Programmer} (LR$^2$TDP) uses \emph{reverse iterative deepening} and LRTDP-FH to incrementally solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$ in order by relying on the fact that a successful policy can be produced by solving an MDP-FH $M(H)$ for a smaller horizon $h < H$.
-A LR$^2$TDP\@ iterates on the distance from the horizon and allows for reusing precomputed state-action plans from converged states.
-However when dealing with large branching factors Bellman computations tend to become prohibitively expensive.
-
-\todo{nog een lijstje schrijven van hoe het werkt en waarom er verbetering nodig is}
-
-%\begin{itemize}
-%	\item In many MDPs, the optimal policy $M(h)$ for some $h < H$ is near optimal for M(H), it thus may have a solution when stopped prematurely
-%	\item it's trials are very short because backchaining from the goal leads to a lots of convergence
-%	\item It optimally memorizes a large fraction of augmented states to save memory
-%	\item a large fraction of state space may be unreachable from $s_0$ and it avoid storing information it does not need
-%	\item it should however use a heuristic to treat states that has never been encountered when stopped prematurely, could be a fall back or a default action.
-%\end{itemize}
+\begin{enumerate}
+	\item Run LRTDP-FH to solve $M(1)$ or $M(s_0, 1)$
+	\item Run LRTDP-FH to solve $M(h)$ or $M(s_0, h)$ where $h < H$ by backchaining from the horizon $H$
+	\item Repeat step 2 until $H$ is reached or time has run out
+\end{enumerate}
+By iterating over the distance from the horizon the state values computed when solving $M(1)$, $M(2)$, \ldots, $M(h-1)$ can be reused.
+Solving $M(h)$ thus only takes an incremental effort over the solution of $M(h-1)$.
+If stopped prematurely  (LR$^2$TDP) is likely to provide a better policy as for many MDPs the optimal policy $\tau^*$ is optimal or near-optimal for $M(H)$.
+By itself,  (LR$^2$TDP) would however not perform well in MDPs with large branching factors as computing the Bellman backups would become too expensive carried out over a large fraction of the state space.
 

### 2014-04-08 FinalPaper/paper.tex
Glutton herschreven

@@
 
-\subsection{\textsc{Glutton}}
-
-\textsc{Glutton} introduces an off-line algorithm based on LR$^2$TDP.
-The \emph{Max-Reward} heuristic used to evaluate \todo{the what?} relies on knowing the maximum reward $R_{max}$ any action can yield in a state or an upper bound on it.
-In addition to LR$^2$TDP, it introduces the following mechanisms to optimize for large branching factors:
-
-\todo{rewrite this list}
-
-\myworries{is this really necessary?}
-
-\begin{itemize}
-	\item Sub sampling the transition function, is not enough to decrease the amount of computations yet
-	\item Separating out Natural Dynamics: to reuse variable samples when generator successors for multiple actions, by separating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both.
-	\item Caching the transition function samples: as LR$^2$TDP populates the state-value hash table lazily, \textsc{Glutton} uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same $(s,h)$ pair.
-When full, it chooses state-action pars for eviction ans replacement randomly.
-	\item Default policies: \textsc{Glutton} uses 3 tricks to determine a policy when stopped prematurely.
-It compares the optimal action from a $h'$ with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.
-\end{itemize}
-
+\subsection{\textsc{GLUTTON}}
+The \textsc{GLUTTON} planner enhances LR$^2$TDP to cope with large branching factors by using several optimization techniques.
+It employs LR$^2$TDP in an off-line fashion by initializing the algorithm with the \emph{Max-Reward} heuristic that places an upper bound on the optimal value function $V^*$.
+It optimizes for large branching factors by performing the transition function in a subset of transition states $s'$.
+It distinguished between \emph{exogenous} effects caused by natural dynamics and \emph{pure} effects caused by the action itself and a mixed of both.
+It also utilized the saved memory space caused by mapping only the converged states in the hash-table by using the free space as cache for storing successor states computed using the transition function.
+Since \textsc{GLUTTON} subsamples the transition function, it may not know a good action to perform in states it missed due to subsampling.
+To compensate for these states, \textsc{GLUTTON} has to resort to a \emph{default policy}.
+\todo{Wel of niet de default policy uitleggen}.
 %---------------------------------------------------------------------
@@
 
-Because real world domains contain Natural Dynamics that introduce large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of states the planner may never reach in a lifetime.
-Such problems are far better solved using online planners by finding an optimal policy $\tau^*$ or an approximation of this policy for the \emph{current} state, executing it and repeating.
-This is done by choosing a certain lookahead value $L$ and solving the MDP $M_s(L)$ to solve $M_0(H)$ where L $<$ H and then select $\pi^*_L(s,L)$ using the evaluation criteria.
+When however dealing with large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of states the planner may never reach in a lifetime.
+Such problems are far better solved using online planners that find an optimal policy $\tau^*$ or an approximation of this policy for the \emph{current} state.
+%This is done by choosing a certain lookahead value $L$ and solving the MDP $M_s(L)$ to solve $M_0(H)$ where L $<$ H and then select $\pi^*_L(s,L)$ using the evaluation criteria.
 This lookahead value is determined using the per-process time constraint.
-
-\todo{elaborate on the per-process time constraint}
 

### 2014-04-08 FinalPaper/paper.tex
rewritten gourmand

@@
 
-\subsection{\textsc{Gourmand}}
-\textsc{Gourmand}, an online adaptation of the \textsc{Glutton} planner answers these remarks by adding a lookahead value $L$. \todo{still finish this}
+\subsection{\textsc{GOURMAND}}
+The \textsc{GOURMAND} is an online adaptation of the \textsc{GLUTTON} planner and ensures a good \emph{anytime performance} using a lookahead value $L$ to approximate a near-optimal policy for $M(H)$ where $L < H$ and is dynamically chosen.
+At every iteration over the distance to the horizon $H$, it divides the total remaining time $\overline{T}$ equally amongst the remaining iterations and virtually allocates time: $T_t = \frac{\overline{T}}{H - t}$.
+During the first epoch, or iteration it estimates how long solving a state takes for different lookahead values.
+Using this estimate and a virtual time allocation \textsc{GOURMAND} determines the largest lookahead value $L_t$ for which it can almost certainly solve the current epoch  and whether it could solve for a larger lookahead $\widehat{L}_t$ by taking away time from the next epoch still guaranteeing that it can solve both epochs.
+If so, it solves the current epoch for $\widehat{L}_t$ and otherwise $L_t$.
+This way \textsc{GOURMAND} never has to resort to default policies and converges relatively fast to a good policy in an online fashion.
+The \textsc{GOURMAND} planner has proven to outperform the current state of the art planners utilizing its robust any-time performance \cite{kolobov2012gourmand}.
 

### 2014-04-08 FinalPaper/paper.tex
gourmand adapted, maybe add a concluding paragraph about the planners

@@
 During the first epoch, or iteration it estimates how long solving a state takes for different lookahead values.
-Using this estimate and a virtual time allocation \textsc{GOURMAND} determines the largest lookahead value $L_t$ for which it can almost certainly solve the current epoch  and whether it could solve for a larger lookahead $\widehat{L}_t$ by taking away time from the next epoch still guaranteeing that it can solve both epochs.
+Using this estimate and a virtual time allocation \textsc{GOURMAND} determines the largest lookahead value $L_t$ for which it can almost certainly solve the current epoch  and whether it could solve for a larger lookahead $\widehat{L}_t$ by taking away time from the next epoch, still guaranteeing that it can solve both epochs.
 If so, it solves the current epoch for $\widehat{L}_t$ and otherwise $L_t$.
 This way \textsc{GOURMAND} never has to resort to default policies and converges relatively fast to a good policy in an online fashion.
-The \textsc{GOURMAND} planner has proven to outperform the current state of the art planners utilizing its robust any-time performance \cite{kolobov2012gourmand}.
+The \textsc{GOURMAND} planner has proven to outperform the current state of the art planners utilizing its robust any-time performance \cite{kolobov2012gourmand} in the following manner:
 
-% always makes an informed choice in any state where it ends up when the time T allocated for solving the MDP runs out because of the online fashion it uses LRTDP.
-\textsc{Gourmand} first divides the time among all remaining epochs, determines the largest lookahead L for which it can almost certainly solve any remaining epoch if T is assigned.
-It then checks if it can solve even for a larger lookahead L by taking away a small configuration time from future epochs  while still guaranteeing that it can solve for Lookahead L in each of them.
-This was \textsc{Gourmand} adaptively picks a good lookahead value at each decision epoch given the per-process constraint T.
-This can only be achieved by knowing how long it takes for LRTDP to solve a state for certain lookahead values.
-It uses LR\textsuperscript{2}TDP to collect this data.
-This version of LRTDP is more efficient because of the early convergences and it allows measuring how long on average the solving of a task takes.
-\textsc{Gourmand} uses the same engineering optimizations to to handle evaluate actions, iterating over the successors of s under a by the Bellman Backups.
-\textsc{Gourmand} eventually outperforms both \textsc{Glutton} and PROST, the winner of the IPPC-11\cite{keller2012prost}.
+\begin{enumerate}
+	\item Start \textsc{GOURMAND} at $s_0$
+	\item Initialization of first epoch
+	\begin{enumerate}
+		\item Virtually allocate time for  $T_t = \frac{\overline{T}}{H}$
+		\item Run LR$^2$TDP($M_s(H), T_t$)
+		\item Adjust running average $\overline{T}$
+	\end{enumerate}
+	\item Virtually allocate time  $T_t = \frac{\overline{T}}{H - t}$
+	\item Check if lookahead can be increased $\widehat{L}_t = L_t + 1$ else $\widehat{L}_t = L_t $
+	\item Run LR$^2$TDP($M_s(\widehat{L}), \widehat{T}_t$)
+	\item Adjust running average $\overline{T}$
+	\item Determine action based on (near) optimal $\tau^*$
+	\item Transition to next state
+	\item Repeat steps 3 - 8 until time has run out
+\end{enumerate}
+
+\todo{write some kind of conclusion}
 

### 2014-04-08 FinalPaper/paper.tex
changed to comments

--- 2014-04-08 FinalPaper/paper.tex
@@
 By introducing finite horizon MDPs in IPPC-11, state of the art planners have been adapted to cope with large branching factors to approximate infinite planning problems.
-Because these "planning problems" can often be solved using a smaller horizon $h < H$ as introduced in Section \ref{sec:background}, they represent optimization problems rather than planning problems, favoring current state of the art planners over replanners.
-This section introduces the shift of the planners towards optimization  by discussing FF-replan and a current state of the art probabilistic planner \textsc{GOURMAND} and its predecessors.
+Because these ``planning problems'' can often be solved using a smaller horizon $h < H$ as introduced in Section \ref{sec:background}, they represent optimization problems rather than planning problems, favoring current state of the art planners over replanners.
+This section introduces the shift of the planners towards optimization  by discussing FF-replan and a current state of the art probabilistic planner \textsc{Gourmand} and its predecessors.
 
@@
 
-Adapting LRTDP to a finite horizon MDP \emph{M(H)} solver \emph{LRTDP-FH} requires for each trial to start at $s_0$ or $M(s_0, H)$ and run for at most $H$ time steps.
+Adapting LRTDP to a finite horizon MDP $M(H)$ solver \emph{LRTDP-FH} requires for each trial to start at $s_0$ or $M(s_0, H)$ and run for at most $H$ time steps.
 All states $H$ steps away from $s_0$ would translate to goal states in a goal-oriented MDP.
@@
 
-\subsection{\textsc{GLUTTON}}
-The \textsc{GLUTTON} planner enhances LR$^2$TDP to cope with large branching factors by using several optimization techniques.
+\subsection{\textsc{Glutton}}
+The \textsc{Glutton} planner enhances LR$^2$TDP to cope with large branching factors by using several optimization techniques.
 It employs LR$^2$TDP in an off-line fashion by initializing the algorithm with the \emph{Max-Reward} heuristic that places an upper bound on the optimal value function $V^*$.
@@
 It also utilized the saved memory space caused by mapping only the converged states in the hash-table by using the free space as cache for storing successor states computed using the transition function.
-Since \textsc{GLUTTON} subsamples the transition function, it may not know a good action to perform in states it missed due to subsampling.
-To compensate for these states, \textsc{GLUTTON} has to resort to a \emph{default policy}.
+Since \textsc{Glutton} subsamples the transition function, it may not know a good action to perform in states it missed due to subsampling.
+To compensate for these states, \textsc{Glutton} has to resort to a \emph{default policy}.
 \todo{Wel of niet de default policy uitleggen}.
@@
 
-\subsection{\textsc{GOURMAND}}
-The \textsc{GOURMAND} is an online adaptation of the \textsc{GLUTTON} planner and ensures a good \emph{anytime performance} using a lookahead value $L$ to approximate a near-optimal policy for $M(H)$ where $L < H$ and is dynamically chosen.
+\subsection{\textsc{Gourmand}}
+The \textsc{Gourmand} is an online adaptation of the \textsc{Glutton} planner and ensures a good \emph{anytime performance} using a lookahead value $L$ to approximate a near-optimal policy for $M(H)$ where $L < H$ and is dynamically chosen.
 At every iteration over the distance to the horizon $H$, it divides the total remaining time $\overline{T}$ equally amongst the remaining iterations and virtually allocates time: $T_t = \frac{\overline{T}}{H - t}$.
 During the first epoch, or iteration it estimates how long solving a state takes for different lookahead values.
-Using this estimate and a virtual time allocation \textsc{GOURMAND} determines the largest lookahead value $L_t$ for which it can almost certainly solve the current epoch  and whether it could solve for a larger lookahead $\widehat{L}_t$ by taking away time from the next epoch, still guaranteeing that it can solve both epochs.
+Using this estimate and a virtual time allocation \textsc{Gourmand} determines the largest lookahead value $L_t$ for which it can almost certainly solve the current epoch  and whether it could solve for a larger lookahead $\widehat{L}_t$ by taking away time from the next epoch, still guaranteeing that it can solve both epochs.
 If so, it solves the current epoch for $\widehat{L}_t$ and otherwise $L_t$.
-This way \textsc{GOURMAND} never has to resort to default policies and converges relatively fast to a good policy in an online fashion.
-The \textsc{GOURMAND} planner has proven to outperform the current state of the art planners utilizing its robust any-time performance \cite{kolobov2012gourmand} in the following manner:
+This way \textsc{Gourmand} never has to resort to default policies and converges relatively fast to a good policy in an online fashion.
+The \textsc{Gourmand} planner has proven to outperform the current state of the art planners utilizing its robust any-time performance \cite{kolobov2012gourmand} in the following manner:
 
 \begin{enumerate}
-	\item Start \textsc{GOURMAND} at $s_0$
+	\item Start \textsc{Gourmand} at $s_0$
 	\item Initialization of first epoch

### 2014-04-08 FinalPaper/paper.tex

@@
 Using the baseline test introduced by Little et al.\@ \cite{little2007probvsreplan}, we can evaluate the probabilistically interestingness of these domains and evaluate the performance of FF-Replan vs.\@ a state of the art probabilistic planner: \textsc{Gourmand}.
+
+\section{Domain Description}
+
+Unmanned Aerial Vehicles (UAVs), or commonly called \emph{Drones} are aircrafts
+without a pilot and often autonomously controlled. Drones are widely used for
+military as well as for civil uses, including inspecting pipelines, counting
+wildlife, agriculture, filming or delivering supplies to inaccessible areas.
+As many uses cases there are, there are many forms of UAVs, bigger fixed wing
+aircrafts, or small helicopter or quad copter like aircrafts that can hover at
+a certain position in the air.
+
+We are particularly interested in monitoring, for example crops or livestock,
+and surveillance UAVs that work together to monitor a large area. Each UAV
+monitors a part of the total area, and if it has monitored something, it has
+to communicate this to a base station. This can't be done directly due to the
+large distance, instead it has to go through neighboring UAVs.
+
+Communicating the message from the sensing UAV to the base station can be
+expressed as a probabilistic planning problem. Initially the sensing UAV
+has the package that has to be sent, and the goal is to bring this package to
+the base station. Each time the package is passed to the neighboring UAV,
+there is a possibility the package is not received correctly. The bigger the
+distance, the higher the probability the delivery failed.
+
+%% TODO maybe UAVs can be on or of too, so it's forced to use a further UAV.
+%% TODO what's also interesting is that Amazon.com uses drones for package deliveries
 

### 2014-04-08 FinalPaper/paper.tex
rewrote introduction and changed order of section domains and section planners

@@
 \section{Introduction}
+The introduction of the International Planning Competition (IPC) in 1998 furthered the field of automated planning and scheduling.
+Since then several state-of-the-art planners such as the FF-planner \cite{Hoffmann01theff} have been introduced optimized for the initial classical planning problems.
+Surprisingly well-performing planners have caused the field to readjust the then supposedly challenging domains to provide a challenge for a wide variety of planners.
+By doing so, the definition of an interesting planning problem has been modified.
 
-Since the first the International Probabilistic Planning Competition (IPPC),
-problems have undergone radical changes. Dominating planners of previous
-incorporations had a strong focus on goal-oriented MDPs, determinizing and
-using powerful classical planners (e.g. FF \cite{Hoffmann01theff}) and
-replanning. New benchmark problems have demonstrated weaknesses in existing
-solution techniques.
+The entrance of FF-Replan \cite{FFReplan}, a replanner based on determinization techniques and the classical FF planner, surprisingly outperformed other participating MDP solvers in the International Probabilistic Planning Competition (IPPC) '04.
+As a result, Little et al.
+have argued for \emph{probabilistically interesting} domains \cite{little2007probvsreplan} and finite horizon MDPs were employed in IPPC-11.
+These approximations of infinite planning problems however strongly resemble optimization problems rather than the goal oriented initial planning domains.
+This shift in the current interesting domains caused the state-of-the-art planners to cope with the large branching factors that are introduced using finite horizon MDPs.
 
-Little and Thi\'ebaux have developed a baseline test in
-\cite{little2007probvsreplan} to evaluate the problems of the fifth International
-Planning Competition (IPC-5). This test determines if a planning problem is
-`probabilistically interesting'. Problems that fail this test are classical
-planning problems in disguise. Knowing this it is easy to design a problem
-where a replanner performs badly or incredibly well.
+This paper presents an overview of interesting domains and concurrent planners that were involved in the redefinition of an interesting planning problem.
+An interesting currently relevant domain is proposed and evaluated amongst previously defined domains.
+By using the probabilistic interestingness baseline test as introduced by Little et al.
+\cite{little2007probvsreplan} a recommendation will be made for the optimal planner to match this problem.
 
-The IPPC-11 introduced Relation Dynamic Influence Diagram Language (RDDL),
-which can design domains that are more probabilistically interesting. The top
-performers were PROST \cite{keller2012prost} and \textsc{Glutton}
-\cite{kolobov2012glutton}.
+Section \ref{sec:problem} introduced the problem formulation this paper addresses while Section \ref{sec:domaind} introduces the details of proposed domain.
+Section \ref{sec:background} introduced the appropriate prior knowledge and Section \ref{sec:domains} and \ref{sec:planners} the interesting domains and planners respectively.
+Section \ref{sec:experiment} briefly elaborates on a possible experiment set-up.
+Finally Section \ref{sec:conclusion} concludes on the evaluation of the domain and an appropriate planner.
 
-While it is interesting to make problems harder and invent better planning
-algorithms to solve those probabilistic complex problems, we evaluate whether
-or not these problems are coherent with real-world situations.
+%Little and Thi\'ebaux have developed a baseline test in
+%\cite{little2007probvsreplan} to evaluate the problems of the fifth International
+%Planning Competition (IPC-5). This test determines if a planning problem is
+%`probabilistically interesting'. Problems that fail this test are classical
+%planning problems in disguise. Knowing this it is easy to design a problem
+%where a replanner performs badly or incredibly well.
+%While it is interesting to make problems harder and invent better planning
+%algorithms to solve those probabilistic complex problems, we evaluate whether
+%or not these problems are coherent with real-world situations.
+%The IPPC-11 introduced Relation Dynamic Influence Diagram Language (RDDL),
+%which can design domains that are more probabilistically interesting. The top
+%performers were PROST \cite{keller2012prost} and \textsc{Glutton}
+%\cite{kolobov2012glutton}.
 
-The main contribution of this paper is an evaluation of FF-Replan versus a
-probabilistically state of the art planner \textsc{Gourmand} in the realistically
-augmented domains of IPPC-11. If these domains fail the baseline test proposed
-by Little et al\., they would translate to classical planning problems in
-disguise and could be easily solved by FF-Replan.
+%The main contribution of this paper is an evaluation of FF-Replan versus a
+%probabilistically state of the art planner \textsc{Gourmand} in the realistically
+%augmented domains of IPPC-11. If these domains fail the baseline test proposed
+%by Little et al\., they would translate to classical planning problems in
+%disguise and could be easily solved by FF-Replan.
 
@@
 \section{Problem formulation}
+\label{sec:problem}
 
@@
 \section{Domain Description}
+\label{sec:domaind}
 
@@
 
+\section{Domains}
+\label{sec:domains}
+
+Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
+Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}.
+This section describes interesting domains in which either FF-Replan or \textsc{Gourmand} prevailed during the International Probabilistic Planning Competitions.
+These domains are evaluated for how well they portray real-world scenarios.
+The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario.
+Little et al.'s baseline test helps us to predict which planner would perform well on these domains.
+We will then conclude our evaluation by comparing these results to the result of our experiments described in Section~\ref{sec:experiment}.
+
+\subsection{IPPC-11 Domains}
+
+The competitor FF-Replan \cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
+The baseline test of Little et al.\@ evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
+IPPC-11 responded by introducing more realistic MDPs and evaluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
+
+\textsc{Gourmand} vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}.
+PROST however mildly outperforms \textsc{Gourmand} on the Game of Life, SysAdmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
+
+\subsubsection{Navigation}
+
+The navigation domain represents a grid in which a robot must reach a goal.
+Every cell offers the robot a different chance of disappearing.
+The robot needs to choose a path which gets it to the goal most reliably within the finite horizon time \cite{sanner2011navigation}.
+Because \textsc{Gourmand} uses a dynamic lookahead, it performs quite well in this domain.
+
+%ADD IMAGE HERE
+
+\subsubsection{Traffic}
+This domain represents a simple binary version of the cell transition model (CTM) for modelling traffic based on the original CTM Tech Report \cite{sanner2011traffic}.
+Because of the binary variables and no intermediate variable restrictions, this model is simplified and ignores traffic aspects such as turns and turn probabilities.
+This model also uses concurrent actions and the total actions has an upper bound of $2^{\#~of~intersections}$.
+
+%ADD IMAGE HERE
+
+\subsection{Elevators}
+
+In the elevators domain there are a number of elevators delivering passengers
+to either the top or bottom floor. Potential passengers arrive at any floor at
+a certain rate (depending on which floor). The elevators can only move in the
+direction it is indicating, so passengers know whether to board or not. The
+goal of the elevators is to transport as many as possible passengers to their
+destinations.
+
+\subsection{SysAdmin}
+
+The SysAdmin domain describes a network of connected servers. Each server has
+a probability that it shuts down, and if is not running, it has a probability
+to reboot. The probability that a server shuts down depends on the number of
+running connected servers.
+
+%\subsection{IPPC-04 Domains}
+%Duing IPPC-04, the domains were written in the Probabilistic PLanning Domain Description Language (PPDDL). 30 trials per problem were to be solved in 15 minutes.
+%
+%\subsubsection{}
+%
+%\subsubsection{}
+
+\subsection{Real-World Domain Evaluation}
+
+\subsubsection{Navigation}
+
+In the navigation problem there is a chance that the robot disappears after
+entering a cell. The disappearing action is a dead end. Disappearing here is a
+metaphor for the robot breaking down, or that it disappears from the radar with
+the base station. In many of such cases it's a big problem, but can be repaired
+with a high cost. In the navigation domain a step to another cell has a cost of
+1. If instead of a dead end the cost is $n$ (e.g. 5) instead of 1, which
+represents the cost of repairing the robot, dead ends are removed. Without dead
+ends the problem becomes probabilistic uninteresting, which makes it suitable for
+replanning planners.
+
+\subsubsection{Traffic}
+
+The traffic domain describes a crossroad with traffic lights, modelled as
+cells. Either the north to south road has a green light, the west to east road
+or all lights are red. The model uses a finite state machine that handles the
+lights so that the lights are never green at the same time. This would be the
+only dangerous situation on the crossroad. The difficulty in this domain is
+the number of states, which grows exponentially with the number of cells.
+Besides that it is an uninteresting probabilistic problem because it does
+not satisfy the probabilistic interesting test.
+
+\subsubsection{Elevators}
+
+\subsection{Baseline test for Probabilistic Interesting domains}
+
+%---------------------------------------------------------------------
+
 \section{Planners}
@@
 This section introduces the shift of the planners towards optimization  by discussing FF-replan and a current state of the art probabilistic planner \textsc{Gourmand} and its predecessors.
-
-\myworries{misschien moet dat laatste zinnetje ergens anders?}
 
@@
 \todo{write some kind of conclusion}
-
-%---------------------------------------------------------------------
-
-\section{Domains}
-Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
-Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}.
-This section describes interesting domains in which either FF-Replan or \textsc{Gourmand} prevailed during the International Probabilistic Planning Competitions.
-These domains are evaluated for how well they portray real-world scenarios.
-The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario.
-Little et al.'s baseline test helps us to predict which planner would perform well on these domains.
-We will then conclude our evaluation by comparing these results to the result of our experiments described in Section~\ref{sec:experiment}.
-
-\subsection{IPPC-11 Domains}
-
-The competitor FF-Replan \cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
-The baseline test of Little et al.\@ evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
-IPPC-11 responded by introducing more realistic MDPs and evaluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
-
-\textsc{Gourmand} vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}.
-PROST however mildly outperforms \textsc{Gourmand} on the Game of Life, SysAdmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
-
-\subsubsection{Navigation}
-
-The navigation domain represents a grid in which a robot must reach a goal.
-Every cell offers the robot a different chance of disappearing.
-The robot needs to choose a path which gets it to the goal most reliably within the finite horizon time \cite{sanner2011navigation}.
-Because \textsc{Gourmand} uses a dynamic lookahead, it performs quite well in this domain.
-
-%ADD IMAGE HERE
-
-\subsubsection{Traffic}
-This domain represents a simple binary version of the cell transition model (CTM) for modelling traffic based on the original CTM Tech Report \cite{sanner2011traffic}.
-Because of the binary variables and no intermediate variable restrictions, this model is simplified and ignores traffic aspects such as turns and turn probabilities.
-This model also uses concurrent actions and the total actions has an upper bound of $2^{\#~of~intersections}$.
-
-%ADD IMAGE HERE
-
-\subsection{Elevators}
-
-In the elevators domain there are a number of elevators delivering passengers
-to either the top or bottom floor. Potential passengers arrive at any floor at
-a certain rate (depending on which floor). The elevators can only move in the
-direction it is indicating, so passengers know whether to board or not. The
-goal of the elevators is to transport as many as possible passengers to their
-destinations.
-
-\subsection{SysAdmin}
-
-The SysAdmin domain describes a network of connected servers. Each server has
-a probability that it shuts down, and if is not running, it has a probability
-to reboot. The probability that a server shuts down depends on the number of
-running connected servers.
-
-%\subsection{IPPC-04 Domains}
-%Duing IPPC-04, the domains were written in the Probabilistic PLanning Domain Description Language (PPDDL). 30 trials per problem were to be solved in 15 minutes.
-%
-%\subsubsection{}
-%
-%\subsubsection{}
-
-\subsection{Real-World Domain Evaluation}
-
-\subsubsection{Navigation}
-
-In the navigation problem there is a chance that the robot disappears after
-entering a cell. The disappearing action is a dead end. Disappearing here is a
-metaphor for the robot breaking down, or that it disappears from the radar with
-the base station. In many of such cases it's a big problem, but can be repaired
-with a high cost. In the navigation domain a step to another cell has a cost of
-1. If instead of a dead end the cost is $n$ (e.g. 5) instead of 1, which
-represents the cost of repairing the robot, dead ends are removed. Without dead
-ends the problem becomes probabilistic uninteresting, which makes it suitable for
-replanning planners.
-
-\subsubsection{Traffic}
-
-The traffic domain describes a crossroad with traffic lights, modelled as
-cells. Either the north to south road has a green light, the west to east road
-or all lights are red. The model uses a finite state machine that handles the
-lights so that the lights are never green at the same time. This would be the
-only dangerous situation on the crossroad. The difficulty in this domain is
-the number of states, which grows exponentially with the number of cells.
-Besides that it is an uninteresting probabilistic problem because it does
-not satisfy the probabilistic interesting test.
-
-\subsubsection{Elevators}
-
-\subsection{Baseline test for Probabilistic Interesting domains}
 

### 2014-04-09 FinalPaper/paper.tex
Working on domains... now, time for sleep

@@
 \usepackage{fixltx2e}
+\usepackage{cite}
 
@@
 
-This paper presents an overview of interesting domains and concurrent planners that were involved in the redefinition of an interesting planning problem.
+This paper presents a new domain involving Unmanned Aerial Vehicles (UAVs) that have to cooperate to deliver data packages from one UAV to the base station.
+To match this problem with an appropriate planner, this paper presents an overview of other interesting domains and probabilistic planners that were involved in the redefinition of an interesting planning problem.
+By evaluating the domains with the help of the probabilistic interestingness baseline test introduced by Little et al.
+\cite{little2007probvsreplan} a recommendation will be made for a suitable planner to match the UAV problem.
+%This paper presents an overview of interesting domains and concurrent planners that were involved in the redefinition of an interesting planning problem.
 An interesting currently relevant domain is proposed and evaluated amongst previously defined domains.
@@
 \section{Domains}
-\label{sec:domains}
 
-Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
+To identify unique properties of the domain and identify properties of the
+domain that work particularly well for a certain type of planner, we describe
+other domains used in the IPPC-11 competition and compare that with the UAV
+domain. Since Little and Thi\'ebauw's baseline test for \emph{probabilistic
+interestingness} of domains, domains of the IPPC competition have shifted to
+those probabilistically interesting domains, which are difficult for
+replanners. Often domains that don't pass this test are deemed to be classical
+planners in disguise, favoring the use of replanners.
+
+%Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
 Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}.
@@
 
-\subsection{IPPC-11 Domains}
+\subsection{IPPC Domains}
 
-The competitor FF-Replan \cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
-The baseline test of Little et al.\@ evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
-IPPC-11 responded by introducing more realistic MDPs and evaluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
+\subsubsection{Blocksworld}
 
-\textsc{Gourmand} vastly outperformed IPPC-11 UCT-based probabilistic track winner PROST by far on goal-oriented domains Navigation and Crossing Traffic \cite{kolobov2012gourmand}.
-PROST however mildly outperforms \textsc{Gourmand} on the Game of Life, SysAdmin and the Traffic domain as UCT does not need to perform expensive Bellman Backups on these domains that include large branching factors.
+A simple domain used in the competition of 2004 is the well known blocksworld
+domain. The uncertainty lies in that the gripper, used to move blocks, has a
+probability that it drops the blocks to the table. Another difference is that
+the blocks are colored, and the goal is to build a tower of certain colored
+blocks, rather than a tower with specific blocks. If for example there are
+four blue blocks, and the goal is a tower of three blue blocks, it does not
+matter which blue blocks are used.
 
@@
 The navigation domain represents a grid in which a robot must reach a goal.
-Every cell offers the robot a different chance of disappearing.
-The robot needs to choose a path which gets it to the goal most reliably within the finite horizon time \cite{sanner2011navigation}.
-Because \textsc{Gourmand} uses a dynamic lookahead, it performs quite well in this domain.
-
-%ADD IMAGE HERE
+Every cell offers the robot a different chance of disappearing. The robot needs
+to choose a path which gets it to the goal most reliably within the finite
+horizon time \cite{sanner2011navigation}.
 
 \subsubsection{Traffic}
-This domain represents a simple binary version of the cell transition model (CTM) for modelling traffic based on the original CTM Tech Report \cite{sanner2011traffic}.
-Because of the binary variables and no intermediate variable restrictions, this model is simplified and ignores traffic aspects such as turns and turn probabilities.
-This model also uses concurrent actions and the total actions has an upper bound of $2^{\#~of~intersections}$.
 
-%ADD IMAGE HERE
+This domain represents a simple binary version of the cell transition model
+(CTM) for modelling traffic based on the original CTM Tech Report
+\cite{sanner2011traffic}. Because of the binary variables and no intermediate
+variable restrictions, this model is simplified and ignores traffic aspects
+such as turns and turn probabilities. This model also uses concurrent actions
+and the total actions has an upper bound of $2^{\#~of~intersections}$.
 
-\subsection{Elevators}
+\subsubsection{Elevators}
 
-In the elevators domain there are a number of elevators delivering passengers
-to either the top or bottom floor. Potential passengers arrive at any floor at
-a certain rate (depending on which floor). The elevators can only move in the
-direction it is indicating, so passengers know whether to board or not. The
-goal of the elevators is to transport as many as possible passengers to their
-destinations.
+The IPPC-06 has an elevators domain, however we describe the latest IPPC-11
+elevators domain. In this domain there are a number of elevators delivering
+passengers to either the top or bottom floor. Potential passengers arrive at
+any floor at a certain rate (depending on which floor). The elevators can only
+move in the direction it is indicating, so passengers know whether to board or
+not. The goal of the elevators is to transport as many as possible passengers
+to their destinations.
 
-\subsection{SysAdmin}
+\subsubsection{SysAdmin}
 
@@
 
-%\subsection{IPPC-04 Domains}
-%Duing IPPC-04, the domains were written in the Probabilistic PLanning Domain Description Language (PPDDL). 30 trials per problem were to be solved in 15 minutes.
-%
-%\subsubsection{}
-%
-%\subsubsection{}
+\subsection{Domain Evaluation}
 
-\subsection{Real-World Domain Evaluation}
+The Blocksworld domain is ideal for
+replanning~\cite{FFReplan, little2007probvsreplan}. As the blocks fall on the
+table, which then can be picked up again, it has no dead ends. This makes it
+probabilistically uninteresting. For this domain FF-Repan performs really well.
 
-\subsubsection{Navigation}
+The IPPC-11 domains, Navigation, Traffic, Elevators and SysAdmin are finite-
+horizon domains. Navigation, however, is actually a goal oriented domain, if
+the goal is reached in the horizon. The method this is defined is that the goal
+state is defined as an absorbing state, and there is no reward or cost
+associated to staying in the goal state, until the horizon is reached.
+
+\textsc{Gourmand} vastly outperformed IPPC-11 UCT-based probabilistic track
+winner PROST by far on goal-oriented domains Navigation and Crossing Traffic
+\cite{kolobov2012gourmand}. PROST however mildly outperforms \textsc{Gourmand}
+on the Game of Life, SysAdmin and the Traffic domain as UCT does not need to
+perform expensive Bellman Backups on these domains that include large branching
+factors.
+
+The reason \textsc{Gourmand} performs quite well on the navigation domain is
+because it uses a dynamic lookahead.
 
@@
 
-\subsubsection{Traffic}
-
 The traffic domain describes a crossroad with traffic lights, modelled as
@@
 
-\subsubsection{Elevators}
+The UAV domain has a resemblance of the Navigation domain. Both are goal
+oriented and have to navigate something (either the robot itself, or a data
+package) from an initial state to a goal. Also after each step a dead end can
+be reached, the robot disappears or the data package is not delivered.
+The probability this happens is static in the navigation domain, but dependent
+on the neighbors in the UAV domain. This variable probability has a resemblance
+of the SysAdmin domain, where the probability that a server shuts down is also
+dependent on the neighbors.
 
-\subsection{Baseline test for Probabilistic Interesting domains}
+%The competitor FF-Replan \cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
+The baseline test of Little et al.\@ evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
+IPPC-11 responded by introducing more realistic MDPs and evaluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
 
-%---------------------------------------------------------------------
+%\subsection{IPPC-04 Domains}
+%Duing IPPC-04, the domains were written in the Probabilistic PLanning Domain Description Language (PPDDL). 30 trials per problem were to be solved in 15 minutes.
+%
 

### 2014-04-09 FinalPaper/paper.tex
Improving domains

--- 2014-04-09 FinalPaper/paper.tex
@@
 domain that work particularly well for a certain type of planner, we describe
-other domains used in the IPPC-11 competition and compare that with the UAV
-domain. Since Little and Thi\'ebauw's baseline test for \emph{probabilistic
-interestingness} of domains, domains of the IPPC competition have shifted to
-those probabilistically interesting domains, which are difficult for
-replanners. Often domains that don't pass this test are deemed to be classical
-planners in disguise, favoring the use of replanners.
+other domains used in the IPPC and compare that with the UAV domain. Since
+Little and Thi\'ebauw's baseline test for \emph{probabilistic interestingness}
+of domains, domains of the IPPC competition have shifted to those
+probabilistically interesting domains, which are difficult for replanners.
+Often domains that don't pass this test are deemed to be classical planners in
+disguise, favoring the use of replanners.
 
@@
 horizon domains. Navigation, however, is actually a goal oriented domain, if
-the goal is reached in the horizon. The method this is defined is that the goal
-state is defined as an absorbing state, and there is no reward or cost
+the goal is reached in the horizon. The method how this is implemented is that
+the goal state is defined as an absorbing state, and there is no reward or cost
 associated to staying in the goal state, until the horizon is reached.
@@
 
-In the navigation problem there is a chance that the robot disappears after
-entering a cell. The disappearing action is a dead end. Disappearing here is a
-metaphor for the robot breaking down, or that it disappears from the radar with
-the base station. In many of such cases it's a big problem, but can be repaired
-with a high cost. In the navigation domain a step to another cell has a cost of
-1. If instead of a dead end the cost is $n$ (e.g. 5) instead of 1, which
-represents the cost of repairing the robot, dead ends are removed. Without dead
-ends the problem becomes probabilistic uninteresting, which makes it suitable for
-replanning planners.
+The domains are constructed such that it will challenge planners to perform
+better. This causes that there are issues with the domains when comparing them
+with the real world.
+
+In the navigation problem there is a chance that the robot
+disappears after entering a cell. The disappearing action is a dead end.
+Disappearing here is a metaphor for the robot breaking down, or that it
+disappears from the radar with the base station. In many of such cases it's a
+big problem, but can be repaired with a high cost. In the navigation domain a
+step to another cell has a cost of 1. If instead of a dead end the cost is $n$
+(e.g. 5) instead of 1, which represents the cost of repairing the robot, dead
+ends are removed. Without dead ends the problem becomes probabilistic
+uninteresting, which makes it suitable for replanning planners.
 

### 2014-04-09 FinalPaper/paper.tex
Remove some old text
Add label for domain

@@
 
-This paper presents a new domain involving Unmanned Aerial Vehicles (UAVs) that have to cooperate to deliver data packages from one UAV to the base station.
+This paper presents a new domain involving Unmanned Aerial Vehicles (UAVs) cooperating to deliver data packages from one UAV to the base station.
 To match this problem with an appropriate planner, this paper presents an overview of other interesting domains and probabilistic planners that were involved in the redefinition of an interesting planning problem.
@@
 \cite{little2007probvsreplan} a recommendation will be made for a suitable planner to match the UAV problem.
-%This paper presents an overview of interesting domains and concurrent planners that were involved in the redefinition of an interesting planning problem.
-An interesting currently relevant domain is proposed and evaluated amongst previously defined domains.
-By using the probabilistic interestingness baseline test as introduced by Little et al.
-\cite{little2007probvsreplan} a recommendation will be made for the optimal planner to match this problem.
 
@@
 Finally Section \ref{sec:conclusion} concludes on the evaluation of the domain and an appropriate planner.
-
-%Little and Thi\'ebaux have developed a baseline test in
-%\cite{little2007probvsreplan} to evaluate the problems of the fifth International
-%Planning Competition (IPC-5). This test determines if a planning problem is
-%`probabilistically interesting'. Problems that fail this test are classical
-%planning problems in disguise. Knowing this it is easy to design a problem
-%where a replanner performs badly or incredibly well.
-%While it is interesting to make problems harder and invent better planning
-%algorithms to solve those probabilistic complex problems, we evaluate whether
-%or not these problems are coherent with real-world situations.
-%The IPPC-11 introduced Relation Dynamic Influence Diagram Language (RDDL),
-%which can design domains that are more probabilistically interesting. The top
-%performers were PROST \cite{keller2012prost} and \textsc{Glutton}
-%\cite{kolobov2012glutton}.
-
-%The main contribution of this paper is an evaluation of FF-Replan versus a
-%probabilistically state of the art planner \textsc{Gourmand} in the realistically
-%augmented domains of IPPC-11. If these domains fail the baseline test proposed
-%by Little et al\., they would translate to classical planning problems in
-%disguise and could be easily solved by FF-Replan.
-
-%\begin{itemize}
-%	\item Describe probabilistic planning problem
-%	\item Introduce planning for uncertainty
-%	\item Describe how deterministic classical planners can be used in probabilistic domains and motivate why this is interesting
-%	\item Introduce the qualities of replanning and the second planning algorithm
-%	\item Describe the need for a new domain for real world applications
-%	\item Describe the goal and tools used to reach this goal
-%\end{itemize}
 
@@
 
-%% TODO maybe UAVs can be on or of too, so it's forced to use a further UAV.
-%% TODO what's also interesting is that Amazon.com uses drones for package deliveries
+\todo{TODO maybe UAVs can be on or of too, so it's forced to use a further UAV.}
+\todo{TODO what's also interesting is that Amazon.com uses drones for package deliveries}
 
@@
 
-%Following existing domains were said to be probabilistically interesting:
-%
-%\begin{itemize}
-%	\item Drive
-%	\item Exploding blocksworld
-%	\item Pitchcatch
-%	\item Schedule
-%	\item Tireworld
-%\end{itemize}
-
-%---------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------------------------------------
 
 \section{Domains}
+\label{sec:domains}
 
@@
 disguise, favoring the use of replanners.
-
-%Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed.
-Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}.
-This section describes interesting domains in which either FF-Replan or \textsc{Gourmand} prevailed during the International Probabilistic Planning Competitions.
-These domains are evaluated for how well they portray real-world scenarios.
-The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario.
-Little et al.'s baseline test helps us to predict which planner would perform well on these domains.
-We will then conclude our evaluation by comparing these results to the result of our experiments described in Section~\ref{sec:experiment}.
 
@@
 
-%The competitor FF-Replan \cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty.
-The baseline test of Little et al.\@ evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners.
-IPPC-11 responded by introducing more realistic MDPs and evaluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.
-
-%\subsection{IPPC-04 Domains}
-%Duing IPPC-04, the domains were written in the Probabilistic PLanning Domain Description Language (PPDDL). 30 trials per problem were to be solved in 15 minutes.
-%
+%---------------------------------------------------------------------------------------------------------------------------------
 
@@
 
-%However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.
 The \emph{Labeled Reverse Real-Time Dynamic Programmer} (LR$^2$TDP) uses \emph{reverse iterative deepening} and LRTDP-FH to incrementally solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$ by relying on the fact that a successful policy can be produced by solving a MDP-FH $M(h)$ for a smaller horizon $h < H$.
-%LR$^2$TDP\@ iterates on the distance from the horizon and allows for reusing precomputed state-action plans from converged states.
 
@@
 %---------------------------------------------------------------------
-%During IPPC-11 1 out of 5 planners used a LRTDP-based system and managed to outperform three other planners using the dominant algorithm for probabilistic planning: UCT.
-This caused to wonder whether LRTDP planners could outperform UCT based systems.
-UCT forces an expert to guess a non-shortsighted lookahead value for which it should be able to converge on encountered states.
-Choosing this value can have very bad consequences and its existence causes the UCT to require some input, taking away from its autonomicity.
-At the IPPC-11 \textsc{Glutton} was an offline LRTDP based planner that came second.
-As PROST employed UCT in an online manner, \textsc{Gourmand} is an online adaptation of the \textsc{Glutton} algorithm to test whether LRTDP performs better if it is employed online.
-%
-%UCT picks an action based on it current quality estimate and an \emph{exploration term} which forces the planner to choose actions that have rarely been tried in the past.
-This makes UCT suitable for a wider scale of scenarios but also implies an unreliable termination condition.
 
@@
 Such problems are far better solved using online planners that find an optimal policy $\tau^*$ or an approximation of this policy for the \emph{current} state.
-%This is done by choosing a certain lookahead value $L$ and solving the MDP $M_s(L)$ to solve $M_0(H)$ where L $<$ H and then select $\pi^*_L(s,L)$ using the evaluation criteria.
-This lookahead value is determined using the per-process time constraint.
 
@@
 
-\subsubsection{PROST}
-
-\subsubsection{FF-H+}
-
-%\subsection{Probabilistic Planning via Determinization in Hindsight (2008)~\cite{yoon2008probabilistic}}
-%
-%Hindsight optimization is an online technique that evaluates one-step-reachable
-%states by sampling future outcomes to generate multiple non-stationary planning
-%problems which are deterministic and can be used using search. It re-interprets
-%FF-Replan's~\cite{FFReplan} strategy randomly generating a set of non-stationary
-%determinized problems and combining their solutions.
-
-%\subsection{Improving Determinization in Hindsight for Online Probabilistic Planning (2010)~\cite{yoon2010improving}}
-%Hindsight optimization has enjoyed some success for online probabilistic
-%planning. Although it has proven to be effective for many domains, it is
-%computationally expensive. This paper presents significant improvements.  1) a
-%method for detecting potential useful actions, 2) exploit determinism in the
-%domain by reusing relevant plans, 2) improves action evaluation by increasing
-%the chance that at least one deterministic plan reaches a goal.
-
-%\subsection{Probabilistic Planning in the Graphplan Framework (1999)~\cite{Blum99probabilisticplanning}}
-%% might not be necessary?
-%Graphplan is a successful planning algorithm for classical STRIPS domains. This
-%paper explores the extend it can be used in \emph{probabilistic} domains. The
-%paper discusses two variations of Graphplan: PGraphplan and TGraphplan.
-%PGraphplan produces an optimal plan, while TGraphplan produces a sub-optimal
-%plan but it has increased speed. By comparing the speed and quality of the
-%two planners the authors are able to estimate how far they are from the ideal.
-
-%\subsection{Compiling Conformant Probabilistic Planning Problems into Classical Planning (2013)~\cite{taig2013conformant}}
-% not necessary?
-
-%\subsection{How Much Does a Household Robot Need To Know In Order To Tidy Up? (2013)~\cite{nebel2013much}}
-%
-%For household robot planning, it appears easy, but actually involves
-%uncertainty. For tidying things up objects might not be there, or sensing
-%operations might tell things wrong. This paper looks into conditions for
-%classical planning in a replanning loop in order to solve nondeterministic
-%partially observable open domains This paper looks into conditions for
-%classical planning in a replanning loop in order to solve nondeterministic
-%partially observable open domains.
-
-%\subsection{Progressive heuristic search for probabilistic planning based on interaction estimates (2013)~\cite{martin2013progressive}}
-%
-%In this paper a probabilistic plan graph heuristic is described which computes
-%information about the interaction between actions and between propositions.
-%This information is used to find better relaxed plans to compute the
-%probability of success. This information guides a forward state space search
-%for high probability, non-branching seed plans. These plans are then used in
-%a planning and scheduling system that handles unexpected outcomes by runtime
-%replanning.
-
-%\subsection{Translation based approaches to probabilistic planning (2013)~\cite{taig2013translation}}
-% I don't think one is valuable
+\subsubsection{PROST ?}
 
@@
 
-%\section{Some papers}
-%
-%\begin{itemize}
-%	\item \cite{Hoffmann01theff}
-%	\item \cite{FFReplan}
-%	\item \cite{teichteil2010incremental}
-%	\item \cite{yoon2008probabilistic}
-%	\item \cite{teichteil2012fast}
-%	\item \cite{bonet2011planning}
-%	\item \cite{taig2013translation}
-%	\item \cite{martin2013progressive}
-%	\item \cite{taig2013conformant}
-%	\item \cite{2013workshop}
-%	\item \cite{nebel2013much}
-%	\item \cite{little2007probvsreplan}
-%	\item \cite{keller2012prost}
-%	\item \cite{kolobov2012glutton}
-%	\item \cite{sanner2008rddl}
-%	\item \cite{kolobov2012gourmand}
-%\end{itemize}
-
 \bibliographystyle{plain}

### 2014-04-09 FinalPaper/paper.tex
Start implementing Peter's comments

@@
 \subsection{Planning problems}
-\subsubsection{Classical Planning problems.
-} Planning is the process of computing several steps of a problem-solving procedure before executing any of them.
-In classical planning problems the environment is assumed to \emph{deterministic, observable and state}.
-Classical planning problems consists out of states, actions, conditions and a goal state and are solved using search and can be aided using heuristics.
+
+Planning is the process of computing several steps of a problem-solving procedure before executing any of them.
+
+\subsubsection{Classical Planning problems.}
+
+A classical planning problem is defined as states, actions, conditions and a goal state and are solved using search and can be aided using heuristics.
+The environment is assumed to be \emph{deterministic, observable and static}.
 The planner tries to find a sequence of actions such that a goal or maximum reward is achieved.
@@
 \subsubsection{Probabilistic Planning problems}
+
 Real-World applications are far from deterministic, induced by natural dynamics and chance.
@@
 These systems can be described using \emph{Markov Decision Processes} (MDPs) and can account for observable uncertainty.
-Probabilistic planning problems can be solved by evaluating iterations and creating policies to reach a goal state, either online or offline.
+Probabilistic planning problems can be solved by evaluating iterations and creating policies to reach a goal state, either online, while executing the plan, or offline, where all possibilities is calculated upfront.
 
 \subsection{Problem domains}
+
 \subsubsection{Goal-oriented MDPs.

### 2014-04-09 FinalPaper/paper.tex
Consistent use of separation lines
Less use of IPPC in the domains

@@
 
-%--------------------------------------------------------------------
+%------------------------------------------------------------------------------
 
@@
 
-%---------------------------------------------------------------------
+%------------------------------------------------------------------------------
 
@@
 
-%---------------------------------------------------------------------------------------------------------------------------------
+%------------------------------------------------------------------------------
 
@@
 Little and Thi\'ebauw's baseline test for \emph{probabilistic interestingness}
-of domains, domains of the IPPC competition have shifted to those
-probabilistically interesting domains, which are difficult for replanners.
-Often domains that don't pass this test are deemed to be classical planners in
-disguise, favoring the use of replanners.
+of domains, domains have shifted to those probabilistically interesting
+domains, which are difficult for replanners. Often domains that don't pass
+this test are deemed to be classical planners in disguise, favoring the use of
+replanners.
 
-\subsection{IPPC Domains}
-
-\subsubsection{Blocksworld}
-
+\paragraph{Blocksworld:}
 A simple domain used in the competition of 2004 is the well known blocksworld
@@
 
-\subsubsection{Navigation}
-
+\paragraph{Navigation:}
 The navigation domain represents a grid in which a robot must reach a goal.
@@
 
-\subsubsection{Traffic}
-
+\paragraph{Traffic:}
 This domain represents a simple binary version of the cell transition model
@@
 
-\subsubsection{Elevators}
+\paragraph{Elevators:}
+The elevators domain has evaluated between the competitions of 2006 and
+2011, we describe the latest version. In this domain there are a number of
+elevators delivering passengers to either the top or bottom floor. Potential
+passengers arrive at any floor at a certain rate (depending on which floor).
+The elevators can only move in the direction it is indicating, so passengers
+know whether to board or not. The goal of the elevators is to transport as many
+as possible passengers to their destinations.
 
-The IPPC-06 has an elevators domain, however we describe the latest IPPC-11
-elevators domain. In this domain there are a number of elevators delivering
-passengers to either the top or bottom floor. Potential passengers arrive at
-any floor at a certain rate (depending on which floor). The elevators can only
-move in the direction it is indicating, so passengers know whether to board or
-not. The goal of the elevators is to transport as many as possible passengers
-to their destinations.
-
-\subsubsection{SysAdmin}
-
+\paragraph{SysAdmin:}
 The SysAdmin domain describes a network of connected servers. Each server has
@@
 
-The IPPC-11 domains, Navigation, Traffic, Elevators and SysAdmin are finite-
+The newer  domains, Navigation, Traffic, Elevators and SysAdmin are finite-
 horizon domains. Navigation, however, is actually a goal oriented domain, if
@@
 
-\textsc{Gourmand} vastly outperformed IPPC-11 UCT-based probabilistic track
-winner PROST by far on goal-oriented domains Navigation and Crossing Traffic
-\cite{kolobov2012gourmand}. PROST however mildly outperforms \textsc{Gourmand}
-on the Game of Life, SysAdmin and the Traffic domain as UCT does not need to
-perform expensive Bellman Backups on these domains that include large branching
-factors.
-
-The reason \textsc{Gourmand} performs quite well on the navigation domain is
-because it uses a dynamic lookahead.
+\textsc{Gourmand} vastly outperformed the UCT-based PROST, the IPPC-11
+probabilistic track winner, by far on goal-oriented domains Navigation and
+Crossing Traffic \cite{kolobov2012gourmand}. This is because of the dynamic
+lookahead feature of \textsc{Gourmand}. PROST however mildly outperforms
+\textsc{Gourmand} on the Game of Life, SysAdmin and the Traffic domain as UCT
+does not need to perform expensive Bellman Backups on these domains that
+include large branching factors.
 
@@
 \todo{Wel of niet de default policy uitleggen}.
-%---------------------------------------------------------------------
+
+%------------------------------------------------------------------------------
 

### 2014-04-09 FinalPaper/paper.tex
Don't repeat what's already said in the introduction

@@
 domain that work particularly well for a certain type of planner, we describe
-other domains used in the IPPC and compare that with the UAV domain. Since
-Little and Thi\'ebauw's baseline test for \emph{probabilistic interestingness}
-of domains, domains have shifted to those probabilistically interesting
-domains, which are difficult for replanners. Often domains that don't pass
-this test are deemed to be classical planners in disguise, favoring the use of
-replanners.
+other domains used in the IPPC and compare that with the UAV domain.
 

### 2014-04-10 FinalPaper/paper.tex
todo changed

@@
 \begin{abstract}
+
+\todo{Rewrite abstract - Imara}
+
 	In contrast to current demand for probabilistically interesting domains in the International Probabilistic Planning Competitions, this papier argues for using real-world appropriate domains.
@@
 
+\todo{rewrite problem formulation - Arian}
 To evaluate FF-Replan and \textsc{Gourmand} in a real world domain a finite horizon MDP is used to represent the realistic \emph{natural dynamics} such as external forces or forces of nature.
@@
 
-\todo{TODO maybe UAVs can be on or of too, so it's forced to use a further UAV.}
-\todo{TODO what's also interesting is that Amazon.com uses drones for package deliveries}
+\myworries{maybe UAVs can be on or of too, so it's forced to use a further UAV.}
+
+\myworries{what's also interesting is that Amazon.com uses drones for package deliveries}
 
@@
 
+\todo{iterate on background - Imara}
 \subsection{Planning problems}

### 2014-04-10 FinalPaper/paper.tex
changed structure of the paper

@@
 
-\section{Domains}
-\label{sec:domains}
-
-To identify unique properties of the domain and identify properties of the
-domain that work particularly well for a certain type of planner, we describe
-other domains used in the IPPC and compare that with the UAV domain.
-
-\paragraph{Blocksworld:}
-A simple domain used in the competition of 2004 is the well known blocksworld
-domain. The uncertainty lies in that the gripper, used to move blocks, has a
-probability that it drops the blocks to the table. Another difference is that
-the blocks are colored, and the goal is to build a tower of certain colored
-blocks, rather than a tower with specific blocks. If for example there are
-four blue blocks, and the goal is a tower of three blue blocks, it does not
-matter which blue blocks are used.
-
-\paragraph{Navigation:}
-The navigation domain represents a grid in which a robot must reach a goal.
-Every cell offers the robot a different chance of disappearing. The robot needs
-to choose a path which gets it to the goal most reliably within the finite
-horizon time \cite{sanner2011navigation}.
-
-\paragraph{Traffic:}
-This domain represents a simple binary version of the cell transition model
-(CTM) for modelling traffic based on the original CTM Tech Report
-\cite{sanner2011traffic}. Because of the binary variables and no intermediate
-variable restrictions, this model is simplified and ignores traffic aspects
-such as turns and turn probabilities. This model also uses concurrent actions
-and the total actions has an upper bound of $2^{\#~of~intersections}$.
-
-\paragraph{Elevators:}
-The elevators domain has evaluated between the competitions of 2006 and
-2011, we describe the latest version. In this domain there are a number of
-elevators delivering passengers to either the top or bottom floor. Potential
-passengers arrive at any floor at a certain rate (depending on which floor).
-The elevators can only move in the direction it is indicating, so passengers
-know whether to board or not. The goal of the elevators is to transport as many
-as possible passengers to their destinations.
-
-\paragraph{SysAdmin:}
-The SysAdmin domain describes a network of connected servers. Each server has
-a probability that it shuts down, and if is not running, it has a probability
-to reboot. The probability that a server shuts down depends on the number of
-running connected servers.
-
-\subsection{Domain Evaluation}
-
-The Blocksworld domain is ideal for
-replanning~\cite{FFReplan, little2007probvsreplan}. As the blocks fall on the
-table, which then can be picked up again, it has no dead ends. This makes it
-probabilistically uninteresting. For this domain FF-Repan performs really well.
-
-The newer  domains, Navigation, Traffic, Elevators and SysAdmin are finite-
-horizon domains. Navigation, however, is actually a goal oriented domain, if
-the goal is reached in the horizon. The method how this is implemented is that
-the goal state is defined as an absorbing state, and there is no reward or cost
-associated to staying in the goal state, until the horizon is reached.
-
-\textsc{Gourmand} vastly outperformed the UCT-based PROST, the IPPC-11
-probabilistic track winner, by far on goal-oriented domains Navigation and
-Crossing Traffic \cite{kolobov2012gourmand}. This is because of the dynamic
-lookahead feature of \textsc{Gourmand}. PROST however mildly outperforms
-\textsc{Gourmand} on the Game of Life, SysAdmin and the Traffic domain as UCT
-does not need to perform expensive Bellman Backups on these domains that
-include large branching factors.
-
-The domains are constructed such that it will challenge planners to perform
-better. This causes that there are issues with the domains when comparing them
-with the real world.
-
-In the navigation problem there is a chance that the robot
-disappears after entering a cell. The disappearing action is a dead end.
-Disappearing here is a metaphor for the robot breaking down, or that it
-disappears from the radar with the base station. In many of such cases it's a
-big problem, but can be repaired with a high cost. In the navigation domain a
-step to another cell has a cost of 1. If instead of a dead end the cost is $n$
-(e.g. 5) instead of 1, which represents the cost of repairing the robot, dead
-ends are removed. Without dead ends the problem becomes probabilistic
-uninteresting, which makes it suitable for replanning planners.
-
-The traffic domain describes a crossroad with traffic lights, modelled as
-cells. Either the north to south road has a green light, the west to east road
-or all lights are red. The model uses a finite state machine that handles the
-lights so that the lights are never green at the same time. This would be the
-only dangerous situation on the crossroad. The difficulty in this domain is
-the number of states, which grows exponentially with the number of cells.
-Besides that it is an uninteresting probabilistic problem because it does
-not satisfy the probabilistic interesting test.
-
-The UAV domain has a resemblance of the Navigation domain. Both are goal
-oriented and have to navigate something (either the robot itself, or a data
-package) from an initial state to a goal. Also after each step a dead end can
-be reached, the robot disappears or the data package is not delivered.
-The probability this happens is static in the navigation domain, but dependent
-on the neighbors in the UAV domain. This variable probability has a resemblance
-of the SysAdmin domain, where the probability that a server shuts down is also
-dependent on the neighbors.
-
-%------------------------------------------------------------------------------
-
 \section{Planners}
@@
 
-%------------------------------------------------------------------------------
+%-------------------------------------------------------------------------------------------------------------------------------------
 
-\section{Future Experiment}
-\label{sec:experiment}
+\section{Domains}
+\label{sec:domains}
 
-Experiments can empirically evaluate the performance of the adjusted domains.
+To identify unique properties of the domain and identify properties of the
+domain that work particularly well for a certain type of planner, we describe
+other domains used in the IPPC and compare that with the UAV domain.
 
-\subsection{Setup}
+\paragraph{Blocksworld:}
+A simple domain used in the competition of 2004 is the well known blocksworld
+domain. The uncertainty lies in that the gripper, used to move blocks, has a
+probability that it drops the blocks to the table. Another difference is that
+the blocks are colored, and the goal is to build a tower of certain colored
+blocks, rather than a tower with specific blocks. If for example there are
+four blue blocks, and the goal is a tower of three blue blocks, it does not
+matter which blue blocks are used.
 
-The planning problems are taken from the IPPC-11 suite and are written in RDDL,
-which are publicity available. A domain consists of the domain description and
-instances of a domain problem. The domain description is read by RDDLSim, which
-is a server a planner can communicate with, and simulates the real world after
-the planner sends an action.
+\paragraph{Navigation:}
+The navigation domain represents a grid in which a robot must reach a goal.
+Every cell offers the robot a different chance of disappearing. The robot needs
+to choose a path which gets it to the goal most reliably within the finite
+horizon time \cite{sanner2011navigation}.
 
-\subsection{FF-Replan with Finite Horizon}
+\paragraph{Traffic:}
+This domain represents a simple binary version of the cell transition model
+(CTM) for modelling traffic based on the original CTM Tech Report
+\cite{sanner2011traffic}. Because of the binary variables and no intermediate
+variable restrictions, this model is simplified and ignores traffic aspects
+such as turns and turn probabilities. This model also uses concurrent actions
+and the total actions has an upper bound of $2^{\#~of~intersections}$.
 
-\textsc{Gourmand} already works with RDDLSim and MDPs with finite horizon. The original
-FF-Replan is a Goal-Oriented MDP planner. For a Finite-Horizon each state at
-the horizon is a goal. To compare \textsc{Gourmand}, that works with MDP-FH, with
-FF-Replan, FF-Replan needs a slight update. It should not only execute FF for
-one goal, but for all goals at the horizon. It could then start executing the
-plan with the highest reward. Depending on the determinization method,
-\emph{single-outcomes} or \emph{all-outcomes}, not all goals might be
-reachable. Of course the performance decreases with an increase of goal states
-at the horizon. A hash-table cache, as FF-Replan already uses can still be used
-to store plans generated by FF from a state to goal states, however not only
-the plan should be stored, but also the reward for this plan should be stored
-to pick the plan with the highest expected reward.
+\paragraph{Elevators:}
+The elevators domain has evaluated between the competitions of 2006 and
+2011, we describe the latest version. In this domain there are a number of
+elevators delivering passengers to either the top or bottom floor. Potential
+passengers arrive at any floor at a certain rate (depending on which floor).
+The elevators can only move in the direction it is indicating, so passengers
+know whether to board or not. The goal of the elevators is to transport as many
+as possible passengers to their destinations.
 
-Using the framework of \textsc{Glutton} and \textsc{Gourmand}, and the FF heuristic found in mGPT
-\cite{bonet2011mgpt}, the updated FF-Replan can be implemented. The first step
-of \textsc{Gourmand} is parsing the problem and creating a structure of the problem.
-Instead of executing the \textsc{Gourmand} algorithm, this structure can be used to
-determinize the problem by setting all probabilities of each action to 1
-(\emph{all-outcome}) or all but one to 0 (\emph{single-outcome}). Using the
-FF heuristic it can find plans for each goal and calculate the expected reward.
-Then it can reuse the \textsc{Gourmand} framework to execute the plan by sending the
-action to the RDDLSim server. Like FF-Replan if the server returns with a state
-that is not in the plan the algorithm will replan. If a goal is reached it will
-output the achieved reward.
+\paragraph{SysAdmin:}
+The SysAdmin domain describes a network of connected servers. Each server has
+a probability that it shuts down, and if is not running, it has a probability
+to reboot. The probability that a server shuts down depends on the number of
+running connected servers.
 
-\subsection{Hypothesis}
+\subsection{Domain Evaluation}
+
+The Blocksworld domain is ideal for
+replanning~\cite{FFReplan, little2007probvsreplan}. As the blocks fall on the
+table, which then can be picked up again, it has no dead ends. This makes it
+probabilistically uninteresting. For this domain FF-Repan performs really well.
+
+The newer  domains, Navigation, Traffic, Elevators and SysAdmin are finite-
+horizon domains. Navigation, however, is actually a goal oriented domain, if
+the goal is reached in the horizon. The method how this is implemented is that
+the goal state is defined as an absorbing state, and there is no reward or cost
+associated to staying in the goal state, until the horizon is reached.
+
+\textsc{Gourmand} vastly outperformed the UCT-based PROST, the IPPC-11
+probabilistic track winner, by far on goal-oriented domains Navigation and
+Crossing Traffic \cite{kolobov2012gourmand}. This is because of the dynamic
+lookahead feature of \textsc{Gourmand}. PROST however mildly outperforms
+\textsc{Gourmand} on the Game of Life, SysAdmin and the Traffic domain as UCT
+does not need to perform expensive Bellman Backups on these domains that
+include large branching factors.
+
+The domains are constructed such that it will challenge planners to perform
+better. This causes that there are issues with the domains when comparing them
+with the real world.
+
+In the navigation problem there is a chance that the robot
+disappears after entering a cell. The disappearing action is a dead end.
+Disappearing here is a metaphor for the robot breaking down, or that it
+disappears from the radar with the base station. In many of such cases it's a
+big problem, but can be repaired with a high cost. In the navigation domain a
+step to another cell has a cost of 1. If instead of a dead end the cost is $n$
+(e.g. 5) instead of 1, which represents the cost of repairing the robot, dead
+ends are removed. Without dead ends the problem becomes probabilistic
+uninteresting, which makes it suitable for replanning planners.
+
+The traffic domain describes a crossroad with traffic lights, modelled as
+cells. Either the north to south road has a green light, the west to east road
+or all lights are red. The model uses a finite state machine that handles the
+lights so that the lights are never green at the same time. This would be the
+only dangerous situation on the crossroad. The difficulty in this domain is
+the number of states, which grows exponentially with the number of cells.
+Besides that it is an uninteresting probabilistic problem because it does
+not satisfy the probabilistic interesting test.
+
+The UAV domain has a resemblance of the Navigation domain. Both are goal
+oriented and have to navigate something (either the robot itself, or a data
+package) from an initial state to a goal. Also after each step a dead end can
+be reached, the robot disappears or the data package is not delivered.
+The probability this happens is static in the navigation domain, but dependent
+on the neighbors in the UAV domain. This variable probability has a resemblance
+of the SysAdmin domain, where the probability that a server shuts down is also
+dependent on the neighbors.
 
@@
 
-In sections above we have described the GOURMAND planner and FF-Replan as two
-probabilistic planners of the IPPC competition.
-RFF~\cite{teichteil2010incremental} is an offline planner that generates a
-policy: for each reachable state it determines a plan to the goal. Like
-FF-Replan it uses determinization and FF\. FF returns an initial plan from the
-initial state to a goal state. For each state in the plan the successor states
-are added to the structure, after which Monte-Carlo sampling is used. States
-where the probability that they're reached is too low (below a threshold) are
-removed. The successor states are used as initial states in the next step. If
-FF fails to find a plan to the goal from this new state, the state is removed
-from the structure too. Results showed that RFF outperformed other competitors.
-A higher threshold means that RFF will generate more policies that are prone to
-replanning.
+%In sections above we have described the GOURMAND planner and FF-Replan as two
+%probabilistic planners of the IPPC competition.
+%RFF~\cite{teichteil2010incremental} is an offline planner that generates a
+%policy: for each reachable state it determines a plan to the goal. Like
+%FF-Replan it uses determinization and FF\. FF returns an initial plan from the
+%initial state to a goal state. For each state in the plan the successor states
+%are added to the structure, after which Monte-Carlo sampling is used. States
+%where the probability that they're reached is too low (below a threshold) are
+%removed. The successor states are used as initial states in the next step. If
+%FF fails to find a plan to the goal from this new state, the state is removed
+%from the structure too. Results showed that RFF outperformed other competitors.
+%A higher threshold means that RFF will generate more policies that are prone to
+%replanning.
 
 \subsubsection{PROST ?}
+\todo{wrote sentence about Prost - Arian}\\
 
-\subsection{Probabilistic planning vs Replanning}
-Inspired by the FF-Replan entrance in the IPPC competition, this paper described a probabilistic interestingness quality of domains.
+\todo{rewrite prob int - Imara}
+
+%\subsection{Probabilistic planning vs Replanning}
+%Inspired by the FF-Replan entrance in the IPPC competition, this paper described a probabilistic interestingness quality of domains.
 It then compares probabilistic planners with replanners in the different domains to draw conclusions.
@@
 Probabilistic planning computes a plan that can handle all foreseeable contingencies and is preferable for quick reactions in closed control loops.
-
-The following structural properties are identified for comparing probabilistic planning with replanning:
-\begin{itemize}
-	\item `dead' end states
-	\item the degree to which the probability of reaching a dead end state can be reduced through choice of actions
-	\item number of distinct trajectories
-	\item presence of mutual exclusion
-\end{itemize}
-
-If there are no dead ends, a replanner will always succeed.
+%
+%The following structural properties are identified for comparing probabilistic planning with replanning:
+%\begin{itemize}
+%	\item `dead' end states
+%	\item the degree to which the probability of reaching a dead end state can be reduced through choice of actions
+%	\item number of distinct trajectories
+%	\item presence of mutual exclusion
+%\end{itemize}
+%
+%If there are no dead ends, a replanner will always succeed.
 It is impossible to improve on the unavoidable dead ends (positive probability of reaching when executing which cannot be reduced without reducing the probability of reaching the goal).
-
-% repetition of what's already stated earlier
-
-A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties:
-
-\begin{itemize}
-	\item there are multiple goal trajectories;
-	\item there is at least on pair of distinct goal trajectories, $\tau$ and $\tau$ ', that share a common sequence of outcomes for the first n-1 outcomes, and where $\tau$\textsubscript{n} and $\tau$'\textsubscript{n} are distinct outcomes of the same action; and
-	\item there exist two distinct goal trajectories $\tau$ and $\tau$' and outcome o $\in$ $\tau$ and o' $\in$ $\tau$' of two distinct actions a = act(o) and a'= act(o') such that executing a strictly decreases the maximum probability of reaching a state where a' can be executed.
-\end{itemize}
-
-Problems that fail to be \emph{probabilistically interesting} are actually classical planning problems in disguise and for those replanners are more appropriate.
+%
+%% repetition of what's already stated earlier
+%
+%A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties:
+%
+%\begin{itemize}
+%	\item there are multiple goal trajectories;
+%	\item there is at least on pair of distinct goal trajectories, $\tau$ and $\tau$ ', that share a common sequence of outcomes for the first n-1 outcomes, and where $\tau$\textsubscript{n} and $\tau$'\textsubscript{n} are distinct outcomes of the same action; and
+%	\item there exist two distinct goal trajectories $\tau$ and $\tau$' and outcome o $\in$ $\tau$ and o' $\in$ $\tau$' of two distinct actions a = act(o) and a'= act(o') such that executing a strictly decreases the maximum probability of reaching a state where a' can be executed.
+%\end{itemize}
+%
+%Problems that fail to be \emph{probabilistically interesting} are actually classical planning problems in disguise and for those replanners are more appropriate.
 A replanner can also perform optimally for probabilistically interesting planning problems whenever the `most promising' goal trajectory is the correct thing to do.
@@
 probabilistic planning.
-
-Following existing domains were said to be probabilistically interesting:
-\begin{itemize}
-	\item Drive
-	\item Exploding blocksworld
-	\item Pitchcatch
-	\item Schedule
-	\item Tireworld
-\end{itemize}
-
-They conclude by stating that the negative perception of probabilistic planning by the ICAPS community was inaccurate.
+%
+%Following existing domains were said to be probabilistically interesting:
+%\begin{itemize}
+%	\item Drive
+%	\item Exploding blocksworld
+%	\item Pitchcatch
+%	\item Schedule
+%	\item Tireworld
+%\end{itemize}
+%
+%They conclude by stating that the negative perception of probabilistic planning by the ICAPS community was inaccurate.
 They state that a synthesis of planning and replanning techniques could make a larger number of probabilistic planning problems practicably solvable than is currently possible.
@@
 
+%------------------------------------------------------------------------------
+
+\section{Future works}
+
 \bibliographystyle{plain}

### 2014-04-10 FinalPaper/paper.tex
Rewrite related work for RFF and PROST

@@
 
-%In sections above we have described the GOURMAND planner and FF-Replan as two
-%probabilistic planners of the IPPC competition.
-%RFF~\cite{teichteil2010incremental} is an offline planner that generates a
-%policy: for each reachable state it determines a plan to the goal. Like
-%FF-Replan it uses determinization and FF\. FF returns an initial plan from the
-%initial state to a goal state. For each state in the plan the successor states
-%are added to the structure, after which Monte-Carlo sampling is used. States
-%where the probability that they're reached is too low (below a threshold) are
-%removed. The successor states are used as initial states in the next step. If
-%FF fails to find a plan to the goal from this new state, the state is removed
-%from the structure too. Results showed that RFF outperformed other competitors.
-%A higher threshold means that RFF will generate more policies that are prone to
-%replanning.
+FF-Replan and \textsc{Gourmand} are top-performing planners at the time they
+were introduced for the domains described earlier. Two other planners are
+\textsc{RFF}, an offline policy planner using FF, and PROST, a UCT algorithm
+based planner.
 
-\subsubsection{PROST ?}
-\todo{wrote sentence about Prost - Arian}\\
+RFF \cite{teichteil2010incremental} generates policies by determinizing the
+given MDP problem, builds partial policies off-line by producing partial
+solution plans to the classical planning problem and incrementally aggregating
+them into a policy, and using sequential Monte-Carlo simulations to asses the
+probability of replanning. Experiments showed that RFF solved more problems
+than FF-Replan because it takes the probability a policy has to replan into
+account.
+
+PROST \cite{keller2012prost} is a probabilistic planner, which contrary to
+\textsc{Gourmand}, is UTC based. It uses techniques to reduce the branching
+factor  and limits the search depth so it can focus more on parts that
+influence the quality of the resulting policy. Reward lock detection is a
+method to detect goals and dead ends in the finite horizon MDP\@. Q-value
+Initialization improves the initial start of the UTC algorithm. In the executed
+IPPC-11 benchmarks it outperforms other planners such as \textsc{Glutton}.
+Later it has been surpassed by \textsc{Gourmand}.
 

### 2014-04-10 FinalPaper/paper.tex
Rewritten future work

--- 2014-04-10 FinalPaper/paper.tex
@@
 
+To empirically test which planner performs best for a certain domain,
+experiments needs to be executed. The domain description language would be RDDL
+\cite{Sanner:RDDL}, as \textsc{Gourmand} already works natively with it.
+FF-Replan does not work with RDDL, but PPDDL instead. FF-Replan could be
+re-implemented in the \textsc{Gourmand} framework, using the FF heuristic found
+in mGPT \cite{bonet2011planning}. Another possibility is to implement the
+domain in both languages and carefully assess if both implementations are fair.
+The two metrics that need to be measured are the rate the goal is reached (and does
+not reach dead ends) and the online execution time.
+
 \bibliographystyle{plain}

### 2014-04-10 FinalPaper/paper.tex

--- 2014-04-10 FinalPaper/paper.tex
@@
 %------------------------------------------------------------------------------
-
-\section{Problem formulation}
-\label{sec:problem}
-
-\todo{rewrite problem formulation - Arian}
-To evaluate FF-Replan and \textsc{Gourmand} in a real world domain a finite horizon MDP is used to represent the realistic \emph{natural dynamics} such as external forces or forces of nature.
-These dynamics introduce large branching factors emphasizing the need for a planner to be scalable.
-To evaluate the model, the planner should also be sensitive to an expected reward maximization criterion.
-Current finite horizon MDP problems as introduced in IPPC-11 are simplified and therefor do not account for the rich set of state-actions as would be available in a real-world planning problem.
-We will reason about the most interesting domains for our evaluation and adjust them to match their real-world equivalent.
-Using the baseline test introduced by Little et al.\@ \cite{little2007probvsreplan}, we can evaluate the probabilistically interestingness of these domains and evaluate the performance of FF-Replan vs.\@ a state of the art probabilistic planner: \textsc{Gourmand}.
 

### 2014-04-10 FinalPaper/paper.tex
abstract herschreven

@@
 %
-\authorrunning{Validating Planners in a Real World Domain}
+\authorrunning{Presenting a }
 % (feature abused for this document to repeat the title also on left hand pages)
@@
 \begin{abstract}
+By introducing and attempting to solve a planning problem domain involving Unmanned Aerial Vehicles (UAVs), this paper provides an overview of how the history of planning problem domains and their matching planners has changed throughout the scope of the International Planning Competitions (IPC).
+After the emergence of the FF-replan planner in 2004, state-of-the-art benchmark domains have been argued to be more \emph{probabilistically interesting} causing a shift from the once dominant goal-oriented domains to the finite-horizon oriented domains.
 
-\todo{Rewrite abstract - Imara}
+This paper presents a currently hot topic domain in which several UAVs  work together to monitor a large area using restricted communication technology.
+To find an optimal planner for this domain, this paper presents an overview of other interesting domains and probabilistic planners that were involved in the redefinition of an interesting planning problem.
 
-	In contrast to current demand for probabilistically interesting domains in the International Probabilistic Planning Competitions, this papier argues for using real-world appropriate domains.
-By relaxing the definition of a dead-end, we argue that for many
-real life domains a simpler planning algorithm can be sufficient and even better than sophisticated probabilistic planners.
-
-In this paper we evaluate the strength of FF-Replan, winner of IPPC-04 and unenrolled winner of IPPC-06, a replanner that uses the classical planner FF on a determinized probabilistic problem against a state of the art probabilistic planner \textsc{Gourmand}, the successor of the Labelled Real-Time Dynamic Probabilistic planner \textsc{Glutton}, runner up of the IPPC-11.
-By translating the Navigation and Traffic domain from IPPC-11 to a matching real-world equivalent and evaluating these using the proposed probabilistically interesting baseline test as proposed by Little et al\.
-we evaluate whether FF-Replan is in fact capable enough to solve enough of these so called classical planning problems in disguise.
 \end{abstract}
@@
 \cite{little2007probvsreplan} a recommendation will be made for a suitable planner to match the UAV problem.
+
+\todo{Arian: Still have to add why this problem is valid, or interesting}
 

### 2014-04-10 FinalPaper/paper.tex
background herschreven

@@
 Unmanned Aerial Vehicles (UAVs), or commonly called \emph{Drones} are aircrafts
-without a pilot and often autonomously controlled. Drones are widely used for
-military as well as for civil uses, including inspecting pipelines, counting
+without a pilot and are often autonomously controlled. Drones are widely used in the
+military as well as for civil uses as inspection of pipelines, counting of
 wildlife, agriculture, filming or delivering supplies to inaccessible areas.
-As many uses cases there are, there are many forms of UAVs, bigger fixed wing
-aircrafts, or small helicopter or quad copter like aircrafts that can hover at
+There are many forms of UAVs to accommodate for these varying tasks: bigger fixed wing
+aircrafts, small helicopters or quad copter like aircrafts that can hover at
 a certain position in the air.
 
-We are particularly interested in monitoring, for example crops or livestock,
+This paper focuses on monitoring, for example crops or livestock,
 and surveillance UAVs that work together to monitor a large area. Each UAV
-monitors a part of the total area, and if it has monitored something, it has
+monitors a part of the total area. If something has to be monitored, it has
 to communicate this to a base station. This can't be done directly due to the
-large distance, instead it has to go through neighboring UAVs.
+large distance and instead it has to go through neighboring UAVs.
 
@@
 
-\todo{iterate on background - Imara}
-\subsection{Planning problems}
+\subsubsection{Planning Problems.
+} Planning is the process of computing several steps of a problem-solving procedure before executing any of them.
+A \emph{classical planning problem} is defined as states, actions, conditions and a goal state and is solved using when finding a state-action sequence from the initial state $s_0$ to a goal state $G$.
+To find a state-action sequence, the environment is assumed to be \emph{deterministic, observable and static}.
 
-Planning is the process of computing several steps of a problem-solving procedure before executing any of them.
-
-\subsubsection{Classical Planning problems.}
-
-A classical planning problem is defined as states, actions, conditions and a goal state and are solved using search and can be aided using heuristics.
-The environment is assumed to be \emph{deterministic, observable and static}.
-The planner tries to find a sequence of actions such that a goal or maximum reward is achieved.
-
-\subsubsection{Probabilistic Planning problems}
-
-Real-World applications are far from deterministic, induced by natural dynamics and chance.
-To accommodate for Real-World domains probabilistic planning problems were introduced.
-These systems can be described using \emph{Markov Decision Processes} (MDPs) and can account for observable uncertainty.
-Probabilistic planning problems can be solved by evaluating iterations and creating policies to reach a goal state, either online, while executing the plan, or offline, where all possibilities is calculated upfront.
-
-\subsection{Problem domains}
+When planning for dynamic environments as is most often the case, natural dynamics and chance are introduced.
+To simulate these planning problems, the classical deterministic domains were extended by adding a \emph{probability} to every action, creating \emph{probabilistic planning problems}.
+These systems can be described using \emph{Markov Decision Processes} or MDPs.
 
 \subsubsection{Goal-oriented MDPs.
-}The problems in IPPC-04 were specified using the Planning Domain Description Language (PPDLL).
-PPDDL specifies a probabistic planning problem as a set of probabilistic action sets and an initial and goal state description in which every action has a certain probability assigned to it \cite{FFReplan}.
-These MDPs are of the form $\mathit{M = (S, A, app, Pr, R)}$ where $\mathit{S}$ and $\mathit{A}$ are a finite set of states and actions, $\mathit{app(s)}$ is the set of all actions applicable in $\mathit{s}$.
-$\mathit{Pr}$ represents the probability of a state transaction $\mathit{(s, a, s')}$ for $\mathit{a}$ and $\mathit{R(s, a, s')}$ is the reward of applying $\mathit{a}$ to $\mathit{s}$ and generating $\mathit{s'}$ The planning problem is defined as a triple $\mathit{P = (M, s\textsubscript{0}, G, \rho)}$ where $\mathit{M = (S, A, app, Pr, R)}$ is an MDP, $\mathit{s\textsubscript{0} \in S}$ is the initial state, $\mathit{G \subseteq S}$ is the set of goal states and $\mathit{0 < \rho < 1}$ is a probability threshold \cite{teichteil2010incremental}.
+}The classical goal-oriented problems in the IPPC-04 were specified using the Probabilistic Planning Domain Description Language (PPDLL).
+PPDDL specifies a probabilistic planning problem as a set of probabilistic actions and an initial and goal state description\cite{FFReplan}.
+These MDPs are of the form $\mathit{M = (S, A, app, Pr, R)}$ where $\mathit{S}$ and $\mathit{A}$ are a finite set of states and actions, $\mathit{app(s)}$ is the set of all actions applicable in the current state $\mathit{s}$.
+$\mathit{Pr}$ represents the probability of a state transition $\mathit{(s, a, s')}$ for action $\mathit{a}$ and $\mathit{R(s, a, s')}$ is the reward of applying $\mathit{a}$ to $\mathit{s}$ and generating $\mathit{s'}$ The planning problem is defined as a triple $\mathit{P = (M, s\textsubscript{0}, G}$ where $\mathit{M = (S, A, app, Pr, R)}$ is an MDP, $\mathit{s\textsubscript{0} \in S}$ is the initial state and $\mathit{G \subseteq S}$ is the set of goal states.
 
- The planners from IPPC-04 were evaluated on how many trials reached the goal per problem and the average number of actions selected when successful.
-These planning problems were however relatively easy to solve as they did not account for \emph{natural dynamics} and/or large branching factors that occur in more realistic systems \cite{kolobov2012glutton}.
-FF-Replan \cite{FFReplan}, as specified in Section \ref{sec:planners} kindly remembered the committee of the IPPC-04 that the specified planning problems that contained no dead-ends were fairly easy to solve using relatively simple tools to handle with uncertainty.
+These planning problems were however relatively easy to solve as they did not account for large branching factors introduced by for instance decay \cite{kolobov2012glutton}.
+Natural dynamics cause the system to grow \myworries{exponentially??} as it introduces exogenous actions in every state.
+After FF-replan \cite{FFReplan}, a replanner as introduced in Section  \ref{sec:planners} kindly reminded the committee of IPPC-04 that the specified planning problems containing no dead-ends were fairly easy to solve using relatively simple tools to handle uncertainty, the finite-horizon MDPs were introduces.
 
 \subsubsection{MDPs with Finite Horizon.
-}IPPC-11 decided to respond by introducing more realistic MDPs and their evaluation criteria by using MDPs with finite horizons.
-The planning problems are defined as tuples of the form \\ $\mathit{M\textsubscript{s0}(H) = \langle \langle S, A, T, R, s\textsubscript{0} \rangle , H \rangle }$ where $\mathit{S}$ s a finite set of states, $\mathit{A}$ a finite set of actions, $\mathit{T}$ is the transition function, similar to $\mathit{Pr}$ in the goal oriented MDP.
-$\mathit{R}$ represents the transitioning reward, $\mathit{s\textsubscript{0}}$ and $\mathit{H}$ is the number of decision epochs after which the process stops.
-Solving $\mathit{M(H)}$ means finding a policy for executing recommended state from the initial state over $\mathit{H}$ decision epochs \cite{kolobov2012gourmand}.
-
-Translating finite horizon MDPs to goal-oriented domains results ends up in all state $H$ steps away from $s\textsubscript{0}$ are goal states.
-The evaluation criteria in finite horizon MDPs is the \emph{expected reward} and not the probability of the policy reaching the goal states.
+} Finite-horizon MDPs are an approximation for infinite planning problems using a finite horizon of a set amount of steps.
+Planning problems are defined as tuples of the form $\mathit{M(H) = \langle \langle S, A, T, R, s\textsubscript{0} \rangle , H \rangle }$ where $\mathit{S}$ is a finite set of states, $\mathit{A}$ a finite set of actions and $\mathit{T}$ is the transition function similar to $\mathit{Pr}$ in the goal oriented MDP.
+$\mathit{R}$ represents the transitioning reward, $\mathit{s\textsubscript{0}}$ the initial state and $\mathit{H}$ is the number of decision epochs after which the process stops.
+Solving $\mathit{M(H)}$ means finding a policy such that executing the recommended actions starting from state $(s_0, H)$ results in accumulating the largest expected reward over $H$ time steps \cite{kolobov2012glutton}.
 
 \subsection{Planning algorithms}
-\subsubsection{Replanning}
-A replanner is a planner that takes a problem as input, plans a state-action policy, executes it online and whenever it encounters a state that was not in its state-action policy, it takes the current state as starting state and plans again until it has reached a goal or dead-end state.
-For our paper have chosen to evaluate FF-Replan \cite{FFReplan}, the winner of IPPC-04 and unenrolled winner of IPPC-06 as an inspiring, fairly simple planner that in our opinion is capable of employment in real-world domains.
 
-\subsubsection{Probabilistic planning}
-Probabilistic planners are used to solve probabilistic planning problems and should be able to account for uncertainty as opposed to classical planners.
-For our evaluation we have chosen to compare FF-Replan to a state-of-the-art probabilistic planner: \textsc{Gourmand}.
-\textsc{Gourmand} is the online successor of the \textsc{Glutton} plan, a Labelled Real-Time Dynamic Programming (LRTDP) based planner and the runner up of IPPC-11.
+These probabilistic MDPs can be solved using different kinds of planners.
+A \emph{replanner} is a planner that takes a problem as input, plans a partial state-action policy, executes it online and whenever it encounters a state that was not in its state-action policy, it takes the current state as starting state and plans again until it has reached a goal or dead-end state.
+To illustrate this technique, the notorious FF-planner is discussed in the next Section.
+
+\emph{Probabilistic planners} use sophisticated planning techniques to plan for uncertainty.
+By using simulations, roll-out policies or lookahead values, these planners prevent dead-ends and were therefore dominantly used for solving MDPs.
+To illustrate a probabilistic planner, the next section introduces \textsc{Gourmand}, an online state-of-the-art probabilistic planner, and its predecessors \textsc{Glutton} and the LRTDP based algorithms.
 
 \subsection{Probabilistic Interestingness}
-After IPPC-06, a baseline test for \emph{probabilistically interesting} planning domains was proposed by Little and Thi\'ebauw \cite{little2007probvsreplan}.
-Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners.
+The \emph{probabilistically interesting} baseline test, proposed by Little and Thi\'ebauw \cite{little2007probvsreplan} after the success of FF-replan initiated the shift of interest in goal-oriented MDPs to finite-horizon MDPs.
+Problems that fail this test are said to be classical planning problems in disguise, favoring the use of replanners.
 A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties \cite{little2007probvsreplan}:
-% reference little & thiebauw again. Maybe also shortly define what all o, n, act etc. are.
 
@@
 	\item there are multiple goal trajectories;
-	\item there is at least on pair of distinct goal trajectories, $\tau$ and $\tau$ ', that share a common sequence of outcomes for the first n-1 outcomes, and where $\tau$\textsubscript{n} and $\tau$'\textsubscript{n} are distinct outcomes of the same action; and
-	\item there exist two distinct goal trajectories $\tau$ and $\tau$' and outcome o $\in$ $\tau$ and o' $\in$ $\tau$' of two distinct actions a = act(o) and a'= act(o') such that executing a strictly decreases the maximum probability of reaching a state where a' can be executed.
+	\item there is at least one pair of distinct goal trajectories, $\tau$ and $\tau'$, that share a common sequence of outcomes for the first $n-1$ outcomes, and where $\tau_n$ and $\tau'_n$ are distinct outcomes of the same action; and
+	\item At least one of the distinct goal trajectories lead to outcomes o $\in$ $\tau$ and o' $\in$ $\tau$' of two distinct actions $a = act(o)$ and $a'= act(o')$ such that executing $a$ decreases the probability of reaching a dead end without influencing the probability of reaching a goal state.
+\myworries{is dit duidelijk genoeg of is het niet wiskunding genoeg?}
 \end{itemize}

### 2014-04-10 FinalPaper/paper.tex
denk dat de replanning vs probplanning al genoeg besproken word en niet meer persé in related work hoeft
Fix related work section, don't say that it should be written in RDDL

--- 2014-04-10 FinalPaper/paper.tex
@@
 %------------------------------------------------------------------------------
+
+\section{Problem formulation}
+\label{sec:problem}
+
+\todo{rewrite problem formulation - Arian}
+To evaluate FF-Replan and \textsc{Gourmand} in a real world domain a finite horizon MDP is used to represent the realistic \emph{natural dynamics} such as external forces or forces of nature.
+These dynamics introduce large branching factors emphasizing the need for a planner to be scalable.
+To evaluate the model, the planner should also be sensitive to an expected reward maximization criterion.
+Current finite horizon MDP problems as introduced in IPPC-11 are simplified and therefor do not account for the rich set of state-actions as would be available in a real-world planning problem.
+We will reason about the most interesting domains for our evaluation and adjust them to match their real-world equivalent.
+Using the baseline test introduced by Little et al.\@ \cite{little2007probvsreplan}, we can evaluate the probabilistically interestingness of these domains and evaluate the performance of FF-Replan vs.\@ a state of the art probabilistic planner: \textsc{Gourmand}.
 
@@
 
+To conclude which planner would perform best on the UAV domain, experiments
+needs to be executed. The domain can be described in PPDDL
+\cite{younes2004ppddl1} or RDDL \cite{Sanner:RDDL}, which are domain
+description languages. RDDL is already used by \textsc{Gourmand} while
+FF-Replan uses PPDDL\@. FF-Replan could be re-implemented in the
+\textsc{Gourmand} framework, using the FF heuristic found in mGPT
+\cite{bonet2011planning}. Another possibility is to implement the domain in
+both languages and carefully assess if both implementations are fair.  The two
+metrics that need to be measured are the rate the goal is reached (and does not
+reach dead ends) and the online execution time.
+
 \bibliographystyle{plain}

### 2014-04-10 FinalPaper/paper.tex
Use a different wording to start the related work with

@@
 
-%In sections above we have described the GOURMAND planner and FF-Replan as two
-%probabilistic planners of the IPPC competition.
-%RFF~\cite{teichteil2010incremental} is an offline planner that generates a
-%policy: for each reachable state it determines a plan to the goal. Like
-%FF-Replan it uses determinization and FF\. FF returns an initial plan from the
-%initial state to a goal state. For each state in the plan the successor states
-%are added to the structure, after which Monte-Carlo sampling is used. States
-%where the probability that they're reached is too low (below a threshold) are
-%removed. The successor states are used as initial states in the next step. If
-%FF fails to find a plan to the goal from this new state, the state is removed
-%from the structure too. Results showed that RFF outperformed other competitors.
-%A higher threshold means that RFF will generate more policies that are prone to
-%replanning.
+FF-Replan replans online, an off-line planner like FF-Replan is RFF
+\cite{teichteil2010incremental}. RFF generates policies by determinizing the
+given MDP problem, builds partial policies off-line by producing partial
+solution plans to the classical planning problem and incrementally aggregating
+them into a policy, and using sequential Monte-Carlo simulations to asses the
+probability of replanning. Experiments showed that RFF solved more problems
+than FF-Replan because it takes the probability a policy has to replan into
+account.
 
-\subsubsection{PROST ?}
-\todo{wrote sentence about Prost - Arian}\\
+PROST \cite{keller2012prost} is a probabilistic planner, which contrary to
+\textsc{Gourmand}, is UTC based. It uses techniques to reduce the branching
+factor  and limits the search depth so it can focus more on parts that
+influence the quality of the resulting policy. Reward lock detection is a
+method to detect goals and dead ends in the finite horizon MDP\@. Q-value
+Initialization improves the initial start of the UTC algorithm. In the executed
+IPPC-11 benchmarks it outperforms other planners such as \textsc{Glutton}.
+Later it has been surpassed by \textsc{Gourmand}.
 
@@
 
-To conclude which planner would perform best on the UAV domain, experiments
-needs to be executed. The domain can be described in PPDDL
-\cite{younes2004ppddl1} or RDDL \cite{Sanner:RDDL}, which are domain
-description languages. RDDL is already used by \textsc{Gourmand} while
-FF-Replan uses PPDDL\@. FF-Replan could be re-implemented in the
-\textsc{Gourmand} framework, using the FF heuristic found in mGPT
-\cite{bonet2011planning}. Another possibility is to implement the domain in
-both languages and carefully assess if both implementations are fair.  The two
-metrics that need to be measured are the rate the goal is reached (and does not
-reach dead ends) and the online execution time.
-
 \bibliographystyle{plain}

### 2014-04-13 FinalPaper/paper.tex
adjusted on comments

--- 2014-04-11 FinalPaper/paper.tex
@@
 \begin{abstract}
+By introducing and attempting to solve a planning problem domain involving Unmanned Aerial Vehicles (UAVs), this paper provides an overview of how the history of planning problem domains and their matching planners has changed throughout the scope of the International Planning Competitions (IPC).
+After the emergence of the FF-Replan planner in 2004, state-of-the-art benchmark domains have been argued to be more \emph{probabilistically interesting} causing a shift from the once dominant goal-oriented domains to the finite-horizon oriented domains.
 
-\todo{Rewrite abstract - Imara}
+This paper presents a currently hot topic domain in which several UAVs  work together to monitor a large area using restricted communication technology.
+To find an optimal planner for this domain, this paper presents an overview of other interesting domains and probabilistic planners that were involved in the redefinition of an interesting planning problem.
 
-	In contrast to current demand for probabilistically interesting domains in the International Probabilistic Planning Competitions, this papier argues for using real-world appropriate domains.
-By relaxing the definition of a dead-end, we argue that for many
-real life domains a simpler planning algorithm can be sufficient and even better than sophisticated probabilistic planners.
-
-In this paper we evaluate the strength of FF-Replan, winner of IPPC-04 and unenrolled winner of IPPC-06, a replanner that uses the classical planner FF on a determinized probabilistic problem against a state of the art probabilistic planner \textsc{Gourmand}, the successor of the Labelled Real-Time Dynamic Probabilistic planner \textsc{Glutton}, runner up of the IPPC-11.
-By translating the Navigation and Traffic domain from IPPC-11 to a matching real-world equivalent and evaluating these using the proposed probabilistically interesting baseline test as proposed by Little et al\.
-we evaluate whether FF-Replan is in fact capable enough to solve enough of these so called classical planning problems in disguise.
 \end{abstract}
@@
 
+\todo{Arian: Still have to add why this problem is valid, or interesting}
+
 Section \ref{sec:problem} introduced the problem formulation this paper addresses while Section \ref{sec:domaind} introduces the details of proposed domain.
@@
 
-\todo{iterate on background - Imara}
-\subsection{Planning problems}
+\subsubsection{Planning Problems.
+} Planning is the process of computing several steps of a problem-solving procedure before executing any of them.
+A \emph{classical planning problem} is defined as states, actions, conditions and a goal state and is solved using when finding a state-action sequence from the initial state $s_0$ to a goal state $G$.
+To find a state-action sequence, the environment is assumed to be \emph{deterministic, observable and static}.
 
-Planning is the process of computing several steps of a problem-solving procedure before executing any of them.
-
-\subsubsection{Classical Planning problems.}
-
-A classical planning problem is defined as states, actions, conditions and a goal state and are solved using search and can be aided using heuristics.
-The environment is assumed to be \emph{deterministic, observable and static}.
-The planner tries to find a sequence of actions such that a goal or maximum reward is achieved.
-
-\subsubsection{Probabilistic Planning problems}
-
-Real-World applications are far from deterministic, induced by natural dynamics and chance.
-To accommodate for Real-World domains probabilistic planning problems were introduced.
-These systems can be described using \emph{Markov Decision Processes} (MDPs) and can account for observable uncertainty.
-Probabilistic planning problems can be solved by evaluating iterations and creating policies to reach a goal state, either online, while executing the plan, or offline, where all possibilities is calculated upfront.
-
-\subsection{Problem domains}
+When planning for dynamic environments as is most often the case, natural dynamics and chance are introduced.
+To simulate these planning problems, the classical deterministic domains were extended by adding a \emph{probability} to every action, creating \emph{probabilistic planning problems}.
+These systems can be described using \emph{Markov Decision Processes} or MDPs.
 
 \subsubsection{Goal-oriented MDPs.
-}The problems in IPPC-04 were specified using the Planning Domain Description Language (PPDLL).
-PPDDL specifies a probabistic planning problem as a set of probabilistic action sets and an initial and goal state description in which every action has a certain probability assigned to it \cite{FFReplan}.
-These MDPs are of the form $\mathit{M = (S, A, app, Pr, R)}$ where $\mathit{S}$ and $\mathit{A}$ are a finite set of states and actions, $\mathit{app(s)}$ is the set of all actions applicable in $\mathit{s}$.
-$\mathit{Pr}$ represents the probability of a state transaction $\mathit{(s, a, s')}$ for $\mathit{a}$ and $\mathit{R(s, a, s')}$ is the reward of applying $\mathit{a}$ to $\mathit{s}$ and generating $\mathit{s'}$ The planning problem is defined as a triple $\mathit{P = (M, s\textsubscript{0}, G, \rho)}$ where $\mathit{M = (S, A, app, Pr, R)}$ is an MDP, $\mathit{s\textsubscript{0} \in S}$ is the initial state, $\mathit{G \subseteq S}$ is the set of goal states and $\mathit{0 < \rho < 1}$ is a probability threshold \cite{teichteil2010incremental}.
+}Cclassical goal-oriented problems are specified using the Probabilistic Planning Domain Description Language (PPDDL).
+PPDDL specifies a probabilistic planning problem as a set of probabilistic actions and an initial and goal state description\cite{FFReplan}.
+These MDPs are of the form $\mathit{M = (S, A, app, Pr, R)}$ where $\mathit{S}$ and $\mathit{A}$ are a finite set of states and actions, $\mathit{app(s)}$ is the set of all actions applicable in the current state $\mathit{s}$.
+$\mathit{Pr}$ represents the probability of a state transition $\mathit{(s, a, s')}$ for action $\mathit{a}$ and $\mathit{R(s, a, s')}$ is the reward of applying $\mathit{a}$ to $\mathit{s}$ and generating $\mathit{s'}$ The planning problem is defined as a triple $\mathit{P = (M, s\textsubscript{0}, G}$ where $\mathit{M = (S, A, app, Pr, R)}$ is an MDP, $\mathit{s\textsubscript{0} \in S}$ is the initial state and $\mathit{G \subseteq S}$ is the set of goal states.
 
- The planners from IPPC-04 were evaluated on how many trials reached the goal per problem and the average number of actions selected when successful.
-These planning problems were however relatively easy to solve as they did not account for \emph{natural dynamics} and/or large branching factors that occur in more realistic systems \cite{kolobov2012glutton}.
-FF-Replan \cite{FFReplan}, as specified in Section \ref{sec:planners} kindly remembered the committee of the IPPC-04 that the specified planning problems that contained no dead-ends were fairly easy to solve using relatively simple tools to handle with uncertainty.
+These planning problems were however relatively easy to solve as they did not account for large branching factors introduced by for instance decay \cite{kolobov2012glutton}.
+Natural dynamics cause the system to grow \myworries{exponentially??} as it introduces exogenous actions in every state.
+After FF-Replan \cite{FFReplan}, a replanner as introduced in Section  \ref{sec:planners} kindly reminded the committee of IPPC-04 that the specified planning problems containing no dead-ends were fairly easy to solve using relatively simple tools to handle uncertainty, the finite-horizon MDPs were introduces.
 
 \subsubsection{MDPs with Finite Horizon.
-}IPPC-11 decided to respond by introducing more realistic MDPs and their evaluation criteria by using MDPs with finite horizons.
-The planning problems are defined as tuples of the form \\ $\mathit{M\textsubscript{s0}(H) = \langle \langle S, A, T, R, s\textsubscript{0} \rangle , H \rangle }$ where $\mathit{S}$ s a finite set of states, $\mathit{A}$ a finite set of actions, $\mathit{T}$ is the transition function, similar to $\mathit{Pr}$ in the goal oriented MDP.
-$\mathit{R}$ represents the transitioning reward, $\mathit{s\textsubscript{0}}$ and $\mathit{H}$ is the number of decision epochs after which the process stops.
-Solving $\mathit{M(H)}$ means finding a policy for executing recommended state from the initial state over $\mathit{H}$ decision epochs \cite{kolobov2012gourmand}.
-
-Translating finite horizon MDPs to goal-oriented domains results ends up in all state $H$ steps away from $s\textsubscript{0}$ are goal states.
-The evaluation criteria in finite horizon MDPs is the \emph{expected reward} and not the probability of the policy reaching the goal states.
+} Finite-horizon MDPs are an approximation for infinite planning problems using a finite horizon of a set amount of steps.
+Planning problems are defined as tuples of the form $\mathit{M(H) = \langle \langle S, A, T, R, s\textsubscript{0} \rangle , H \rangle }$ where $\mathit{S}$ is a finite set of states, $\mathit{A}$ a finite set of actions and $\mathit{T}$ is the transition function similar to $\mathit{Pr}$ in the goal oriented MDP.
+$\mathit{R}$ represents the transitioning reward, $\mathit{s\textsubscript{0}}$ the initial state and $\mathit{H}$ is the number of decision epochs after which the process stops.
+Solving $\mathit{M(H)}$ means finding a policy such that executing the recommended actions starting from state $(s_0, H)$ results in accumulating the largest expected reward over $H$ time steps \cite{kolobov2012glutton}.
 
 \subsection{Planning algorithms}
-\subsubsection{Replanning}
-A replanner is a planner that takes a problem as input, plans a state-action policy, executes it online and whenever it encounters a state that was not in its state-action policy, it takes the current state as starting state and plans again until it has reached a goal or dead-end state.
-For our paper have chosen to evaluate FF-Replan \cite{FFReplan}, the winner of IPPC-04 and unenrolled winner of IPPC-06 as an inspiring, fairly simple planner that in our opinion is capable of employment in real-world domains.
 
-\subsubsection{Probabilistic planning}
-Probabilistic planners are used to solve probabilistic planning problems and should be able to account for uncertainty as opposed to classical planners.
-For our evaluation we have chosen to compare FF-Replan to a state-of-the-art probabilistic planner: \textsc{Gourmand}.
-\textsc{Gourmand} is the online successor of the \textsc{Glutton} plan, a Labelled Real-Time Dynamic Programming (LRTDP) based planner and the runner up of IPPC-11.
+These probabilistic MDPs can be solved using different kinds of planners.
+A \emph{replanner} is a planner that takes a problem as input, plans a partial state-action policy, executes it online and whenever it encounters a state that was not in its state-action policy, it takes the current state as starting state and plans again until it has reached a goal or dead-end state.
+To illustrate this technique, the notorious FF-planner is discussed in the next section.
+
+\emph{Probabilistic planners} use sophisticated planning techniques to plan for uncertainty.
+By using simulations, roll-out policies or lookahead values, these planners prevent dead-ends and were therefore dominantly used for solving MDPs.
+To illustrate a probabilistic planner, the next section introduces \textsc{Gourmand}, an online state-of-the-art probabilistic planner, and its predecessors \textsc{Glutton} and the LRTDP based algorithms.
 
 \subsection{Probabilistic Interestingness}
-After IPPC-06, a baseline test for \emph{probabilistically interesting} planning domains was proposed by Little and Thi\'ebauw \cite{little2007probvsreplan}.
-Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners.
+The \emph{probabilistically interesting} baseline test, proposed by Little and Thi\'ebauw \cite{little2007probvsreplan} after the success of FF-Replan initiated the shift of interest in goal-oriented MDPs to finite-horizon MDPs.
+Problems that fail this test are said to be classical planning problems in disguise, favoring the use of replanners.
 A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties \cite{little2007probvsreplan}:
-% reference little & thiebauw again. Maybe also shortly define what all o, n, act etc. are.
 
@@
 	\item there are multiple goal trajectories;
-	\item there is at least on pair of distinct goal trajectories, $\tau$ and $\tau$ ', that share a common sequence of outcomes for the first n-1 outcomes, and where $\tau$\textsubscript{n} and $\tau$'\textsubscript{n} are distinct outcomes of the same action; and
-	\item there exist two distinct goal trajectories $\tau$ and $\tau$' and outcome o $\in$ $\tau$ and o' $\in$ $\tau$' of two distinct actions a = act(o) and a'= act(o') such that executing a strictly decreases the maximum probability of reaching a state where a' can be executed.
+	\item there is at least one pair of distinct goal trajectories, $\tau$ and $\tau'$, that share a common sequence of outcomes for the first $n-1$ outcomes, and where $\tau_n$ and $\tau'_n$ are distinct outcomes of the same action; and
+	\item At least one of the distinct goal trajectories lead to outcomes o $\in$ $\tau$ and o' $\in$ $\tau$' of two distinct actions $a = act(o)$ and $a'= act(o')$ such that executing $a$ decreases the probability of reaching a dead end without influencing the probability of reaching a goal state.
 \end{itemize}
@@
 FF-Replan \cite{FFReplan}, a replanner based on determinization techniques and a classical planner, surprisingly outperformed other participating MDP solvers in the IPPC-04 and by doing so changed the course of the planning competition entirely.
-By relying on search and removing all probabilistic information from the problem, FF-replan functions with enormous speed and efficiency.
+By relying on search and removing all probabilistic information from the problem, FF-Replan functions with enormous speed and efficiency.
 This method has proven to outperform MDP solvers, the state-of-the-art probabilistic planners for uncertainty of that time.
@@
 Because these ``planning problems'' can often be solved using a smaller horizon $h < H$ as introduced in Section \ref{sec:background}, they represent optimization problems rather than planning problems, favoring current state of the art planners over replanners.
-This section introduces the shift of the planners towards optimization  by discussing FF-replan and a current state of the art probabilistic planner \textsc{Gourmand} and its predecessors.
+This section introduces the shift of the planners towards optimization  by discussing FF-Replan and a current state of the art probabilistic planner \textsc{Gourmand} and its predecessors.
 
-\subsection{FF-replan}
+\subsection{FF-ReFF-replanplan}
 \label{sec:ffreplan}
@@
 The success of the planner is therefore fully reliable on the chosen determinization heuristic.
-As FF-replan uses no roll-out policy or future simulation, it has no way of avoiding \emph{avoidable} dead-ends.
-This explains why FF-replan performs poorly in domains containing dead-ends.
+As FF-Replan uses no roll-out policy or future simulation, it has no way of avoiding \emph{avoidable} dead-ends.
+This explains why  performs poorly in domains containing dead-ends.
 
@@
 
-FF-Replan replans online, an off-line planner like FF-Replan is RFF
-\cite{teichteil2010incremental}. RFF generates policies by determinizing the
-given MDP problem, builds partial policies off-line by producing partial
-solution plans to the classical planning problem and incrementally aggregating
-them into a policy, and using sequential Monte-Carlo simulations to asses the
-probability of replanning. Experiments showed that RFF solved more problems
-than FF-Replan because it takes the probability a policy has to replan into
-account.
+%In sections above we have described the GOURMAND planner and FF-Replan as two
+%probabilistic planners of the IPPC competition.
+%RFF~\cite{teichteil2010incremental} is an offline planner that generates a
+%policy: for each reachable state it determines a plan to the goal. Like
+%FF-Replan it uses determinization and FF\. FF returns an initial plan from the
+%initial state to a goal state. For each state in the plan the successor states
+%are added to the structure, after which Monte-Carlo sampling is used. States
+%where the probability that they're reached is too low (below a threshold) are
+%removed. The successor states are used as initial states in the next step. If
+%FF fails to find a plan to the goal from this new state, the state is removed
+%from the structure too. Results showed that RFF outperformed other competitors.
+%A higher threshold means that RFF will generate more policies that are prone to
+%replanning.
 
-PROST \cite{keller2012prost} is a probabilistic planner, which contrary to
-\textsc{Gourmand}, is UTC based. It uses techniques to reduce the branching
-factor  and limits the search depth so it can focus more on parts that
-influence the quality of the resulting policy. Reward lock detection is a
-method to detect goals and dead ends in the finite horizon MDP\@. Q-value
-Initialization improves the initial start of the UTC algorithm. In the executed
-IPPC-11 benchmarks it outperforms other planners such as \textsc{Glutton}.
-Later it has been surpassed by \textsc{Gourmand}.
-
-\todo{rewrite prob int - Imara}
-
-%\subsection{Probabilistic planning vs Replanning}
-%Inspired by the FF-Replan entrance in the IPPC competition, this paper described a probabilistic interestingness quality of domains.
-It then compares probabilistic planners with replanners in the different domains to draw conclusions.
-Classical planning with replanning upon failure when there is so little or so much uncertainty about the world that it is not worth modelling and reasoning about or when goals dynamically change or when the problem is too large to solve at once.
-Probabilistic planners are more appropriate when avoiding irreparable or costly failures.
-Probabilistic planning computes a plan that can handle all foreseeable contingencies and is preferable for quick reactions in closed control loops.
-%
-%The following structural properties are identified for comparing probabilistic planning with replanning:
-%\begin{itemize}
-%	\item `dead' end states
-%	\item the degree to which the probability of reaching a dead end state can be reduced through choice of actions
-%	\item number of distinct trajectories
-%	\item presence of mutual exclusion
-%\end{itemize}
-%
-%If there are no dead ends, a replanner will always succeed.
-It is impossible to improve on the unavoidable dead ends (positive probability of reaching when executing which cannot be reduced without reducing the probability of reaching the goal).
-%
-%% repetition of what's already stated earlier
-%
-%A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties:
-%
-%\begin{itemize}
-%	\item there are multiple goal trajectories;
-%	\item there is at least on pair of distinct goal trajectories, $\tau$ and $\tau$ ', that share a common sequence of outcomes for the first n-1 outcomes, and where $\tau$\textsubscript{n} and $\tau$'\textsubscript{n} are distinct outcomes of the same action; and
-%	\item there exist two distinct goal trajectories $\tau$ and $\tau$' and outcome o $\in$ $\tau$ and o' $\in$ $\tau$' of two distinct actions a = act(o) and a'= act(o') such that executing a strictly decreases the maximum probability of reaching a state where a' can be executed.
-%\end{itemize}
-%
-%Problems that fail to be \emph{probabilistically interesting} are actually classical planning problems in disguise and for those replanners are more appropriate.
-A replanner can also perform optimally for probabilistically interesting planning problems whenever the `most promising' goal trajectory is the correct thing to do.
-They create several domains to explore the issue of replanning vs\@.
-probabilistic planning.
-%
-%Following existing domains were said to be probabilistically interesting:
-%\begin{itemize}
-%	\item Drive
-%	\item Exploding blocksworld
-%	\item Pitchcatch
-%	\item Schedule
-%	\item Tireworld
-%\end{itemize}
-%
-%They conclude by stating that the negative perception of probabilistic planning by the ICAPS community was inaccurate.
-They state that a synthesis of planning and replanning techniques could make a larger number of probabilistic planning problems practicably solvable than is currently possible.
+\subsubsection{PROST ?}
+\todo{wrote sentence about Prost - Arian}\\
 

### 2014-04-13 FinalPaper/paper.tex
adjusted up untill domains

@@
 % first the title is needed
-\title{Realistically Interesting Domains for Probabilistic Planners}
+\title{Solving a probabilistic planning problem by presenting a history in the field of probabilistic planning}
 
 % a short form should be given in case it is too long for the running head
-\titlerunning{Real World Domains}
+\titlerunning{Probabilistic planning}
 
@@
 %
-\authorrunning{Presenting a }
+%\authorrunning{Presenting a }
 % (feature abused for this document to repeat the title also on left hand pages)
@@
 By introducing and attempting to solve a planning problem domain involving Unmanned Aerial Vehicles (UAVs), this paper provides an overview of how the history of planning problem domains and their matching planners has changed throughout the scope of the International Planning Competitions (IPC).
-After the emergence of the FF-Replan planner in 2004, state-of-the-art benchmark domains have been argued to be more \emph{probabilistically interesting} causing a shift from the once dominant goal-oriented domains to the finite-horizon oriented domains.
+After the emergence of the FF-Replan planner in 2004, state-of-the-art benchmark domains have been argued to be more \emph{probabilistically interesting}, causing a shift from the once dominant goal-oriented domains to the finite-horizon oriented domains.
 
@@
 Since then several state-of-the-art planners such as the FF-planner \cite{Hoffmann01theff} have been introduced optimized for the initial classical planning problems.
-Surprisingly well-performing planners have caused the field to readjust the then supposedly challenging domains to provide a challenge for a wide variety of planners.
-By doing so, the definition of an interesting planning problem has been modified.
+Surprisingly well-performing planners have caused the field to readjust the supposedly challenging domains to provide a challenge for a wide variety of planners.
+By doing so, the definition of an interesting planning problem has been modified thoughout the years.
 
@@
 have argued for \emph{probabilistically interesting} domains \cite{little2007probvsreplan} and finite horizon MDPs were employed in IPPC-11.
-These approximations of infinite planning problems however strongly resemble optimization problems rather than the goal oriented initial planning domains.
-This shift in the current interesting domains caused the state-of-the-art planners to cope with the large branching factors that are introduced using finite horizon MDPs.
+These approximations of infinite planning problems however strongly resemble optimization problems rather than the initial goal oriented planning domains.
+This shift in the current interesting domains caused the state-of-the-art planners to change in order to cope with the large branching factors that were introduced using finite horizon MDPs.
 
@@
 By evaluating the domains with the help of the probabilistic interestingness baseline test introduced by Little et al.
-\cite{little2007probvsreplan} a recommendation will be made for a suitable planner to match the UAV problem.
+\cite{little2007probvsreplan}, a recommendation will be made for a suitable planner to match the UAV problem.
 
@@
 
-Section \ref{sec:problem} introduced the problem formulation this paper addresses while Section \ref{sec:domaind} introduces the details of proposed domain.
+Section \ref{sec:domaind} introduces the details of proposed domain.
 Section \ref{sec:background} introduced the appropriate prior knowledge and Section \ref{sec:domains} and \ref{sec:planners} the interesting domains and planners respectively.
-Section \ref{sec:experiment} briefly elaborates on a possible experiment set-up.
-Finally Section \ref{sec:conclusion} concludes on the evaluation of the domain and an appropriate planner.
+Section \ref{sec:experiment} briefly elaborates on a possible experiment set-up and finally Section \ref{sec:conclusion} concludes on the evaluation of the domain and an appropriate planner.
 
@@
 
-Unmanned Aerial Vehicles (UAVs), or commonly called \emph{Drones} are aircrafts
+Unmanned Aerial Vehicles (UAVs), commonly called \emph{Drones} are aircrafts
 without a pilot and are often autonomously controlled. Drones are widely used in the
-military as well as for civil uses as inspection of pipelines, counting of
-wildlife, agriculture, filming or delivering supplies to inaccessible areas.
+military as well as for civil uses for the inspection of pipelines, counting of
+wildlife, inspection of agriculture, filming or delivering supplies to inaccessible areas.
 There are many forms of UAVs to accommodate for these varying tasks: bigger fixed wing
-aircrafts, small helicopters or quad copter like aircrafts that can hover at
-a certain position in the air.
+aircrafts, small helicopters or quad-copter like aircrafts that are able to hover. These
+embedded systems have been a hot topic since the introduction of drones at Amazon.com and 
+are still gaining in interest.
 
-This paper focuses on monitoring, for example crops or livestock,
-and surveillance UAVs that work together to monitor a large area. Each UAV
-monitors a part of the total area. If something has to be monitored, it has
-to communicate this to a base station. This can't be done directly due to the
-large distance and instead it has to go through neighboring UAVs.
+This paper focuses on monitoring UAVs that work together to monitor a large area
+either to inspect livestock or for surveillance purposes. Each UAV is responsible
+for its own subset of the area and is responsible for communication with a base
+station whenever something has to be monitored. This can't be done directly due to
+large distances and instead it has to undergo several hops though neighboring UAVs.
 
 Communicating the message from the sensing UAV to the base station can be
-expressed as a probabilistic planning problem. Initially the sensing UAV
-has the package that has to be sent, and the goal is to bring this package to
-the base station. Each time the package is passed to the neighboring UAV,
+expressed as a probabilistic planning problem. The package has to be sent from
+the initial UAV to the goal base station.  Each time the package is passed to the neighboring UAV,
 there is a possibility the package is not received correctly. The bigger the
@@
 
-\myworries{maybe UAVs can be on or of too, so it's forced to use a further UAV.}
-
-\myworries{what's also interesting is that Amazon.com uses drones for package deliveries}
-
+%\myworries{maybe UAVs can be on or of too, so it's forced to use a further UAV.}
 %------------------------------------------------------------------------------

### 2014-04-13 FinalPaper/paper.tex
changed background
Changed the order of probabilistic interestingness as it is needed in the part about goal oriented and finite horizon

@@
 } Planning is the process of computing several steps of a problem-solving procedure before executing any of them.
-A \emph{classical planning problem} is defined as states, actions, conditions and a goal state and is solved using when finding a state-action sequence from the initial state $s_0$ to a goal state $G$.
+A \emph{classical planning problem} is defined as a set of states, actions, conditions and a goal state.
+This problem is solved when a state-action sequence from the initial state $s_0$ to a goal state $G$ is found.
 To find a state-action sequence, the environment is assumed to be \emph{deterministic, observable and static}.
 
-When planning for dynamic environments as is most often the case, natural dynamics and chance are introduced.
+However, when dealing with dynamic environments - as is most often the case, natural dynamics and chances are introduced.
 To simulate these planning problems, the classical deterministic domains were extended by adding a \emph{probability} to every action, creating \emph{probabilistic planning problems}.
@@
 
+\subsubsection{Probabilistic Interestingness}
+\label{sec:interesting}
+The \emph{probabilistically interesting} baseline test, proposed by Little and Thi\'ebauw \cite{little2007probvsreplan} after the success of FF-Replan initiated the shift of interest in goal-oriented MDPs to finite-horizon MDPs.
+Problems that fail this test are said to be classical planning problems in disguise, favoring the use of replanners.
+A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties \cite{little2007probvsreplan}:
+
+\begin{itemize}
+	\item there are multiple goal trajectories;
+	\item there is at least one pair of distinct goal trajectories, $\tau$ and $\tau'$, that share a common sequence of outcomes for the first $n-1$ outcomes, and where $\tau_n$ and $\tau'_n$ are distinct outcomes of the same action; and
+	\item At least one of the distinct goal trajectories lead to outcomes o $\in$ $\tau$ and o' $\in$ $\tau$' of two distinct actions $a = act(o)$ and $a'= act(o')$ such that executing $a$ decreases the probability of reaching a dead end without influencing the probability of reaching a goal state.
+\end{itemize}
+
 \subsubsection{Goal-oriented MDPs.
-}Cclassical goal-oriented problems are specified using the Probabilistic Planning Domain Description Language (PPDDL).
-PPDDL specifies a probabilistic planning problem as a set of probabilistic actions and an initial and goal state description\cite{FFReplan}.
+} Classical goal-oriented problems are specified using the Probabilistic Planning Domain Description Language (PPDDL).
+PPDDL specifies a probabilistic planning problem as a set of probabilistic actions and an initial and goal state description \cite{FFReplan}.
 These MDPs are of the form $\mathit{M = (S, A, app, Pr, R)}$ where $\mathit{S}$ and $\mathit{A}$ are a finite set of states and actions, $\mathit{app(s)}$ is the set of all actions applicable in the current state $\mathit{s}$.
@@
 These planning problems were however relatively easy to solve as they did not account for large branching factors introduced by for instance decay \cite{kolobov2012glutton}.
-Natural dynamics cause the system to grow \myworries{exponentially??} as it introduces exogenous actions in every state.
-After FF-Replan \cite{FFReplan}, a replanner as introduced in Section  \ref{sec:planners} kindly reminded the committee of IPPC-04 that the specified planning problems containing no dead-ends were fairly easy to solve using relatively simple tools to handle uncertainty, the finite-horizon MDPs were introduces.
+Natural dynamics cause the system to grow exponentially as it introduces exogenous actions in every state.
+After FF-Replan \cite{FFReplan}, a replanner as introduced in Section  \ref{sec:planners} kindly reminded the committee of IPPC-04 that the specified planning problems containing no dead-ends were fairly easy to solve using relatively simple tools to handle uncertainty, the more probabilistically interesting finite-horizon MDPs were introduced.
 
@@
 These probabilistic MDPs can be solved using different kinds of planners.
-A \emph{replanner} is a planner that takes a problem as input, plans a partial state-action policy, executes it online and whenever it encounters a state that was not in its state-action policy, it takes the current state as starting state and plans again until it has reached a goal or dead-end state.
+A \emph{replanner} is a planner that takes a problem as input and plans a partial state-action policy.
+This policy is executed online until it encounters a state that was not in its state-action policy.
+The current state is then set at the starting state after which the planner plans again until it has reached a goal or dead-end state.
 To illustrate this technique, the notorious FF-planner is discussed in the next section.
@@
 To illustrate a probabilistic planner, the next section introduces \textsc{Gourmand}, an online state-of-the-art probabilistic planner, and its predecessors \textsc{Glutton} and the LRTDP based algorithms.
-
-\subsection{Probabilistic Interestingness}
-The \emph{probabilistically interesting} baseline test, proposed by Little and Thi\'ebauw \cite{little2007probvsreplan} after the success of FF-Replan initiated the shift of interest in goal-oriented MDPs to finite-horizon MDPs.
-Problems that fail this test are said to be classical planning problems in disguise, favoring the use of replanners.
-A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties \cite{little2007probvsreplan}:
-
-\begin{itemize}
-	\item there are multiple goal trajectories;
-	\item there is at least one pair of distinct goal trajectories, $\tau$ and $\tau'$, that share a common sequence of outcomes for the first $n-1$ outcomes, and where $\tau_n$ and $\tau'_n$ are distinct outcomes of the same action; and
-	\item At least one of the distinct goal trajectories lead to outcomes o $\in$ $\tau$ and o' $\in$ $\tau$' of two distinct actions $a = act(o)$ and $a'= act(o')$ such that executing $a$ decreases the probability of reaching a dead end without influencing the probability of reaching a goal state.
-\end{itemize}
 

### 2014-04-13 FinalPaper/paper.tex
planners herschreven
Wil je nog een conclusie bij de planners?

@@
 Since then, Little et al.
-has argued for \emph{probabilistically interesting} domains.
+have argued for \emph{probabilistically interesting} domains.
 By introducing finite horizon MDPs in IPPC-11, state of the art planners have been adapted to cope with large branching factors to approximate infinite planning problems.
 Because these ``planning problems'' can often be solved using a smaller horizon $h < H$ as introduced in Section \ref{sec:background}, they represent optimization problems rather than planning problems, favoring current state of the art planners over replanners.
-This section introduces the shift of the planners towards optimization  by discussing FF-Replan and a current state of the art probabilistic planner \textsc{Gourmand} and its predecessors.
+This section introduces the shift of the planners towards optimization schedulers by discussing FF-Replan and a current state of the art probabilistic planner \textsc{Gourmand} and its predecessors.
 
-\subsection{FF-ReFF-replanplan}
+\subsection{FF-Replan}
 \label{sec:ffreplan}
@@
 This classical deterministic planning problem allows for the use of the classical FF planner \cite{Hoffmann01theff}.
-The FF planner then returns an ordered state-action plan for the deterministic problem of the current state.
+The FF planner then returns a partial ordered state-action plan for the deterministic problem of the current state.
 This plan is executed until an unexpected state is encountered in the following manner:
@@
 	\item Start planning at $s_0$
-	\item Determinizes the input domain
+	\item Determinize the input domain
 	\item Use FF on the classical planning problem
-	\item Executes ordered state-action plan until
+	\item Execute ordered state-action plan until
 	\item Unexpected state is encountered or
@@
 The success of the planner is therefore fully reliable on the chosen determinization heuristic.
-As FF-Replan uses no roll-out policy or future simulation, it has no way of avoiding \emph{avoidable} dead-ends.
-This explains why  performs poorly in domains containing dead-ends.
+As FF-Replan uses no roll-out policy or future simulation, it has no way of avoiding \emph{avoidable}(by selecting an action leading to an alternative path) dead-ends.
+This explains why FF-Replan performs poorly in domains containing dead-ends.
 
@@
 
-The LRTDP algorithm tries to reach the goal using a series of trials starting from $s_0$ and is specifically convenient for only memorizing states reachable from $s_0$ and therefore uses and needs less memory space in the following manner:
+The LRTDP algorithm tries to reach the goal using a series of trials starting from $s_0$ and is specifically convenient for only memorizing states reachable from $s_0$.
+It therefore uses and requires less memory space in the following manner:
 
@@
 	\item Start trial at $s_0$
-	\item Take action based on current value function $V$
+	\item Take action based on current value function $V$ (similar to reward) \myworries{moeten we bellman backup of value function nog uitleggen}
 	\item Perform Bellman backup
@@
 The \emph{Labeled Reverse Real-Time Dynamic Programmer} (LR$^2$TDP) uses \emph{reverse iterative deepening} and LRTDP-FH to incrementally solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$ by relying on the fact that a successful policy can be produced by solving a MDP-FH $M(h)$ for a smaller horizon $h < H$.
+LR$^2$TDP works in the following manner:
 
@@
 Solving $M(h)$ thus only takes an incremental effort over the solution of $M(h-1)$.
-If stopped prematurely  (LR$^2$TDP) is likely to provide a better policy as for many MDPs the optimal policy $\tau^*$ is optimal or near-optimal for $M(H)$.
-By itself,  (LR$^2$TDP) would however not perform well in MDPs with large branching factors as computing the Bellman backups would become too expensive carried out over a large fraction of the state space.
+If stopped prematurely LR$^2$TDP is likely to provide a better policy as for many MDPs the optimal policy $\tau^*$ is optimal or near-optimal for $M(H)$.
+By itself, LR$^2$TDP would however not perform well in MDPs with large branching factors as computing the Bellman backups would become too expensive carried out over a large fraction of the state space.
 
@@
 It optimizes for large branching factors by performing the transition function in a subset of transition states $s'$.
-It distinguished between \emph{exogenous} effects caused by natural dynamics and \emph{pure} effects caused by the action itself and a mixed of both.
-It also utilized the saved memory space caused by mapping only the converged states in the hash-table by using the free space as cache for storing successor states computed using the transition function.
+It distinguishes between \emph{exogenous} effects caused by natural dynamics and \emph{pure} effects caused by the action itself and a mixed of both.
+It also utilizes the saved memory space caused by mapping only the converged states in the hash-table and uses the free space as cache for storing successor states computed using the transition function.
 Since \textsc{Glutton} subsamples the transition function, it may not know a good action to perform in states it missed due to subsampling.
 To compensate for these states, \textsc{Glutton} has to resort to a \emph{default policy}.
-\todo{Wel of niet de default policy uitleggen}.
+These default policies are similar to using heuristics for finding an approximate optimal action in the current state and therefore decrease the reliability of the planner.
 
@@
 
-When however dealing with large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of states the planner may never reach in a lifetime.
+When dealing with large branching factors, offline planning is often a waste of time and memory space since there is a vast amount of states the planner may never reach in a lifetime.
 Such problems are far better solved using online planners that find an optimal policy $\tau^*$ or an approximation of this policy for the \emph{current} state.
@@
 \subsection{\textsc{Gourmand}}
-The \textsc{Gourmand} is an online adaptation of the \textsc{Glutton} planner and ensures a good \emph{anytime performance} using a lookahead value $L$ to approximate a near-optimal policy for $M(H)$ where $L < H$ and is dynamically chosen.
+The \textsc{Gourmand} is an online adaptation of the \textsc{Glutton} planner and ensures a good \emph{anytime performance} using a lookahead value $L$ to approximate a near-optimal policy for $M(H)$ where $L < H$ is dynamically chosen.
 At every iteration over the distance to the horizon $H$, it divides the total remaining time $\overline{T}$ equally amongst the remaining iterations and virtually allocates time: $T_t = \frac{\overline{T}}{H - t}$.
 During the first epoch, or iteration it estimates how long solving a state takes for different lookahead values.
-Using this estimate and a virtual time allocation \textsc{Gourmand} determines the largest lookahead value $L_t$ for which it can almost certainly solve the current epoch  and whether it could solve for a larger lookahead $\widehat{L}_t$ by taking away time from the next epoch, still guaranteeing that it can solve both epochs.
+Using this estimate and a virtual time allocation \textsc{Gourmand} determines the largest lookahead value $L_t$ for which it can almost certainly solve the current epoch and whether it could solve it for a larger lookahead $\widehat{L}_t$ by taking away time from the next epoch, still guaranteeing that it can solve both epochs.
 If so, it solves the current epoch for $\widehat{L}_t$ and otherwise $L_t$.
@@
 	\item Start \textsc{Gourmand} at $s_0$
-	\item Initialization of first epoch
+	\item Initialise first epoch
 	\begin{enumerate}
@@
 \end{enumerate}
-
-\todo{write some kind of conclusion}
 

### 2014-04-13 FinalPaper/paper.tex
changed domains, veel meer op het doel van de paper richten, alles echt uitleggen, waarom wel of niet probabilistic interesting etc

@@
 
-\author{I.C.T.M Speek, A.C. Stolwijk}
+\author{I.C.T.M Speek \& A.C. Stolwijk}
 
@@
 
-\todo{Arian: Still have to add why this problem is valid, or interesting}
-
 Section \ref{sec:domaind} introduces the details of proposed domain.
-Section \ref{sec:background} introduced the appropriate prior knowledge and Section \ref{sec:domains} and \ref{sec:planners} the interesting domains and planners respectively.
-Section \ref{sec:experiment} briefly elaborates on a possible experiment set-up and finally Section \ref{sec:conclusion} concludes on the evaluation of the domain and an appropriate planner.
+Section \ref{sec:background} introduced the appropriate prior knowledge and Section \ref{sec:planners} and  \ref{sec:domains} the interesting planners and domains respectively.
+Section \ref{sec:related} elaborates on different planning solutions and finally Section \ref{sec:conclusion} concludes on the evaluation of the domain and an appropriate planner.
 
@@
 PPDDL specifies a probabilistic planning problem as a set of probabilistic actions and an initial and goal state description \cite{FFReplan}.
-These MDPs are of the form $\mathit{M = (S, A, app, Pr, R)}$ where $\mathit{S}$ and $\mathit{A}$ are a finite set of states and actions, $\mathit{app(s)}$ is the set of all actions applicable in the current state $\mathit{s}$.
+These MDPs are of the form \\ $\mathit{M = (S, A, app, Pr, R)}$ where $\mathit{S}$ and $\mathit{A}$ are a finite set of states and actions, $\mathit{app(s)}$ is the set of all actions applicable in the current state $\mathit{s}$.
 $\mathit{Pr}$ represents the probability of a state transition $\mathit{(s, a, s')}$ for action $\mathit{a}$ and $\mathit{R(s, a, s')}$ is the reward of applying $\mathit{a}$ to $\mathit{s}$ and generating $\mathit{s'}$ The planning problem is defined as a triple $\mathit{P = (M, s\textsubscript{0}, G}$ where $\mathit{M = (S, A, app, Pr, R)}$ is an MDP, $\mathit{s\textsubscript{0} \in S}$ is the initial state and $\mathit{G \subseteq S}$ is the set of goal states.
@@
 
-To identify unique properties of the domain and identify properties of the
-domain that work particularly well for a certain type of planner, we describe
-other domains used in the IPPC and compare that with the UAV domain.
+To identify unique properties of the domain that work particularly well for a certain type of planner, we describe
+other domains in which FF-Replan or Gourmand performed poorly or excellent and compare these with the UAV domain.
 
-\paragraph{Blocksworld:}
-A simple domain used in the competition of 2004 is the well known blocksworld
-domain. The uncertainty lies in that the gripper, used to move blocks, has a
-probability that it drops the blocks to the table. Another difference is that
-the blocks are colored, and the goal is to build a tower of certain colored
-blocks, rather than a tower with specific blocks. If for example there are
-four blue blocks, and the goal is a tower of three blue blocks, it does not
-matter which blue blocks are used.
+A simple domain in which FF-Replan excelled is the \textsc{Blocksworld}
+domain. The uncertainty lies in that the gripper used to move blocks has a
+probability of dropping the block. The blocks have certain color properties and 
+a preferred order in which the blocks should be build. This is the exact point 
+in which the UAV domain differs as it does not yet differentiate between messages.
 
-\paragraph{Navigation:}
-The navigation domain represents a grid in which a robot must reach a goal.
+The \textsc{Navigation} domain represents a grid in which a robot must reach a goal similarly to the UAV domain.
 Every cell offers the robot a different chance of disappearing. The robot needs
 to choose a path which gets it to the goal most reliably within the finite
-horizon time \cite{sanner2011navigation}.
+horizon time \cite{sanner2011navigation}. Although FF-Replan performed poorly in this domain, \textsc{Gourmand} was 
+able to perform much better by using the lookahead value $L$.
 
-\paragraph{Traffic:}
-This domain represents a simple binary version of the cell transition model
-(CTM) for modelling traffic based on the original CTM Tech Report
+The \textsc{Traffic} domain represents a simple binary version of the cell transition model
+(CTM) for modeling traffic based on the original CTM Tech Report
 \cite{sanner2011traffic}. Because of the binary variables and no intermediate
 variable restrictions, this model is simplified and ignores traffic aspects
-such as turns and turn probabilities. This model also uses concurrent actions
-and the total actions has an upper bound of $2^{\#~of~intersections}$.
+such as turns and turn probabilities. Although it models the CTM correctly, it isn't a strong
+representation of the domain in its real-world equivalent where accidents can occur.
+This model differentiates itself as it uses and plans for concurrent actions.
 
-\paragraph{Elevators:}
-The elevators domain has evaluated between the competitions of 2006 and
-2011, we describe the latest version. In this domain there are a number of
-elevators delivering passengers to either the top or bottom floor. Potential
+In the latest \textsc{Elevators} domain a number of elevators deliver passengers to either the top or bottom floor. Potential
 passengers arrive at any floor at a certain rate (depending on which floor).
@@
 know whether to board or not. The goal of the elevators is to transport as many
-as possible passengers to their destinations.
+as possible passengers to their destinations. This domain is one of the first emerging
+optimization problems and is therefore inherently different from its previous goal-related version.
 
-\paragraph{SysAdmin:}
-The SysAdmin domain describes a network of connected servers. Each server has
-a probability that it shuts down, and if is not running, it has a probability
-to reboot. The probability that a server shuts down depends on the number of
-running connected servers.
+In the same way does the \textsc{SysAdmin} domain describe a network of connected servers. Each server has
+a probability that it shuts down or reboots whenever it is down. The probability that a server shuts down depends on the number of
+running connected servers. This domain is important as it represents the large branching factors introduced by natural dynamics. The introduction
+of the \textsc{noop()} operation increases the size exponentially.
 
 \subsection{Domain Evaluation}
+\myworries{hier alleen een evalutie geven, niet wederom een uitleg, anders moet je het hierboven uitleggen. Alles wat je zegt, moet een reden hebben, anders kan het weg}
 
-The Blocksworld domain is ideal for
-replanning~\cite{FFReplan, little2007probvsreplan}. As the blocks fall on the
-table, which then can be picked up again, it has no dead ends. This makes it
-probabilistically uninteresting. For this domain FF-Repan performs really well.
+The \textsc{Blocksworld} domain is ideal for
+replanning~\cite{FFReplan, little2007probvsreplan} as it has no dead ends. This makes it
+probabilistically uninteresting and thus a classical planning problem in disguise, ideally to solve for FF-Replan.
 
-The newer  domains, Navigation, Traffic, Elevators and SysAdmin are finite-
-horizon domains. Navigation, however, is actually a goal oriented domain, if
-the goal is reached in the horizon. The method how this is implemented is that
-the goal state is defined as an absorbing state, and there is no reward or cost
-associated to staying in the goal state, until the horizon is reached.
+The domains are constructed to challenge planners to perform
+better. This creates issues when comparing the domains to their real-world match as can be easily seen 
+in the \textsc{Traffic} domain.
 
-\textsc{Gourmand} vastly outperformed the UCT-based PROST, the IPPC-11
-probabilistic track winner, by far on goal-oriented domains Navigation and
-Crossing Traffic \cite{kolobov2012gourmand}. This is because of the dynamic
-lookahead feature of \textsc{Gourmand}. PROST however mildly outperforms
-\textsc{Gourmand} on the Game of Life, SysAdmin and the Traffic domain as UCT
-does not need to perform expensive Bellman Backups on these domains that
-include large branching factors.
-
-The domains are constructed such that it will challenge planners to perform
-better. This causes that there are issues with the domains when comparing them
-with the real world.
-
-In the navigation problem there is a chance that the robot
-disappears after entering a cell. The disappearing action is a dead end.
-Disappearing here is a metaphor for the robot breaking down, or that it
-disappears from the radar with the base station. In many of such cases it's a
-big problem, but can be repaired with a high cost. In the navigation domain a
-step to another cell has a cost of 1. If instead of a dead end the cost is $n$
-(e.g. 5) instead of 1, which represents the cost of repairing the robot, dead
-ends are removed. Without dead ends the problem becomes probabilistic
-uninteresting, which makes it suitable for replanning planners.
+Dead-ends in the \textsc{Navigation} domain are represented by the act of disappearing. 
+This is a metaphor for the robot breaking down, or that it
+disappears from the radar.
+Although these actions cause troubles in the system, they can be repaired with a high cost.
+By replacing dead-ends with high cost actions, the problem becomes less probabilistically interesting.
+Although the problem would become suitable for replanners, one could argue that this would only be valid for less critical applications. When applied for
+navigating satellites, the failure of the system would be set as such a high cost, it would essentially represent a dead-end.
 
@@
 \section{Related Work}
+\label{sec:related}
 
@@
 \section{Conclusion}
+\label{sec:conclusion}
 

### 2014-04-13 FinalPaper/paper.tex
saved

@@
 better. This creates issues when comparing the domains to their real-world match as can be easily seen 
-in the \textsc{Traffic} domain.
+in the \textsc{Traffic} domain. Although the current domain contains no dead-ends and is thus probabilistically
+uninteresting, it will gain probabilistic interestingness by introducing the uncertain behavior of drivers and failure
+of the lighting system. If so, the performance of FF-Replan will be strongly decreased, whilst \textsc{Gourmand} will keep its anytime performance.
 
@@
 
-The traffic domain describes a crossroad with traffic lights, modelled as
-cells. Either the north to south road has a green light, the west to east road
-or all lights are red. The model uses a finite state machine that handles the
-lights so that the lights are never green at the same time. This would be the
-only dangerous situation on the crossroad. The difficulty in this domain is
-the number of states, which grows exponentially with the number of cells.
-Besides that it is an uninteresting probabilistic problem because it does
-not satisfy the probabilistic interesting test.
-
-The UAV domain has a resemblance of the Navigation domain. Both are goal
+The UAV domain has some resemblance with the \textsc{Navigation} domain. Both are goal
 oriented and have to navigate something (either the robot itself, or a data
-package) from an initial state to a goal. Also after each step a dead end can
-be reached, the robot disappears or the data package is not delivered.
-The probability this happens is static in the navigation domain, but dependent
-on the neighbors in the UAV domain. This variable probability has a resemblance
+package) from an initial state to a goal. After each step a dead end can
+be reached where the robot disappears or the data package is not delivered.
+Although the probability of disappearing is static in the \textsc{Navigation} domain, the probability is dependent of the 
+amount of neighbors and distance in the UAV domain. This variable probability has a resemblance
 of the SysAdmin domain, where the probability that a server shuts down is also

### 2014-04-13 FinalPaper/paper.tex
last revision

@@
 
-FF-Replan replans online, an off-line planner like FF-Replan is RFF
+While FF-Replan is an online planner, a similar off-line planner is the RFF planner
 \cite{teichteil2010incremental}. RFF generates policies by determinizing the
-given MDP problem, builds partial policies off-line by producing partial
+given MDP problem similarly to FF-Replan. It then builds partial policies off-line by producing partial
 solution plans to the classical planning problem and incrementally aggregating
-them into a policy, and using sequential Monte-Carlo simulations to asses the
+them into a policy. Using sequential Monte-Carlo simulations, it estimates the
 probability of replanning. Experiments showed that RFF solved more problems
@@
 
-PROST \cite{keller2012prost} is a probabilistic planner, which contrary to
-\textsc{Gourmand}, is UTC based. It uses techniques to reduce the branching
-factor  and limits the search depth so it can focus more on parts that
+PROST \cite{keller2012prost} is a probabilistic planner, which in contrary to
+\textsc{Gourmand} is UTC based. It uses techniques to reduce the branching
+factor and limits the search depth so it can focus on parts that
 influence the quality of the resulting policy. Reward lock detection is a
@@
 Later it has been surpassed by \textsc{Gourmand}.
+
+\todo{connect back to the purpose of the paper}
 
@@
 
+\todo{we hadden hier al meer voor klaar staan dan alleen dit toch? Het is nog niet echt een aanbeveling}
+
 \bibliographystyle{plain}

### 2014-04-13 FinalPaper/paper.tex
Initial conclusion

@@
 
-\begin{itemize}
-	\item Conclude the work done in the paper
-	\item Hint to some future work developments
-\end{itemize}
+To choose an appropriate planner for the domain involving Unmanned Aerial
+Vehicles, we have given an overview of probabilistic planning. Probabilistic
+planning problems are usually represented in Markov Decision Processes. The
+IPPC, a competition for probabilistic planners, used Goal-Oriented MDPs for
+benchmark domains.
+
+Little et al\. however argued for \emph{probabilistic
+interestingness}. Little et al\. proposed a test to test for \emph{probabilistic
+interestingness}: a) multiple goal trajectories, b) at least one pair of goal
+trajectories that have a common initial sequence and c) there is at least one
+goal trajectory that if a action is executed the probability reaching a dead
+end decreases.
+
+Two types of probabilistic planners are MDP solvers and replanners.
+Surprisingly replanners performed extremely well in the first IPPC
+competitions, especially FF-Replan in IPPC-04. Later, with FH-MDPs replanners
+failed to be scalable and sensitive to an expected reward maximization, the
+evaluation criteria for those domains. \textsc{Gourmand} is a state-of-the-art
+MDP solver that performed better than other planners like \textsc{Glutton} or
+PROST.
+
+To choose an appropriate planner for the UAV domain, we have discussed other
+existing benchmark domains used in the IPPC.
 

### 2014-04-13 FinalPaper/paper.tex
More conclusion

@@
 To choose an appropriate planner for the UAV domain, we have discussed other
-existing benchmark domains used in the IPPC.
+existing benchmark domains used in the IPPC\. By looking closely at the domains
+we identified some issues with the domains, to make it more difficult for
+FF-Replan (in the case of the \textsc{Traffic} domain), of how to make a domain
+easier for a replanner in the \textsc{Navigation} domain. The UAV domain seems
+to have resemblances of the \textsc{Navigation} domain and the
+\textsc{SysAdmin} domain.
+
+Finally we described to other relevant planners RFF and PROST\. RFF is a
+planner similar to FF-Replan, but instead works off-line and generates
+policies. PROST is a UTC based probabilistic planner that outperformed
+\textsc{Gourmand}'s predecessor \textsc{Glutton}.
 

### 2014-04-13 FinalPaper/paper.tex
Improve conclusion

@@
 
-Two types of probabilistic planners are MDP solvers and replanners.
-Surprisingly replanners performed extremely well in the first IPPC
-competitions, especially FF-Replan in IPPC-04. Later, with FH-MDPs replanners
+Replanners surprisingly performed extremely well in the first IPPC domains,
+especially FF-Replan in IPPC-04. The good performance for replanners was
+because of the way domains were constructed. Later, with FH-MDPs replanners
 failed to be scalable and sensitive to an expected reward maximization, the
@@
 
-Finally we described to other relevant planners RFF and PROST\. RFF is a
-planner similar to FF-Replan, but instead works off-line and generates
-policies. PROST is a UTC based probabilistic planner that outperformed
-\textsc{Gourmand}'s predecessor \textsc{Glutton}.
+The UAV domain has, like the \textsc{Navigation} domain many probabilities to
+hit a dead end, in case a data package is not received correctly. There are
+multiple goal trajectories, there can be goal trajectory pairs with the same
+initial sequence and if the data package is near the base station the
+probability a dead end is reached is decreased. In this case it satisfies the
+\emph{probabilistic interestingness} test. \textsc{Gourmand} would be the
+preferred planner for the UAV domain. However in real communication systems
+failure of communication can often detected using acknowledgements. If a UAV
+knows the transmission has failed, it can do something else, so dead ends
+disappear from the domain. For such a definition of the UAV domain, a replanner
+would work satisfactory. Based on the exact conditions of the domain, a type of
+planner can be chosen. If those conditions are slightly tweaked, another type
+of planner can be favorable.
 

### 2014-04-13 FinalPaper/paper.tex
Improving conclusion

--- 2014-04-13 FinalPaper/paper.tex
@@
 
-Two types of probabilistic planners are MDP solvers and replanners.
-Surprisingly replanners performed extremely well in the first IPPC
-competitions, especially FF-Replan in IPPC-04. Later, with FH-MDPs replanners
-failed to be scalable and sensitive to an expected reward maximization, the
-evaluation criteria for those domains. \textsc{Gourmand} is a state-of-the-art
-MDP solver that performed better than other planners like \textsc{Glutton} or
-PROST.
+Replanners surprisingly outperformed other planners in the first IPPC domains,
+especially FF-Replan in IPPC-04. The good performance for replanners was
+because of the way domains were constructed. Later competitions used FH-MDPs.
+\textsc{Gourmand} is a state-of-the-art MDP solver that performed better than
+other planners like \textsc{Glutton} or PROST for FH-MDP benchmark domains.
 
@@
 
-Finally we described to other relevant planners RFF and PROST\. RFF is a
-planner similar to FF-Replan, but instead works off-line and generates
-policies. PROST is a UTC based probabilistic planner that outperformed
-\textsc{Gourmand}'s predecessor \textsc{Glutton}.
+As the current planning domain is probabilistically interesting, the
+\textsc{Gourmand} planner is favorable. However, by modifying the drone's
+communication protocol by adding a handshake protocol any communication failure
+can be detected. The UAV can therefore choose to initiate another transmission
+of the message until it received an acknowledgment. This way the dead-ends are
+replaced with higher costs actions similarly to the \textsc{Navigation} domain.
+These higher cost actions are however somewhat more realistic as they do not
+mean the disappearance of a highly expensive piece of equipment, but rather a
+data package. As this is a realistic and often occurring communicating
+protocol, we believe that FF-Replan is in fact a proper alternative for the
+current state-of-the-art probabilistic planner.
 

### 2014-04-13 FinalPaper/paper.tex
Add prob interstingness of domain to conclusion

@@
 
+In the domain several goal paths follow the state-action sequences. However,
+the UAVs can decide to send a package to a closer neighbor rather than a
+further one. This increases the amount of time necessary, but decreases the
+probability of the package not being received. This means the domain is
+probabilistically interesting.
+
 As the current planning domain is probabilistically interesting, the
@@
 can be detected. The UAV can therefore choose to initiate another transmission
-of the message until it received an acknowledgment. This way the dead-ends are
+of the message until it received an acknowledgment. This way the dead ends are
 replaced with higher costs actions similarly to the \textsc{Navigation} domain.

### 2014-04-13 FinalPaper/paper.tex
Adding communication protocol of UAVs to domain evaluation

@@
 
+Dead ends can be avoided in the \textsc{Navigation} domain by adding actions
+with a high cost. If a handshake protocol is added to the UAV communication,
+the sending UAV knows if the transmission failed and initiate another
+transmission of the message until it received an acknowledgement. This takes
+more time but it avoids dead ends in the UAV domain.
+
 %------------------------------------------------------------------------------

### 2014-04-13 FinalPaper/paper.tex
Final tweaks

@@
 
-Little et al\. however argued for \emph{probabilistic
-interestingness}. Little et al\. proposed a test to test for \emph{probabilistic
+Little et al.\@ however argued for \emph{probabilistic
+interestingness}. Little et al.\@ proposed a test to test for \emph{probabilistic
 interestingness}: a) multiple goal trajectories, b) at least one pair of goal
@@
 Replanners surprisingly outperformed other planners in the first IPPC domains,
-especially FF-Replan in IPPC-04. The good performance for replanners was
-because of the way domains were constructed. Later competitions used FH-MDPs.
-\textsc{Gourmand} is a state-of-the-art MDP solver that performed better than
-other planners like \textsc{Glutton} or PROST for FH-MDP benchmark domains.
+especially replanner FF-Replan in IPPC-04. The good performance for replanners was
+because of the way domains were constructed, with no or few dead ends.
+Later competitions used FH-MDPs. \textsc{Gourmand} is a state-of-the-art MDP
+solver that performed better than other planners like \textsc{Glutton} or PROST
+for FH-MDP benchmark domains.
 
@@
 existing benchmark domains used in the IPPC\. By looking closely at the domains
-we identified some issues with the domains, to make it more difficult for
+we identified some issues with the domains, to make it less interesting for
 FF-Replan (in the case of the \textsc{Traffic} domain), of how to make a domain
-easier for a replanner in the \textsc{Navigation} domain. The UAV domain seems
-to have resemblances of the \textsc{Navigation} domain and the
+more interesting for a replanner in the \textsc{Navigation} domain. The UAV
+domain seems to have resemblances of the \textsc{Navigation} domain and the
 \textsc{SysAdmin} domain.

### 2014-04-13 FinalPaper/paper.tex
Rewrite paragraph in the conclusion

@@
 
-To choose an appropriate planner for the UAV domain, we have discussed other
-existing benchmark domains used in the IPPC\. By looking closely at the domains
-we identified some issues with the domains, to make it less interesting for
-FF-Replan (in the case of the \textsc{Traffic} domain), of how to make a domain
-more interesting for a replanner in the \textsc{Navigation} domain. The UAV
-domain seems to have resemblances of the \textsc{Navigation} domain and the
-\textsc{SysAdmin} domain.
+To choose an appropriate planner for our UAV domain, we have analyzed some of
+the most important domains in the course of history of probabilistic planners.
+The UAV domain seems to have resemblances of the \textsc{Navigation} domain
+and the \textsc{SysAdmin} domain. With this knowledge a proposal can be made
+for a matching planner.
 

### 2014-04-13 FinalPaper/paper.tex
Comment todos and worries

@@
 	\item Start trial at $s_0$
-	\item Take action based on current value function $V$ (similar to reward) \myworries{moeten we bellman backup of value function nog uitleggen}
+	\item Take action based on current value function $V$ (similar to reward)
+%\myworries{moeten we bellman backup of value function nog uitleggen}
 	\item Perform Bellman backup
@@
 \subsection{Domain Evaluation}
-\myworries{hier alleen een evalutie geven, niet wederom een uitleg, anders moet je het hierboven uitleggen. Alles wat je zegt, moet een reden hebben, anders kan het weg}
+%\myworries{hier alleen een evalutie geven, niet wederom een uitleg, anders moet je het hierboven uitleggen. Alles wat je zegt, moet een reden hebben, anders kan het weg}
 
@@
 
-\todo{connect back to the purpose of the paper}
+%\todo{connect back to the purpose of the paper}
 
@@
 the most important domains in the course of history of probabilistic planners.
-The UAV domain seems to have resemblances of the \textsc{Navigation} domain
+The UAV domain seems to have resemblances to the \textsc{Navigation} domain
 and the \textsc{SysAdmin} domain. With this knowledge a proposal can be made
@@
 
-\todo{we hadden hier al meer voor klaar staan dan alleen dit toch? Het is nog niet echt een aanbeveling}
+%\todo{we hadden hier al meer voor klaar staan dan alleen dit toch? Het is nog niet echt een aanbeveling}
 
